```{r,echo=FALSE}
n = 8
pows = c("1","i","-1","-i")
while(T){
    x = sort(sample(10:99,n))
    ans = pows[(x%%4)+1]
    if(length(unique(ans))==4 || n<5){break}
}

qstr = paste0("* $i^{",x,"}=$ ##ANSWER",1:n,"##",collapse="\n")
p = c("i","-1","-i","1")
al = paste0("* ",p,collapse="\n")
tal = paste0(rep(al,n),collapse="\n")

sols = character()
for(i in 1:n){
    sol = paste0(1*(p==ans[i]),collapse="")
    sols = c(sols,sol)
}

```

Question
========

Consider the [imaginary unit](https://en.wikipedia.org/wiki/Imaginary_unit). Historically, the imaginary unit, $i$, was defined as the square root of negative 1.

$$i~\stackrel{\text{def}}{=}~\sqrt{-1}$$

Although this number is "imaginary", and difficult to picture in our physical world, there are real-world calculations that make use of the imaginary unit. Common examples are in electrical engineering and quantum physics.

For us, in algebra, we will find an elegance in extending our numbers into [the complex plane](https://en.wikipedia.org/wiki/Complex_plane). Specifically, we are heading toward appreciating the [fundamental theorem of algebra](https://en.wikipedia.org/wiki/Fundamental_theorem_of_algebra).

To start understanding the imaginary unit, consider the following pattern:

$$i^1 = i$$
$$i^2 = -1$$
$$i^3 = -i$$
$$i^4 = 1$$
$$i^5 = i$$
$$i^6 = -1$$
$$i^7 = -i$$
$$i^8 = 1$$

As we continue to increment the exponent, we will see this 4-step pattern repeat indefinitely. **Find the following powers of $i$**.


`r qstr`

Answerlist
--------

`r tal`


Solution
========

For any positive integer $p$, we can evaluate $i^p$ by determining the remainder when $p$ is divided by 4.

| Remainder of $p/4$ | $i^p$ |
|:---:|:---:|
| 0 | $1$ |
| 1 | $i$ |
| 2 | $-1$ |
| 3 | $-i$ |

In computer programming, the [modulo operator](https://en.wikipedia.org/wiki/Modulo) returns the remainder. This operation is used so frequently, that it is often abbreviated to a single symbol (for example, in Python, `5%2` represents the remainder when 5 is divided by 2.)

I will represent the remainders using the [Desmos](https://www.desmos.com/calculator) notation.

```{r,echo=F}
calcs = paste0("* $\\mathrm{mod}(",x,",4)","=",x%%4,"$ so $i^{",x,"}=",ans,"$",collapse="\n")
```

`r calcs`

To find the remainder using a scientific calculator, I would divide by 4, [floor](https://en.wikipedia.org/wiki/Floor_and_ceiling_functions) the result, multiply by 4, and subtract that amount from the original.

$$\mathrm{mod}(x,4)~=~x-4\cdot \left\lfloor\frac{x}{4}\right\rfloor$$




Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: i_to_power