```{r,echo=FALSE}
library(MASS)
aposs = c(-3,-2,-1/2,-1/3,-1/4,-1/9,1/9,1/4,1/3,1/2,2,3)
a = sample(aposs,1)
hk = sample(0:6,2)*sample(c(-1,1),2,T)
h = hk[1]
k = hk[2]

eq = paste0("y=",fractions(a),"\\cdot (x+",-h,")^2+",k,collapse="")
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+0","",eq,fixed=T)

ach1 = paste0(fractions(aposs))
ach2 = -6:6
ach3 = -6:6
ach4 = c("There are 0 x-intercepts.","There is 1 x-intercept.","There are 2 x-intercepts.")

al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")
al3 = paste0("* ",ach3,collapse="\n")
al4 = paste0("* ",ach4,collapse="\n")

sol1 = paste0(1*(ach1==paste0(fractions(a))),collapse="")
sol2 = paste0(1*(ach2==h),collapse="")
sol3 = paste0(1*(ach3==k),collapse="")

if(sign(a)==sign(k)){
    sol4 = "100"
}
if(sign(a)==-sign(k)){
    sol4 = "001"
}
if(k==0){
    sol4 = "010"
}

```

Question
========

A parabola is randomly generated by randomly choosing parameters $a$, $h$, and $k$ in the vertex-form equation:

$$y~=~a(x-h)^2+k$$

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
for(j in -10:10){
    lines(c(-10,10),c(j,j),col="grey",lwd=0.5)
    lines(c(j,j),c(-10,10),col="grey",lwd=0.5)
}
for(j in seq(-10,10,5)){
    lines(c(-10,10),c(j,j),col="darkgrey",lwd=1)
    lines(c(j,j),c(-10,10),col="darkgrey",lwd=1)
}
arrows(-11,0,11,0,0.05,20,3,lwd=1.5)
arrows(0,-11,0,11,0.05,20,3,lwd=1.5)
text(10,0,"10",adj=c(0.5,1.2))
text(0,10,"10",adj=c(1.2,0.5))
text(10,0,"x",adj=c(-0.2,-0.5))
text(0,10,"y",adj=c(-0.5,-0.2))
x = seq(-10,10,0.01)
y = a*(x-h)^2+k
x = x[abs(y)<=10]
y = y[abs(y)<=10]
lines(x,y,col="blue",lwd=2)
x = seq(-10,10,1)
y = a*(x-h)^2+k
x = x[abs(y)<=10]
y = y[abs(y)<=10]
x = x[y%%1==0]
y = y[y%%1==0]
points(x,y,col="blue",pch=19)

```
\

Find the parameters.

* $a=$ ##ANSWER1##
* $h=$ ##ANSWER2##
* $k=$ ##ANSWER3##

How many $x$-intercepts does the parabola have? (Some might not show on the graph.)

* ##ANSWER4##

Answerlist
-------

`r al1`
`r al2`
`r al3`
`r al4`

Solution
========

To find $a$, you might use [this reference](https://artockthedino.github.io/algtwo2026/u06/1218/Stretched_Parabolas_Reference.html). Notice, if $a$ is negative, the parabola faces down, and if $a$ is positive, the parabola faces up. If $|a|$ is bigger than 1, then the parent $y=x^2$ is stretched vertically. If $|a|$ is less than 1, then the parent $y=x^2$ is shrunk vertically. To find the exact value, you need to look at precisely where the curve intersects the lattice points.

To find $h$ and $k$, you can just find the coordinates of the vertex.

To determine the number of roots... 

* If the vertex is on the $x$ axis, there is one root.
* If the parabola opens **up** and the vertex is **above** the $x$ axis, then 0 roots.
* If the parabola opens **down** and the vertex is **above** the $x$ axis, then 2 roots.
* If the parabola opens **up** and the vertex is **below** the $x$ axis, then 2 roots.
* If the parabola opens **down** and the vertex is **below** the $x$ axis, then 0 roots.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: ahk_count_roots