```{r,echo=FALSE}
options(scipen=99)
library(numbers)
pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

# -b/2a +- sqrt(b^2-4ac)/2a
# (x-(h+p*sqrt(q)))(x-(h-p*sqrt(q)))
# (x-(h+sqrt(p^2*q)))(x-(h-sqrt(p^2*q)))

# x^2 - 2*h + h^2-p^2*q

h = sample(2:9,1)*sample(c(-1,1),1)
p = sample(2:6,1)
q = sample(c(2,3,5,6,10),1)
a = 1
b = -2*h
c = h^2-p^2*q

eq = paste0(pn(c(a,b,c),2:0),"=0")
fx = pn(c(a,b,c),2:0)

ach1 = -10:10
# ach2 = c("2","2i","3","3i","4","4i","5","5i","6","6i","7","7i","8","8i","9","9i","10","10i")
ach2 = 2:10
ach3 = 2:10


al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")
al3 = paste0("* ",ach3,collapse="\n")

sol1 = paste0(1*(ach1==h),collapse="")
sol2 = paste0(1*(ach2==p),collapse="")
sol3 = paste0(1*(ach3==q),collapse="")


```


Question
========

Let quadratic function $f$ be defined below:

$$f(x)~=~`r fx`$$

When curve $y=f(x)$ is graphed, we see two $x$-intercepts at $(x_1,0)$ and $(x_2,0)$.

```{r,echo=F,fig.dim=c(4,4)}
library(latex2exp)
par(mar=c(5,5,0,0))
k = -(b^2-4*a*c)/4/a
r1 = h-p*sqrt(q)
r2 = h+p*sqrt(q)
dx = 2*p*sqrt(q)
dy = abs(k)*1.5
plot(0,0,"n",xlim=c(h-dx,h+dx),ylim=c(-abs(k)*1.5,abs(k)*1.5),xlab="x",ylab="y")
abline(h=0,lwd=2)
abline(v=0,lwd=2)
xx = seq(h-dx,h+dx,dx/100)
yy = a*xx^2+b*xx+c
lines(xx,yy,col="blue",lwd=2)
points(c(r1,r2),c(0,0),pch=19,col="red")
text(r1,0,TeX("$(x_1,0)$"),adj=c(-0.1,-0.2),col="red",cex=1.1)
text(r2,0,TeX("$(x_2,0)$"),adj=c(1.1,-0.2),col="red",cex=1.1)
legend("topleft",TeX("$y=f(x)$"),lwd=2,col="blue")

```
\

In exact form, those $x$ intercepts can be expressed as $h\pm p\sqrt{q}$. 

$$x_1=h-p\sqrt{q}$$
$$x_2=h+p\sqrt{q}$$

Find the values of $h$, $p$, and $q$.

$h=$ ##ANSWER1##

$p=$ ##ANSWER2##

$q=$ ##ANSWER3##


Answerlist
--------

`r al1`
`r al2`
`r al3`


Solution
========

The $x$ intercepts occur when either $x_1$ or $x_2$ satisfies $f(x)=0$.

$$`r eq`$$

Identify the coefficients.

$$a=`r a`$$
$$b=`r b`$$
$$c=`r c`$$

Plug numbers into the quadratic formula!

$$x = \frac{-(`r b`)\pm\sqrt{(`r b`)^2-4(`r a`)(`r c`)}}{2(`r a`)} $$

Simplify.

$$x = \frac{`r -b` \pm \sqrt{`r b^2`-(`r 4*a*c`)}}{`r 2*a`}$$

Simplify.

$$x = \frac{`r -b` \pm \sqrt{`r b^2-4*a*c`}}{`r 2*a`}$$



Use prime factorization.

$$x = \frac{`r -b` \pm \sqrt{`r paste0(primeFactors(b^2-4*a*c),collapse="\\cdot")`}}{`r 2*a`}$$


Isolate the twin factors.

$$x = \frac{`r -b` \pm \sqrt{`r paste0(primeFactors(4*p^2),collapse="\\cdot")`}\cdot \sqrt{`r paste0(primeFactors(q),collapse="\\cdot")`}}{`r 2*a`}$$

Simplify the square root of the square.

$$x = \frac{`r -b` \pm `r paste0(primeFactors(2*p),collapse="\\cdot")`\cdot \sqrt{`r paste0(primeFactors(q),collapse="\\cdot")`}}{`r 2*a`}$$

Simplify the integer products.

$$x = \frac{`r -b` \pm `r 2*p`\cdot \sqrt{`r q`}}{`r 2*a`}$$

Split the fraction.

$$x = \frac{`r -b`}{`r 2*a`} \pm \frac{`r 2*p`\cdot \sqrt{`r q`}}{`r 2*a`}$$

Both numerators contain a factor of 2.


$$x = `r h` \pm `r p`\sqrt{`r q`}$$

So, $h=`r h`$ and $p=`r p`$ and $q=`r q`$.


I should mention this means we could now write the function in **factored form**.

$$f(x)~=~\left[x-(`r h`-`r p`\sqrt{`r q`})\right]\cdot\left[x-(`r h`+`r p`\sqrt{`r q`})\right]$$

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: et_qf_radical_solns