---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

\renewcommand{\arraystretch}{1.2}

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]
```

Name: \vspace{0.1in} \hrule

## `r bn` (v_`r params$rseed`)

```{r}
matpr = function(A){
  pra = "\\begin{bmatrix}\n"
  for(i in 1:dim(A)[1]){
    pra = paste0(pra,paste0(A[i,],collapse=" & "))
    if(i<dim(A)[1]){pra = paste0(pra,"\\\\\n")} else {pra = paste0(pra,"\n")}
  }
  pra = paste0(pra,"\\end{bmatrix}")
  return(pra)
}
```


Below are some (left-multiplicative) transformation matrices. 

\begin{tabular}{c c c c }
2D rotation & horizontal reflection & vertical reflection & scale \\  
$\begin{bmatrix}\cos(\theta) & \sin(\theta) \\ -\sin(\theta) & \cos(\theta) \end{bmatrix}$ & $\begin{bmatrix} -1 & 0 \\ 0 & 1 \end{bmatrix}$ & $\begin{bmatrix} 1 & 0 \\ 0 & -1 \end{bmatrix}$ & $\begin{bmatrix} k & 0 \\ 0 & k \end{bmatrix}$ \\\\
swap $x$ and $y$ & horizontal shear & vertical shear & squeeze\\
$\begin{bmatrix} 0 & 1 \\ 1 & 0 \end{bmatrix}$ & 
$\begin{bmatrix} 1 & m \\ 0 & 1 \end{bmatrix}$ &
$\begin{bmatrix} 1 & 0 \\ m & 1 \end{bmatrix}$ & 
$\begin{bmatrix} k & 0 \\ 0 & \frac{1}{k} \end{bmatrix}$\\
\end{tabular}


### Example:

Let's start with a triangle with vertices at $(0,0)$ and $(5,0)$ and $(5,5)$. We wish to shear it horizontally by $m=2$, then shear it vertically by $m=4$, then squeeze it by $k=2$, and then rotate by $\theta=`r atan(4/3)/pi*180`^{\circ}$. To find the new coordinates, we could complete the following multiplication.

```{r,echo=F}
th = atan(4/3)
```


$$\begin{bmatrix}`r cos(th)` & `r sin(th)` \\ `r -sin(th)` & `r cos(th)` \end{bmatrix} \cdot \begin{bmatrix} 2 & 0 \\ 0 & \frac{1}{2} \end{bmatrix} \cdot \begin{bmatrix} 1 & 0 \\ 4 & 1 \end{bmatrix} \cdot \begin{bmatrix} 1 & 2 \\ 0 & 1 \end{bmatrix} \cdot \begin{bmatrix} 0 & 5 & 5 \\ 0 & 0 & 5 \end{bmatrix}$$

Notice, the order seems backward. This is the standard way of representing transformations.



