```{r,echo=F}
myorder = sample(1:4)
wrds = c("translation","rotation","glide","mirror")
mywrds = wrds[myorder]

al = paste0("* ",wrds,collapse="\n")
sol1 = paste0(1*(myorder[1]==1:4),collapse="")
sol2 = paste0(1*(myorder[2]==1:4),collapse="")
sol3 = paste0(1*(myorder[3]==1:4),collapse="")
sol4 = paste0(1*(myorder[4]==1:4),collapse="")

getbasedots = function(fg=1,n=4){
    if(fg<6){
        x = runif(2*n,0.1,0.9)
        y = runif(2*n,0.1,0.9)-0.5
        h = runif(2*n)
        p = sample(1:20,2*n)
    } else {
        x = runif(n,0.1,0.9)
        y = runif(n,0.1,0.9)-0.5
        h = runif(n)
        p = sample(1:20,n)
        x = c(x,x)
        y = c(y,-y)
        h = c(h,h)
        p = c(p,p) 
    }
    dots = data.frame(x,y,h,p)
    return(dots)
}



translate = function(dots,dx=1){
    tdots = data.frame(dots)
    tdots$x = dots$x+dx
    return(tdots)
}
rotate = function(dots,xr){
    tdots = data.frame(dots)
    tdots$x = tdots$x-xr
    tdots$x = -tdots$x+xr
    tdots$y = -tdots$y
    return(tdots)
}
glide = function(dots,dx){
    tdots = data.frame(dots)
    tdots$x = tdots$x+dx
    tdots$y = -tdots$y
    return(tdots)
}
mirror = function(dots,xr){
    tdots = data.frame(dots)
    tdots$x = tdots$x-xr
    tdots$x = -tdots$x+xr
    return(tdots)
}



```

Question
========

```{r,echo=F,fig.dim=c(3,6)}

lwd=3
col="blue"

```
\


Label the four transformations:

## Transformation 1

```{r,echo=F,fig.dim=c(4,2)}
NN = 6
cex = 3
par(mar=c(0,0,0,0))
dots = getbasedots(1,NN)
pch = sample(c(0,1,3,4,5,7,8,9,10,11,12,13,15,16,18,19,20),2*NN,F)
hues = seq(0,1,length.out=2*NN+1)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[1]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
# lines(dots$x,dots$y,lwd=lwd,col=col)
# lines(d2$x,d2$y,lwd=lwd,col=col)
points(dots$x,dots$y,pch=pch,col=hsv(hues,0.8,0.8),cex=cex)
points(d2$x,d2$y,pch=pch,col=hsv(hues,0.8,0.8),cex=cex)
abline(v=seq(0,2,1),lty=2)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))
```
\

* ##ANSWER1##


## Transformation 2

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
# dots = getbasedots(1,6)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[2]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
# lines(dots$x,dots$y,lwd=lwd,col=col)
# lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))
points(dots$x,dots$y,pch=pch,col=hsv(hues,0.8,0.8),cex=cex)
points(d2$x,d2$y,pch=pch,col=hsv(hues,0.8,0.8),cex=cex)
```
\

* ##ANSWER2##


## Transformation 3

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
# dots = getbasedots(1,6)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[3]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
# lines(dots$x,dots$y,lwd=lwd,col=col)
# lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))
points(dots$x,dots$y,pch=pch,col=hsv(hues,0.8,0.8),cex=cex)
points(d2$x,d2$y,pch=pch,col=hsv(hues,0.8,0.8),cex=cex)
```
\

* ##ANSWER3##

## Transformation 4

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
# dots = getbasedots(1,6)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[4]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
# lines(dots$x,dots$y,lwd=lwd,col=col)
# lines(d2$x,d2$y,lwd=lwd,col=col)
abline(v=seq(0,2,1),lty=2)
abline(h=c(0.5,-0.5))
abline(v=c(0,2))
points(dots$x,dots$y,pch=pch,col=hsv(hues,0.8,0.8),cex=cex)
points(d2$x,d2$y,pch=pch,col=hsv(hues,0.8,0.8),cex=cex)
```
\

* ##ANSWER4##




Answerlist
--------

`r al`
`r al`
`r al`
`r al`


Solution
========

* Transformation 1: `r mywrds[1]`.
* Transformation 2: `r mywrds[2]`.
* Transformation 3: `r mywrds[3]`.
* Transformation 4: `r mywrds[4]`.

`r myorder`

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: tra_rot_gli_mir