```{r,echo=FALSE}
M = 2+1/4
H = 1+29/32
J = 19/32

```

Question
========

In plumbing, elbows change the direction of pipe. For fitting pipes, there are some key measurements:

* $\theta=$ the elbow angle. 
    * Notice, this is a turn angle, so 22.5° is a gentle turn, 45° is a sharper turn, and 90° is a sharp right turn.
* $J=$ the "take-off"
    * Initial calculations are based on the center line ("center to center"), but the actual pipes are cut shorter than the central line, because of the geometry of the elbow. This means some amount is "taken off" from the initial calculated length.




A common plumbing conundrum involves connecting two parallel pipes using two elbows and a section of diagonal pipe.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")

# xp1 = c(0,0.3,0.3,0)
# yp1 = c(0,0,0.1,0.1)

thet = pi/6
j = 0.15
r1 = 0.2
r2 = 0.16
r3 = 0.12
h = 0.4

elbow = function(r,H,th=pi/4){
    x0 = -r
    y0 = -r*tan(th/2)
    ths = seq(0,th,length.out=600)
    xarc = x0+2*r*cos(ths)
    yarc = y0+2*r*sin(ths)
    xbot = c(-r,r)
    ybot = c(-H,-H)
    phi = th+pi/2
    xtop = c(H*cos(phi)+r*cos(th),H*cos(phi)-r*cos(th))
    ytop = c(H*sin(phi)+r*sin(th),H*sin(phi)-r*sin(th))
    xs = c(x0,xbot,xarc,xtop)
    ys = c(y0,ybot,yarc,ytop)
    return(list(xs,ys))
}
elbowin = function(r,r2,r3,J,H,th=pi/4){
    x0 = -r
    y0 = -r*tan(th/2)
    ths = seq(0,th,length.out=100)
    phi = th+pi/2
    xs = c(-r3,-r2,-r2,r2,r2,r3,x0+(r+r3)*cos(ths),J*cos(phi)+r3*cos(th),J*cos(phi)+r2*cos(th),H*cos(phi)+r2*cos(th),H*cos(phi)-r2*cos(th),J*cos(phi)-r2*cos(th),J*cos(phi)-r3*cos(th),x0+(r-r3)*cos(rev(ths)))
    ys = c(-J,-J,-H,-H,-J,-J,y0+(r+r3)*sin(ths),J*sin(phi)+r3*sin(th),J*sin(phi)+r2*sin(th),H*sin(phi)+r2*sin(th),H*sin(phi)-r2*sin(th),J*sin(phi)-r2*sin(th),J*sin(phi)-r3*sin(th),y0+(r-r3)*sin(rev(ths)))
    return(list(xs,ys))
}


plot(0,0,"n",xlim=c(-1,1),ylim=c(-1,1),axes=F,ann=F)

e1 = elbow(r1,h,thet)
polygon(e1[[1]],e1[[2]],col="grey")
ei1 = elbowin(r1,r2,r3,j,h,thet)
polygon(ei1[[1]],ei1[[2]],col = "white")

phi = thet+pi/2
polygon(c(-r2,r2,r2,-r2),c(-1,-1,-j,-j),col=rgb(1,0,0,0.2),border = NA)
polygon(c(r3,r2,r2,r3),c(-1,-1,-j,-j),col=rgb(1,0,0,1),border = NA)
polygon(c(-r3,-r2,-r2,-r3),c(-1,-1,-j,-j),col=rgb(1,0,0,1),border = NA)

polygon(c(j*cos(phi)+r2*cos(thet),1*cos(phi)+r2*cos(thet),1*cos(phi)-r2*cos(thet),j*cos(phi)-r2*cos(thet)),c(j*sin(phi)+r2*sin(thet),1*sin(phi)+r2*sin(thet),1*sin(phi)-r2*sin(thet),j*sin(phi)-r2*sin(thet)),col=rgb(0,0,1,0.2),border = NA)

polygon(c(j*cos(phi)+r2*cos(thet),j*cos(phi)+r3*cos(thet),1*cos(phi)+r3*cos(thet),1*cos(phi)+r2*cos(thet)),c(j*sin(phi)+r2*sin(thet),j*sin(phi)+r3*sin(thet),1*sin(phi)+r3*sin(thet),1*sin(phi)+r2*sin(thet)),col=rgb(0,0,1,0.6),border = NA)

polygon(c(j*cos(phi)-r2*cos(thet),j*cos(phi)-r3*cos(thet),1*cos(phi)-r3*cos(thet),1*cos(phi)-r2*cos(thet)),c(j*sin(phi)-r2*sin(thet),j*sin(phi)-r3*sin(thet),1*sin(phi)-r3*sin(thet),1*sin(phi)-r2*sin(thet)),col=rgb(0,0,1,0.6),border = NA)


xmid = c(0,0,cos(thet+pi/2))
ymid = c(-1,0,sin(thet+pi/2))
lines(xmid,ymid,lty=3)


polygon(e1[[1]],e1[[2]],border="black",lwd=2)

```
\


Solution
========




Meta-information
============
extype: num
exsolution: 
exname: pyth_thrm_get_leg
extol: 0.1