```{r,echo=FALSE}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

fsimp = function(top,bot){
    gg = abs(gcd(c(top,bot)))
    top = round(abs(top)/gg*sign(top*bot))
    bot = round(abs(mbot)/gg)
    if(bot==1){
        return(top)
    } else {
        return(paste0("\\frac{",top,"}{",bot,"}"))
    }
}

xpar = c(1,4,9)
ypar = c(1,2,3)
yext = c(-1,-2,-3)

# horizontal shift before possible reflection

# y = a*sqrt(bx-h)+k

h = sample(-9:1,1)
k = sample(-4:4,1)
a = sample(c(-2,-1,1,2),1)
b = sample(c(-1,1),1)

xc = (xpar+h)/b
yc = a*ypar+k
xd = xc
yd = k-a*ypar

ii = sample(1:3,2)
xv = xc[ii[1]]
yv = yc[ii[1]]
xe = xc[ii[2]]
ye = yd[ii[2]]

mtop = diff(c(yv,ye))
mbot = diff(c(xv,xe))

mf = fsimp(mtop,mbot)

```

Question
========

A transformed square-root function, $y=f(x)$, is graphed below. A linear function, $y=L(x)$, is not shown, but it goes through point $(`r xv`,`r yv`)$ and has a slope of $`r mf`$.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s",mar=c(4,4,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="y")

for(i in -10:10){
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
yy = a*sqrt(b*xx-h)+k

xx = xx[abs(yy)<=10]
yy = yy[abs(yy)<=10]


lines(xx,yy,col="blue",lwd=2)

x2 = (c(0,1,4,9,16)+h)/b
y2 = a*c(0,1,2,3,4)+k
x2 = x2[abs(y2)<=10]
y2 = y2[abs(y2)<=10]

points(x2,y2,pch=19,col="blue")

```
\

If standard algebraic steps were used to find $x$ values that satisfy equation $f(x)=L(x)$, what extraneous solution would be found?


Solution
========

You should be able to complete the picture. Use symmetry to complete the parabola, and use the slope to extend the line.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s",mar=c(4,4,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="y")

for(i in -10:10){
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
yy = a*sqrt(b*xx-h)+k

xx = xx[abs(yy)<=10]
yy = yy[abs(yy)<=10]


lines(xx,yy,col="blue",lwd=2)

x2 = (c(0,1,4,9,16)+h)/b
y2 = a*c(0,1,2,3,4)+k
x2 = x2[abs(y2)<=10]
y2 = y2[abs(y2)<=10]

# points(x2,y2,pch=19,col="blue")

xl = seq(-10,10,0.1)
yl = mtop/mbot*(xl-xv)+yv
xl = xl[abs(yl)<=10]
yl = yl[abs(yl)<=10]

lines(xl,yl,col="red",lwd=2)

xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
yy = -a*sqrt(b*xx-h)+k

xx = xx[abs(yy)<=10]
yy = yy[abs(yy)<=10]

lines(xx,yy,col="grey",lwd=2,lty=2)

points(xe,ye,pch=19,col="red")

```
\

The intersection of the line with the second half of the parabola is at point $(`r xe`,`r ye`)$. Thus the extraneous solution is $x=`r xe`$.



Meta-information
============
extype: num
exsolution: `r xe`
exname: x_find_extraneous_graph