---
output: slidy_presentation
---

# Pingala Rhythms

* Musical rhythms have mathematical connections!
* Pingala was an Indian poet around 300 BCE.
* Pingala described the Fibonacci sequence over 1000 years before "Fibonacci".

```{r,echo=F,warning=F,results='hide',comment=F,message=F}
library(gm)
```

# Quarter notes and half notes

* A quarter note is filled in. It represents 1 beat.
* A half note is open. It represents 2 beats.
* For example, the "Jingle Bells" rhythm is two quarters followed by a half.


```{r,echo=F,cache=TRUE}
m <- Music()

durations = c(1,1,2,1,1,2)
pitches = rep("E5",length(durations))

m <- m + Meter(4,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

m <- Music()
m <- m + Meter(4,4) +
  Line(pitches = rep(pitches,4), durations = rep(durations,4))
show(m, to = c("audio"))

```


Notice, the time signature, $\substack{4 \\ 4}$, shows 4 beats per measure (and the four underneath says a quarter note represents a single beat). Try tapping out the 4 beats while the Jingle-Bell rhythm plays.


# How many 3-beat rhythms?

When filling a measure of $\substack{3 \\ 4}$ with quarter notes and half notes, there are only 3 possible rhythms.

```{r,echo=F,cache=TRUE}
m <- Music()
durations = c(1,1,1)
pitches = rep("F4",length(durations))
m <- m + Meter(3,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

m <- Music()
durations = c(1,2)
pitches = rep("F4",length(durations))
m <- m + Meter(3,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

m <- Music()
durations = c(2,1)
pitches = rep("F4",length(durations))
m <- m + Meter(3,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

```

>- Can you clap out these rhythms? As one person repeatedly, and evenly, counts "one, two, three", try clapping on the 1 and 2, but not the three. Or, try clapping on the 1 and 3, but not the 2. Start slowly!



# How many 4-beat rhythms?

Can you find all the 4-beat rhythms? In other words, how many ways can you fill a measure of $\substack{4 \\ 4}$ with quarter notes and half notes?

# How many 4-beat rhythms?

When filling a measure of $\substack{4 \\ 4}$ with quarter notes and half notes, there are only **5** possible rhythms.

```{r,echo=F,cache=TRUE}
m <- Music()
durations = c(1,1,1,1)
pitches = rep("F4",length(durations))
m <- m + Meter(4,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

m <- Music()
durations = c(1,1,2)
pitches = rep("F4",length(durations))
m <- m + Meter(4,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

m <- Music()
durations = c(1,2,1)
pitches = rep("F4",length(durations))
m <- m + Meter(4,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))


m <- Music()
durations = c(2,1,1)
pitches = rep("F4",length(durations))
m <- m + Meter(4,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))


m <- Music()
durations = c(2,2)
pitches = rep("F4",length(durations))
m <- m + Meter(4,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))
```


# How many 5-beat rhythms?

Can you find all the 5-beat rhythms? In other words, how many ways can you fill a measure of $\substack{5 \\ 4}$ with quarter notes and half notes?


# How many 5-beat rhythms?

When filling a measure of $\substack{5 \\ 4}$ with quarter notes and half notes, there are **8** possible rhythms.

```{r,echo=F,cache=TRUE}

rhythms = list(c(1,1,1,1,1),
               c(1,1,1,2),
               c(1,1,2,1),
               c(1,2,1,1),
               c(1,2,2),
               c(2,1,1,1),
               c(2,1,2),
               c(2,2,1))


m <- Music()
for(i in 1:length(rhythms)){
    durations = rhythms[[i]]
    pitches = rep("F4",length(durations))
    m <- m + Meter(5,4) +
      Line(pitches = pitches, durations = durations)
}
show(m, to = c("score"))

```


If you can clap all these... you've got RHYTHM!

# How can we systematically produce the 5-beat rhythms?

Notice, to make **all** of the 5-beat rhythms:

* Put a quarter note in front of each 4-beat rhythm.
* Put a half note in front of each 3-beat rhythm.

```{r,echo=F,cache=TRUE}
rhythms = list(c(1,1,1,1,1),
               c(1,1,1,2),
               c(1,1,2,1),
               c(1,2,1,1),
               c(1,2,2),
               c(2,1,1,1),
               c(2,1,2),
               c(2,2,1))

notehead2 <- Notehead(1, color = "#FF0000")
m <- Music()
for(i in 1:length(rhythms)){
    durations = rhythms[[i]]
    pitches = rep("F4",length(durations))
    m <- m + Meter(5,4) +
      Line(pitches = pitches, durations = durations)+notehead2
}
show(m, to = c("score"))

```


# Let's start a table

```{r,echo=F}
bpm = paste0(1:8)
nr = c("1","2","3","5","8"," "," "," ")

mytab = data.frame(bpm,nr)
colnames(mytab) = c("Beats per measure","How many rhythms?")

kableExtra::kable_styling(kableExtra::kable(mytab),bootstrap_options = c("striped", "bordered", "hover"), full_width = F)
```



# How many 6-beat rhythms?

Can you find all the 6-beat rhythms? In other words, how many ways can you fill a measure of $\substack{6 \\ 4}$ with quarter notes and half notes?



