---
output: pdf_document
---

\hspace{4in} Name: \vspace{5pt} \hrule

# Pingala Rhythms

```{r,echo=F,message=F,warning=F}
library(gm)
```

When filling a measure of $\substack{3 \\ 4}$ with quarter notes and half notes, there are only 3 possible rhythms.

```{r,echo=F}
m <- Music()
durations = c(1,1,1)
pitches = rep("F4",length(durations))
m <- m + Meter(3,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

m <- Music()
durations = c(1,2)
pitches = rep("F4",length(durations))
m <- m + Meter(3,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

m <- Music()
durations = c(2,1)
pitches = rep("F4",length(durations))
m <- m + Meter(3,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

```


When filling a measure of $\substack{4 \\ 4}$ with quarter notes and half notes, there are 5 possible rhythms.


```{r,echo=F}

rhythms = list(c(1,1,1,1),
               c(1,1,2),
               c(1,2,1),
               c(2,1,1),
               c(2,2))

m <- Music()
durations = unlist(rhythms)
pitches = rep("F4",length(durations))
m <- m + Meter(4,4) +
  Line(pitches = pitches, durations = durations)
show(m, to = c("score"))

```

\vspace{12 pt}

1. Find all the ways to fill a $\substack{5 \\ 4}$ measure with quarter notes and half notes.

\vfill

2. Find all the ways to fill a $\substack{6 \\ 4}$ measure with quarter notes and half notes.

\vfill

\newpage

3. Make a table that shows how many Pingala rhythms are possible for any number of beats per measure between 1 and 10.

```{r,echo=F,fig.dim=c(5,8)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,1),ylim=c(0,1))
lines(c(0,0),c(0,1))
lines(c(0.5,0.5),c(0,1))
lines(c(1,1),c(0,1))
lines(c(0,1),c(1,1))
abline(h=0.9,lwd=3)
text(0.25,0.95,"Beats per measure")
text(0.75,0.95,"How many rhythms?")

for(i in 1:10){
    text(0.25,0.95-0.9/10*i,i)
    lines(c(0,1),rep(0.95-0.9/10*(i+0.5),2))
}

```




