---
output: pdf_document
params:
    rseed: 2
    showsol: true
header-includes:
  - \usepackage{multicol}
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]

pn = function(c,d){
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    p = gsub("-{1i}","-i",p,fixed=T)
    p = gsub("+{1i}","+i",p,fixed=T)
    return(p)
}

gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
```

## `r bn`

# Example 1

```{r}
p1s = character()
p2s = character()
p3s = character()
p4s = character()

maxn = 6
maxc = 9
# while(T){
#     nt1 = sample(2:4,1)
#     nt2 = sample(2:4,1)
#     nt3 = nt1*nt2
#     if(nt3<=9 && nt3>4){break}
# }
nt1 = 4
nt2 = 2
nt3 = 8

while(T){
    n1 = rev(sort(sample(0:maxn,nt1)))
    n2 = rev(sort(sample(0:maxn,nt2)))
    c1 = sample(1:maxc,nt1,T)*sample(c(-1,1),nt1,T)
    c2 = sample(1:maxc,nt2,T)*sample(c(-1,1),nt2,T)
    n3 = numeric()
    c3 = numeric()
    for(i in 1:nt1){
        for(j in 1:nt2){
            n3 = c(n3,n1[i]+n2[j])
            c3 = c(c3,c1[i]*c2[j])
        }
    }
    n3poss = 0:(2*maxn)
    c3sums = rep(0,2*maxn+1)
    for(i in n3poss){
        for(j in 1:length(n3)){
            if(i==n3[j]){
                c3sums[i+1] = c3sums[i+1]+c3[j]
            }
        }
    }
    n3poss = rev(n3poss)
    c3sums = rev(c3sums)
    n4 = n3poss[c3sums!=0]
    c4 = c3sums[c3sums!=0]
    if(length(c4)<length(c3) && sum(sign(c1))>=0 && sum(sign(c2))>=0){break}
}
p1s = c(p1s,pn(c1,n1))
p2s = c(p2s,pn(c2,n2))
p3s = c(p3s,pn(c3,n3))
p4s = c(p4s,pn(c4,n4))

```

Expand the product into standard form.

$$\left(`r pn(c1,n1)`\right)\cdot\left(`r pn(c2,n2)`\right)$$

\color{red}

Multiply each term of the first polynomial by each term of the second polynomial.

```{r,results='asis',warning=F}

terms1 = character()
terms2 = character()
terms3 = character()

for(i in 1:length(c1)){
    terms1 = c(terms1,paste0("$",pn(c1[i],n1[i]),"$"))
}
for(i in 1:length(c2)){
    terms2 = c(terms2,paste0("$",pn(c2[i],n2[i]),"$"))
}
for(i in 1:length(c1)){
    for(j in 1:length(c2)){
        terms3 = c(terms3,paste0("$",pn(c1[i]*c2[j],n1[i]+n2[j]),"$"))
    }
}
M <- matrix(terms3, nrow=nt2, ncol=nt1, byrow = F,dimnames = list(terms2, terms1))

library(kableExtra)
kable(M, format = "latex", escape = F, booktabs = TRUE) %>%
  column_spec(1, border_right = TRUE, border_left = T) %>%
  column_spec(nt1+1, border_right = TRUE)

```


$$`r pn(c3,n3)`$$

Combine like terms.

$$`r pn(c4,n4)`$$


\color{black}




# Example 2

```{r}
# while(T){
#     nt1 = sample(2:4,1)
#     nt2 = sample(2:4,1)
#     nt3 = nt1*nt2
#     if(nt3<=9 && nt3>4){break}
# }

nt1 = 3
nt2 = 3
nt3 = 9

while(T){
    n1 = rev(sort(sample(0:maxn,nt1)))
    n2 = rev(sort(sample(0:maxn,nt2)))
    c1 = sample(1:maxc,nt1,T)*sample(c(-1,1),nt1,T)
    c2 = sample(1:maxc,nt2,T)*sample(c(-1,1),nt2,T)
    n3 = numeric()
    c3 = numeric()
    for(i in 1:nt1){
        for(j in 1:nt2){
            n3 = c(n3,n1[i]+n2[j])
            c3 = c(c3,c1[i]*c2[j])
        }
    }
    n3poss = 0:(2*maxn)
    c3sums = rep(0,2*maxn+1)
    for(i in n3poss){
        for(j in 1:length(n3)){
            if(i==n3[j]){
                c3sums[i+1] = c3sums[i+1]+c3[j]
            }
        }
    }
    n3poss = rev(n3poss)
    c3sums = rev(c3sums)
    n4 = n3poss[c3sums!=0]
    c4 = c3sums[c3sums!=0]
    p1 = pn(c1,n1)
    p2 = pn(c2,n2)
    p3 = pn(c3,n3)
    p4 = pn(c4,n4)
    if(length(c4)<length(c3) && sum(sign(c1))>=0 && sum(sign(c2))>=0 && !(p4 %in% p4s)){break}
}
p1s = c(p1s,p1)
p2s = c(p2s,p2)
p3s = c(p3s,p3)
p4s = c(p4s,p4)

```

Expand the product into standard form.

$$\left(`r pn(c1,n1)`\right)\cdot\left(`r pn(c2,n2)`\right)$$

\color{red}

Multiply each term of the first polynomial by each term of the second polynomial.

```{r,results='asis',warning=F}

terms1 = character()
terms2 = character()
terms3 = character()

for(i in 1:length(c1)){
    terms1 = c(terms1,paste0("$",pn(c1[i],n1[i]),"$"))
}
for(i in 1:length(c2)){
    terms2 = c(terms2,paste0("$",pn(c2[i],n2[i]),"$"))
}
for(i in 1:length(c1)){
    for(j in 1:length(c2)){
        terms3 = c(terms3,paste0("$",pn(c1[i]*c2[j],n1[i]+n2[j]),"$"))
    }
}
M <- matrix(terms3, nrow=nt2, ncol=nt1, byrow = F,dimnames = list(terms2, terms1))

library(kableExtra)
kable(M, format = "latex", escape = F, booktabs = TRUE) %>%
  column_spec(1, border_right = TRUE, border_left = T) %>%
  column_spec(nt1+1, border_right = TRUE)

```


$$`r pn(c3,n3)`$$

Combine like terms.

$$`r pn(c4,n4)`$$


\color{black}

\newpage

```{r}
for(i in 1:19){
    while(T){
        nt1 = sample(2:4,1)
        nt2 = sample(2:4,1)
        nt3 = nt1*nt2
        if(nt3<=9 && nt3>4){break}
    }
    while(T){
        n1 = rev(sort(sample(0:maxn,nt1)))
        n2 = rev(sort(sample(0:maxn,nt2)))
        c1 = sample(1:maxc,nt1,T)*sample(c(-1,1),nt1,T)
        c2 = sample(1:maxc,nt2,T)*sample(c(-1,1),nt2,T)
        n3 = numeric()
        c3 = numeric()
        for(i in 1:nt1){
            for(j in 1:nt2){
                n3 = c(n3,n1[i]+n2[j])
                c3 = c(c3,c1[i]*c2[j])
            }
        }
        n3poss = 0:(2*maxn)
        c3sums = rep(0,2*maxn+1)
        for(i in n3poss){
            for(j in 1:length(n3)){
                if(i==n3[j]){
                    c3sums[i+1] = c3sums[i+1]+c3[j]
                }
            }
        }
        n3poss = rev(n3poss)
        c3sums = rev(c3sums)
        n4 = n3poss[c3sums!=0]
        c4 = c3sums[c3sums!=0]
        p1 = pn(c1,n1)
        p2 = pn(c2,n2)
        p3 = pn(c3,n3)
        p4 = pn(c4,n4)
        if(length(c4)<length(c3) && sum(sign(c1))>=0 && sum(sign(c2))>=0 && !(p4 %in% p4s)){break}
    }
    p1s = c(p1s,p1)
    p2s = c(p2s,p2)
    p3s = c(p3s,p3)
    p4s = c(p4s,p4)
}
prods = paste0("\\left(",p1s,"\\right)\\cdot\\left(",p2s,"\\right)")
```

Expand the following products of polynomials into standard form.

\begin{align*}
```{r,results='asis'}
for(i in 3:length(prods)){
    cat(paste0("&",prods[i],"&&&\\color{gray}",p4s[i],"\\color{black}\\\\\\\\\n"))
}
```
\end{align*}

