```{r,echo=F}
fgs = sample(1:7,7)

sols = character()
for(i in 1:length(fgs)){
    sols = c(sols,paste0(1*(1:7==fgs[i]),collapse=""))
}

w1 = c("p1 (hop)","p11g (step)","p1m1 (sidle)","p2 (spinning hop)","p2mg (spinning sidle)","p11m (jump)","p2mm (spinning jump)")

wrds = w1[fgs]

# w2 = c("hop","step","sidle","spinning hop","spinning sidle","jump","spinning jump")
# wrd1a = w1[fg1]
# wrd1b = w2[fg1]
# wrd2a = w1[fg2]
# wrd2b = w2[fg2]


getbasedots = function(fg=1,n=4){
    if(fg<6){
        x = runif(2*n,0.05,0.95)
        y = runif(2*n)-0.5
        h = runif(2*n)
        p = sample(c(0,1,3,4,5,7,8,9,10,11,12,13,15,16,18,19,20),2*n,T)
    } else {
        x = runif(n,0.05,0.95)
        y = runif(n)-0.5
        h = runif(n)
        p = sample(c(0,1,3,4,5,7,8,9,10,11,12,13,15,16,18,19,20),n,T)
        x = c(x,x)
        y = c(y,-y)
        h = c(h,h)
        p = c(p,p) 
    }
    dots = data.frame(x,y,h,p)
    return(dots)
}

translate = function(dots,dx=1){
    tdots = data.frame(dots)
    tdots$x = dots$x+dx
    return(tdots)
}
rotate = function(dots,xr){
    tdots = data.frame(dots)
    tdots$x = tdots$x-xr
    tdots$x = -tdots$x+xr
    tdots$y = -tdots$y
    return(tdots)
}
glide = function(dots,dx){
    tdots = data.frame(dots)
    tdots$x = tdots$x+dx
    tdots$y = -tdots$y
    return(tdots)
}
mirror = function(dots,xr){
    tdots = data.frame(dots)
    tdots$x = tdots$x-xr
    tdots$x = -tdots$x+xr
    return(tdots)
}

drawdots = function(dots,fg,val=1){
    for(iii in 0:6){
        lines(c(iii,iii),c(-0.6,0.6),col="lightgrey")
    }
    points(dots$x,dots$y,col=hsv(dots$h,1,val),pch=dots$p)
    if(fg==1){
        for(i in 1:5){
            dots = translate(dots,1)
            points(dots$x,dots$y,col=hsv(dots$h,1,val),pch=dots$p)
        }
    }
    if(fg==2){
        for(i in 1:5){
            dots = glide(dots,1)
            points(dots$x,dots$y,col=hsv(dots$h,1,val),pch=dots$p)
        }
    }
    if(fg==3){
        for(i in 1:5){
            dots = mirror(dots,i)
            points(dots$x,dots$y,col=hsv(dots$h,1,val),pch=dots$p)
        }
    }
    if(fg==4){
        for(i in 1:5){
            dots = rotate(dots,i)
            points(dots$x,dots$y,col=hsv(dots$h,1,val),pch=dots$p)
        }
    }
    if(fg==5){
        for(i in 1:5){
            if(i%%2==1){
                dots = mirror(dots,i)
            } else {
                dots = rotate(dots,i)
            }
            points(dots$x,dots$y,col=hsv(dots$h,1,val),pch=dots$p)
        }
    }
    if(fg==6){
        for(i in 1:5){
            dots = translate(dots,1)
            points(dots$x,dots$y,col=hsv(dots$h,1,val),pch=dots$p)
        }
    }
    if(fg==7){
        for(i in 1:5){
            dots = mirror(dots,i)
            points(dots$x,dots$y,col=hsv(dots$h,1,val),pch=dots$p)
        }
    }
}



```

Question
========


For each of the patterns below, determine the Frieze group.

## Pattern 1

```{r,echo=F,fig.dim=c(6.2,1.4)}
par(mar=c(0,0,0,0))
dots = getbasedots(fgs[1],5)
plot(0,0,type="n",xlim=c(-0.1,6.1),ylim=c(-0.7,0.7),axes=F,ann=F)
drawdots(dots,fgs[1],0.7)
polygon(c(0,0,6,6),c(-0.6,0.6,0.6,-0.6),border="lightgrey")
```
\

Frieze group: ##ANSWER1##

## Pattern 2

```{r,echo=F,fig.dim=c(6.2,1.4)}
par(mar=c(0,0,0,0))
dots = getbasedots(fgs[2],5)
plot(0,0,type="n",xlim=c(-0.1,6.1),ylim=c(-0.7,0.7),axes=F,ann=F)
drawdots(dots,fgs[2],0.7)
polygon(c(0,0,6,6),c(-0.6,0.6,0.6,-0.6),border="lightgrey")
```
\

Frieze group: ##ANSWER2##

## Pattern 3

```{r,echo=F,fig.dim=c(6.2,1.4)}
par(mar=c(0,0,0,0))
dots = getbasedots(fgs[3],5)
plot(0,0,type="n",xlim=c(-0.1,6.1),ylim=c(-0.7,0.7),axes=F,ann=F)
drawdots(dots,fgs[3],0.7)
polygon(c(0,0,6,6),c(-0.6,0.6,0.6,-0.6),border="lightgrey")
```
\

Frieze group: ##ANSWER3##

## Pattern 4

```{r,echo=F,fig.dim=c(6.2,1.4)}
par(mar=c(0,0,0,0))
dots = getbasedots(fgs[4],5)
plot(0,0,type="n",xlim=c(-0.1,6.1),ylim=c(-0.7,0.7),axes=F,ann=F)
drawdots(dots,fgs[4],0.7)
polygon(c(0,0,6,6),c(-0.6,0.6,0.6,-0.6),border="lightgrey")
```
\

Frieze group: ##ANSWER4##

## Pattern 5

```{r,echo=F,fig.dim=c(6.2,1.4)}
par(mar=c(0,0,0,0))
dots = getbasedots(fgs[5],5)
plot(0,0,type="n",xlim=c(-0.1,6.1),ylim=c(-0.7,0.7),axes=F,ann=F)
drawdots(dots,fgs[5],0.7)
polygon(c(0,0,6,6),c(-0.6,0.6,0.6,-0.6),border="lightgrey")
```
\

Frieze group: ##ANSWER5##

## Pattern 6

```{r,echo=F,fig.dim=c(6.2,1.4)}
par(mar=c(0,0,0,0))
dots = getbasedots(fgs[6],5)
plot(0,0,type="n",xlim=c(-0.1,6.1),ylim=c(-0.7,0.7),axes=F,ann=F)
drawdots(dots,fgs[6],0.7)
polygon(c(0,0,6,6),c(-0.6,0.6,0.6,-0.6),border="lightgrey")
```
\

Frieze group: ##ANSWER6##

## Pattern 7

```{r,echo=F,fig.dim=c(6.2,1.4)}
par(mar=c(0,0,0,0))
dots = getbasedots(fgs[7],5)
plot(0,0,type="n",xlim=c(-0.1,6.1),ylim=c(-0.7,0.7),axes=F,ann=F)
drawdots(dots,fgs[7],0.7)
polygon(c(0,0,6,6),c(-0.6,0.6,0.6,-0.6),border="lightgrey")
```
\

Frieze group: ##ANSWER7##








Answerlist
--------

`r paste0("* ",w1,collapse="\n")`
`r paste0("* ",w1,collapse="\n")`
`r paste0("* ",w1,collapse="\n")`
`r paste0("* ",w1,collapse="\n")`
`r paste0("* ",w1,collapse="\n")`
`r paste0("* ",w1,collapse="\n")`
`r paste0("* ",w1,collapse="\n")`


Solution
========

* The first pattern is a `r wrds[1]`.
* The second pattern is a `r wrds[2]`.
* The third pattern is a `r wrds[3]`.
* The fourth pattern is a `r wrds[4]`.
* The fifth pattern is a `r wrds[5]`.
* The sixth pattern is a `r wrds[6]`.
* The seventh pattern is a `r wrds[7]`.


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",length(fgs)),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: recognize_Frieze_group