```{r,echo=FALSE,warning=FALSE}
# This problem assumes 4 candidates.
# 14 Yes/No ballots are represented (not all yes or all no)
# Each ballot count at top... total votes between 40 and 200

while(T){
    nv = sample(40:200,1)
    counts = c(0,diff(c(0,sort(sample(1:(nv-1),13)),nv)),0)
    ballots = list(c(1,1,1,1),
                   c(1,1,1,0),
                   c(1,1,0,1),
                   c(1,1,0,0),
                   c(1,0,1,1),
                   c(1,0,1,0),
                   c(1,0,0,1),
                   c(1,0,0,0),
                   c(0,1,1,1),
                   c(0,1,1,0),
                   c(0,1,0,1),
                   c(0,1,0,0),
                   c(0,0,1,1),
                   c(0,0,1,0),
                   c(0,0,0,1),
                   c(0,0,0,0))
    votes = rep(0,4)
    for(i in 1:16){
        votes = votes+counts[i]*ballots[[i]]
    }
    if(length(unique(votes))==4 && min(votes)>5){
        break
    }
}

extras = c(votes-1,votes+1,votes-2,votes+2,votes-3,votes+3,votes-4,votes+4)
ach = votes
ppp = 1
while(length(ach)<10){
    ppp = ppp+1
    if(ppp<10){
        ach = sort(unique(c(ach,sample(extras,1))))
    } else {
        ach = sort(unique(c(ach,sample(1:100,1))))
    }
}

cans = c("W","X","Y","Z")

sol1 = paste0(1*(ach==votes[1]),collapse="")
sol2 = paste0(1*(ach==votes[2]),collapse="")
sol3 = paste0(1*(ach==votes[3]),collapse="")
sol4 = paste0(1*(ach==votes[4]),collapse="")
sol5 = paste0(1*(max(votes)==votes),collapse="")

al1 = paste0("* ",ach,collapse="\n")
al5 = paste0("* Candidate ",cans,collapse="\n")

```

Question
========

In an [approval-vote election](https://en.wikipedia.org/wiki/Approval_voting), there are 4 candidates and `r nv` voters. Each voter indicated which candidates they approve of (with a 1) or disapprove of (with a 0). All possible ballots are shown below, and the table indicates how many of each type of ballot was cast.

| Number of ballots | `r paste0(counts," | ",collapse="")`
|`r paste0(rep(":---:|",17),collapse="")`
```{r, echo=F, results='asis'}
for(i in 1:4){
    cat("| Candidate",cans[i],"|")
    for(j in 1:16){
        cat(paste0(ballots[[j]][i]," | "))
    }
    cat("\n")
}
```

(You probably want to copy/paste this table into [sheets](https://sheets.new).)

1. How many approvals did Candidate W get? ##ANSWER1##
2. How many approvals did Candidate X get? ##ANSWER2##
3. How many approvals did Candidate Y get? ##ANSWER3##
4. How many approvals did Candidate Z get? ##ANSWER4##
5. Who won the election? ##ANSWER5##


Answerlist
--------

`r al1`
`r al1`
`r al1`
`r al1`
`r al5`


Solution
========

Each "1" corresponds to the ballot count number of votes. We can make another table with votes counts.

| Number of ballots | `r paste0(counts," | ",collapse="")`|
|`r paste0(rep(":---:|",17),collapse="")`
```{r, echo=F, results='asis'}
for(i in 1:4){
    cat("| Candidate",cans[i],"|")
    for(j in 1:16){
        cat(paste0(ballots[[j]][i]*counts[j]," | "))
    }
    cat("\n")
}
```

And then just sum each row.

* Candidate W got `r votes[1]` approvals
* Candidate X got `r votes[2]` approvals
* Candidate Y got `r votes[3]` approvals
* Candidate Z got `r votes[4]` approvals

And we see that Candidate `r cans[which(votes==max(votes))]` is the winner.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`|`r sol5`
exname: approval