```{r,echo=FALSE,warning=FALSE}
nc = sample(4:5,1)
nv = sample(6:9,1)

compare = function(prefs,i,j){
    pi = 0
    pj = 0
    for(k in 1:nv){
        prefi = prefs[[k]][i]
        prefj = prefs[[k]][j]
        if(prefi < prefj){
            pi = pi+1
        }
        if(prefj < prefi){
            pj = pj+1
        }
    }
    if(pi>pj){
        win = i
        lose = j
    }
    if(pj>pi){
        win = j
        lose = i
    }
    if(pj==pi){
        win = 0
        lose = 0
    }
    return(c(pi,pj,win,lose))
}

condorcet = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    alwayswin = rep(T,nc)
    for(i in 1:(nc-1)){
        for(j in (i+1):nc){
            pi = 0
            pj = 0
            for(k in 1:nv){
                prefi = prefs[[k]][i]
                prefj = prefs[[k]][j]
                if(prefi < prefj){
                    pi = pi+1
                }
                if(prefj < prefi){
                    pj = pj+1
                }
            }
            if(pi <= pj){
                alwayswin[i] = F
            }
            if(pi >= pj){
                alwayswin[j] = F
            }
        }
    }
    if(length(unique(alwayswin))==2){
        return(which(alwayswin))
    } else {
        return(0)
    }
}

plurality = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    points = rep(0,nc)
    for(k in 1:nv){
        wo = which(prefs[[k]]==1)
        points[wo] = points[wo]+1
    }
    mp = max(points)
    if(sum(mp==points)==1){
        return(which(points==mp))
    } else {
        return(0)
    }
}

borda = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    win = which(bps==max(bps))
    if(length(win)>1){
        return(0)
    } else {
        return(win)
    }
}

borda_pts = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    return(bps)
}

nocond = sample(c(T,F),1,F,c(1,nc))

while(T){
    prefs = list()
    for(i in 1:nv){
        pref = sample(1:nc)
        prefs[[i]] = pref
    }
    cond = condorcet(prefs)
    plur = plurality(prefs)
    bord = borda(prefs)
    if(bord!=plur && bord!=0 && bord != cond){
        break
    }
}
cans = LETTERS[26-nc+1:nc]
bp = borda_pts(prefs)
ach = sort(unique(c(bp,sample(c(bp-1,bp+1,bp-2,bp+2))))[1:10])
while(length(ach)<10){
    ach = sort(unique(c(ach,sample(1:(max(bp)+10),1))))
}

al = paste0("* ",ach,collapse="\n")
al2 = paste0("* Candidate ",cans,collapse="\n")
sol = character()
for(i in 1:nc){
    sol = c(sol,paste0(1*(bp[i]==ach),collapse=""))
}
sol = c(sol,paste0(1*(1:nc==bord),collapse=""))

```

Question
========

In Adams, Massachusetts, `r nc` candidates (`r LETTERS[26-nc+1]` through Z) are running in an election with a single winner. There are `r nv` voters (A through `r LETTERS[nv]`) who each rank the candidates from 1 to `r nc`, with 1 meaning first choice and `r nc` meaning last choice. Those rankings are shown below. Each column represents a single voter's ranking.

|    | `r paste0("voter ",LETTERS[1:nv]," | ",collapse="")`
|:---:|`r paste0(rep(":---:|",nv),collapse="")`
```{r,echo=F,results='asis'}
for(i in 1:nc){
    cat(paste0("| candidate ",LETTERS[26-nc+i]," | "))
    for(j in 1:nv){
        cat(paste0(prefs[[j]][i]," | "))
    }
    cat("\n")
}
```


What [Borda count](https://en.wikipedia.org/wiki/Borda_count) would each candidate get?

```{r,echo=F,results='asis'}
for(i in 1:nc){
    cat(paste0("* Borda count of candidate ",cans[i],": ##ANSWER",i,"##\n"))
}
cat(paste0("* Who wins the Borda election? ##ANSWER",nc+1,"##\n"))
```

Answerlist
--------

`r paste0(rep(al,nc),collapse="\n")`
`r al2`

Solution
========

There are `r nc` candidates. So, we subtract each preference number from `r nc` to get Borda points. We then add all the Borda points from each voter.

```{r,echo=F,fig.dim=c(2+nv/3,1+nc/3)}
bordtable = function(prefs){
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-1,nv+1),ylim=c(0.5,nc+1.5),axes=F,ann=F)
    bp = borda_pts(prefs)
    for(i in 1:nc){
        text(-0.5,nc+1-i,cans[i])
        for(j in 1:nv){
            text(j-0.5,nc+1-i,nc-prefs[[j]][i],col="red")
        }
        text(nv+0.5,nc+1-i,bp[i],col="red",cex=1.2)
    }
    for(j in 1:nv){
        text(j-0.5,nc+1,LETTERS[j])
    }
    abline(h=nc+0.5)
    abline(v=0)
    abline(v=nv)
    text(nv+0.5,nc+1,"TOTAL",cex=0.8)
}
bordtable(prefs)
```



Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",nc+1),collapse=" | ")`
exsolution: `r paste0(sol,collapse=" | ")`
exname: borda