```{r,echo=FALSE,warning=FALSE}
nc = sample(3:6,1)
nv = 7

compare = function(prefs,i,j){
    pi = 0
    pj = 0
    for(k in 1:nv){
        prefi = prefs[[k]][i]
        prefj = prefs[[k]][j]
        if(prefi < prefj){
            pi = pi+1
        }
        if(prefj < prefi){
            pj = pj+1
        }
    }
    if(pi>pj){
        win = i
        lose = j
    }
    if(pj>pi){
        win = j
        lose = i
    }
    if(pj==pi){
        win = 0
        lose = 0
    }
    return(c(pi,pj,win,lose))
}

condorcet = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    alwayswin = rep(T,nc)
    for(i in 1:(nc-1)){
        for(j in (i+1):nc){
            pi = 0
            pj = 0
            for(k in 1:nv){
                prefi = prefs[[k]][i]
                prefj = prefs[[k]][j]
                if(prefi < prefj){
                    pi = pi+1
                }
                if(prefj < prefi){
                    pj = pj+1
                }
            }
            if(pi <= pj){
                alwayswin[i] = F
            }
            if(pi >= pj){
                alwayswin[j] = F
            }
        }
    }
    if(length(unique(alwayswin))==2){
        return(which(alwayswin))
    } else {
        return(0)
    }
}

plurality = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    points = rep(0,nc)
    for(k in 1:nv){
        wo = which(prefs[[k]]==1)
        points[wo] = points[wo]+1
    }
    mp = max(points)
    if(sum(mp==points)==1){
        return(which(points==mp))
    } else {
        return(0)
    }
}

borda = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    win = which(bps==max(bps))
    if(length(win)>1){
        return(0)
    } else {
        return(win)
    }
}

borda_pts = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    return(bps)
}

nocond = sample(c(T,F),1,F,c(1,nc))

while(T){
    prefs = list()
    for(i in 1:nv){
        pref = sample(1:nc)
        prefs[[i]] = pref
    }
    cond = condorcet(prefs)
    plur = plurality(prefs)
    if(cond!=0 && cond!=plur && nocond==F){
        sol = paste0(1*(cond==1:(nc+1)),collapse="")
        break
    }
    if(nocond==T && cond==0 && plur!=0){
        sol = paste0(paste0(rep(0,nc),collapse=""),"1")
        break
    }
}

wo = sample(1:nc,1)
ans = borda_pts(prefs)[wo]
cans = LETTERS[26-nc+1:nc]

```

Question
========

In Adams, Massachusetts, `r nc` candidates (`r LETTERS[26-nc+1]` through Z) are running in an election with a single winner. There are `r nv` voters (A through `r LETTERS[nv]`) who each rank the candidates from 1 to `r nc`, with 1 meaning first choice and `r nc` meaning last choice. Those rankings are shown below. Each column represents a single voter's ranking.

|    | `r paste0("voter ",LETTERS[1:nv]," | ",collapse="")`
|:---:|`r paste0(rep(":---:|",nv),collapse="")`
```{r,echo=F,results='asis'}
for(i in 1:nc){
    cat(paste0("| candidate ",LETTERS[26-nc+i]," | "))
    for(j in 1:nv){
        cat(paste0(prefs[[j]][i]," | "))
    }
    cat("\n")
}
```

A [Borda winner](https://en.wikipedia.org/wiki/Borda_count) is a candidate that gets the most Borda points, where each voter's ranking gives 0 points to the last choice, 1 point to the next lowest, etc.

How many Borda points would candidate `r cans[wo]` get from all `r nv` voters combined?


Solution
========

There are `r nc` candidates. So, we subtract each preference number from `r nc` to get Borda points. We then add all the Borda points from each voter.

```{r,echo=F,fig.dim=c(5,1)}
mkbtab = function(prefs,i=1){
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-1,nv+1),ylim=c(0.5,3.5),axes=F,ann=F)
    text(-0.5,2,cans[i])
    text(-0.5,1,"Borda",col="red")
    for(k in 1:nv){
        text(k-0.5,3,LETTERS[k])
        text(k-0.5,2,prefs[[k]][i])
        text(k-0.5,1,nc-prefs[[k]][i],col="red")
        # if(prefs[[k]][i]>prefs[[k]][j]){
        #     mkcirc(k-0.5,1)
        # } else {
        #     mkcirc(k-0.5,2)
        # }
    }
    # text(nv+0.5,2,cc[1],col="red",cex=1.2)
    text(nv+0.5,1,borda_pts(prefs)[i],col="red",cex=1.2)
    abline(h=2.5)
    abline(v=0)
    abline(v=nv)
    text(nv+0.5,3,"TOTAL",cex=0.8)
}
mkbtab(prefs,wo)
```



Meta-information
============
extype: num
exsolution: `r ans`
exname: borda_points