```{r,echo=FALSE,warning=FALSE}
nc = 4
nv = 7
compare = function(prefs,i,j){
    pi = 0
    pj = 0
    for(k in 1:nv){
        prefi = prefs[[k]][i]
        prefj = prefs[[k]][j]
        if(prefi < prefj){
            pi = pi+1
        }
        if(prefj < prefi){
            pj = pj+1
        }
    }
    if(pi>pj){
        win = i
        lose = j
    }
    if(pj>pi){
        win = j
        lose = i
    }
    if(pj==pi){
        win = 0
        lose = 0
    }
    return(c(pi,pj,win,lose))
}

condorcet = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    alwayswin = rep(T,nc)
    for(i in 1:(nc-1)){
        for(j in (i+1):nc){
            pi = 0
            pj = 0
            for(k in 1:nv){
                prefi = prefs[[k]][i]
                prefj = prefs[[k]][j]
                if(prefi < prefj){
                    pi = pi+1
                }
                if(prefj < prefi){
                    pj = pj+1
                }
            }
            if(pi <= pj){
                alwayswin[i] = F
            }
            if(pi >= pj){
                alwayswin[j] = F
            }
        }
    }
    if(length(unique(alwayswin))==2){
        return(which(alwayswin))
    } else {
        return(0)
    }
}

plurality = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    points = rep(0,nc)
    for(k in 1:nv){
        wo = which(prefs[[k]]==1)
        points[wo] = points[wo]+1
    }
    mp = max(points)
    if(sum(mp==points)==1){
        return(which(points==mp))
    } else {
        return(0)
    }
}

nocond = sample(c(T,F),1,F,c(1,nc))

while(T){
    prefs = list()
    for(i in 1:nv){
        pref = sample(1:nc)
        prefs[[i]] = pref
    }
    cond = condorcet(prefs)
    plur = plurality(prefs)
    if(cond!=0 && cond!=plur && nocond==F){
        sol = paste0(1*(cond==1:(nc+1)),collapse="")
        break
    }
    if(nocond==T && cond==0 && plur!=0){
        sol = paste0(paste0(rep(0,nc),collapse=""),"1")
        break
    }
}

ach = c(LETTERS[26-nc+(1:nc)],"No Condorcet winner!")
al = paste0("* ",ach,collapse="\n")

cans = LETTERS[26-nc+(1:nc)]

```

Question
========

In Adams, Massachusetts, `r nc` candidates (`r LETTERS[26-nc+1]` through Z) are running in an election with a single winner. There are `r nv` voters (A through `r LETTERS[nv]`) who each rank the candidates from 1 to `r nc`, with 1 meaning first choice and `r nc` meaning last choice. Those rankings are shown below. Each column represents a single voter's ranking.

|    | `r paste0(LETTERS[1:nv]," | ",collapse="")`
|:---:|`r paste0(rep(":---:|",nv),collapse="")`
```{r,echo=F,results='asis'}
for(i in 1:nc){
    cat(paste0("| candidate ",LETTERS[26-nc+i]," | "))
    for(j in 1:nv){
        cat(paste0(prefs[[j]][i]," | "))
    }
    cat("\n")
}
```

A [Condorcet winner](https://en.wikipedia.org/wiki/Condorcet_method) would win in a head-to-head election against any other candidate. Who is the Condorcet winner? (Or, possibly, there is none.)

Answerlist
--------

`r al`

Solution
========

Consider every head-to-head election. With `r nc` candidates, there will be ${`r nc`\choose 2 }= `r choose(nc,2)`$  pairings (see [combinations](https://en.wikipedia.org/wiki/Binomial_coefficient)).

```{r,echo=F}
mkcirc = function(x,y){
    th = seq(0,2*pi,pi/100)
    lines(x+0.4*cos(th),y+0.4*sin(th),col="red")
}
mktab = function(prefs,i=1,j=2){
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-1,nv+1),ylim=c(0.5,3.5),axes=F,ann=F)
    text(-0.5,2,cans[i])
    text(-0.5,1,cans[j])
    for(k in 1:nv){
        text(k-0.5,3,LETTERS[k])
        text(k-0.5,2,prefs[[k]][i])
        text(k-0.5,1,prefs[[k]][j])
        if(prefs[[k]][i]>prefs[[k]][j]){
            mkcirc(k-0.5,1)
        } else {
            mkcirc(k-0.5,2)
        }
    }
    cc = compare(prefs,i,j)
    text(nv+0.5,2,cc[1],col="red",cex=1.2)
    text(nv+0.5,1,cc[2],col="red",cex=1.2)
    abline(h=2.5)
    abline(v=0)
    abline(v=nv)
    text(nv+0.5,3,"votes",cex=0.8)
}
```


```{r,echo=F,fig.dim=c(5,1),results='asis'}
for(i in 1:(nc-1)){
    for(j in (i+1):nc){
        cat(paste0("Compare candidates ",cans[i]," and ",cans[j],".\n\n"))
        mktab(prefs,i,j)
        cc = compare(prefs,i,j)
        cat(paste0("\n\nSo, ",cans[cc[3]]," beats ",cans[cc[4]],".\n\n"))
    }
}
```
\


Organize all this into a winner table.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0))
plot(0,0,"n",ann=F,axes=F,xlim=c(0,nc+1),ylim=c(-nc-1,0))
for(i in 1:nc){
    text(0.5,-i-0.5,cans[i])
    text(i+0.5,-0.5,cans[i])
    lines(c(i,i),c(-1,-nc-1))
    lines(c(1,nc+1),c(-i,-i))
}
lines(c(nc+1,nc+1),c(-1,-nc-1))
lines(c(1,nc+1),c(-nc-1,-nc-1))

for(i in 1:nc){
    for(j in 1:nc){
        if(i!=j){
            cc = compare(prefs,i,j)
            text(i+0.5,-j-0.5,cans[cc[3]])
        } else {
            polygon(c(i,i,i+1,i+1),-c(i,i+1,i+1,i),col="grey")
        }
    }
}

if(cond!=0){
    polygon(cond+c(-1,-1,1,1)*0.4+0.5,c(-1.1,-nc-0.9,-nc-0.9,-1.1),border="red",col=rgb(1,0,0,0.1))
    polygon(c(1.1,nc+0.9,nc+0.9,1.1),-cond+c(-1,-1,1,1)*0.4-0.5,border="red",col=rgb(1,0,0,0.1))
}

```

```{r,echo=F,results="asis"}
if(cond==0){
    cat("No candidate wins against every other candidate. There is no Condorcet winner.")
} else {
    cat(paste0("Notice ",cans[cond]," wins against all other candidates. Thus ",cans[cond]," is the Condorcet winner."))
}
```


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: condorcet