```{r,echo=FALSE,warning=FALSE}
compare = function(prefs,i,j){
    pi = 0
    pj = 0
    for(k in 1:nv){
        prefi = prefs[[k]][i]
        prefj = prefs[[k]][j]
        if(prefi < prefj){
            pi = pi+1
        }
        if(prefj < prefi){
            pj = pj+1
        }
    }
    if(pi>pj){
        win = i
        lose = j
    }
    if(pj>pi){
        win = j
        lose = i
    }
    if(pj==pi){
        win = 0
        lose = 0
    }
    return(c(pi,pj,win,lose))
}

condorcet = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    alwayswin = rep(T,nc)
    for(i in 1:(nc-1)){
        for(j in (i+1):nc){
            pi = 0
            pj = 0
            for(k in 1:nv){
                prefi = prefs[[k]][i]
                prefj = prefs[[k]][j]
                if(prefi < prefj){
                    pi = pi+1
                }
                if(prefj < prefi){
                    pj = pj+1
                }
            }
            if(pi <= pj){
                alwayswin[i] = F
            }
            if(pi >= pj){
                alwayswin[j] = F
            }
        }
    }
    if(length(unique(alwayswin))==2){
        return(which(alwayswin))
    } else {
        return(0)
    }
}

plurality = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    points = rep(0,nc)
    for(k in 1:nv){
        wo = which(prefs[[k]]==1)
        points[wo] = points[wo]+1
    }
    mp = max(points)
    if(sum(mp==points)==1){
        return(which(points==mp))
    } else {
        return(0)
    }
}

borda = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    win = which(bps==max(bps))
    if(length(win)>1){
        return(0)
    } else {
        return(win)
    }
}

borda_pts = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    return(bps)
}

inst_run = function(prefs){
    counts = rep(1,length(prefs))
    nrounds = 0
    whowon = 0
    N = sum(counts)
    np = length(prefs)
    nc = length(prefs[[1]])
    majority = N%/%2+1
    winner = F
    cannies = 1:nc
    ppp = 0
    while(winner==F){
        ppp = ppp+1
        if(ppp>(nc)){
            return(c(0,ppp))
        }
        # print(cannies)
        nrounds = nrounds+1
        vcs = rep(0,length(cannies))
        for(i in 1:np){
            p = prefs[[i]]
            jj = which(p==min(p[cannies]))
            vcs[which(cannies==jj)] = vcs[which(cannies==jj)]+counts[i]
        }
        # print(vcs)
        if(max(vcs)>=majority){
            winner=T
            whowon = cannies[which(vcs==max(vcs))]
        } else {
            if(length(cannies)==2){
                return(c(0,nrounds))
            }
            jj = which(vcs==min(vcs))
            if(length(jj)>1){
                return(c(0,nrounds))
            }
            # print(jj)
            cannies = cannies[-jj]
        }
    }
    return(c(whowon,nrounds))
}

while(T){
    nc = sample(4:6,1)
    nv = sample(8:12,1)
    prefs = list()
    for(i in 1:nv){
        pref = sample(1:nc)
        prefs[[i]] = pref
    }
    # cond = condorcet(prefs)
    plur = plurality(prefs)
    # bord = borda(prefs)
    inru = inst_run(prefs)[1]
    inruro = inst_run(prefs)[2]
    has1 = rep(F,nc)
    for(i in 1:nv){
        for(j in 1:nc){
            if(prefs[[i]][j]==1){
                has1[j] = T
            }
        }
    }
    if(inru!=0 && inruro>1 && inru!=plur && length(unique(has1))==1){
        break
    }
}

cans = LETTERS[26-nc+1:nc]
bp = borda_pts(prefs)
ach = sort(unique(c(bp,sample(c(bp-1,bp+1,bp-2,bp+2))))[1:10])
while(length(ach)<10){
    ach = sort(unique(c(ach,sample(1:(max(bp)+10),1))))
}


al2 = paste0("* Candidate ",cans,collapse="\n")

sol = paste0(1*(1:nc==inru),collapse="")

```

Question
========

In Adams, Massachusetts, `r nc` candidates (`r LETTERS[26-nc+1]` through Z) are running in an election with a single winner. There are `r nv` voters (A through `r LETTERS[nv]`) who each rank the candidates from 1 to `r nc`, with 1 meaning first choice and `r nc` meaning last choice. Those rankings are shown below. Each column represents a single voter's ranking.


```{r,echo=F,fig.dim=c(2+nv/3,1+nc/3),results='asis'}
inrutab1 = function(prefs,surv=1:length(prefs[[1]])){
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-1,nv+1),ylim=c(0.5,nc+1.5),axes=F,ann=F)
    tots = rep(0,length(prefs[[1]]))
    for(i in surv){
        text(-0.5,nc+1-i,cans[i])
        for(j in 1:nv){
            text(j-0.5,nc+1-i,prefs[[j]][i])
            if(prefs[[j]][i]==min(prefs[[j]][surv])){
                # tots[i] = tots[i]+1
                # mkcirc(j-0.5,nc+1-i)
            }
        }
        # text(nv+0.5,nc+1-i,tots[i],col="red",cex=1.2)
    }
    for(j in 1:nv){
        text(j-0.5,nc+1,LETTERS[j])
    }
    abline(h=nc+0.5)
    abline(v=0)
}
inrutab1(prefs)
```
\

Who would win an [instant-runoff election](https://en.wikipedia.org/wiki/Instant-runoff_voting)?

Answerlist
--------

`r al2`

Solution
========

First, there are `r nv` voters, so a candidate needs at least `r nv%/%2+1` votes to win a majority.


```{r,echo=F,fig.dim=c(2+nv/3,1+nc/3),results="asis"}
mkcirc = function(x,y){
    th = seq(0,2*pi,pi/100)
    lines(x+0.4*cos(th),y+0.4*sin(th),col="red")
}
inrutab = function(prefs,surv){
    # cat("\n\nfunc surv ",surv,"\n\n")
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-1,nv+1),ylim=c(0.5,nc+1.5),axes=F,ann=F)
    tots = rep(0,length(prefs[[1]]))
    for(i in surv){
        text(-0.5,nc+1-i,cans[i])
        for(j in 1:nv){
            text(j-0.5,nc+1-i,prefs[[j]][i])
            if(prefs[[j]][i]==min(prefs[[j]][surv])){
                tots[i] = tots[i]+1
                mkcirc(j-0.5,nc+1-i)
            }
        }
        text(nv+0.5,nc+1-i,tots[i],col="red",cex=1.2)
    }
    # cat("\n\nfunc tots ",tots,"\n\n")
    for(j in 1:nv){
        text(j-0.5,nc+1,LETTERS[j])
    }
    abline(h=nc+0.5)
    abline(v=0)
    abline(v=nv)
    text(nv+0.5,nc+1,"votes",cex=0.7)
    return(tots)
}
maj = nv%/%2+1
totals = rep(0,nc)
survivors = 1:nc
ppp = 0
while(T){
    totals = inrutab(prefs,survivors)
    # cat("\n\ntot ",totals,"\n\nsurv ",survivors,"\n\ntotsurv ",totals[survivors],"\n\n")
    # cat("\n\nmintotsurv ",min(totals[survivors]),"\n\ntotsurv ",totals[survivors],"\n\nwhich ",which(totals[survivors]==min(totals[survivors])))
    if(max(totals)[1]<maj){
        loser_num = which(totals[survivors]==min(totals[survivors]))
        cat(paste0("\n\nNobody has a majority. Candidate ",cans[survivors[loser_num]]," has the fewest votes. Eliminate candidate ",cans[survivors[loser_num]]," from the contest. Each voter's vote goes to their top candidate still in the election.\n\n"))
        survivors = survivors[-loser_num]
    } else {
        winner_num = which(totals[survivors]==max(totals[survivors]))
        cat(paste0("\n\nCandidate ",cans[survivors[winner_num]]," has gotten majority vote. Candidate ",cans[survivors[winner_num]]," wins!"))
        break
    }
    # cat("\n\n",paste0(cans[survivors],collapse=" "),"\n\n")
}

```
\


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: instant_runoff