---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

\renewcommand{\arraystretch}{1.2}

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    ex1 = gsub("{","",ex1,fixed=T)
    ex1 = gsub("}","",ex1,fixed=T)
    return(ex1)
}
```

Name: \vspace{0.1in} \hrule

## `r bn` (v`r params$rseed`)

```{r,echo=F}
nc = sample(4:5,1)
nv = sample(6:9,1)

compare = function(prefs,i,j){
    pi = 0
    pj = 0
    for(k in 1:nv){
        prefi = prefs[[k]][i]
        prefj = prefs[[k]][j]
        if(prefi < prefj){
            pi = pi+1
        }
        if(prefj < prefi){
            pj = pj+1
        }
    }
    if(pi>pj){
        win = i
        lose = j
    }
    if(pj>pi){
        win = j
        lose = i
    }
    if(pj==pi){
        win = 0
        lose = 0
    }
    return(c(pi,pj,win,lose))
}

condorcet = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    alwayswin = rep(T,nc)
    for(i in 1:(nc-1)){
        for(j in (i+1):nc){
            pi = 0
            pj = 0
            for(k in 1:nv){
                prefi = prefs[[k]][i]
                prefj = prefs[[k]][j]
                if(prefi < prefj){
                    pi = pi+1
                }
                if(prefj < prefi){
                    pj = pj+1
                }
            }
            if(pi <= pj){
                alwayswin[i] = F
            }
            if(pi >= pj){
                alwayswin[j] = F
            }
        }
    }
    if(length(unique(alwayswin))==2){
        return(which(alwayswin))
    } else {
        return(0)
    }
}

plurality = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    points = rep(0,nc)
    for(k in 1:nv){
        wo = which(prefs[[k]]==1)
        points[wo] = points[wo]+1
    }
    mp = max(points)
    if(sum(mp==points)==1){
        return(which(points==mp))
    } else {
        return(0)
    }
}

borda = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    win = which(bps==max(bps))
    if(length(win)>1){
        return(0)
    } else {
        return(win)
    }
}

borda_pts = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    return(bps)
}

nocond = sample(c(T,F),1,F,c(1,nc))

while(T){
    prefs = list()
    for(i in 1:nv){
        pref = sample(1:nc)
        prefs[[i]] = pref
    }
    cond = condorcet(prefs)
    plur = plurality(prefs)
    bord = borda(prefs)
    if(bord!=plur && bord!=0 && bord != cond){
        break
    }
}
cans = LETTERS[26-nc+1:nc]
bp = borda_pts(prefs)
```

### Question 1

`r nc` candidates (`r LETTERS[26-nc+1]` through Z) are running in an election with a single winner. There are `r nv` voters (A through `r LETTERS[nv]`) who each rank the candidates from 1 to `r nc`, with 1 meaning first choice and `r nc` meaning last choice. Those rankings are shown below. Each column represents a single voter's ranking.

|    | `r paste0("voter ",LETTERS[1:nv]," | ",collapse="")`
|:---:|`r paste0(rep(":---:|",nv),collapse="")`
```{r,echo=F,results='asis'}
for(i in 1:nc){
    cat(paste0("| candidate ",LETTERS[26-nc+i]," | "))
    for(j in 1:nv){
        cat(paste0(prefs[[j]][i]," | "))
    }
    cat("\n")
}
```


1. What [Borda count](https://en.wikipedia.org/wiki/Borda_count) would each candidate get?
2. Who wins a Borda-count election?

```{r,echo=F,eval=params$showsol,results='asis'}
cat("\\color{red}\n\n")
cat(bp)
cat(" ... ")
cat(cans[which(bp==max(bp))])
cat("\n\n\\color{black}")

```

\vfill

### Question 2

```{r,echo=FALSE,warning=FALSE}
compare = function(prefs,i,j){
    pi = 0
    pj = 0
    for(k in 1:nv){
        prefi = prefs[[k]][i]
        prefj = prefs[[k]][j]
        if(prefi < prefj){
            pi = pi+1
        }
        if(prefj < prefi){
            pj = pj+1
        }
    }
    if(pi>pj){
        win = i
        lose = j
    }
    if(pj>pi){
        win = j
        lose = i
    }
    if(pj==pi){
        win = 0
        lose = 0
    }
    return(c(pi,pj,win,lose))
}

condorcet = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    alwayswin = rep(T,nc)
    for(i in 1:(nc-1)){
        for(j in (i+1):nc){
            pi = 0
            pj = 0
            for(k in 1:nv){
                prefi = prefs[[k]][i]
                prefj = prefs[[k]][j]
                if(prefi < prefj){
                    pi = pi+1
                }
                if(prefj < prefi){
                    pj = pj+1
                }
            }
            if(pi <= pj){
                alwayswin[i] = F
            }
            if(pi >= pj){
                alwayswin[j] = F
            }
        }
    }
    if(length(unique(alwayswin))==2){
        return(which(alwayswin))
    } else {
        return(0)
    }
}

plurality = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    points = rep(0,nc)
    for(k in 1:nv){
        wo = which(prefs[[k]]==1)
        points[wo] = points[wo]+1
    }
    mp = max(points)
    if(sum(mp==points)==1){
        return(which(points==mp))
    } else {
        return(0)
    }
}

borda = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    win = which(bps==max(bps))
    if(length(win)>1){
        return(0)
    } else {
        return(win)
    }
}

borda_pts = function(prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    return(bps)
}

inst_run = function(prefs){
    counts = rep(1,length(prefs))
    nrounds = 0
    whowon = 0
    N = sum(counts)
    np = length(prefs)
    nc = length(prefs[[1]])
    majority = N%/%2+1
    winner = F
    cannies = 1:nc
    ppp = 0
    while(winner==F){
        ppp = ppp+1
        if(ppp>(nc)){
            return(c(0,ppp))
        }
        # print(cannies)
        nrounds = nrounds+1
        vcs = rep(0,length(cannies))
        for(i in 1:np){
            p = prefs[[i]]
            jj = which(p==min(p[cannies]))
            vcs[which(cannies==jj)] = vcs[which(cannies==jj)]+counts[i]
        }
        # print(vcs)
        if(max(vcs)>=majority){
            winner=T
            whowon = cannies[which(vcs==max(vcs))]
        } else {
            if(length(cannies)==2){
                return(c(0,nrounds))
            }
            jj = which(vcs==min(vcs))
            if(length(jj)>1){
                return(c(0,nrounds))
            }
            # print(jj)
            cannies = cannies[-jj]
        }
    }
    return(c(whowon,nrounds))
}

while(T){
    nc = sample(4:6,1)
    nv = sample(8:12,1)
    prefs = list()
    for(i in 1:nv){
        pref = sample(1:nc)
        prefs[[i]] = pref
    }
    # cond = condorcet(prefs)
    plur = plurality(prefs)
    # bord = borda(prefs)
    inru = inst_run(prefs)[1]
    inruro = inst_run(prefs)[2]
    has1 = rep(F,nc)
    for(i in 1:nv){
        for(j in 1:nc){
            if(prefs[[i]][j]==1){
                has1[j] = T
            }
        }
    }
    if(inru!=0 && inruro>1 && inru!=plur && length(unique(has1))==1){
        break
    }
}

cans = LETTERS[26-nc+1:nc]
```


`r nc` candidates (`r LETTERS[26-nc+1]` through Z) are running in an election with a single winner. There are `r nv` voters (A through `r LETTERS[nv]`) who each rank the candidates from 1 to `r nc`, with 1 meaning first choice and `r nc` meaning last choice. Those rankings are shown below. Each column represents a single voter's ranking.


```{r,echo=F,fig.dim=c(2+nv/3,1+nc/3),results='asis'}
inrutab1 = function(prefs,surv=1:length(prefs[[1]])){
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-1,nv+1),ylim=c(0.5,nc+1.5),axes=F,ann=F)
    tots = rep(0,length(prefs[[1]]))
    for(i in surv){
        text(-0.5,nc+1-i,cans[i])
        for(j in 1:nv){
            text(j-0.5,nc+1-i,prefs[[j]][i])
            if(prefs[[j]][i]==min(prefs[[j]][surv])){
                # tots[i] = tots[i]+1
                # mkcirc(j-0.5,nc+1-i)
            }
        }
        # text(nv+0.5,nc+1-i,tots[i],col="red",cex=1.2)
    }
    for(j in 1:nv){
        text(j-0.5,nc+1,LETTERS[j])
    }
    abline(h=nc+0.5)
    abline(v=0)
}
inrutab1(prefs)
```
\

Who would win an [instant-runoff election](https://en.wikipedia.org/wiki/Instant-runoff_voting)?


```{r,echo=F,fig.dim=c(2+nv/3,1+nc/3),results="asis",eval=params$showsol}
mkcirc = function(x,y){
    th = seq(0,2*pi,pi/100)
    lines(x+0.4*cos(th),y+0.4*sin(th),col="red")
}
inrutab = function(prefs,surv){
    # cat("\n\nfunc surv ",surv,"\n\n")
    # par(mar=c(0,0,0,0))
    # plot(0,0,"n",xlim=c(-1,nv+1),ylim=c(0.5,nc+1.5),axes=F,ann=F)
    tots = rep(0,length(prefs[[1]]))
    for(i in surv){
        # text(-0.5,nc+1-i,cans[i])
        for(j in 1:nv){
            # text(j-0.5,nc+1-i,prefs[[j]][i])
            if(prefs[[j]][i]==min(prefs[[j]][surv])){
                tots[i] = tots[i]+1
                # mkcirc(j-0.5,nc+1-i)
            }
        }
        # text(nv+0.5,nc+1-i,tots[i],col="red",cex=1.2)
    }
    # cat("\n\nfunc tots ",tots,"\n\n")
    # for(j in 1:nv){
        # text(j-0.5,nc+1,LETTERS[j])
    # }
    # abline(h=nc+0.5)
    # abline(v=0)
    # abline(v=nv)
    # text(nv+0.5,nc+1,"votes",cex=0.7)
    return(tots)
}
maj = nv%/%2+1
totals = rep(0,nc)
survivors = 1:nc
ppp = 0
while(T){
    totals = inrutab(prefs,survivors)
    # cat("\n\ntot ",totals,"\n\nsurv ",survivors,"\n\ntotsurv ",totals[survivors],"\n\n")
    # cat("\n\nmintotsurv ",min(totals[survivors]),"\n\ntotsurv ",totals[survivors],"\n\nwhich ",which(totals[survivors]==min(totals[survivors])))
    if(max(totals)[1]<maj){
        loser_num = which(totals[survivors]==min(totals[survivors]))
        # cat(paste0("\n\nNobody has a majority. Candidate ",cans[survivors[loser_num]]," has the fewest votes. Eliminate candidate ",cans[survivors[loser_num]]," from the contest. Each voter's vote goes to their top candidate still in the election.\n\n"))
        survivors = survivors[-loser_num]
    } else {
        winner_num = which(totals[survivors]==max(totals[survivors]))
        cat(paste0("\n\n\\color{red}\n\nCandidate ",cans[survivors[winner_num]]," wins!\n\n\\color{black}"))
        break
    }
    # cat("\n\n",paste0(cans[survivors],collapse=" "),"\n\n")
}

```
\

\newpage

```{r,echo=FALSE,warning=FALSE}
nc = 4
nv = 7
compare = function(prefs,i,j){
    pi = 0
    pj = 0
    for(k in 1:nv){
        prefi = prefs[[k]][i]
        prefj = prefs[[k]][j]
        if(prefi < prefj){
            pi = pi+1
        }
        if(prefj < prefi){
            pj = pj+1
        }
    }
    if(pi>pj){
        win = i
        lose = j
    }
    if(pj>pi){
        win = j
        lose = i
    }
    if(pj==pi){
        win = 0
        lose = 0
    }
    return(c(pi,pj,win,lose))
}

condorcet = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    alwayswin = rep(T,nc)
    for(i in 1:(nc-1)){
        for(j in (i+1):nc){
            pi = 0
            pj = 0
            for(k in 1:nv){
                prefi = prefs[[k]][i]
                prefj = prefs[[k]][j]
                if(prefi < prefj){
                    pi = pi+1
                }
                if(prefj < prefi){
                    pj = pj+1
                }
            }
            if(pi <= pj){
                alwayswin[i] = F
            }
            if(pi >= pj){
                alwayswin[j] = F
            }
        }
    }
    if(length(unique(alwayswin))==2){
        return(which(alwayswin))
    } else {
        return(0)
    }
}

plurality = function(prefs){
    nv = length(prefs)
    nc = length(prefs[[1]])
    points = rep(0,nc)
    for(k in 1:nv){
        wo = which(prefs[[k]]==1)
        points[wo] = points[wo]+1
    }
    mp = max(points)
    if(sum(mp==points)==1){
        return(which(points==mp))
    } else {
        return(0)
    }
}

nocond = sample(c(T,F),1,F,c(1,nc))

while(T){
    prefs = list()
    for(i in 1:nv){
        pref = sample(1:nc)
        prefs[[i]] = pref
    }
    cond = condorcet(prefs)
    plur = plurality(prefs)
    if(cond!=0 && cond!=plur && nocond==F){
        sol = paste0(1*(cond==1:(nc+1)),collapse="")
        break
    }
    if(nocond==T && cond==0 && plur!=0){
        sol = paste0(paste0(rep(0,nc),collapse=""),"1")
        break
    }
}

ach = c(LETTERS[26-nc+(1:nc)],"No Condorcet winner!")
al = paste0("* ",ach,collapse="\n")

cans = LETTERS[26-nc+(1:nc)]

```

### Question 3

`r nc` candidates (`r LETTERS[26-nc+1]` through Z) are running in an election with a single winner. There are `r nv` voters (A through `r LETTERS[nv]`) who each rank the candidates from 1 to `r nc`, with 1 meaning first choice and `r nc` meaning last choice. Those rankings are shown below. Each column represents a single voter's ranking.

```{r,echo=F,fig.dim=c((nv+1)*1/2,(nc+1)*1/3)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,nv+1),ylim=c(0,nc+1),axes=F,ann=F)
abline(v=1)
abline(h=nc)
for(i in 1:nc){
    text(0.5,nc-i+0.5,cans[i])
}
for(j in 1:nv){
    text(j+0.5,nc+0.5,LETTERS[j])
}
for(i in 1:nc){
    for(j in 1:nv){
        text(j+0.5,nc-i+0.5,prefs[[j]][i])
    }
}

```
\

A [Condorcet winner](https://en.wikipedia.org/wiki/Condorcet_method) would win in a head-to-head election against any other candidate. Who is the Condorcet winner? (Or, possibly, there is none.)

```{r,echo=F,results="asis",eval=params$showsol}
cat("\n\n\\color{red}\n\n")
if(cond==0){
    cat("No candidate wins against every other candidate. There is no Condorcet winner.")
} else {
    cat(paste0("Notice ",cans[cond]," wins against all other candidates. Thus ",cans[cond]," is the Condorcet winner."))
}
cat("\n\n\\color{black}\n\n")
```

### Question 4

```{r,echo=FALSE,warning=FALSE}
# This problem assumes 4 candidates.
# 14 Yes/No ballots are represented (not all yes or all no)
# Each ballot count at top... total votes between 40 and 200

while(T){
    nv = sample(40:200,1)
    counts = c(0,diff(c(0,sort(sample(1:(nv-1),13)),nv)),0)
    ballots = list(c(1,1,1,1),
                   c(1,1,1,0),
                   c(1,1,0,1),
                   c(1,1,0,0),
                   c(1,0,1,1),
                   c(1,0,1,0),
                   c(1,0,0,1),
                   c(1,0,0,0),
                   c(0,1,1,1),
                   c(0,1,1,0),
                   c(0,1,0,1),
                   c(0,1,0,0),
                   c(0,0,1,1),
                   c(0,0,1,0),
                   c(0,0,0,1),
                   c(0,0,0,0))
    votes = rep(0,4)
    for(i in 1:16){
        votes = votes+counts[i]*ballots[[i]]
    }
    if(length(unique(votes))==4 && min(votes)>5){
        break
    }
}

extras = c(votes-1,votes+1,votes-2,votes+2,votes-3,votes+3,votes-4,votes+4)
ach = votes
ppp = 1
while(length(ach)<10){
    ppp = ppp+1
    if(ppp<10){
        ach = sort(unique(c(ach,sample(extras,1))))
    } else {
        ach = sort(unique(c(ach,sample(1:100,1))))
    }
}

cans = c("W","X","Y","Z")

sol1 = paste0(1*(ach==votes[1]),collapse="")
sol2 = paste0(1*(ach==votes[2]),collapse="")
sol3 = paste0(1*(ach==votes[3]),collapse="")
sol4 = paste0(1*(ach==votes[4]),collapse="")
sol5 = paste0(1*(max(votes)==votes),collapse="")

al1 = paste0("* ",ach,collapse="\n")
al5 = paste0("* Candidate ",cans,collapse="\n")

```

In an [approval-vote election](https://en.wikipedia.org/wiki/Approval_voting), there are 4 candidates and `r nv` voters. Each voter indicated which candidates they approve of (with a "Y") or disapprove of (with a "N"). All possible ballots are shown below, and the table indicates how many of each type of ballot was cast.


```{r,echo=F,fig.dim=c((16+2)*1/2,(4+1)*1/3)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-1,16+1),ylim=c(0,4+1),axes=F,ann=F)
abline(v=1)
abline(h=4)
text(1,4+0.5,"Ballot Count",adj=1.1)
for(i in 1:4){
    text(0.5,4-i+0.5,cans[i])
}
for(j in 1:16){
    text(j+0.5,4+0.5,counts[j])
}
for(i in 1:4){
    for(j in 1:16){
        if(ballots[[j]][i]==1){
            text(j+0.5,4-i+0.5,"Y",col="darkgreen")
        } else {
            text(j+0.5,4-i+0.5,"N",col="grey")
        }
        
    }
}
```
\

1. How many approvals did Candidate W get? 
2. How many approvals did Candidate X get? 
3. How many approvals did Candidate Y get?
4. How many approvals did Candidate Z get?
5. Who won the election?


```{r,echo=F,results='asis',eval=params$showsol}
cat("\n\n\\color{red}\n\n")
cat(votes)
cat(" ... So ")
cat(cans[which(votes==max(votes))])
cat(" wins.")

cat("\n\n\\color{black}\n\n")
```

