```{r,echo=FALSE,warning=FALSE}
## ALSO NEED 2-round runoff

ncand = 6
npref = 10
nvote = 101

borda = function(counts,prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    bps = rep(0,nc)
    for(i in 1:np){
        for(j in 1:nc){
            bp = nc-prefs[[i]][j]
            bps[j] = bps[j]+bp
        }
    }
    win = which(bps==max(bps))
    if(length(win)>1){
        return(0)
    } else {
        return(win)
    }
}

rcv = function(counts,prefs){
    nrounds = 0
    whowon = 0
    N = sum(counts)
    np = length(prefs)
    nc = length(prefs[[1]])
    majority = N%/%2+1
    winner = F
    cannies = 1:nc
    while(winner==F){
        # print(cannies)
        nrounds = nrounds+1
        vcs = rep(0,length(cannies))
        for(i in 1:np){
            p = prefs[[i]]
            jj = which(p==min(p[cannies]))
            vcs[which(cannies==jj)] = vcs[which(cannies==jj)]+counts[i]
        }
        # print(vcs)
        if(max(vcs)>=majority){
            winner=T
            whowon = cannies[which(vcs==max(vcs))]
        } else {
            if(length(cannies)==2){
                return(c(0,nrounds))
            }
            jj = which(vcs==min(vcs))
            if(length(jj)>1){
                return(c(0,nrounds))
            }
            # print(jj)
            cannies = cannies[-jj]
        }
    }
    return(c(whowon,nrounds))
}

most1s = function(counts,prefs){
    np = length(prefs)
    nc = length(prefs[[1]])
    vcs = rep(0,nc)
    for(i in 1:np){
        p = prefs[[i]]
        j = which(p==min(p))
        vcs[j] = vcs[j]+counts[i]
    }
    jj = which(vcs==max(vcs))
    if(length(jj)>1){
        return(0)
    } else {
        return(jj)
    }
}

while(T){
    prefs = list()
    while(length(prefs)<npref){
        pref = sample(1:ncand)
        if(!(list(pref)%in%prefs)){
            prefs[[length(prefs)+1]] = pref
        }
    }
    cuts = sort(c(0,sample(1:(nvote-1),npref-1),nvote))
    counts = diff(cuts)
    allgot1 = T
    for(i in 1:ncand){
        got1 = F
        for(j in 1:npref){
            if(prefs[[j]][i]==1){
                got1 = T
            }
        }
        if(got1 == F){
            allgot1 = F
            break
        }
    }
    RCV = rcv(counts,prefs)
    BORDA = borda(counts,prefs)
    m1 = most1s(counts,prefs)
    if(RCV[2]>1 && allgot1 && RCV[1]>0 && RCV[1]!=m1 && BORDA!=0 && BORDA!=m1 && BORDA != RCV[1] && m1!=0){break}
}

ach = paste0("Candidate ",LETTERS[1:ncand])
al = paste0("* ",ach,collapse="\n")
sol1 = paste0(1*(1:ncand==m1),collapse="")
sol2 = paste0(1*(1:ncand==RCV[1]),collapse="")
sol3 = paste0(1*(1:ncand==BORDA),collapse="")

# prefs = list()
# while(length(prefs)<npref){
#     pref = sample(1:ncand)
#     if(!(list(pref)%in%prefs)){
#         prefs[[length(prefs)+1]] = pref
#     }
# }
# cuts = sort(c(0,sample(1:(nvote-1),npref-1),nvote))
# counts = diff(cuts)

```

Question
========

In an election, `r nvote` voters filled out ranked preferences for `r ncand` candidates. Luckily, although there are `r factorial(ncand)` possible rankings, only `r npref` rankings were cast.

| candidate | `r paste0(counts," voters | ",collapse="")`
|:---:|`r paste0(rep(":---:|",npref),collapse="")`
```{r,echo=F,results='asis'}
for(i in 1:ncand){
    cat(paste0("| candidate ",LETTERS[i]," | "))
    for(j in 1:npref){
        cat(paste0(prefs[[j]][i]," | "))
    }
    cat("\n")
}
```

1. Who won the most 1st-place votes?
##ANSWER1##
2. Who won using ranked-choice (instant runoff) voting system?
##ANSWER2##
3. Who won using Borda count voting system?
##ANSWER3##

Answerlist
--------

`r al`
`r al`
`r al`



Solution
========


Sorry, I'm still working on an explanation.

* The winner of most first-place votes is `r ach[m1]`.
* The winner of RCV is `r ach[RCV[1]]`.
* The winner of Borda voting is `r ach[BORDA]`.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: voting_methods