---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

```{r,echo=F,warning=FALSE,message=FALSE}
library(numbers)
if(params$rseed !=0){
    set.seed(params$rseed)
}

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}
gcd2 <- function(a, b) {
    if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
```

Name: \vspace{5pt} \hrule

## a0106p_qf_radical_complex_sols (v`r params$rseed`)

Remember the quadratic formula:

$$\begin{aligned}
\text{if}\\ & ax^2+bx+c = 0\\ 
\text{then} \\
& x = \frac{-b}{2a}\pm \frac{\sqrt{b^2-4ac}}{2a}
\end{aligned}$$


\color{red}
### Example: use quadratic formula to solve a quadratic equation with complex solutions


```{r,echo=F}
# (x-(r+qi))(x-(r-qi))
# x^2 - 2*r*x + (r^2+q^2)

# -b/2a +- sqrt(b^2-4ac)/2a
# (x-(h+i*p*sqrt(q)))(x-(h-i*p*sqrt(q)))
# (x-(h+i*sqrt(p^2*q)))(x-(h-i*sqrt(p^2*q)))

# x^2 - 2*h + h^2+p^2*q

h = -7 #sample(2:10,1)*sample(c(-1,1),1)
p = 5 #sample(c(2,3,4,5,6),1)
q = 3 #sample(c(2,3,5,6,10),1)
a = 1
b = -2*h
c = h^2+p^2*q
eq = paste0(pn(c(a,b,c),2:0),"=0")
soln = paste0("$$x=\\frac{",-b,"}{2(",a,")}\\pm \\frac{\\sqrt{(",b,")^2-4(",a,")(",c,")}}{2(",a,")}$$\n\n")
soln = paste0(soln,"$$x=",-b/2/a,"\\pm\\frac{\\sqrt{",b^2,"-",4*a*c,"}}{",2*a,"}$$\n\n")
soln = paste0(soln,"$$x=",-b/2/a,"\\pm\\frac{\\sqrt{",b^2-4*a*c,"}}{",2*a,"}$$\n\n")
soln = paste0(soln,"$$x=",-b/2/a,"\\pm\\frac{\\sqrt{(-1)\\cdot",paste0(primeFactors(-b^2+4*a*c),collapse="\\cdot"),"}}{",2*a,"}$$\n\n")
soln = paste0(soln,"$$x=",-b/2/a,"\\pm\\frac{",paste0(primeFactors(2*p),collapse="\\cdot"),"\\cdot i \\cdot \\sqrt{",paste0(primeFactors(q),collapse="\\cdot"),"}}{",2*a,"}$$\n\n")
soln = paste0(soln,"$$x=",h,"\\pm",p,"i\\sqrt{",q,"}$$")

hs = h
ps = p
qs = q
eqs = eq
solns = soln

for(i in 1:4){
    while(T){
        h = sample(2:10,1)*sample(c(-1,1),1)
        p = sample(c(2,3,4,5,6),1)
        q = sample(c(2,3,5,6,10),1)
        a = 1
        b = -2*h
        c = h^2+p^2*q
        if(!(abs(h) %in% abs(hs)) && !(abs(p)%in%abs(ps)) && !(abs(q)%in%abs(qs))){
            hs = c(hs,h)
            ps = c(ps,p)
            qs = c(qs,q)
            eqs = c(eqs,paste0(pn(c(a,b,c),2:0),"=0"))
            if(params$showsol){
                soln = paste0("\\color{red}$$x=\\frac{",-b,"}{2(",a,")}\\pm \\frac{\\sqrt{(",b,")^2-4(",a,")(",c,")}}{2(",a,")}$$\n\n")
                soln = paste0(soln,"$$x=",-b/2/a,"\\pm\\frac{\\sqrt{",b^2,"-",4*a*c,"}}{",2*a,"}$$\n\n")
                soln = paste0(soln,"$$x=",-b/2/a,"\\pm\\frac{\\sqrt{",b^2-4*a*c,"}}{",2*a,"}$$\n\n")
                soln = paste0(soln,"$$x=",-b/2/a,"\\pm\\frac{\\sqrt{(-1)\\cdot",paste0(primeFactors(-b^2+4*a*c),collapse="\\cdot"),"}}{",2*a,"}$$\n\n")
                soln = paste0(soln,"$$x=",h,"\\pm",p,"i\\sqrt{",q,"}$$\n\n\\color{black}")
            } else {
                soln = " "
            }
            solns = c(solns,soln)
            break
        }
    }
}

```

Solve $`r eqs[1]`$.


`r solns[1]`

\color{black}


## Exercise 1


Solve $`r eqs[2]`$. Write your answer in simplified form.

`r solns[2]`

\newpage

## Exercise 2

Solve $`r eqs[3]`$. Write your answer in simplified form.
`r solns[3]`


\vfill

## Exercise 3

Solve $`r eqs[4]`$. Write your answer in simplified form.
`r solns[4]`

\vfill

## Exercise 4

Solve $`r eqs[5]`$.
`r solns[5]`



\vfill



