```{r data generation, echo = FALSE, results = "hide"}




while(T){
  h = sample(-4:4,1)
  k = sample(-4:4,1)
  m = sample(1:2,1)*sample(c(-1,1),1)
  x = seq(-10,10,0.001)
  y = m*(x-h)+sin((x-h)*pi/2)+k
  xp = sample(1:10,1)*sample(c(-1,1),1)
  yp = y[x==xp]
  yp2 = y[x==-xp]
  if(abs(yp)<10 && abs(yp2)<10 && yp!=0 && y[x==0]!=0 && abs(yp)!=abs(yp2)){
    break
  }
}

divisor = paste0("x-",xp,collapse="")
divisor = gsub("--","+",divisor,fixed=T)

```

Question
========

This problem is based on the [polynomial remainder theorem](https://en.wikipedia.org/wiki/Polynomial_remainder_theorem). A polynomial function, $y=p(x)$, is plotted below.

```{r,echo=F,fig.dim=c(5,5)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in c(-10:-1,1:10)){
  lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.7)
  lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.7)
}
for(i in c(-10,-5,5,10)){
  lines(c(-10,10),c(i,i),col="grey",lwd=0.9)
  lines(c(i,i),c(-10,10),col="grey",lwd=0.9)
}
abline(h=0,lwd=1.5)
abline(v=0,lwd=1.5)

lines(x[abs(y)<=10],y[abs(y)<=10],col="blue",lwd=2)
```
\

What is the remainder when $p(x)$ is divided by $`r divisor`$?


Solution
========

The remainder theorem tells us that the remainder when $p(x)$ is divided by $`r divisor`$ is equivalent to $p(`r xp`)$.

The curve goes through point $(`r xp`,`r yp`)$. Thus, $p(`r xp`)=`r yp`$.

So, the answer is `r yp`.


Meta-information
============
extype: num
exsolution: `r yp`
exname: remainder_theorem