```{r,echo=FALSE}
library(latex2exp)
options(scipen=99)
# (x-(r+mi))(x-(r-mi))(ax+b)(cx+d)
# (x-r-mi)(x-r+mi)(ax+b)(cx+d)
# -b/a and -d/c
# (x^2-2rx+(r^2+m^2))(acx^2+(ad+bc)x+bd)
# acx^4 + (ad+bc-2rac)x^3 + (acr^2+acm^2-2rad-2rbc+bd)x^2 + (-2rbd+adr^2+adm^2+bcr^2+bcm^2)x + (bdr^2+bdm^2)
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

rats = list(c(1,1),c(2,1),c(3,1),c(4,1),c(5,1),c(6,1),c(7,1),c(8,1),c(9,1),
            c(1,2),c(3,2),c(5,2),c(7,2),c(9,2),
            c(1,3),c(2,3),c(4,3),c(5,3),c(7,3),c(8,3),
            c(1,4),c(3,4),c(5,4),c(7,4),c(9,4),
            c(1,5),c(2,5),c(3,5),c(4,5),c(6,5),c(7,5),c(8,5),c(9,5),
            c(1,6),c(5,6),c(7,6),
            c(1,7),c(2,7),c(3,7),c(4,7),c(5,7),c(6,7),c(8,7),c(9,7),
            c(1,8),c(3,8),c(5,8),c(7,8),c(9,8),
            c(1,9),c(2,9),c(4,9),c(5,9),c(7,9))
while(T){
    rat = sample(rats,3)
    
    r = rat[[1]][1]*sample(c(-1,1),1)
    m = rat[[1]][2]*sample(c(-1,1),1)
    a = rat[[2]][1]
    b = rat[[2]][2]*sample(c(-1,1),1)
    c = rat[[3]][1]
    d = rat[[3]][2]*sample(c(-1,1),1)
    
    # acx^4 + (ad+bc-2rac)x^3 + (acr^2+acm^2-2rad-2rbc+bd)x^2 + (-2rbd+adr^2+adm^2+bcr^2+bcm^2)x + (bdr^2+bdm^2)
    A = a*c
    B = a*d+b*c-2*r*a*c
    C = a*c*r^2+a*c*m^2-2*r*a*d-2*r*b*c+b*d
    D = -2*r*b*d+a*d*r^2+a*d*m^2+b*c*r^2+b*c*m^2
    E = b*d*r^2+b*d*m^2
    cf4 = c(A,B,C,D,E)
    # (x^2-2rx+(r^2+m^2))(acx^2+(ad+bc)x+bd)
    qa = a*c
    qb = a*d+b*c
    qc = b*d
    cfq = c(qa,qb,qc)
    ca = 1
    cb = -2*r
    cc = r^2+m^2
    cfc = c(ca,cb,cc)
    if(max(abs(cf4))<500){break}
}

numer1 = -qb+round(sqrt(qb^2-4*qa*qc))
denom1 = 2*qa
numer2 = -qb-round(sqrt(qb^2-4*qa*qc))
denom2 = 2*qa

nn1 = numer1/gcd(c(numer1,denom1))
dd1 = denom1/gcd(c(numer1,denom1))
nn2 = numer2/gcd(c(numer2,denom2))
dd2 = denom2/gcd(c(numer2,denom2))

cn = function(real,imag){
    ss = paste0("{",real,"}+",imag,"i")
    ss = gsub("+-","-",ss,fixed=T)
    ss = gsub("+1i","+i",ss,fixed=T)
    ss = gsub("-1i","-i",ss,fixed=T)
    ss = gsub("+0i","",ss,fixed=T)
    ss = gsub("{0}+","",ss,fixed=T)
    ss = gsub("{0}-","",ss,fixed=T)
    ss = gsub("{","",ss,fixed=T)
    ss = gsub("}","",ss,fixed=T)
    return(ss)
}

frac = function(num,den){
    if(den!=1){
        ss = paste0("\\frac{",num,"}{",den,"}")
    }
    else{
        ss = paste0(num)
    }
    return(ss)
}

pn = function(c,d){
    d = d[c!=0]
    c = c[c!=0]
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

ach = character()

for(i in 1:length(rats)){
    ach = c(ach,frac(rats[[i]][2],rats[[i]][1]))
    ach = c(ach,frac(-rats[[i]][2],rats[[i]][1]))
}
ach = sort(ach)
al = paste0("* $",ach,"$",collapse="\n")

sol1 = frac(-b,a)==ach
sol2 = frac(-d,c)==ach
sol3 = sol1+sol2
sol3 = paste0(1*(sol3),collapse="")


```

Question
========

Let $f$ represent a quartic (4th degree) polynomial with integer coefficients.

$$f(x)~=~`r pn(cf4,4:0)`$$

One of the roots is $`r cn(r,m)`$, where $i=\sqrt{-1}$.

$$f(`r cn(r,m)`)~=~0$$

This quartic polynomial has at least 1 rational root. Find all the rational roots.

Answerlist
--------

`r al`


Solution
========

We know that complex roots show up as complex-conjugate pairs. So, since $`r cn(r,m)`$ is a root, we also know $`r cn(r,-m)`$ is another root. This accounts for two roots.

The [fundamental theorem of algebra](https://en.wikipedia.org/wiki/Fundamental_theorem_of_algebra) promises "every non-zero, single-variable, degree n polynomial with complex coefficients has, counted with multiplicity, exactly n complex roots."

So, we know there will be a total of 4 roots. 

Thus, we should be able to express $f(x)$ in a semi-factored form (with yet to be determined coefficients $a$ and $b$ and $c$).

$$f(x)~=~(ax^2+bx+c)(x-(`r cn(r,m)`))(x-(`r cn(r,-m)`))$$

Distribute the negatives across the inner parentheses.

```{r,echo=F}
f2 = paste0("(ax^2+bx+c)(x+",-r,"+",-m,"i)(x+",-r,"+",m,"i)")
f2 = gsub("+-","-",f2,fixed=T)
f2 = gsub("+1i","+i",f2,fixed=T)
f2 = gsub("-1i","-i",f2,fixed=T)
```


$$f(x)~=~`r f2`$$

Now use a box to multiply the two complex factors.

```{r,echo=F,fig.dim=c(3,2)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,4),ylim=c(0,4))
abline(v=1)
abline(h=3)
va = -0.5
text(0.5,3.5,"*")
text(0.5,2.1,"x",adj=c(0.5,va))
text(0.5,1.1,-r,adj=c(0.5,va))
text(0.5,0.1,paste0(-m,"i"),adj=c(0.5,va))
text(1.5,3.1,"x",adj=c(0.5,va))
text(2.5,3.1,-r,adj=c(0.5,va))
text(3.5,3.1,paste0(m,"i"),adj=c(0.5,va))

text(1.5,2.1,TeX(paste0("$x^2$")),adj=c(0.5,va))
text(2.5,2.1,TeX(paste0("$",-r,"x$")),adj=c(0.5,va))
text(3.5,2.1,TeX(paste0("$",m,"ix$")),adj=c(0.5,va))

text(1.5,1.1,TeX(paste0("$",-r,"x$")),adj=c(0.5,va))
text(2.5,1.1,r^2,adj=c(0.5,va))
text(3.5,1.1,TeX(paste0("$",-r*m,"i$")),adj=c(0.5,va))

text(1.5,0.1,TeX(paste0("$",-m,"ix$")),adj=c(0.5,va))
text(2.5,0.1,TeX(paste0("$",r*m,"i$")),adj=c(0.5,va))
text(3.5,0.1,TeX(paste0("$-",m^2,"i^2$")),adj=c(0.5,va))
```
\

Remember, $i^2=-1$, so $-`r m^2`i^2=`r m^2`$. Combine like terms.

```{r,echo=F}

# (x-r-mi)(x-r+mi)

f4 = paste0("(ax^2+bx+c)(x^2+",-2*r,"x+",r^2,"+",-m^2,"(-1))")
f4 = gsub("+-","-",f4,fixed=T)

f5 = paste0("(ax^2+bx+c)(x^2+",-2*r,"x+",r^2,"+",m^2,")")
f5 = gsub("+-","-",f5,fixed=T)

f6 = paste0("(ax^2+bx+c)(x^2+",-2*r,"x+",r^2+m^2,")")
f6 = gsub("+-","-",f6,fixed=T)
```

$$f(x)~=~`r f6`$$

Now... we know this semi-factored form and the standard form are equivalent expressions.

$$`r f6`~\equiv~`r pn(cf4,4:0)`$$

So, we can divide both sides by $`r pn(c(1,-2*r,r^2+m^2),2:0)`$.

$$ax^2+bx+c~=~\frac{`r pn(cf4,4:0)`}{`r pn(c(1,-2*r,r^2+m^2),2:0)`}$$

Use the box method to divide.

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,4),ylim=c(0,4),axes=F,ann=F)
abline(h=3)
abline(v=1)
text(0.5,2.5,TeX("$x^2$"))
text(0.5,1.5,TeX(paste0("$",-2*r,"x$")))
text(0.5,0.5,TeX(paste0("$",r^2+m^2,"$")))

text(1.5,2.5,TeX(paste0("$",cfq[1],"x^4$")))
text(1.5,3.5,TeX(paste0("$",cfq[1],"x^2$")))
text(1.5,1.5,TeX(paste0("$",cfq[1]*cfc[2],"x^3$")))
text(1.5,0.5,TeX(paste0("$",cfq[1]*cfc[3],"x^2$")))

text(2.5,2.5,TeX(paste0("$",cfq[2]*cfc[1],"x^3$")))
text(2.5,3.5,TeX(paste0("$",cfq[2]*cfc[1],"x$")))
text(2.5,1.5,TeX(paste0("$",cfq[2]*cfc[2],"x^2$")))
text(2.5,0.5,TeX(paste0("$",cfq[2]*cfc[3],"x$")))

text(3.5,2.5,TeX(paste0("$",cfq[3]*cfc[1],"x^2$")))
text(3.5,3.5,TeX(paste0("$",cfq[3]*cfc[1],"$")))
text(3.5,1.5,TeX(paste0("$",cfq[3]*cfc[2],"x$")))
text(3.5,0.5,TeX(paste0("$",cfq[3]*cfc[3],"$")))

```
\

So,


$$f(x)~=~(`r pn(cfq,2:0)`)(`r pn(cfc,2:0)`)$$

We have expressed the quartic polynomial as the product of two quadratic polynomials. Remember, our goal is to find solutions to $f(x)=0$. We already know that $x=`r cn(r,m)`$ and $x=`r cn(r,-m)`$ are solutions, and those two roots correspond to the factor $`r pn(cfc,2:0)`$ equaling 0. By setting the other quadratic factor, $`r pn(cfq,2:0)`$, equal to zero, we can find the other roots.

$$`r pn(cfq,2:0)`=0$$

Use the quadratic formula: if $ax^2+bx+c=0$ then $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$.

$$x=\frac{-(`r qb`)\pm\sqrt{(`r qb`)^2-4(`r qa`)(`r qc`)}}{2(`r qa`)}$$

Simplify.

```{r,echo=F}
qf2 = paste0("\\frac{",-qb,"\\pm\\sqrt{",qb^2,"-",4*qa*qc,"}}{",2*qa,"}")
qf2 = gsub("--","+",qf2,fixed=T)
```

$$x=`r qf2`$$

Simplify.

$$x=\frac{`r -qb`\pm\sqrt{`r qb^2-4*qa*qc`}}{`r 2*qa`}$$

Simplify.

$$x=\frac{`r -qb`\pm`r round(sqrt(qb^2-4*qa*qc))`}{`r 2*qa`}$$

Split into two different fraction.

\begin{align}
x&=\frac{`r -qb`+`r round(sqrt(qb^2-4*qa*qc))`}{`r 2*qa`} &&& x&=\frac{`r -qb`-`r round(sqrt(qb^2-4*qa*qc))`}{`r 2*qa`} \\\\
x&=\frac{`r -qb+round(sqrt(qb^2-4*qa*qc))`}{`r 2*qa`} &&& x&=\frac{`r -qb-round(sqrt(qb^2-4*qa*qc))`}{`r 2*qa`} \\\\
x&=`r frac(nn1,dd1)` &&& x&=`r frac(nn2,dd2)`
\end{align}

Now we know all four roots. We could express $f$ in fully factored form.

$$f(x)~=~(`r pn(c(a,b),1:0)`)(`r pn(c(c,d),1:0)`)(x-(`r cn(r,m)`))(x-(`r cn(r,-m)`))$$

Or, if you are not into complex factors, you could also express $f$ as factored as possible with integer coefficients.

$$f(x)~=~(`r pn(c(a,b),1:0)`)(`r pn(c(c,d),1:0)`)(`r pn(cfc,2:0)`)$$

Anyway, the two rational roots are $`r frac(-b,a)`$ and $`r frac(-d,c)`$.

Meta-information
============
extype: mchoice
exsolution: `r sol3`
exname: x_standard_2_rat_1_comp