```{r,echo=FALSE}

nval = 1 #sample(0:2,1)

while(T){
    rs = sample(1:10,2)*sample(c(-1,1),2,T)
    qea = 1
    qeb = sum(-rs)
    qec = prod(-rs)
    psa = 1
    psb = qeb+sample(2:9,1)*sample(c(-1,1),1)
    if(psb%%2==1){
        psb = psb+sample(c(-1,1),1)
    }
    psc = (psb/2)^2
    
    rm = psb-qeb
    rb = psc-qec
    
    k = sample(1:9,1)*sample(c(-1,1),1)
    
    lm = sample(c(-1,1),1)
    lb = (psb/2)*sign(lm)+k
    
    ra = sample(c(-1,1),1)
    
    eq = paste0(k,"+{",ra,"}\\sqrt{",rm,"x+",rb,"}=",lm,"x+",lb)
    eq = gsub("+-","-",eq,fixed=T)
    eq = gsub("+{-1}","-",eq,fixed=T)
    eq = gsub("+{1}","+",eq,fixed=T)
    eq = gsub("=1x","=x",eq,fixed=T)
    eq = gsub("=-1x","=-x",eq,fixed=T)
    
    psol1 = min(rs)
    psol2 = max(rs)
    
    val1 = (k+ra*sqrt(rm*psol1+rb)==lm*psol1+lb)
    val2 = (k+ra*sqrt(rm*psol2+rb)==lm*psol2+lb)
    
    if(k!=lb && abs(psb)<19 && abs(rm)>1 && rb!=0 && lb!=0 && (1*val1+1*val2)==nval){break}
}

ach = -10:10
al = paste0("* ",ach,collapse="\n")
ach2 = c("an extraneous","a valid")
al2 = paste0("* ",ach2,collapse="\n")

sol1 = paste0(1*(ach==psol1),collapse="")
sol2 = paste0(1*(c(F,T)==val1),collapse="")
sol3 = paste0(1*(ach==psol2),collapse="")
sol4 = paste0(1*(c(F,T)==val2),collapse="")


```

Question
========

When solving the equation below with standard algebraic methods, two possible solutions are found.

$$`r eq`$$

Let $x_1$ and $x_2$ represent the two possible solutions, such that $x_1<x_2$. Find both possible solutions and determine whether each is valid or extraneous.

* $x_1=$ ##ANSWER1##
* $x_1$ is ##ANSWER2## solution.
* $x_2=$ ##ANSWER3##
* $x_2$ is ##ANSWER4## solution.

Answerlist
--------

`r al`
`r al2`
`r al`
`r al2`

Solution
========

$$`r eq`$$

```{r,echo=F,results='asis'}
if(k<0){
    cat(paste0("Add ",abs(k)," to both sides of the equation."))
} else {
    cat(paste0("Subtract ",abs(k)," from both sides of the equation."))
}
eq = paste0("{",ra,"}\\sqrt{",rm,"x+",rb,"}=",lm,"x+",lb-k)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("{-1}","-",eq,fixed=T)
eq = gsub("{1}","",eq,fixed=T)
eq = gsub("=1x","=x",eq,fixed=T)
eq = gsub("=-1x","=-x",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

if(ra<0){
    cat("Multiply both sides by $-1$.")
    eq = paste0("{",-ra,"}\\sqrt{",rm,"x+",rb,"}=",-lm,"x+",-(lb-k))
    eq = gsub("+-","-",eq,fixed=T)
    eq = gsub("{-1}","-",eq,fixed=T)
    eq = gsub("{1}","",eq,fixed=T)
    eq = gsub("=1x","=x",eq,fixed=T)
    eq = gsub("=-1x","=-x",eq,fixed=T)
    cat(paste0("\n$$",eq,"$$\n"))
}

cat("Square both sides of the equation. Remember, you'll need to FOIL the right side.")

eq = paste0(rm,"x+",rb,"=",psa,"x^2+",psb,"x+",psc)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("=1x","=x",eq,fixed=T)
eq = gsub("=-1x","=-x",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

ls = paste0("{",rm,"}x+",rb)
ls = gsub("+-","-",ls,fixed=T)
ls = gsub("{1}","",ls,fixed=T)
ls = gsub("{-1}","-",ls,fixed=T)
ls = gsub("{","",ls,fixed=T)
ls = gsub("}","",ls,fixed=T)

cat("Subtract $(",ls,")$ from both sides.")

eq = paste0("0={",qea,"}x^2+{",qeb,"}x+",qec)
eq = gsub("{1}","",eq,fixed=T)
eq = gsub("{-1}","-",eq,fixed=T)
eq = gsub("{","",eq,fixed=T)
eq = gsub("}","",eq,fixed=T)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

cat("From here, you can either factor or use quadratic formula. It is easy enough to factor this one.")

eq = paste0("0=(x+",-psol1,")(x+",-psol2,")")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

cat(paste0("Use the zero-product property to identify the possible solutions are $x_1=",psol1,"$ and $x_2=",psol2,"$. Notice we correctly ordered them such that $x_1<x_2$. Now we check which solution is valid by plugging both into the original equation.\n\n"))

cat(paste0("Start with possible solution $x=",psol1,"$"))

eq = paste0(k,"+{",ra,"}\\sqrt{",rm,"(",psol1,")+",rb,"}={",lm,"}(",psol1,")+",lb)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+{-1}","-",eq,fixed=T)
eq = gsub("+{1}","+",eq,fixed=T)
eq = gsub("={1}","=",eq,fixed=T)
eq = gsub("={-1}","=-",eq,fixed=T)
eq = gsub("=","\\stackrel{?}{=}",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

eq = paste0(k,"+{",ra,"}\\sqrt{",rm*psol1,"+",rb,"}=",lm*psol1,"+",lb)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+{-1}","-",eq,fixed=T)
eq = gsub("+{1}","+",eq,fixed=T)
eq = gsub("=1x","=x",eq,fixed=T)
eq = gsub("=-1x","=-x",eq,fixed=T)
eq = gsub("=","\\stackrel{?}{=}",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

eq = paste0(k,"+{",ra,"}\\sqrt{",rm*psol1+rb,"}=",lm*psol1+lb)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+{-1}","-",eq,fixed=T)
eq = gsub("+{1}","+",eq,fixed=T)
eq = gsub("=1x","=x",eq,fixed=T)
eq = gsub("=-1x","=-x",eq,fixed=T)
eq = gsub("=","\\stackrel{?}{=}",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

eq = paste0(k,"+{",ra,"}",sqrt(rm*psol1+rb),"=",lm*psol1+lb)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+{-1}","-",eq,fixed=T)
eq = gsub("+{1}","+",eq,fixed=T)
eq = gsub("=1x","=x",eq,fixed=T)
eq = gsub("=-1x","=-x",eq,fixed=T)
eq = gsub("=","\\stackrel{?}{=}",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

eq = paste0(k+ra*sqrt(rm*psol1+rb),"=",lm*psol1+lb)
if(val1){
    eq = gsub("=","=",eq,fixed=T)
    cat(paste0("\n$$",eq,"$$\n"))
    cat(paste0("So we see $x=",psol1,"$ is a valid solution."))
} else {
    eq = gsub("=","\\ne ",eq,fixed=T)
    cat(paste0("\n$$",eq,"$$\n"))
    cat(paste0("So we see $x=",psol1,"$ is an extraneous solution."))
}


cat(paste0("\n\nNow check possible solution $x=",psol2,"$"))

eq = paste0(k,"+{",ra,"}\\sqrt{",rm,"(",psol2,")+",rb,"}={",lm,"}(",psol2,")+",lb)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+{-1}","-",eq,fixed=T)
eq = gsub("+{1}","+",eq,fixed=T)
eq = gsub("={1}","=",eq,fixed=T)
eq = gsub("={-1}","=-",eq,fixed=T)
eq = gsub("=","\\stackrel{?}{=}",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

eq = paste0(k,"+{",ra,"}\\sqrt{",rm*psol2,"+",rb,"}=",lm*psol2,"+",lb)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+{-1}","-",eq,fixed=T)
eq = gsub("+{1}","+",eq,fixed=T)
eq = gsub("=1x","=x",eq,fixed=T)
eq = gsub("=-1x","=-x",eq,fixed=T)
eq = gsub("=","\\stackrel{?}{=}",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

eq = paste0(k,"+{",ra,"}\\sqrt{",rm*psol2+rb,"}=",lm*psol2+lb)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+{-1}","-",eq,fixed=T)
eq = gsub("+{1}","+",eq,fixed=T)
eq = gsub("=1x","=x",eq,fixed=T)
eq = gsub("=-1x","=-x",eq,fixed=T)
eq = gsub("=","\\stackrel{?}{=}",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

eq = paste0(k,"+{",ra,"}",sqrt(rm*psol2+rb),"=",lm*psol2+lb)
eq = gsub("+-","-",eq,fixed=T)
eq = gsub("+{-1}","-",eq,fixed=T)
eq = gsub("+{1}","+",eq,fixed=T)
eq = gsub("=1x","=x",eq,fixed=T)
eq = gsub("=-1x","=-x",eq,fixed=T)
eq = gsub("=","\\stackrel{?}{=}",eq,fixed=T)
cat(paste0("\n$$",eq,"$$\n"))

eq = paste0(k+ra*sqrt(rm*psol2+rb),"=",lm*psol2+lb)
if(val2){
    eq = gsub("=","=",eq,fixed=T)
    cat(paste0("\n$$",eq,"$$\n"))
    cat(paste0("So we see $x=",psol2,"$ is a valid solution."))
} else {
    eq = gsub("=","\\ne ",eq,fixed=T)
    cat(paste0("\n$$",eq,"$$\n"))
    cat(paste0("So we see $x=",psol2,"$ is an extraneous solution."))
}
```


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: w_2val_1val_0val