```{r,echo=FALSE}
options(scipen=99)
library(numbers)
library(MASS)
# (a+bi)/(c+di)

# (a+bi)(c-di)/(c^2+d^2)
# ((ac+bd)+(bc-ad)i)/(c^2+d^2)
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

while(T){
    x1 = sort(sample(1:12,1)*sample(c(-1,1),1,T))
    x2 = x1+sample(2:12,1)
    xs = c(x1,x2)
    ys = sample(1:12,2)*sample(c(-1,1),2,T)
    h = sample((xs[1]+1):(xs[2]-1),1)
    y1 = ys[1]
    y2 = ys[2]
    atop = y2-y1
    abot = (x2-h)^2-(x1-h)^2
    gg = abs(gcd2(atop,abot))
    atop = round(atop/gg)
    abot = round(abot/gg)
    
    a = fractions(atop/abot)
    ktop = y1*abot-atop*(x1-h)^2
    kbot = abot
    gg = abs(gcd2(ktop,kbot))
    ktop = abs(round(ktop/gg))*sign(ktop*kbot)
    kbot = abs(round(kbot/gg))
    k = fractions(ktop/kbot)
    
    mtop = x2-x1
    mbot = y2-y1
    gg = abs(gcd2(mtop,mbot))
    mtop = mtop/gg
    mbot = mbot/gg
    btop = -(x2-x1)*y1+(y2-y1)*x1
    bbot = y2-y1
    gg = abs(gcd2(btop,bbot))
    btop = btop/gg
    bbot = bbot/gg
    nums = c(abot,atop,ktop,kbot,h,mtop,mbot,btop,bbot)
    n2 = c(abot)
    abot = abs(abot)*sign(abot*atop)
    ktop = abs(ktop)*sign(ktop*kbot)
    mtop = abs(mtop)*sign(mtop*mbot)
    btop = abs(btop)*sign(btop*bbot)
    p = abot
    pk = p*k
    k = ktop/kbot
    h = h
    m = mtop
    b = btop
    sol1 = min(c(y1,y2))
    sol2 = max(c(y1,y2))
    A = m^2
    B = 2*m*(b-h)-p
    C = (b-h)^2+pk
    if(max(abs(nums))<50 && min(abs(nums))>0 && (abs(pk)%%1==0) && sum(abs(c(atop,mbot,bbot))==1)==3 && min(abs(n2))>1 && max(abs(c(A,B,C)))<1000 && abs(pk)<200 && h!=b && mtop==1){break}
}


gg = abs(gcd(c(A,B,C)))
A2 = A/gg
B2 = B/gg
C2 = C/gg
D2 = B2^2-4*A2*C2


eq1 = paste0("\\sqrt{",abot,"x+",-pk,"}+",h)
eq2 = paste0(mtop,"x+",btop)
eq1 = gsub("+-","-",eq1,fixed=T)
eq2 = gsub("+-","-",eq2,fixed=T)
eq2 = gsub("+-","-",eq2,fixed=T)

# y = sqrt(p(x-k))+h
# y = mx+b

ls1 = h+sqrt(p*sol1-pk)
rs1 = m*sol1+b
ls2 = h+sqrt(p*sol2-pk)
rs2 = m*sol2+b


e1 = paste0(h,"+\\sqrt{",p,"x+",-pk,"}=",m,"x+",b)
e1 = gsub("+-","-",e1,fixed=T)
e1 = gsub("=1x","=x",e1,fixed=T)
e1 = gsub("=-1x","=-x",e1,fixed=T)
if(h>0){
    wrd1 = paste0("Subtract ",h," from both sides.")
} else {
    wrd1 = paste0("Add ",abs(h)," to both sides.")
}

e2 = paste0("\\sqrt{",p,"x+",-pk,"}=",m,"x+",b-h)
e2 = gsub("+-","-",e2,fixed=T)
e2 = gsub("=1x","=x",e2,fixed=T)
e2 = gsub("=-1x","=-x",e2,fixed=T)

e3 = paste0(p,"x+",-pk,"=",m^2,"x^2+",2*m*(b-h),"x+",(b-h)^2)
e3 = gsub("+-","-",e3,fixed=T)
e3 = gsub("=1x","=x",e3,fixed=T)
e3 = gsub("=-1x","=-x",e3,fixed=T)

e4 = paste0(p,"x+",-p*k,"=",m^2,"x^2+",2*m*(b-h),"x+",(b-h)^2)
e4 = gsub("+-","-",e4,fixed=T)
e4 = gsub("=1x","=x",e4,fixed=T)
e4 = gsub("=-1x","=-x",e4,fixed=T)

wrd2 = paste0("Subtract $",p,"x+",-p*k,"$ from both sides.")
wrd2 = gsub("+-","-",wrd2,fixed=T)

e5 = paste0("0=",m^2,"x^2+",2*m*(b-h)-p,"x+",(b-h)^2+p*k)
e5 = gsub("+-","-",e5,fixed=T)
e5 = gsub("=1x","=x",e5,fixed=T)
e5 = gsub("=-1x","=-x",e5,fixed=T)



gg = gcd(c(A,B,C))
if(abs(gg)>1){
    wrd3 = paste0("Notice all coefficients are multiples of ",abs(gg),". So divide both sides by ",abs(gg),".$$0={",A2,"}x^2+{",B2,"}x+{",C2,"}$$")
    wrd3 = gsub("{1}","",wrd3,fixed=T)
    wrd3 = gsub("{-1}","-",wrd3,fixed=T)
    wrd3 = gsub("{","",wrd3,fixed=T)
    wrd3 = gsub("}","",wrd3,fixed=T)
    wrd3 = gsub("+-","-",wrd3,fixed=T)
} else {
    wrd3 = ""
}

ach1 = -12:12
ach2 = -12:12
ach3 = c("an extraneous","a valid")
ach4 = c("an extraneous","a valid")

al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")
al3 = paste0("* ",ach3,collapse="\n")
al4 = paste0("* ",ach4,collapse="\n")

ans1 = paste0(1*(ach1==sol1),collapse="")
ans2 = paste0(1*(ach2==sol2),collapse="")
ans3 = paste0(1*(c(F,T)==(ls1==rs1)),collapse="")
ans4 = paste0(1*(c(F,T)==(ls2==rs2)),collapse="")

```

Question
========

Consider the equation.

$$`r e1`$$

By using algebra, find both **possible** solutions. Try validating both possible solutions to determine whether each is [extraneous](https://en.wikipedia.org/wiki/Extraneous_and_missing_solutions) or valid.

Let $x_1$ and $x_2$ represent the two possible solutions such that $x_1<x_2$.

* $x_1=$ ##ANSWER1##
* $x_2=$ ##ANSWER2##
* $x_1$ is ##ANSWER3## solution.
* $x_2$ is ##ANSWER4## solution.


Answerlist
--------

`r al1`
`r al2`
`r al3`
`r al4`


Solution
========

$$`r e1`$$

`r wrd1`

$$`r e2`$$

Square both sides.

$$`r e3`$$

`r wrd2`

$$`r e5`$$

`r wrd3`

Factor the quadratic expression (or you can use quadratic formula to find *possible* solutions).

```{r,echo=F}
factored = paste0("y=(x+",-sol1,")(x+",-sol2,")",collapse="")
factored = gsub("+-","-",factored,fixed=T)
```

$$`r factored`$$

So the two possible solutions are $x_1=`r sol1`$ and $x_2=`r sol2`$. Notice $x_1<x_2$, as required. But, we need to check these, because it is possible one (or both) of them is an [extraneous solution](https://en.wikipedia.org/wiki/Extraneous_and_missing_solutions).

```{r,echo=F}
check1 = gsub("x",paste0("(",sol1,")"),e1,fixed=T)
check1 = gsub("=","\\stackrel{?}{=}",check1,fixed=T)
check2 = gsub("x",paste0("(",sol2,")"),e1,fixed=T)
check2 = gsub("=","\\stackrel{?}{=}",check2,fixed=T)

check1b = paste0(h,"+\\sqrt{",p*sol1-pk,"}\\stackrel{?}{=}",m*sol1+b)
check2b = paste0(h,"+\\sqrt{",p*sol2-pk,"}\\stackrel{?}{=}",m*sol2+b)


check1c = paste0(h,"+",sqrt(p*sol1-pk),"\\stackrel{?}{=}",m*sol1+b)
check2c = paste0(h,"+",sqrt(p*sol2-pk),"\\stackrel{?}{=}",m*sol2+b)

if(ls1==rs1){
    say1 = paste0("Yes! So ",sol1," is a valid solution.")
} else {
    say1 = paste0("Nope! So ",sol1," is an extraneous solution.")
}

if(ls2==rs2){
    say2 = paste0("Yes! So ",sol2," is a valid solution.")
} else {
    say2 = paste0("Nope! So ",sol2," is an extraneous solution.")
}

```

First substitute $`r sol1`$ for $x$ in the original equation. Simplify both sides to check if solution is valid.

$$`r check1`$$
$$`r check1b`$$
$$`r check1c`$$
$$`r ls1`\stackrel{?}{=}`r rs1`$$

`r say1`

Now substitute $`r sol2`$ for $x$ in the original equation. Simplify both sides to check if solution is valid.

$$`r check2`$$


$$`r check2b`$$


$$`r check2c`$$

$$`r ls2`\stackrel{?}{=}`r rs2`$$


`r say2`


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r ans1`|`r ans2`|`r ans3`|`r ans4`
exname: sqrt_line_one_extran