```{r,echo=FALSE}
n = sample(3:10,1)
a = sample(c(-1,1),1)
rs = (1:n)*(20/(n+1))-10
# print(n)
# print(rs)

ach1 = paste0("n≥",1:12)
ach2 = c("n is even","n is odd")
ach3 = c("aₙ is negative","aₙ is positive")

if(a==1){
    nmin = n%/%2
    nmax = (n-1)%/%2
    rend = "up"
    asign = "positive"
} else {
    nmax = n%/%2
    nmin = (n-1)%/%2
    rend = "down"
    asign = "negative"
}

if(n%%2==0){
    nex = "odd"
    par = "even"
} else {
    nex = "even"
    par = "odd"
}

al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")
al3 = paste0("* ",ach3,collapse="\n")

sol1 = paste0(1*(n==1:12),collapse="")
if(n%%2==0){
    sol2 = "10"
} else {
    sol2 = "01"
}
if(a>0){
    sol3 = "01"
} else {
    sol3 = "10"
}


```


Question
========

**BACKGROUND**

A generalized ([univariate](https://en.wikipedia.org/wiki/Univariate)) polynomial function in standard form can be expressed as:

$$y=a_nx^n+a_{n-1}x^{n-1}+\cdots+a_2x^2+a_1x+a_0$$

where $n$ represents the [degree](https://en.wikipedia.org/wiki/Degree_of_a_polynomial) of the polynomial, $a_n$ is the leading coefficient, $a_i$ is the $i^{\mathrm{th}}$-degree coefficient, $a_2$ is the quadratic coefficient, $a_1$ is the linear coefficient, and $a_0$ is the constant. It should be mentioned that $a_n\ne 0$, but the other coefficients could equal 0.

When a polynomial of degree $n$ is graphed, the **most** possible number of [extrema](https://en.wikipedia.org/wiki/Maximum_and_minimum) is $n-1$. For example, a quadratic polynomial function has one extreme, but a cubic polynomial function can have either 2 extrema or none, and a quartic (4th-degree) polynomial can have either 3 extrema or 1.

The end behavior of polynomials dictates that an even-degree polynomial will have an odd number of extrema, and an odd-degree polynomial will have an even number of extrema.

The leading coefficient's [sign](https://en.wikipedia.org/wiki/Sign_(mathematics)) dictates the right-side end behavior. If as $x\to\infty$ we see $y\to\infty$, then $a_n>0$. On the other hand, if as $x\to\infty$ we see $y\to-\infty$, then $a_n<0$.

**SPECIFIC PROBLEM**

Consider the polynomial function graphed below.

```{r,echo=F,fig.dim=c(5,5)}
x = seq(-10,10,0.01)
y = rep(1,length(x))
for(i in 1:length(x)){
    y[i] = a*prod(x[i]-rs)
}
minr = min(rs)
maxr = max(rs)
maxay = max(abs(y[abs(x)<maxr]))
new_scale = sample(3:30,1)
y = y/maxay*new_scale*log10(10*n)+2*new_scale
par(mar=c(5,5,0,0))
plot(x+10,y,"l",xlab="x",ylab="y",ylim=c(0,4*new_scale),col="blue",lwd=2)

```
\

Assume this graph contains all the extrema of the function, so the end-behavior is also indicated.

1. What is the lowest possible degree of the polynomial? ##ANSWER1##
2. What is the polynomial degree's [parity](https://en.wikipedia.org/wiki/Parity_(mathematics))? ##ANSWER2##
3. What is the sign of the leading coefficient? ##ANSWER3##

Answerlist
--------

`r al1`
`r al2`
`r al3`



Solution
========

The graph contains $`r n-1`$ extrema. Specifically:

* The number of minima (valley bottoms) is `r nmin`.
* The number of maxima (mountain peaks) is `r nmax`.

To have $`r n-1`$ extrema, the polynomial's degree must be at least $`r n`$. So, $n\ge `r n`$.

Notice, the number of extrema (`r n-1`) is `r nex`. This indicates the polynomial's degree must be `r par`.

On the right side of the graph, as $x\to \infty$, we see the curve heads `r rend`. This tells us that the leading coefficient, $a_n$, is `r asign`.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`
exname: x_min_deg