```{r,echo=FALSE}
n = sample(2:5,1)
while(T){
    root = sort(sample(1:8,n)*sample(c(-1,1),n,T))
    pows = sample(1:2,n,T)
    pow2 = sample(1:2,n,T)
    if(min(diff(root))>1 && max(diff(root))<7 && sum(pows==pow2)!=n && sum(pows)>n && sum(pows)<2*n){break}
}

a = sample(c(-1,1),1)
ord = sample(1:n)
rmix = root[ord]
pmix = pows[ord]
pmix2 = pow2[ord]

if(a==1){
    exp1 = paste0("(x+",-rmix,")^",pmix,collapse="")
    exp2 = paste0("(x+",-rmix,")^",pmix2,collapse="")
    exp3 = paste0("-",paste0("(x+",-rmix,")^",pmix,collapse=""))
    exp4 = paste0("-",paste0("(x+",-rmix,")^",pmix2,collapse=""))
    exp5 = paste0("(x+",-root,")^",pows,collapse="")
    exp6 = paste0("a",paste0("(x+",-root,")^",pows,collapse=""))
} else {
    exp1 = paste0("-",paste0("(x+",-rmix,")^",pmix,collapse=""))
    exp2 = paste0("-",paste0("(x+",-rmix,")^",pmix2,collapse=""))
    exp3 = paste0("(x+",-rmix,")^",pmix,collapse="")
    exp4 = paste0("(x+",-rmix,")^",pmix2,collapse="")
    exp5 = paste0("-",paste0("(x+",-root,")^",pows,collapse=""))
    exp6 = paste0("a",paste0("(x+",-root,")^",pows,collapse=""))
}
exp1 = gsub("+-","-",exp1,fixed=T)
exp2 = gsub("+-","-",exp2,fixed=T)
exp3 = gsub("+-","-",exp3,fixed=T)
exp4 = gsub("+-","-",exp4,fixed=T)
exp5 = gsub("+-","-",exp5,fixed=T)
exp6 = gsub("+-","-",exp6,fixed=T)

exp1 = gsub("^1","",exp1,fixed=T)
exp2 = gsub("^1","",exp2,fixed=T)
exp3 = gsub("^1","",exp3,fixed=T)
exp4 = gsub("^1","",exp4,fixed=T)
exp5 = gsub("^1","",exp5,fixed=T)
exp6 = gsub("^1","",exp6,fixed=T)

exps = sample(c(exp1,exp2,exp3,exp4))
al = paste0("* $y=",exps,"$",collapse="\n")
sol = paste0(1*(exps==exp1),collapse="")

```

Question
========

A polynomial is sketched below.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-10,10),ylim=c(-2,2))
abline(v=0,lwd=1)
abline(h=0,lwd=2)
for(i in -10:10){
    if(i%%5==0 && i!=0){
        lines(c(i,i),c(-0.1,0.1))
        text(i,-0.2,i)
    } else {
        lines(c(i,i),c(-0.05,0.05))
    }
}
xs = root
fx = function(x,a,root,pows){
    b = a
    for(i in 1:length(root)){
        b = b*(x-root[i])^pows[i]
    }
    return(b)
}
xmid = c(xs[1]-1,(xs[2:n]+xs[1:(n-1)])/2,xs[n]+1)
sss = 1.3
xx = xmid[1]
yy = sign(fx(xmid[1],a,root,pows))
mm = -yy*sss
for(i in 1:n){
    xx = c(xx,xs[i])
    yy = c(yy,0)
    if(sign(fx(xs[i]-0.1,a,root,pows))==sign(fx(xs[i]+0.1,a,root,pows))){
        mm = c(mm,0)
    }
    if(sign(fx(xs[i]-0.1,a,root,pows))==-1 && sign(fx(xs[i]+0.1,a,root,pows))==1){
        mm = c(mm,sss)
    }
    if(sign(fx(xs[i]-0.1,a,root,pows))==1 && sign(fx(xs[i]+0.1,a,root,pows))==-1){
        mm = c(mm,-sss)
    }
    xx = c(xx,xmid[i+1])
    if(i<n){
        mm = c(mm,0)
        yy = c(yy,pi/2*sign(fx(xmid[i+1],a,root,pows)))
    } else {
        mm = c(mm,sign(a)*sss)
        yy = c(yy,sign(fx(xmid[i+1],a,root,pows)))
    }
}


xwave = seq(min(xs),max(xs),0.1)
sf = splinefunH(xx,yy,mm)
lines(xwave,sin(sf(xwave)),col="blue",lwd=3)
points(root,rep(0,n),pch=19,col="blue")
xlo = seq(min(xs)-1,min(xs),0.1)
lines(xlo,sf(xlo),col="blue",lwd=3)
xhi = seq(max(xs),max(xs)+1,0.1)
lines(xhi,sf(xhi),col="blue",lwd=3)

# lines(c(max(root),max(root)+2),c(0,2*a),col="blue",lwd=3)
# lines(c(min(root),min(root)-2),c(0,2*a*(-1)^n),col="blue",lwd=3)
arrows(xx[2*n+1],yy[2*n+1],xx[2*n+1]+0.5,yy[2*n+1]+0.5*sign(a)*sss,col="blue",lwd=3,length=0.1,angle=15)
arrows(xx[1],yy[1],xx[1]-0.5,yy[1]+0.5*sign(yy[1])*sss,col="blue",lwd=3,length=0.1,angle=15)

```
\

Which polynomial (in factored form) best matches the sketch?

Answerlist
--------

`r al`


Solution
========

If a polynomial has a factor of $x-r$, then there will be an $x$-intercept at point $(r,0)$.

In this case, the roots (the $x$-intercepts) are at:

$$`r paste0(root, collapse=",\\,")`$$

```{r,echo=F}
ss = paste0("$x+",-root,"$",collapse=" and ")
ss = gsub("+-","-",ss,fixed=T)
```

Thus, the factors are `r ss`. Notice, the $x$-intercepts where the curve "bounces" off the $x$ axis correspond to an [even multiplicity](https://en.wikipedia.org/wiki/Multiplicity_(mathematics)), in this case a multiplicity of 2. So, we know the curve could be represented by the function below:

$$y=`r exp6`$$

where $a$ is some constant.

Lastly, we need to determine whether $a$ should be positive or negative. In this problem, either $a=1$ or $a=-1$. To determine this, look at the right side of the graph. Specifically, we are considering the [end behavior of polynomials](https://www.khanacademy.org/math/algebra2/x2ec2f6f830c9fb89:poly-graphs/x2ec2f6f830c9fb89:poly-end-behavior/a/end-behavior-of-polynomials). Notice that once $x$ is larger than $`r max(root)`$, all the factors will be positive, so only $a$ will dictate whether the function on the right side is positive or negative.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-10,10),ylim=c(-2,2))
abline(v=0,lwd=1)
abline(h=0,lwd=2)
for(i in -10:10){
    if(i%%5==0 && i!=0){
        lines(c(i,i),c(-0.1,0.1))
        text(i,-0.2,i)
    } else {
        lines(c(i,i),c(-0.05,0.05))
    }
}
xs = root
fx = function(x,a,root,pows){
    b = a
    for(i in 1:length(root)){
        b = b*(x-root[i])^pows[i]
    }
    return(b)
}
xmid = c(xs[1]-1,(xs[2:n]+xs[1:(n-1)])/2,xs[n]+1)
sss = 1.3
xx = xmid[1]
yy = sign(fx(xmid[1],a,root,pows))
mm = -yy*sss
for(i in 1:n){
    xx = c(xx,xs[i])
    yy = c(yy,0)
    if(sign(fx(xs[i]-0.1,a,root,pows))==sign(fx(xs[i]+0.1,a,root,pows))){
        mm = c(mm,0)
    }
    if(sign(fx(xs[i]-0.1,a,root,pows))==-1 && sign(fx(xs[i]+0.1,a,root,pows))==1){
        mm = c(mm,sss)
    }
    if(sign(fx(xs[i]-0.1,a,root,pows))==1 && sign(fx(xs[i]+0.1,a,root,pows))==-1){
        mm = c(mm,-sss)
    }
    xx = c(xx,xmid[i+1])
    if(i<n){
        mm = c(mm,0)
        yy = c(yy,pi/2*sign(fx(xmid[i+1],a,root,pows)))
    } else {
        mm = c(mm,sign(a)*sss)
        yy = c(yy,sign(fx(xmid[i+1],a,root,pows)))
    }
}


xwave = seq(min(xs),max(xs),0.1)
sf = splinefunH(xx,yy,mm)
lines(xwave,sin(sf(xwave)),col="grey",lwd=3)
points(root,rep(0,n),pch=19,col="grey")
xlo = seq(min(xs)-1,min(xs),0.1)
lines(xlo,sf(xlo),col="grey",lwd=3)
xhi = seq(max(xs),max(xs)+1,0.1)
lines(xhi,sf(xhi),col="grey",lwd=3)

# lines(c(max(root),max(root)+2),c(0,2*a),col="blue",lwd=3)
# lines(c(min(root),min(root)-2),c(0,2*a*(-1)^n),col="blue",lwd=3)
arrows(xx[2*n+1],yy[2*n+1],xx[2*n+1]+0.5,yy[2*n+1]+0.5*sign(a)*sss,col="red",lwd=3,length=0.1,angle=15)
arrows(xx[1],yy[1],xx[1]-0.5,yy[1]+0.5*sign(yy[1])*sss,col="grey",lwd=3,length=0.1,angle=15)

if(a>0){
    wrd1 = "up"
    wrd2 = "positive"
} else {
    wrd1 = "down"
    wrd2 = "negative"
}

```
\

Notice, on the right side, the function is heading `r wrd1`. I guess more importantly, as $x\to \infty$ we see the function is `r wrd2`. This implies that $a$ is `r wrd2`. So, in this case, $a=`r a`$.

$$y=`r exp5`$$

```{r,echo=F,results="asis"}
if(exp5!=exp1){
    cat("And then, since multiplication is commutative, the factors can be written in any order. In this case, the correct answer is:")
    cat(paste0("\n\n$$y=",exp1,"$$"))
}
```



Meta-information
============
extype: schoice
exsolution: `r sol`
exname: poly_sketch