---
output: pdf_document
params:
    rseed: 0
    showsol: true
header-includes:
  - \usepackage{multicol}
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]
```

## `r bn`

```{r}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
```


### Example

Rationalize denominator and simplify:
$$\frac{8+7\sqrt{3}}{4+2\sqrt{3}}$$

\color{red}

Multiply the numerator and the denominator by the **CONJUGATE** of the denominator.

$$\frac{(8+7\sqrt{3})(4-2\sqrt{3})}{(4+2\sqrt{3})(4-2\sqrt{3})}$$

Expand the numerator and expand the denominator. You can FOIL or use a box method.

$$\frac{32-16\sqrt{3}+28\sqrt{3}-14\cdot3}{16-8\sqrt{3}+8\sqrt{3}-4\cdot3}$$


$$\frac{32-16\sqrt{3}+28\sqrt{3}-42}{16-8\sqrt{3}+8\sqrt{3}-12}$$

Combine like terms.

$$\frac{-10+12\sqrt{3}}{4}$$

Notice both terms in the numerator and the factor in the denominator share a common factor of $2$. Divide numerator and denominator by this common factor.

$$\frac{-5+6\sqrt{3}}{2}$$


\color{black}

\newpage

```{r,echo=F}
qs = c("\\frac{8+7\\sqrt{3}}{4+2\\sqrt{3}}")
answers = c("\\frac{-5+6\\sqrt{3}}{2}")
while(length(qs)<31){
    while(T){
        if(length(qs)<20){
            a = sample(1:9,1)*sample(c(-1,1),1)
            b = sample(1:9,1)*sample(c(-1,1),1)
            c = sample(c(2,3,5,6,7,10),1)
            d = sample(1:9,1)
            e = sample(1:9,1)*sample(c(-1,1),1)
        } else {
            a = sample(2:9,1)*sample(c(-1,1),1)
            b = sample(2:9,1)*sample(c(-1,1),1)
            c = sample(c(2,3,5,6,7,10),1)
            d = sample(2:9,1)
            e = sample(2:9,1)*sample(c(-1,1),1)
        }
        
        q = paste0("\\frac{",a,"+[",b,"]\\sqrt{",c,"}}{",d,"+[",e,"]\\sqrt{",c,"}}")
        q = gsub("+[-1]","-",q,fixed=T)
        q = gsub("+[1]","+",q,fixed=T)
        q = gsub("[","",q,fixed=T)
        q = gsub("]","",q,fixed=T)
        q = gsub("+-","-",q,fixed=T)
        A = a*d-b*e*c
        B = b*d-a*e
        D = d^2-e^2*c
        gg = abs(gcd(c(A,B,D)))*sign(D)
        if(gg != 0){
            A = A/gg
            B = B/gg
            D = D/gg
        }
        answer = paste0("\\frac{",A,"+",B,"\\sqrt{",c,"}}{",D,"}")
        if(D==1){
            answer = paste0(A,"+",B,"\\sqrt{",c,"}")
        }
        answer = gsub("+-","-",answer,fixed=T)
        answer = gsub("+1\\sqrt","+\\sqrt",answer,fixed=T)
        answer = gsub("-1\\sqrt","-\\sqrt",answer,fixed=T)
        if(A!=0 && B!=0 && D!=0 && abs(A)<11 && abs(B)<11 && abs(D)<11 && abs(b*e*c)<100 && abs(e^2*c)<100 && gg>1 && abs(gcd(c(a,b,d,e)))==1 && sum(sign(c(a,b,d,e)))>=0 && !(q %in% qs) && !(answer %in% answers)){
            break
        }
    }
    qs = c(qs,q)
    answers = c(answers,answer)
}

```

For each expression below, rationalize the denominator and simplify:


```{r,echo=F,results='asis'}

s = ""
for(i in 2:length(qs)){
    s = paste0(s,qs[i])
    if(i%%5==1 && i<length(qs)){
        s = paste0(s," \\\\\n\\\\\n")
    } else {
        s = paste0(s," && ")
    }
}

cat(paste0("\\begin{align*}\n"))
cat(s)
cat(paste0("\n\\end{align*}"))

```

\vfill

```{r,echo=F,results='asis'}
s = ""
for(i in 2:length(answers)){
    s = paste0(s,answers[i])
    if(i%%5==1 && i<length(answers)){
        s = paste0(s," \\\\\n\\\\\n")
    } else {
        s = paste0(s," && ")
    }
}
cat("\\color{gray}\n")
cat("### Answers\n\n")
cat(paste0("\\begin{align*}\n"))
cat(s)
cat(paste0("\n\\end{align*}"))
cat("\n\\color{black}\n")
```