---
output: pdf_document
params:
    rseed: 1
    showsol: true
header-includes:
  - \usepackage{multicol}
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]
```

## `r bn`

```{r}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
```


### Example

Rationalize denominator and simplify:
$$\frac{105\sqrt{15}}{6\sqrt{50}}$$

\color{red}


Use prime factorization. Also use the identity $\sqrt{a\cdot b}\equiv \sqrt{a}\cdot \sqrt{b}$.

$$\frac{3\cdot 5\cdot 7 \cdot \sqrt{3} \cdot \sqrt{5}}{2\cdot 3 \cdot \sqrt{2} \cdot \sqrt{5} \cdot \sqrt{5}}$$

Eliminate common factors. In this case we have $3$ and $\sqrt{5}$ as common factors.

$$\frac{5\cdot 7 \cdot \sqrt{3}}{2 \cdot \sqrt{2} \cdot \sqrt{5}}$$


Multiply numerator and denominator by the denominator's radical factors (which are $\sqrt{2}$ and $\sqrt{5}$ in this case.

$$\frac{5\cdot 7\cdot \sqrt{3}\cdot \sqrt{2}\cdot\sqrt{5}}{2\cdot \sqrt{2}\cdot\sqrt{5}\cdot \sqrt{2}\cdot\sqrt{5}}$$

Use the identity $\sqrt{a}\cdot\sqrt{a}\equiv a$. Specifically, this denominator has two factors of $\sqrt{2}$ and two factors of $\sqrt{5}$.

$$\frac{5\cdot 7\cdot \sqrt{3}\cdot \sqrt{2}\cdot\sqrt{5}}{2\cdot 2 \cdot 5}$$

Eliminate common factors. In this case we have a common factor of $5$.

$$\frac{7 \cdot \sqrt{3}\cdot \sqrt{2}\cdot\sqrt{5}}{2\cdot 2}$$

Evaluate products.
$$\frac{7 \sqrt{30}}{4}$$



\color{black}

\newpage


```{r,echo=F}
psfs = rev((2:30)^2)

# a*sqrt(b)/(c*sqrt(d))
# a*sqrt(b*d)/(c*d)
# A*sqrt(R)/(D)

ex1s = c("\\frac{105\\sqrt{15}}{6\\sqrt{50}}","\\frac{2\\sqrt{3}}{5\\sqrt{7}}","\\frac{1}{\\sqrt{7}}","\\frac{3}{\\sqrt{3}}","\\frac{10}{3\\sqrt{5}}")
ans1s = c("\\frac{7 \\sqrt{30}}{4}","\\frac{2\\sqrt{21}}{35}","\\frac{\\sqrt{7}}{7}","\\sqrt{3}","\\frac{2\\sqrt{5}}{3}")

while(length(ex1s)<31){
    while(T){
        canpass = T
        a = sample(c(1:10,12,14,15,16,18,20,24),1)
        b = sample(c(1,2,3,5,6,7,10,14,15),1)
        c = sample(c(1:10,12,14,15,16,18,20,24),1)
        d = sample(c(2,3,5,6,7,10,14,15),1)
        if(a==c || gcd(c(b,d))==d){
            canpass = F
        }
        ex1 = paste0("\\frac{[",a,"]\\sqrt{",b,"}}{[",c,"]\\sqrt{",d,"}}")
        ex1 = gsub("[1]\\sqrt{1}","1",ex1,fixed=T)
        ex1 = gsub("[1]","",ex1,fixed=T)
        ex1 = gsub("[","",ex1,fixed=T)
        ex1 = gsub("]","",ex1,fixed=T)
        ex1 = gsub("\\sqrt{1}","",ex1,fixed=T)
        A1 = a
        R1 = b*d
        D1 = c*d
        A2 = A1
        R2 = R1
        D2 = D1
        for(psf in psfs){
            if(R2%%psf==0){
                A2 = round(A1*sqrt(psf))
                R2 = round(R1/psf)
            }
        }
        gg = gcd(c(A2,D2))
        A3 = round(A2/gg)
        D3 = round(D2/gg)
        if(D3>1){
            ans1 = paste0("\\frac{[",A3,"]\\sqrt{",R2,"}}{",D3,"}")
        } else {
            ans1 = paste0("[",A3,"]\\sqrt{",R2,"}")
        }
        ans1 = gsub("[1]\\sqrt{1}","1",ans1,fixed=T)
        ans1 = gsub("[1]","",ans1,fixed=T)
        ans1 = gsub("[","",ans1,fixed=T)
        ans1 = gsub("]","",ans1,fixed=T)
        ans1 = gsub("\\sqrt{1}","",ans1,fixed=T)
        if(canpass && max(c(A3,D3,R2))<=100 && abs(gg)>1 && !(ex1 %in% ex1s) && !(ans1 %in% ans1s)){break}
    }
    ex1s = c(ex1s,ex1)
    ans1s = c(ans1s,ans1)
}

```

### Practice

For each of the expressions below, rationalize the denominator and simplify.

```{r,echo=F,results='asis'}

s = ""
for(i in 2:length(ex1s)){
    s = paste0(s,ex1s[i])
    if(i%%5==1 && i<length(ex1s)){
        s = paste0(s," \\\\\n\\\\\n")
    } else {
        s = paste0(s," && ")
    }
}

cat(paste0("\\begin{align*}\n"))
cat(s)
cat(paste0("\n\\end{align*}"))

```

\vfill

```{r,echo=F,results='asis'}
s = ""
for(i in 2:length(ans1s)){
    s = paste0(s,ans1s[i])
    if(i%%5==1 && i<length(ex1s)){
        s = paste0(s," \\\\\n\\\\\n")
    } else {
        s = paste0(s," && ")
    }
}
cat("\\color{gray}\n")
cat("### Answers\n\n")
cat(paste0("\\begin{align*}\n"))
cat(s)
cat(paste0("\n\\end{align*}"))
cat("\n\\color{black}\n")
```
