---
output: pdf_document
params:
    rseed: 2
    showsol: true
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]
```

## `r bn`

### Example 1

```{r}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
```



```{r}
fsimp = function(top,bot){
    gg = abs(gcd(c(top,bot)))
    top = round(abs(top)/gg*sign(top*bot))
    bot = round(abs(mbot)/gg)
    if(bot==1){
        return(paste0(top))
    } else {
        return(paste0("\\frac{",top,"}{",bot,"}"))
    }
}

xpar = c(0,1,4,9)
ypar = c(0,1,2,3)
xext = c(1,4,9)
yext = c(-1,-2,-3)

# horizontal shift before possible reflection

# y = a*sqrt(bx-h)+k

h = sample(c(-9:-1,1),1)
a = sample(c(-3,-2,-1,1,2,3),1)
k = sample(c(((-10+3*abs(a)):-1),(1:(10-3*abs(a)))),1)
b = sample(c(-1,1),1)
xc = (xpar+h)/b
yc = a*ypar+k
xd = (xext+h)/b
yd = k+a*yext
nval = 1

if(nval==0){
    ii = sample(1:length(xd),2)
    xi = xd[ii]
    yi = yd[ii]
    isval = c(F,F)
    wrd = c("an extraneous","an extraneous")
}
if(nval==1){
    while(T){
        ic = sample(1:length(xc),1)
        id = sample(1:length(xd),1)
        xic = xc[ic]
        yic = yc[ic]
        xid = xd[id]
        yid = yd[id]
        ii = sample(1:2)
        xi = c(xic,xid)[ii]
        yi = c(yic,yid)[ii]
        isval = c(T,F)[ii]
        wrd = c("a valid","an extraneous")[ii]
        if(xic!=xid){break}
    }
}
if(nval==2){
    ii = sample(1:length(xc),2)
    xi = xc[ii]
    yi = yc[ii]
    isval = c(T,T)
    wrd = c("a valid","a valid")
}

mtop = diff(yi)
mbot = diff(xi)
mf = fsimp(mtop,mbot)


while(T){
    xp = sample(-10:10,1)
    yp = mtop*(xp-xi[1])/mbot+yi[1]
    if(abs(yp)<=10 && abs(yp)%%1==0 && yp!=yi[1] && yp!=yi[2] && min(abs(c(xp,yp)))>0){break}
}

if(b==-1){
    fx = paste0(k,"+[",a,"]\\sqrt{-x+",-h,"}")
} else {
    fx = paste0(k,"+[",a,"]\\sqrt{x+",-h,"}")
}
fx = gsub("[1]","",fx,fixed=T)
fx = gsub("[-1]","-",fx,fixed=T)
fx = gsub("[","",fx,fixed=T)
fx = gsub("]","",fx,fixed=T)
fx = gsub("+-","-",fx,fixed=T)
Lx = paste0("[",mf,"](x+",-xp,")+",yp)
Lx = gsub("+-","-",Lx,fixed=T)
Lx = gsub("[1]","",Lx,fixed=T)
Lx = gsub("[-1]","-",Lx,fixed=T)
Lx = gsub("[","",Lx,fixed=T)
Lx = gsub("]","",Lx,fixed=T)

doit = function(i){
    cat(paste0("Accurately plot the following two functions (and also plot the extraneous half of the parabola):\n\n$$y=",fx,"$$\n$$y=",Lx,"$$\n\n"))
    
    cat("\\color{red}\n\nFor the radical equation, make an $x,y$ table; choose $x$ values to make the radicand 0, 1, 4, and 9.\n\n")
    
    cat(paste0("| $x$ | $y=",fx,"$ |\n|:---:|:---:|\n"))
    x2 = (c(0,1,4,9)+h)/b
    y2 = a*c(0,1,2,3)+k
    cat(paste0("| ",x2," | ",y2," |",collapse="\n"))
    cat("\n\n")
    
    cat("To complete the extraneous half of the parabola, reflect those dots over the line of symmetry.\n\n")
    
    cat(paste0("For the point-slope linear equation, recognize that $x=",xp,"$ makes the expression in parentheses equal 0, which leads to $y=",yp,"$. From slope, the rise is ",abs(mtop)/abs(gcd(c(mtop,mbot)))*sign(mtop*mbot)," and the run is ",abs(mbot)/abs(gcd(c(mtop,mbot))),".\n\n"))
    
    par(pty="s",mar=c(0,0,0,0),mfrow=c(1,2))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),ann=F,axes=F)
    
    for(i in -10:10){
        lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
        lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    }
    for(i in seq(-10,10,5)){
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
    }
    abline(h=0,lwd=2)
    abline(v=0,lwd=2)
    text(10,0,"x",adj=c(-0.2,-0.2))
    text(0,10,"y",adj=c(-0.2,-0.2))
    text(10,0,"10",adj=c(0.5,1.2),cex=0.7)
    text(0,10,"10",adj=c(1.1,0.5),cex=0.7)
    
    if(params$showsol){
        xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
        yy = -a*sqrt(b*xx-h)+k
        
        xx = xx[abs(yy)<=10]
        yy = yy[abs(yy)<=10]
        
        lines(xx,yy,col="grey",lwd=2,lty=2)
        
        x2 = (c(0,1,4,9,16)+h)/b
        y2 = -a*c(0,1,2,3,4)+k
        x2 = x2[abs(y2)<=10]
        y2 = y2[abs(y2)<=10]
        
        points(x2,y2,pch=19,col="grey")
        
        xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
        yy = a*sqrt(b*xx-h)+k
        
        xx = xx[abs(yy)<=10]
        yy = yy[abs(yy)<=10]
        abline(h=k,col="cyan",lty=2)
        
        lines(xx,yy,col="blue",lwd=2)
        
        x2 = (c(0,1,4,9,16)+h)/b
        y2 = a*c(0,1,2,3,4)+k
        x2 = x2[abs(y2)<=10]
        y2 = y2[abs(y2)<=10]
        
        points(x2,y2,pch=19,col="blue")
        
        xl = seq(-10,10,0.1)
        yl = mtop/mbot*(xl-xi[1])+yi[1]
        xl = xl[abs(yl)<=10]
        yl = yl[abs(yl)<=10]
        lines(xl,yl,col="red",lwd=2)
    
        points(xi,yi,pch=19,col="red")
        points(xp,yp,pch=19,col="red")
        plot(0,0,"n",axes=F,ann=F)
        legend("left",c("valid half of parabola","extraneous half of parabola","line"),col=c("blue","grey","red"),lwd=c(2,2,2),lty=c(1,2,1))
        }
    
    cat(paste0("\\\n\n\\color{black}If the equation $",fx,"=",Lx,"$ was solved using algebra, what two possible solutions would be found? "))
    cat("For each possible solution, state whether it would be a valid solution or an extraneous solution.\n\n\\vfill\n\n")
    if(params$showsol){
        cat("\\color{red}")
        cat("\n\n")
        cat(paste0("$x=",xi,"$ is ",wrd," solution.",collapse="\n\n"))
        cat("\n\n\\color{black}\n\n")
    }
    cat("\\vfill\n\n")
}
```

```{r,echo=F,fig.dim=c(8,4),results="asis"}
doit(1)
```


\newpage


### Example 2

```{r}
set.seed(50)
fsimp = function(top,bot){
    gg = abs(gcd(c(top,bot)))
    top = round(abs(top)/gg*sign(top*bot))
    bot = round(abs(mbot)/gg)
    if(bot==1){
        return(paste0(top))
    } else {
        return(paste0("\\frac{",top,"}{",bot,"}"))
    }
}

xpar = c(0,1,4,9)
ypar = c(0,1,2,3)
xext = c(1,4,9)
yext = c(-1,-2,-3)

# horizontal shift before possible reflection

# y = a*sqrt(bx-h)+k

h = sample(c(-9:-1,1),1)
a = sample(c(-3,-2,-1,1,2,3),1)
k = sample(c(((-10+3*abs(a)):-1),(1:(10-3*abs(a)))),1)
b = sample(c(-1,1),1)
xc = (xpar+h)/b
yc = a*ypar+k
xd = (xext+h)/b
yd = k+a*yext
nval = 0

if(nval==0){
    ii = sample(1:length(xd),2)
    xi = xd[ii]
    yi = yd[ii]
    isval = c(F,F)
    wrd = c("an extraneous","an extraneous")
}
if(nval==1){
    while(T){
        ic = sample(1:length(xc),1)
        id = sample(1:length(xd),1)
        xic = xc[ic]
        yic = yc[ic]
        xid = xd[id]
        yid = yd[id]
        ii = sample(1:2)
        xi = c(xic,xid)[ii]
        yi = c(yic,yid)[ii]
        isval = c(T,F)[ii]
        wrd = c("a valid","an extraneous")[ii]
        if(xic!=xid){break}
    }
}
if(nval==2){
    ii = sample(1:length(xc),2)
    xi = xc[ii]
    yi = yc[ii]
    isval = c(T,T)
    wrd = c("a valid","a valid")
}

mtop = diff(yi)
mbot = diff(xi)
mf = fsimp(mtop,mbot)

while(T){
    xp = sample(-10:10,1)
    yp = mtop*(xp-xi[1])/mbot+yi[1]
    if(abs(yp)<=10 && abs(yp)%%1==0 && yp!=yi[1] && yp!=yi[2] && min(abs(c(xp,yp)))>0){break}
}

if(b==-1){
    fx = paste0(k,"+[",a,"]\\sqrt{-x+",-h,"}")
} else {
    fx = paste0(k,"+[",a,"]\\sqrt{x+",-h,"}")
}
fx = gsub("[1]","",fx,fixed=T)
fx = gsub("[-1]","-",fx,fixed=T)
fx = gsub("[","",fx,fixed=T)
fx = gsub("]","",fx,fixed=T)
fx = gsub("+-","-",fx,fixed=T)
Lx = paste0("[",mf,"](x+",-xp,")+",yp)
Lx = gsub("+-","-",Lx,fixed=T)
Lx = gsub("[1]","",Lx,fixed=T)
Lx = gsub("[-1]","-",Lx,fixed=T)
Lx = gsub("[","",Lx,fixed=T)
Lx = gsub("]","",Lx,fixed=T)

doit = function(i){
    cat(paste0("Accurately plot the following two functions (and also plot the extraneous half of the parabola):\n\n$$y=",fx,"$$\n$$y=",Lx,"$$\n\n"))
    
    cat("\\color{red}\n\nFor the radical equation, make an $x,y$ table; choose $x$ values to make the radicand 0, 1, 4, and 9.\n\n")
    
    cat(paste0("| $x$ | $y=",fx,"$ |\n|:---:|:---:|\n"))
    x2 = (c(0,1,4,9)+h)/b
    y2 = a*c(0,1,2,3)+k
    cat(paste0("| ",x2," | ",y2," |",collapse="\n"))
    cat("\n\n")
    
    cat("To complete the extraneous half of the parabola, reflect those dots over the line of symmetry.\n\n")
    
    cat(paste0("For the point-slope linear equation, recognize that $x=",xp,"$ makes the expression in parentheses equal 0, which leads to $y=",yp,"$. From slope, the rise is ",abs(mtop)/abs(gcd(c(mtop,mbot)))*sign(mtop*mbot)," and the run is ",abs(mbot)/abs(gcd(c(mtop,mbot))),".\n\n"))
    
    par(pty="s",mar=c(0,0,0,0),mfrow=c(1,2))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),ann=F,axes=F)
    
    for(i in -10:10){
        lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
        lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    }
    for(i in seq(-10,10,5)){
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
    }
    abline(h=0,lwd=2)
    abline(v=0,lwd=2)
    text(10,0,"x",adj=c(-0.2,-0.2))
    text(0,10,"y",adj=c(-0.2,-0.2))
    text(10,0,"10",adj=c(0.5,1.2),cex=0.7)
    text(0,10,"10",adj=c(1.1,0.5),cex=0.7)
    
    if(params$showsol){
        xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
        yy = -a*sqrt(b*xx-h)+k
        
        xx = xx[abs(yy)<=10]
        yy = yy[abs(yy)<=10]
        
        lines(xx,yy,col="grey",lwd=2,lty=2)
        
        x2 = (c(0,1,4,9,16)+h)/b
        y2 = -a*c(0,1,2,3,4)+k
        x2 = x2[abs(y2)<=10]
        y2 = y2[abs(y2)<=10]
        
        points(x2,y2,pch=19,col="grey")
        
        xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
        yy = a*sqrt(b*xx-h)+k
        
        xx = xx[abs(yy)<=10]
        yy = yy[abs(yy)<=10]
        abline(h=k,col="cyan",lty=2)
        
        lines(xx,yy,col="blue",lwd=2)
        
        x2 = (c(0,1,4,9,16)+h)/b
        y2 = a*c(0,1,2,3,4)+k
        x2 = x2[abs(y2)<=10]
        y2 = y2[abs(y2)<=10]
        
        points(x2,y2,pch=19,col="blue")
        
        xl = seq(-10,10,0.1)
        yl = mtop/mbot*(xl-xi[1])+yi[1]
        xl = xl[abs(yl)<=10]
        yl = yl[abs(yl)<=10]
        lines(xl,yl,col="red",lwd=2)
    
        points(xi,yi,pch=19,col="red")
        points(xp,yp,pch=19,col="red")
        plot(0,0,"n",axes=F,ann=F)
        legend("left",c("valid half of parabola","extraneous half of parabola","line"),col=c("blue","grey","red"),lwd=c(2,2,2),lty=c(1,2,1))
        }
    
    cat(paste0("\\\n\n\\color{black}If the equation $",fx,"=",Lx,"$ was solved using algebra, what two possible solutions would be found? "))
    cat("For each possible solution, state whether it would be a valid solution or an extraneous solution.\n\n\\vfill\n\n")
    if(params$showsol){
        cat("\\color{red}")
        cat("\n\n")
        cat(paste0("$x=",xi,"$ is ",wrd," solution.",collapse="\n\n"))
        cat("\n\n\\color{black}\n\n")
    }
    cat("\\vfill\n\n")
}
```

```{r,echo=F,fig.dim=c(8,4),results="asis"}
doit(1)
```


\newpage

```{r,echo=F}
fxs = character()
Lxs = character()
ks = numeric()
as = numeric()
hs = numeric()
bs = numeric()
mtops = numeric()
mbots = numeric()
xis = list()
yis = list()
wrds = list()
mfs = character()
xps = numeric()
yps = numeric()
nvals = numeric()

while(length(fxs)<9){
    h = sample(c(-9:-1,1),1)
    a = sample(c(-3,-2,-1,1,2,3),1)
    k = sample(c(((-10+3*abs(a)):-1),(1:(10-3*abs(a)))),1)
    b = sample(c(-1,1),1)
    xc = (xpar+h)/b
    yc = a*ypar+k
    xd = (xext+h)/b
    yd = k+a*yext
    
    nval = sample(0:2,1)
    
    if(nval==0){
        ii = sample(1:length(xd),2)
        xi = xd[ii]
        yi = yd[ii]
        isval = c(F,F)
        wrd = c("an extraneous","an extraneous")
    }
    if(nval==1){
        while(T){
            ic = sample(1:length(xc),1)
            id = sample(1:length(xd),1)
            xic = xc[ic]
            yic = yc[ic]
            xid = xd[id]
            yid = yd[id]
            ii = sample(1:2)
            xi = c(xic,xid)[ii]
            yi = c(yic,yid)[ii]
            isval = c(T,F)[ii]
            wrd = c("a valid","an extraneous")[ii]
            if(xic!=xid){break}
        }
    }
    if(nval==2){
        ii = sample(1:length(xc),2)
        xi = xc[ii]
        yi = yc[ii]
        isval = c(T,T)
        wrd = c("a valid","a valid")
    }
    
    mtop = diff(yi)
    mbot = diff(xi)
    mf = fsimp(mtop,mbot)
    
    
    while(T){
        xp = sample(-10:10,1)
        yp = mtop*(xp-xi[1])/mbot+yi[1]
        if(abs(yp)<=10 && abs(yp)%%1==0 && yp!=yi[1] && yp!=yi[2] && min(abs(c(xp,yp)))>0){break}
    }
    
    if(b==-1){
        fx = paste0(k,"+[",a,"]\\sqrt{-x+",-h,"}")
    } else {
        fx = paste0(k,"+[",a,"]\\sqrt{x+",-h,"}")
    }
    fx = gsub("[1]","",fx,fixed=T)
    fx = gsub("[-1]","-",fx,fixed=T)
    fx = gsub("[","",fx,fixed=T)
    fx = gsub("]","",fx,fixed=T)
    fx = gsub("+-","-",fx,fixed=T)
    Lx = paste0("[",mf,"](x+",-xp,")+",yp)
    Lx = gsub("+-","-",Lx,fixed=T)
    Lx = gsub("[1]","",Lx,fixed=T)
    Lx = gsub("[-1]","-",Lx,fixed=T)
    Lx = gsub("[","",Lx,fixed=T)
    Lx = gsub("]","",Lx,fixed=T)
    if(!(fx %in% fxs) && !(Lx %in% Lxs) && max(as.numeric(table(c(nvals,nval))))<=3 && max(as.numeric(table(c(sign(bs),sign(b)))))<=5 && max(as.numeric(table(c(sign(as),sign(a)))))<=5){
        fxs = c(fxs,fx)
        Lxs = c(Lxs,Lx)
        ks = c(ks,k)
        as = c(as,a)
        hs = c(hs,h)
        bs = c(bs,b)
        mtops = c(mtops,mtop)
        mbots = c(mbots,mbot)
        xis[[length(xis)+1]] = xi
        yis[[length(yis)+1]] = yi
        wrds[[length(wrds)+1]] = wrd
        mfs = c(mfs,mf)
        xps = c(xps,xp)
        yps = c(yps,yp)
        nvals = c(nvals,nval)
    }
}

doitA = function(JJ){
    cat("Consider the two functions below.\n")
    cat(paste0("$$y=",fxs[JJ],"$$\n$$y=",Lxs[JJ],"$$\n\n"))
    cat(paste0("1. Graph the given valid half of the parabola. Label it.\n2. Graph the extraneous half of the parabola. Label it.\n3. Graph the given line.\n
4. By inspecting the graph, list the possible solutions to  $",fxs[JJ],"=",Lxs[JJ],"$ that would be found algebraically.\n
5. By inspecting the graph, determine whether each possible solution is valid or extraneous.
\n\n"))
    par(pty="s",mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),ann=F,axes=F)
    
    for(i in -10:10){
        lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
        lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    }
    for(i in seq(-10,10,5)){
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
    }
    abline(h=0,lwd=2)
    abline(v=0,lwd=2)
    text(10,0,"x",adj=c(-0.2,-0.2))
    text(0,10,"y",adj=c(-0.2,-0.2))
    text(10,0,"10",adj=c(0.5,1.2),cex=0.7)
    text(0,10,"10",adj=c(1.1,0.5),cex=0.7)
}
doitB = function(JJ){
    cat(paste0("$$y=",fxs[JJ],"$$\n$$y=",Lxs[JJ],"$$\n\n"))
    
    cat("\\color{red}\n\nFor the radical equation, make an $x,y$ table; choose $x$ values to make the radicand 0, 1, 4, and 9.\n\n")
    
    cat(paste0("| $x$ | $y=",fxs[JJ],"$ |\n|:---:|:---:|\n"))
    x2 = (c(0,1,4,9)+hs[JJ])/bs[JJ]
    y2 = as[JJ]*c(0,1,2,3)+ks[JJ]
    cat(paste0("| ",x2," | ",y2," |",collapse="\n"))
    cat("\n\n")
    
    cat("To complete the extraneous half of the parabola, reflect those dots over the line of symmetry.\n\n")
    
    cat(paste0("For the point-slope linear equation, recognize that $x=",xps[JJ],"$ makes the expression in parentheses equal 0, which leads to $y=",yps[JJ],"$. From slope, the rise is ",abs(mtops[JJ])/abs(gcd(c(mtops[JJ],mbots[JJ])))*sign(mtops[JJ]*mbots[JJ])," and the run is ",abs(mbots[JJ])/abs(gcd(c(mtops[JJ],mbots[JJ]))),".\n\n"))
    
    par(pty="s",mar=c(0,0,0,0),mfrow=c(1,2))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),ann=F,axes=F)
    
    for(i in -10:10){
        lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
        lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    }
    for(i in seq(-10,10,5)){
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
    }
    abline(h=0,lwd=2)
    abline(v=0,lwd=2)
    text(10,0,"x",adj=c(-0.2,-0.2))
    text(0,10,"y",adj=c(-0.2,-0.2))
    text(10,0,"10",adj=c(0.5,1.2),cex=0.7)
    text(0,10,"10",adj=c(1.1,0.5),cex=0.7)
    
    if(params$showsol){
        xx = seq(hs[JJ]*sign(bs[JJ]),10*sign(bs[JJ]),0.01*sign(bs[JJ]))
        yy = -as[JJ]*sqrt(bs[JJ]*xx-hs[JJ])+ks[JJ]
        
        xx = xx[abs(yy)<=10]
        yy = yy[abs(yy)<=10]
        
        lines(xx,yy,col="grey",lwd=2,lty=2)
        
        x2 = (c(0,1,4,9,16)+hs[JJ])/bs[JJ]
        y2 = -as[JJ]*c(0,1,2,3,4)+ks[JJ]
        x2 = x2[abs(y2)<=10]
        y2 = y2[abs(y2)<=10]
        
        points(x2,y2,pch=19,col="grey")
        
        xx = seq(hs[JJ]*sign(bs[JJ]),10*sign(bs[JJ]),0.01*sign(bs[JJ]))
        yy = as[JJ]*sqrt(bs[JJ]*xx-hs[JJ])+ks[JJ]
        
        xx = xx[abs(yy)<=10]
        yy = yy[abs(yy)<=10]
        abline(h=ks[JJ],col="cyan",lty=2)
        
        lines(xx,yy,col="blue",lwd=2)
        
        x2 = (c(0,1,4,9,16)+hs[JJ])/bs[JJ]
        y2 = as[JJ]*c(0,1,2,3,4)+ks[JJ]
        x2 = x2[abs(y2)<=10]
        y2 = y2[abs(y2)<=10]
        
        points(x2,y2,pch=19,col="blue")
        
        xl = seq(-10,10,0.1)
        yl = mtops[JJ]/mbots[JJ]*(xl-xis[[JJ]][1])+yis[[JJ]][1]
        xl = xl[abs(yl)<=10]
        yl = yl[abs(yl)<=10]
        lines(xl,yl,col="red",lwd=2)
    
        points(xis[[JJ]],yis[[JJ]],pch=19,col="red")
        points(xps[JJ],yps[JJ],pch=19,col="red")
        plot(0,0,"n",axes=F,ann=F)
        legend("left",c("valid half of parabola","extraneous half of parabola","line","LOS"),col=c("blue","grey","red","cyan"),lwd=c(2,2,2,1),lty=c(1,2,1,2))
        }
    
    cat("\\color{red}")
    cat("\n\n")
    cat(paste0("$x=",xis[[JJ]],"$ is ",wrds[[JJ]]," solution.",collapse="\n\n"))
    cat("\n\n\\color{black}\n\n")
    cat("\\vfill\n\n")
}
```

### Practice Problem 1

```{r,echo=F,fig.dim=c(5,5),results='asis'}
doitA(1)
```

\newpage

### Solution to Practice Problem 1

```{r,echo=F,fig.dim=c(8,4),results='asis'}
doitB(1)
```

\newpage

### Practice Problem 2

```{r,echo=F,fig.dim=c(5,5),results='asis'}
doitA(2)
```

\newpage

### Solution to Practice Problem 2

```{r,echo=F,fig.dim=c(8,4),results='asis'}
doitB(2)
```

\newpage


### Practice Problem 3

```{r,echo=F,fig.dim=c(5,5),results='asis'}
doitA(3)
```

\newpage

### Solution to Practice Problem 3

```{r,echo=F,fig.dim=c(8,4),results='asis'}
doitB(3)
```

\newpage


### Practice Problem 4

```{r,echo=F,fig.dim=c(5,5),results='asis'}
doitA(4)
```

\newpage

### Solution to Practice Problem 4

```{r,echo=F,fig.dim=c(8,4),results='asis'}
doitB(4)
```

\newpage


### Practice Problem 5

```{r,echo=F,fig.dim=c(5,5),results='asis'}
doitA(5)
```

\newpage

### Solution to Practice Problem 5

```{r,echo=F,fig.dim=c(8,4),results='asis'}
doitB(5)
```

\newpage


