---
output: pdf_document
params:
    rseed: 1
    showsol: true
header-includes:
  - \usepackage{multicol}
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]
```

## `r bn`

```{r}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
```


### Two-step equations with a square-root and a basic arithmetic operation

The four basic arithmetic operations are addition, subtraction, multiplication, and division. In a two-step radical equation, we might need to undo the square-root before or after the other operation. There are eight possible combinations to consider.

\begin{align*}
\sqrt{x+1} &= 3 & \sqrt{x}+1 &= 5 \\
\text{square both sides} && \text{subtract 1 from both sides}\\
x+1 &= 9 & \sqrt{x} &= 4 \\
\text{subtract 1 from both sides} && \text{square both sides}\\
x &= 8 & x &= 16 \\\\\\\\
\sqrt{x-1} &= 4 & \sqrt{x}-4 &= 5 \\
\text{square both sides} && \text{add 4 to both sides} \\
x-1 &= 16 & \sqrt{x} &= 9 \\
\text{add 1 to both sides} && \text{square both sides}  \\
x &= 17 & x &= 81 \\\\\\\\
\sqrt{2x} &= 4 & 3\sqrt{x} &= 12 \\
\text{square both sides} && \text{divide both sides by 3}\\
2x &= 16 & \sqrt{x} &= 4 \\
\text{divide both sides by 2} && \text{square both sides}\\
x &= 8 & x &= 16 \\\\\\\\
\sqrt{\frac{x}{7}} &= 3 & \frac{\sqrt{x}}{3} &= 2 \\
\text{square both sides} && \text{multiply both sides by 3} \\
\frac{x}{7} &= 9 & \sqrt{x} &= 6 \\
\text{multiply both sides by 7} && \text{square both sides}  \\
x &= 63 & x &= 36 
\end{align*}



\newpage

```{r,echo=F}
qt = c(c(1,4,1,4,2,5,3,6),sample(1:6),sample(c(1:6,1:6,1:6)),sample(1:6,3))
eqs = character()
sols = character()
for(qti in qt){
    while(T){
        if(qti == 1){
            a = sample(1:9,1)*sample(c(-1,1),1)
            b = sample(2:10,1)
            eq = paste0("\\sqrt{x+",a,"}=",b)
            eq = gsub("+-","-",eq,fixed=T)
            x = b^2-a
        }
        if(qti == 2){
            b = sample(2:5,1)
            a = sample(c(2:5,10),1)*sample(c(-1,1),1)
            x = a*b^2
            eq = paste0("\\sqrt{\\frac{x}{",a,"}}=",b)
        }
        if(qti == 3){
            while(T){
                b = sample(2:12,1)
                a = sample(2:6,1)*sample(c(-1,1),1)
                x = b^2/a
                if(x%%1==0 && abs(a)!=abs(b)){break}
            }
            eq = paste0("\\sqrt{",a,"x}=",b)
        }
        if(qti == 4){
            while(T){
                a = sample(1:15,1)*sample(c(-1,1),1)
                b = sample(1:15,1)*sample(c(-1,1),1)
                if((b-a)>1 && (b-a)<13){
                    break
                    }
            }
            eq = paste0("\\sqrt{x}+",a,"=",b)
            eq = gsub("+-","-",eq,fixed=T)
            x = (b-a)^2
        }
        if(qti == 5){
            while(T){
                sab = sample(c(-1,1),1)
                a = sample(2:6,1)*sab
                b = sample(2:6,1)*sab
                sqrtx = a*b
                x = (a*b)^2
                if(sqrtx<17){break}
            }
            eq = paste0("\\frac{\\sqrt{x}}{",a,"}=",b)
        }
        if(qti == 6){
            while(T){
                sab = sample(c(-1,1),1)
                multer = sample(2:10,1)
                a = sample(2:6,1)*sab
                b = a*multer
                x = (b/a)^2
                if(x%%1==0 && abs(a)!=abs(b)){break}
            }
            eq = paste0(a,"\\sqrt{x}=",b)
        }
        if(!(eq %in% eqs)){break}
    }
    
    eqs = c(eqs,eq)
    sols = c(sols,paste0("x=",x))
}

```

Solve the following equations:


```{r,echo=F,results='asis'}

s = ""
for(i in 1:length(eqs)){
    s = paste0(s,eqs[i])
    if(i%%5==0 && i<length(eqs)){
        s = paste0(s," \\\\\n\\\\\n")
    } else {
        s = paste0(s," && ")
    }
}

cat(paste0("\\begin{align*}\n"))
cat(s)
cat(paste0("\n\\end{align*}"))

```

\vfill

```{r,echo=F,results='asis'}
s = ""
for(i in 1:length(sols)){
    s = paste0(s,sols[i])
    if(i%%5==0 && i<length(sols)){
        s = paste0(s," \\\\\n\\\\\n")
    } else {
        s = paste0(s," && ")
    }
}
cat("\\color{gray}\n")
cat("### Answers\n\n")
cat(paste0("\\begin{align*}\n"))
cat(s)
cat(paste0("\n\\end{align*}"))
cat("\n\\color{black}\n")
```



