---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}
```

## `r bn`

To factor cubic polynomials, you need to find factors that divide into the polynomial with a remainder of 0. Once one factor is known, there will still be a quadratic factor that might itself have factors. On this worksheet, each cubic polynomial can be factored fully to be expressed as $(x-a)(x-b)(x-c)$, where $a$, $b$, and $c$ are integers.

### Example

```{r,echo=F}

while(T){
    r = sample(c(-8:-1,1:8),3)
    a = 1
    b = -sum(r)
    c = r[1]*r[2]+r[2]*r[3]+r[1]*r[3]
    d = -r[1]*r[2]*r[3]
    A = a
    B = b+r[1]*a
    C = c+r[1]*(b+r[1]*a)
    if(min(abs(c(a,b,c,d,A,B,C)))>0){break}
}
```

Factor the polynomial $f(x)=`r pn(c(a,b,c,d),3:0)`$. Hint: one factor is $`r pn(c(1,-r[1]),1:0)`$. 

\vfill

\color{red}

### Example solution

Use synthetic division to divide $`r pn(c(a,b,c,d),3:0)`$ by $`r pn(c(1,-r[1]),1:0)`$.

\begin{center}
\begin{tabular}{c|c c c c}
          & `r a` & `r b`       & `r c`                 & `r d` \\
`r r[1]` &       & `r r[1]*a` & `r r[1]*(b+r[1]*a)`  & `r r[1]*(c+r[1]*(b+r[1]*a))` \\ \hline
          & `r a` & `r b+r[1]*a`& `r c+r[1]*(b+r[1]*a)` & `r d+r[1]*(c+r[1]*(b+r[1]*a))`
\end{tabular}
\end{center}

Notice the remainder is 0, as promised, because $`r pn(c(1,-r[1]),1:0)`$ is a factor. We can write the semi-factored form.

$$f(x)~=~(`r pn(c(1,-r[1]),1:0)`)(`r pn(c(a,b+r[1]*a,c+r[1]*(b+r[1]*a)),2:0)`)$$

Now we should try to further factor the quadratic factor into two linear binomials. You can use guess-and-check... looking for two numbers with a product of `r c+r[1]*(b+r[1]*a)` and a sum of `r b+r[1]*a`. If you struggle with that, you can also use the quadratic formula to find $x$-intercepts, and produce the factors from those.

Anyway,

$$f(x)~=~(`r pn(c(1,-r[1]),1:0)`)(`r pn(c(1,-r[2]),1:0)`)(`r pn(c(1,-r[3]),1:0)`)$$

Notice this function has $x$-intercepts at $x=`r r[1]`$ and $x=`r r[2]`$ and $x=`r r[3]`$.


\color{black}

\vfill

If the hint is not given, you will have to guess until finding a factor. You might find the [Rational Root Theorem](https://en.wikipedia.org/wiki/Rational_root_theorem) helpful (specifically the Integral Root Theorem).


\newpage



```{r,echo=F}
probs = c(paste0("Factor $",pn(c(a,b,c,d),3:0),"$."))
hints = c(paste0("Hint, $",pn(c(1,-r[1]),1:0),"$ is a factor."))
solutions = c(paste0("$(",pn(c(1,-r[1]),1:0),")(",pn(c(1,-r[2]),1:0),")(",pn(c(1,-r[3]),1:0),")$"))

while(length(probs)<=20){
    while(T){
        r = sample(c(-9:-1,1:9),3)
        a = 1
        b = -sum(r)
        c = r[1]*r[2]+r[2]*r[3]+r[1]*r[3]
        d = -r[1]*r[2]*r[3]
        A = a
        B = b+r[1]*a
        C = c+r[1]*(b+r[1]*a)
        prob = paste0("Factor $",pn(c(a,b,c,d),3:0),"$.")
        hint = paste0("Hint, $",pn(c(1,-r[1]),1:0),"$ is a factor.")
        solution = paste0("$(",pn(c(1,-r[1]),1:0),")(",pn(c(1,-r[2]),1:0),")(",pn(c(1,-r[3]),1:0),")$")
        if(min(abs(c(a,b,c,d,A,B,C)))>0 && !(prob %in% probs)){break}
    }
    probs = c(probs,prob)
    hints = c(hints,hint)
    solutions = c(solutions,solution)
}

```

```{r,echo=F,results="asis"}
for(i in 1:10){
    cat(paste0(i,". ",probs[i+1]," ",hints[i+1],"\n\n\\vfill\n\n"))
}

cat("\n\n\\newpage\n\n")

for(i in 11:20){
    cat(paste0(i,". ",probs[i+1],"\n\n\\vfill\n\n"))
}

cat("\n\n\\newpage\n\n")

for(i in 1:20){
    cat(paste0(i,". Factored form: ",solutions[i+1],"\n\n\\vfill\n\n"))
}
```












