```{r,echo=F}
options(scipen=999)
pn = function(c,d){
    d = d[c!=0]
    c = c[c!=0]
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    p = gsub("{","",p,fixed=T)
    p = gsub("}","",p,fixed=T)
    return(p)
}

x = -6:6
y = sample(x)
root = x[y==0]
f = pn(c(1,-root),1:0)

ach = character()

for(i in 1:length(x)){
    ach = c(ach,pn(c(1,x[i]),1:0))
}

al = paste0("* $",ach,"$",collapse="\n")

sol = paste0(1*(f==ach),collapse="")

df = data.frame(x,y)

```



Question
========

A high-degree polynomial, $p$, when graphed as $y=p(x)$, contains the points in the table below:

```{r,echo=F,warning=FALSE}
library(kableExtra)
kable_styling(kable(df),bootstrap_options = c("striped", "bordered"),full_width = FALSE)

```

Which of the following linear binomials is a factor of the polynomial?


Answerlist
--------

`r al`


Solution
========

See the [factor theorem](https://en.wikipedia.org/wiki/Factor_theorem).

If a polynomial has an $x$ intercept at $(a,0)$, then it has a factor $(x-a)$. In this case, there was an $x$ intercept at $`r root`$, so the known factor is $`r f`$.


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: factor_theorem_01