```{r,echo=FALSE}
nval = 1 #sample(0:2,1)
while(T){
    rs = sample(1:10,2)*sample(c(-1,1),2,T)
    qea = 1
    qeb = sum(-rs)
    qec = prod(-rs)
    psa = 1
    psb = qeb+sample(2:9,1)*sample(c(-1,1),1)
    if(psb%%2==1){
        psb = psb+sample(c(-1,1),1)
    }
    psc = (psb/2)^2
    
    rm = psb-qeb
    rb = psc-qec
    h = -rb/rm
    
    k = sample(1:9,1)*sample(c(-1,1),1)
    
    lm = sample(c(-1,1),1)
    lb = (psb/2)*sign(lm)+k
    
    ra = sample(c(-1,1),1)
    
    eq = paste0(k,"+{",ra,"}\\sqrt{",rm,"x+",rb,"}=",lm,"x+",lb)
    eq = gsub("+-","-",eq,fixed=T)
    eq = gsub("+{-1}","-",eq,fixed=T)
    eq = gsub("+{1}","+",eq,fixed=T)
    eq = gsub("=1x","=x",eq,fixed=T)
    eq = gsub("=-1x","=-x",eq,fixed=T)
    
    psol1 = min(rs)
    psol2 = max(rs)
    
    val1 = (k+ra*sqrt(rm*psol1+rb)==lm*psol1+lb)
    val2 = (k+ra*sqrt(rm*psol2+rb)==lm*psol2+lb)
    
    y1 = k+ra*sqrt(rm*psol1+rb)
    y2 = k+ra*sqrt(rm*psol2+rb)
    y3 = k-ra*sqrt(rm*psol1+rb)
    y4 = k-ra*sqrt(rm*psol2+rb)

    if(max(abs(c(y1,y2,y3,y4)))<=10 && k!=lb && abs(psb)<19 && abs(rm)>1 && abs(rm)<=10 && rb!=0 && lb!=0 && (1*val1+1*val2)==nval && abs(h)<10){break}
}

ach = -10:10
al = paste0("* ",ach,collapse="\n")
ach2 = c("an extraneous","a valid")
al2 = paste0("* ",ach2,collapse="\n")

sol1 = paste0(1*(ach==psol1),collapse="")
sol2 = paste0(1*(c(F,T)==val1),collapse="")
sol3 = paste0(1*(ach==psol2),collapse="")
sol4 = paste0(1*(c(F,T)==val2),collapse="")


    
```

Question
========

A transformed square-root function, $f(x)$, and line, $L(x)$, are parameterized and graphed below.

$$f(x)=a\sqrt{n(x-h)}+k$$

$$L(x)=mx+b$$
The parameters:
$$\begin{aligned}
a &= \text{vertical flip and stretch} \\
n &= \text{horizontal flip and stretch} \\
h &= \text{horizontal translation} \\
k &= \text{vertical translation} \\
m &= \text{slope} \\
b &= \text{y-intercept}
\end{aligned}$$

```{r,echo=F,fig.dim=c(10,5)}
par(mar=c(4,4,0,0),mfrow=c(1,2),pty="s")
xtnt = 10
plot(0,0,"n",xlim=c(-xtnt,xtnt),ylim=c(-xtnt,xtnt),xlab="x",ylab="y")
for(i in -xtnt:xtnt){
    lines(c(-xtnt,xtnt),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-xtnt,xtnt),col="grey",lwd=0.5)
}
for(i in -xtnt:xtnt){
    if(i%%5==0){
        lines(c(-xtnt,xtnt),c(i,i),col="darkgrey",lwd=1)
        lines(c(i,i),c(-xtnt,xtnt),col="darkgrey",lwd=1)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
xf = seq(h,h+40*sign(rm),length.out=1000)
yf = k+ra*sqrt(rm*xf+rb)
xL = seq(-30,30,10)
yL = lm*xL+lb
xg = seq(h,h+40*sign(rm),length.out=1000)
yg = k-ra*sqrt(rm*xg+rb)
lines(xf,yf,col="red",lwd=2)
lines(xL,yL,col="blue",lwd=2)
lines(xg,yg,col="grey",lwd=2,lty=2)
points(psol1,lm*psol1+lb,col="purple",pch=19)
points(psol2,lm*psol2+lb,col="purple",pch=19)

plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("topleft",c(TeX(paste0("$y=f(x)$")),
                TeX(paste0("$y=L(x)$")),
                TeX(paste0("$y=g(x)$"))),
       col=c("red","blue","grey"),
       lty=c(1,1,2),
       lwd=c(2,2,2))

```
\

Notice, another transformed square-root function, $g(x)$, is also graphed above. It represents the other half of the parabola.

$$g(x)=-a\sqrt{n(x-h)}+k$$

Now, consider algebraically solving for values of $x_{i}$ that satisfy the equation $f(x_i)=L(x_i)$. Let $x_1$ and $x_2$ represent the two possible solutions such that $x_1<x_2$. Find both possible solutions (by inspecting the graph) and determine whether each is valid or extraneous.

* $x_1=$ ##ANSWER1##
* $x_1$ is ##ANSWER2## solution.
* $x_2=$ ##ANSWER3##
* $x_2$ is ##ANSWER4## solution.

Answerlist
--------

`r al`
`r al2`
`r al`
`r al2`

Solution
========

Just read off the two $x$ values of the two purple points. The point further left is at point $(x_1,L(x_1))$ and the point further right is at point $(x_2,L(x_2))$. That way $x_1<x_2$, as required in the problem statement.

If the purple dot is on the red $y=f(x)$ curve, then the possible solution is a valid solution. If the purple dot is on the dashed-grey $y=g(x)$ curve, then the possible solution is extraneous. Lastly, if the purple dot is at the vertex of the parabol, then the solution is also valid.

So, in this case:

$$\begin{aligned}
x_1 &= `r psol1` \\
x_1 &\text{ is `r ach2[val1+1]` solution} \\
x_2 &= `r psol2` \\
x_2 &\text{ is `r ach2[val2+1]` solution}
\end{aligned}$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: w_2val_1val_0val