```{r,echo=FALSE}
options(scipen=99)
library(numbers)
library(MASS)
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

fsimp = function(top,bot){
    gg = abs(gcd(c(top,bot)))
    top = round(abs(top)/gg*sign(top*bot))
    bot = round(abs(mbot)/gg)
    if(bot==1){
        return(top)
    } else {
        return(paste0("\\frac{",top,"}{",bot,"}"))
    }
}

# y = a*sqrt(s(x-h))+k

x0s = c(1,4,9,16)
y0s = c(1,2,3,4)
x0e = c(1,4,9,16)
y0e = c(-1,-2,-3,-4)
qt = 2 #sample(1:3,1)

while(T){
    a = sample(2:4,1)*sample(c(-1,1),1)
    h = sample(1:9,1)*sample(c(-1,1),1)
    k = sample(1:9,1)*sample(c(-1,1),1)
    s = sample(c(-1,1),1)
    x1s = x0s*s+h
    y1s = y0s*a+k
    x1e = x0e*s+h
    y1e = y0e*a+k
    # if(qt==1){ #Two valid real solutions
    #     ns = sample(1:length(x1s),2)
    #     xi = x1s[ns]
    #     yi = y1s[ns]
    # }
    if(qt==2){ #One valid, one extraneous
        while(T){
            ns = sample(1:length(x1s),1)
            ne = sample(1:length(x1e),1)
            xis = x1s[ns]
            yis = y1s[ns]
            xie = x1e[ne]
            yie = y1e[ne]
            if(xis != xie){
                xi = c(xis,xie)
                yi = c(yis,yie)
                nn = sample(1:2)
                xi = xi[nn]
                yi = yi[nn]
                break
            }
        }
    }
    # if(qt==3){ #Two extraneous
    #     ns = sample(1:length(x1e),2)
    #     xi = x1e[ns]
    #     yi = y1e[ns]
    # }
    mtop = diff(yi)
    mbot = diff(xi)
    gg = abs(gcd(c(mtop,mbot)))
    mtop = round(abs(mtop)/gg*sign(mtop*mbot))
    mbot = round(abs(mbot)/gg)
    m = fsimp(mtop,mbot)
    btop = (yi[1]*mbot-mtop*xi[1])
    bbot = mbot
    gg = abs(gcd(c(btop,bbot)))
    b = fsimp(btop,bbot)
    if(max(abs(xi))<13 && max(abs(yi))<15 && min(abs(xi))>0 && mbot!=0){break}
}

eq1 = paste0(k,"+{",a,"}\\sqrt{{",s,"}(x+",-h,")}")
eq1 = gsub("{1}","",eq1,fixed=T)
eq1 = gsub("{-1}","-",eq1,fixed=T)
eq1 = gsub("+{-","-{",eq1,fixed=T)
eq1 = gsub("+-","-",eq1,fixed=T)
if(s==1){
    eq1 = paste0(k,"+{",a,"}\\sqrt{x+",-h,"}")
    eq1 = gsub("{1}","",eq1,fixed=T)
    eq1 = gsub("{-1}","-",eq1,fixed=T)
    eq1 = gsub("+{-","-{",eq1,fixed=T)
    eq1 = gsub("+-","-",eq1,fixed=T)
}

eq2 = paste0(k,"+{",-a,"}\\sqrt{{",s,"}(x+",-h,")}")
eq2 = gsub("{1}","",eq2,fixed=T)
eq2 = gsub("{-1}","-",eq2,fixed=T)
eq2 = gsub("+{-","-{",eq2,fixed=T)
eq2 = gsub("+-","-",eq2,fixed=T)
if(s==1){
    eq2 = paste0(k,"+{",-a,"}\\sqrt{x+",-h,"}")
    eq2 = gsub("{1}","",eq2,fixed=T)
    eq2 = gsub("{-1}","-",eq2,fixed=T)
    eq2 = gsub("+{-","-{",eq2,fixed=T)
    eq2 = gsub("+-","-",eq2,fixed=T)
}

## y = m(x-x0)+y0
## y = mx + y0-m*x0
## b = (y0*mbot-mtop*x0)/mbot

leq = paste0("[",fsimp(mtop,mbot),"]x+",fsimp(btop,bbot))
leq = gsub("[1]","",leq,fixed=T)
leq = gsub("[-1]","-",leq,fixed=T)
leq = gsub("[","",leq,fixed=T)
leq = gsub("]","",leq,fixed=T)
leq = gsub("+-","-",leq,fixed=T)
leq = gsub("+\\frac{-","-\\frac{",leq,fixed=T)
leq = gsub("+0","",leq,fixed=T)
leq = gsub("-0","",leq,fixed=T)


ach = (-12):12
al = paste0("* ",ach,collapse="\n")

if(round(k+a*sqrt(s*xi[1]-h),3) == round(mtop/mbot*xi[1]+btop/bbot,3)){
    val1 = 1
    xv = xi[1]
    xe = xi[2]
} else {
    val1 = 0
    xv = xi[2]
    xe = xi[1]
}

# assumes qt==2 for into problem

if(val1){
    sol1 = paste0(1*(ach==xi[1]),collapse="")
    sol2 = paste0(1*(ach==xi[2]),collapse="")
} else {
    sol1 = paste0(1*(ach==xi[2]),collapse="")
    sol2 = paste0(1*(ach==xi[1]),collapse="")
}

```

Question
========


The equation below has one extraneous solution and one valid solution.

$$`r eq1`~=~`r leq`$$

We can find both using [Desmos](https://www.desmos.com/calculator). To find the valid solution, find the intersection of the following two curves:

$$f(x)=`r eq1`$$
$$L(x)=`r leq`$$

You should see half a parabola facing sideways and a line. Click where the two paths cross. The $x$ value is the valid solution.

The extraneous solution also has a geometric interpretation! We need to complete the parabola by plotting the following curve:

$$g(x)=`r eq2`$$

You should see the line crosses this second half of the parabola. Click on the intersection. The $x$ value is the extraneous solution.

* Valid: ##ANSWER1##
* Extraneous: ##ANSWER2##

Answerlist
--------

`r al`
`r al`


Solution
========

The valid solution is $x=`r xv`$. The extraneous solution is $x=`r xe`$. Below is a sketch that should resemble your Desmos graph.

```{r,echo=F,fig.dim=c(8,4)}
par(pty="s",mfrow=c(1,2),mar=c(5,5,1,1))
xr = seq(h,h+40*s,length.out=1000)
yr = a*sqrt(s*(xr-h))+k
yr2 = -a*sqrt(s*(xr-h))+k
xl = seq(-20,20,1)
yl = mtop*xl/mbot+btop/bbot
plot(0,0,"n",xlim=c(-20,20),ylim=c(-20,20),xlab="x",ylab="y")
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(xr,yr,col="red")
lines(xr,yr2,col="grey",lty=2)
lines(xl,yl,col="blue")
points(xi,yi,pch=19,col="purple")
plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("topleft",c(TeX(paste0("$y=f(x)$")),
                TeX(paste0("$y=L(x)$")),
                TeX(paste0("$y=g(x)$"))),
       col=c("red","blue","grey"),
       lty=c(1,1,2),
       lwd=c(2,2,2))
```
\


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: extraneous_easy_graphs