```{r,echo=FALSE}

nval = 1 #sample(0:2,1)

# 0 = (x-r)(x-s)
# 0 = x^2+(-r-s)x+rs
# 0 = x^2+2Px+P^2+(-r-s-2P)x+(rs-P^2)
# 0 = x^2+2Px+P^2+(-r-s-2P)x+(rs-P^2)
# (r+s+2P)x + (P^2-rs) = x^2+2Px+P^2
# sqrt( (r+s+2P)x + (P^2-rs) ) = x+P
# sqrt( (r+s+2P)x + (P^2-rs) ) = x+P or sqrt( (r+s+2P)x + (P^2-rs) ) = -x-P
# a*sqrt( (r+s+2P)x + (P^2-rs) ) = ax+aP or asqrt( (r+s+2P)x + (P^2-rs) ) = -ax-aP
# ehhhh a=1
# sqrt( (r+s+2P)x + (P^2-rs) )+k = vx+vP+k
# h = (rs-P^2)/(r+s+2*P)

# P = sample(1:9,1)

while(T){
    rs = sample(1:10,2)*sample(c(-1,1),2,T)
    a = sample(c(-2,2),1)
    r = rs[1]
    s = rs[2]
    P = sample(1:9,1)
    v = sample(c(-1,1),1)
    k = sample(2:8,1)*sample(c(-1,1),1)
    h = (r*s-P^2)/(r+s+2*P)
    fr = k+a*sqrt((r+s+2*P)*r+P^2-r*s)
    fs = k+a*sqrt((r+s+2*P)*s+P^2-r*s)
    gr = k-a*sqrt((r+s+2*P)*r+P^2-r*s)
    gs = k-a*sqrt((r+s+2*P)*s+P^2-r*s)
    Lr = v*a*r+v*a*P+k
    Ls = v*a*s+v*a*P+k
    if(fr==Lr){
        valr = T
    } else {
        valr = F
    }
    if(fs==Ls){
        vals = T
    } else {
        vals = F
    }
    if(abs(r+s+2*P)>1 && (v*a*P+k)!=0 && abs(k)!=abs(P^2-r*s) && max(abs(c(fr,fs,gr,gs)))<=20 && sum(1*valr+1*vals)==nval && h!=r && h!=s && (v*a*P+k)!=0){break}
}


f = paste0(k,"+",a,"\\sqrt{",r+s+2*P,"x+",P^2-r*s,"}",collapse="")
f = gsub("+-","-",f,fixed=T)
L = paste0(v*a,"x+",v*a*P+k,collapse="")
L = gsub("+-","-",L,fixed=T)
L = gsub("-1x","-x",L,fixed=T)
L = gsub("1x","x",L,fixed=T)
g = paste0(k,"+",-a,"\\sqrt{",r+s+2*P,"x+",P^2-r*s,"}",collapse="")
g = gsub("+-","-",g,fixed=T)

ach = -10:10
al = paste0("* ",ach,collapse="\n")
ach2 = c("an extraneous","a valid")
al2 = paste0("* ",ach2,collapse="\n")



if(fr==Lr){
    sol1 = paste0(1*(ach==r),collapse="")
    sol2 = paste0(1*(ach==s),collapse="")
    sv = r
    se = s
} else {
    sol1 = paste0(1*(ach==s),collapse="")
    sol2 = paste0(1*(ach==r),collapse="")
    sv = s
    se = r
}

# sol1 = paste0(1*(ach==psol1),collapse="")
# sol2 = paste0(1*(c(F,T)==val1),collapse="")
# sol3 = paste0(1*(ach==psol2),collapse="")
# sol4 = paste0(1*(c(F,T)==val2),collapse="")


```

Question
========

The equation below has one extraneous solution and one valid solution.

$$`r f`~=~`r L`$$

We can find both using [Desmos](https://www.desmos.com/calculator). To find the valid solution, find the intersection of the following two curves:

$$f(x)=`r f`$$
$$L(x)=`r L`$$

You should see half a parabola facing sideways and a line. Click where the two curves cross. The $x$ value is the valid solution.

The extraneous solution also has a geometric interpretation! We need to complete the parabola by plotting the following curve:

$$g(x)=`r g`$$

You should see the line crosses this second half of the parabola. Click on the intersection. The $x$ value is the extraneous solution.

* Valid: ##ANSWER1##
* Extraneous: ##ANSWER2##

Answerlist
--------

`r al`
`r al`

Solution
========

The valid solution is $x=`r sv`$, and the extraneous solution is $x=`r se`$. Your Desmos graph should look somewhat similar to the graph below:

```{r,echo=F,fig.dim=c(8,4)}

xlow = min(c(h,r,s))
xhigh = max(c(h,r,s))
xmid = mean(c(xlow,xhigh))
xwid = xhigh-xmid
ylow = min(c(fr,fs,gr,gs))
yhigh = max(c(fr,fs,gr,gs))
ymid = mean(c(ylow,yhigh))
ywid = yhigh-ymid

par(mfrow=c(1,2),mar=c(5,5,1,1))
xf = seq(h,h+3*xwid*sign(r-h),length.out=1000)
yf = k+a*sqrt((r+s+2*P)*xf+P^2-r*s)
xg = xf
yg = k-a*sqrt((r+s+2*P)*xf+P^2-r*s)
xl = seq(xmid-2*xwid,xmid+2*xwid,length.out=5)
yl = v*a*xl+v*a*P+k
sf = 1.2
plot(0,0,"n",xlim=c(xmid-sf*xwid,xmid+sf*xwid),ylim=c(ymid-sf*ywid,ymid+sf*ywid),xlab="x",ylab="y")
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(xf,yf,col="red")
lines(xg,yg,col="grey",lty=2)
lines(xl,yl,col="blue")
points(c(r,s),c(Lr,Ls),pch=19,col="purple")
plot(0,0,"n",axes=F,ann=F)
library(latex2exp)
legend("topleft",c(TeX(paste0("$y=f(x)$")),
                TeX(paste0("$y=L(x)$")),
                TeX(paste0("$y=g(x)$"))),
       col=c("red","blue","grey"),
       lty=c(1,1,2),
       lwd=c(2,2,2))
```
\


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: zzz