```{r,echo=FALSE}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

fsimp = function(top,bot){
    gg = abs(gcd(c(top,bot)))
    top = round(abs(top)/gg*sign(top*bot))
    bot = round(abs(mbot)/gg)
    if(bot==1){
        return(top)
    } else {
        return(paste0("\\frac{",top,"}{",bot,"}"))
    }
}

xpar = c(0,1,4,9)
ypar = c(0,1,2,3)
xext = c(1,4,9)
yext = c(-1,-2,-3)

# horizontal shift before possible reflection

# y = a*sqrt(bx-h)+k

h = sample(c(-9:-1,1),1)
a = sample(c(-3,-2,-1,1,2,3),1)
k = sample(c(((-10+3*abs(a)):-1),(1:(10-3*abs(a)))),1)
b = sample(c(-1,1),1)


xc = (xpar+h)/b
yc = a*ypar+k
xd = (xext+h)/b
yd = k+a*yext

nval = 1 #sample(0:2,1)

if(nval==0){
    ii = sample(1:length(xd),2)
    xi = xd[ii]
    yi = yd[ii]
    isval = c(F,F)
    wrd = c("an extraneous","an extraneous")
}
if(nval==1){
    while(T){
        ic = sample(1:length(xc),1)
        id = sample(1:length(xd),1)
        xic = xc[ic]
        yic = yc[ic]
        xid = xd[id]
        yid = yd[id]
        ii = sample(1:2)
        xi = c(xic,xid)[ii]
        yi = c(yic,yid)[ii]
        isval = c(T,F)[ii]
        wrd = c("a valid","an extraneous")[ii]
        if(xic!=xid){break}
    }
}
if(nval==2){
    ii = sample(1:length(xc),2)
    xi = xc[ii]
    yi = yc[ii]
    isval = c(T,T)
    wrd = c("a valid","a valid")
}

mtop = diff(yi)
mbot = diff(xi)
mf = fsimp(mtop,mbot)


while(T){
    xp = sample(-10:10,1)
    yp = mtop*(xp-xi[1])/mbot+yi[1]
    if(abs(yp)<=10 && abs(yp)%%1==0 && yp!=yi[1] && yp!=yi[2]){break}
}

if(b==-1){
    fx = paste0(k,"+",a,"\\sqrt{-x+",-h,"}")
} else {
    fx = paste0(k,"+",a,"\\sqrt{x+",-h,"}")
}
Lx = paste0(mf,"(x+",-xp,")+",yp)
fx = gsub("+-","-",fx,fixed=T)
Lx = gsub("+-","-",Lx,fixed=T)
Lx = gsub("=1(","=(",Lx,fixed=T)
Lx = gsub("=-1(","=-(",Lx,fixed=T)

ach = -10:10
ava = c("an extraneous","a valid")

al1 = paste0("* ",ach,collapse="\n")
al2 = paste0("* ",ava,collapse="\n")

minxii = which(xi==min(xi))
maxxii = which(xi==max(xi))

sol1 = paste0(1*(ach==xi[minxii]),collapse="")
sol2 = paste0(1*(c(F,T)==isval[minxii]),collapse="")
sol3 = paste0(1*(ach==xi[maxxii]),collapse="")
sol4 = paste0(1*(c(F,T)==isval[maxxii]),collapse="")

```

Question
========

A transformed square-root function, $y=f(x)$, is graphed below. A linear function, $y=L(x)$, is not shown, but it goes through point $(`r xp`,`r yp`)$ and has a slope of $`r mf`$.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s",mar=c(4,4,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="y")

for(i in -10:10){
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
yy = a*sqrt(b*xx-h)+k

xx = xx[abs(yy)<=10]
yy = yy[abs(yy)<=10]


lines(xx,yy,col="blue",lwd=2)

x2 = (c(0,1,4,9,16)+h)/b
y2 = a*c(0,1,2,3,4)+k
x2 = x2[abs(y2)<=10]
y2 = y2[abs(y2)<=10]

points(x2,y2,pch=19,col="blue")

```
\

If standard algebraic steps were used to find $x$ values that satisfy equation $f(x)=L(x)$, two possible solutions $x_1$ and $x_2$ will be found such that $x_1<x_2$. Determine the possible solutions, and check if each is valid or extraneous.

* $x_1=$ ##ANSWER1##
* $x_1$ is ##ANSWER2## solution
* $x_2=$ ##ANSWER3##
* $x_2$ is ##ANSWER4## solution

Answerlist
--------

`r al1`
`r al2`
`r al1`
`r al2`


Solution
========

You should be able to complete the picture. Use symmetry to complete the parabola, and use the slope to extend the line.

```{r,echo=F,fig.dim=c(5,5)}
par(pty="s",mar=c(4,4,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),xlab="x",ylab="y")

for(i in -10:10){
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)

xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
yy = a*sqrt(b*xx-h)+k

xx = xx[abs(yy)<=10]
yy = yy[abs(yy)<=10]


lines(xx,yy,col="blue",lwd=2)

x2 = (c(0,1,4,9,16)+h)/b
y2 = a*c(0,1,2,3,4)+k
x2 = x2[abs(y2)<=10]
y2 = y2[abs(y2)<=10]

# points(x2,y2,pch=19,col="blue")

xl = seq(-10,10,0.1)
yl = mtop/mbot*(xl-xi[1])+yi[1]
xl = xl[abs(yl)<=10]
yl = yl[abs(yl)<=10]

lines(xl,yl,col="red",lwd=2)

xx = seq(h*sign(b),10*sign(b),0.01*sign(b))
yy = -a*sqrt(b*xx-h)+k

xx = xx[abs(yy)<=10]
yy = yy[abs(yy)<=10]

lines(xx,yy,col="grey",lwd=2,lty=2)

points(xi,yi,pch=19,col="red")

```
\

The intersection further left is at $x_1=`r xi[minxii]`$ and it is `r wrd[minxii]` solution.

The intersection further right is at $x_2=`r xi[maxxii]`$ and it is `r wrd[maxxii]` solution.

I'll also mention that you could solve approach this problem algebraically. First, examine curve $y=f(x)$ to find the transformations. From those transformations, you can write an algebraic definition of $f(x)$.

$$f(x)=`r fx`$$

To write an algebraic definition of $L(x)$, use point-slope form.

$$L(x)=`r Lx`$$

Then set up the equation to solve.

$$`r fx`=`r Lx`$$

By doing the algebraic manipulations, you'll find two possible solutions: $x_1=`r xi[minxii]`$ and $x_2=`r xi[maxxii]`$. If you test each in the equation, you'll find that $x=`r xi[minxii]`$ is `r wrd[minxii]` solution, and $x=`r xi[maxxii]`$ is `r wrd[maxxii]` solution.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: x_find_valext012_graph