```{r,echo=FALSE}
options(scipen=999)
cn = function(a,b){
  cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
  cn = gsub("0+0i","0",cn,fixed=TRUE)
  cn = gsub("+1i","+i",cn,fixed=TRUE)
  cn = gsub("-1i","-i",cn,fixed=TRUE)
  cn = gsub("+0i","",cn,fixed=TRUE)
  cn = gsub("-0i","",cn,fixed=TRUE)
  if(length(cn)>1 && substr(cn, start = 1, stop = 2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
  if(length(cn)>1 && substr(cn, start = 1, stop = 2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
  return(cn)
}

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

while(T){
    abcrq = sample(2:9,5)*sample(c(-1,1),5,T)
    a = abcrq[1]
    b = abcrq[2]
    c = abcrq[3]
    r = abcrq[4]
    q = abcrq[5]
    R = a*r^2-a*q^2+b*r+c
    Q = 2*a*r*q+b*q
    M = sqrt(R^2+Q^2)
    if(min(abs(c(R,Q)))>0 && M<1000){break}
}


```

Question
========

In [complex analysis](https://en.wikipedia.org/wiki/Complex_analysis), complex numbers are used as inputs and outputs of various functions.

Consider the function $f$ defined below.

$$f(x)~=~`r pn(c(a,b,c),2:0)`$$

Evaluate $\Big|f(`r cn(r,q)`)\Big|$. In other words, find the [modulus](https://en.wikipedia.org/wiki/Absolute_value#Complex_numbers) of the output of $f$ when the input is $`r cn(r,q)`$.

*The tolerance is $\pm 0.1$.*


Solution
========

```{r,echo=F}
cn1 = cn(r,q)
exp1 = paste0(a,"(",cn1,")^2+",b,"(",cn1,")+",c,collapse="")
exp1 = gsub("+-","-",exp1,fixed=T)
```

$$f(`r cn(r,q)`) ~=~ `r exp1`$$

The most challenging part is squaring the complex input. Remember, raising to the power of 2 means multiplying by itself. When we multiply two complex numbers, we basically "FOIL".


```{r,echo=F}
exp2 = paste0(r^2,"+",r*q,"i+",r*q,"i+",q^2,"i^2")
exp2 = gsub("+-","-",exp2,fixed=T)
exp3 = paste0(r^2,"+",r*q,"i+",r*q,"i+",-q^2)
exp3 = gsub("+-","-",exp3,fixed=T)

exp4 = paste0(r^2-q^2,"+",2*r*q,"i")
exp4 = gsub("+-","-",exp4,fixed=T)
cn2 = cn(r^2-q^2,2*r*q)
r2 = r^2-q^2
q2 = 2*r*q
```

$$(`r cn1`)^2~\equiv~(`r cn1`)(`r cn1`)~\equiv~`r exp2`$$

Remember, $i^2=-1$.


$$(`r cn1`)^2~\equiv~`r exp3`$$

Combine like terms.


$$(`r cn1`)^2~\equiv~`r exp4`$$

So, now return to the full expression, replacing $(`r cn1`)^2$ with $`r exp4`$.

```{r,echo=F}
exp5 = paste0(a,"(",cn2,")+",b,"(",cn1,")+",c,collapse="")
exp5 = gsub("+-","-",exp5,fixed=T)
exp6 = paste0(a*r2,"+",a*q2,"i+",b*r,"+",b*q,"i+",c)
exp6 = gsub("+-","-",exp6,fixed=T)
```

$$f(`r cn(r,q)`) ~=~ `r exp5`$$

Distribute.

$$f(`r cn(r,q)`) ~=~ `r exp6`$$

Combine like terms.


$$f(`r cn(r,q)`) ~=~ `r cn(R,Q)`$$

Use the formula for the modulus.

$$\sqrt{(`r R`)^2+(`r Q`)^2} ~=~ `r M`$$

Thus, the correct answer is `r M`.

Meta-information
============
extype: num
exsolution: `r M`
exname: complex_analysis
extol: 0.1