---
output: pdf_document
params:
    rseed: 0
    showsol: true
header-includes:
  - \usepackage{multicol}
---


Name: \vspace{5pt} \hrule

# Final Practice 01

1. Solve the linear equation.
$$20=4(x+3)$$

\vfill

2. Let function $f$ be defined by the algebraic expression below:
$$f(x)=\frac{x}{5}+9$$
Evaluate $f(-15)$.

\vfill

3. Let function $f$ be defined by the algebraic expression below: $$f(x)=\sqrt[5]{x-4}+3$$
Find the inverse of function $f$.

\vfill

4. When a relation is displayed as a curve on an $x,y$ plane:
   a. What is needed for $y$ to be a function of $x$?
   b. What is needed for $x$ to be a function of $y$?
   c. What is needed for the curve to represent a one-to-one function?

\vfill

5. Solve the radical equation: $$7-\sqrt{x+10}=4$$

\vfill

\newpage

6. Solve the equation.
$$(8x-3)(5x+6)=0$$

\vfill

7. State the quadratic formula.

\vfill

8. Factor the quadratic expression.
$$x^2-10x+9$$

\vfill

9. Factor the quadratic expression.
$$3x^2+x-10$$

\vfill


10. Expand the quadratic expression. $(x+6)(x+7)$

\vfill

11. Rationalize the denominator. Remember, $i=\sqrt{-1}$. $$\frac{3-2i}{5-9i}$$

\vfill

12. Expand the quadratic polynomial with complex roots.
$$(x-(5+2i))(x-(5-2i))$$

\vfill

13. Solve the quadratic equation. $$x^2-6x+13=0$$

\vfill

\newpage

The questions on this page refer to this graph.

```{r,echo=F,fig.dim=c(5,5),fig.align='center'}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
for(i in -10:10){
  lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.6)
  lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.6)
}
for(i in c(-10,-5,5,10)){
  lines(c(i,i),c(-10,10),col="grey",lwd=0.9)
  lines(c(-10,10),c(i,i),col="grey",lwd=0.9)
}
abline(h=0)
abline(v=0)
text(10,0,"x",adj=c(-0.3,-0.3))
text(0,10,"y",adj=c(-0.3,-0.3))
text(10,0,"10",adj=c(0.5,1.5))
text(0,10,"10",adj=c(1.5,0.5))

x1 = seq(-12,12,0.1)
y1 = x1+3

x2 = seq(-3,12,0.01)
y2 = -sqrt(x2+3)+2

lines(x1,y1,col="red")
lines(x2,y2,col="blue")

legend("topleft",c("y=f(x)","y=g(x)"),col=c("red","blue"),lwd=c(1,1))

```

14. Write an equation in slope-intercept form for $f(x)$.

\vfill

15. Write an equation for $g(x)$.

\vfill

16. Find the valid solution to $f(x)=g(x)$.

\vfill

17. Find the extraneous solution to $f(x)=g(x)$.

\vfill


\newpage

18. Remember $i=\sqrt{-1}$. Simplify $i^{82}$.

\vfill

19. Expand the binomial power expression.
$$(3x+2)^4$$

\vfill


20. Expand the product.
$$(x^4+2x+3)(x^3-6)$$

\vfill

21. Use polynomial division to express as a polynomial plus the remainder over the divisor.
$$\frac{2x^3-13x^2+22x+2}{x-3}$$


\vfill

22. If $f(x)$ is a polynomial and $\frac{f(x)}{x-5}=2x^5-3x^3+2x+8$ for all values of $x$ (except $x=5$), then the remainder theorem promises that $f(5)$ equals what and why?

\vfill

23. What is the $y$ intercept of the polynomial function $y=5x^3-2x^2+3x-8$?

\vfill

24. Factor the polynomial $x^3-2x^2-11x+12$.

\vfill

25. Simplify the radical $\sqrt{75}$.

\vfill

\newpage


26. A polynomial function is plotted below.
    ```{r,echo=F,fig.dim=c(5,1.5),fig.align='center'}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-1,1),axes=F,ann=F)
    xx = seq(-10,10,0.01)
    yy = -(xx+7)^2*(xx+2)*(xx-5)^2
    yy = yy/max(abs(yy[abs(xx+1)<=6]))
    abline(v=0)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-0.1,0.1),col="grey")
      text(i,-0.3,i,col="grey")
    }
    abline(h=0)
    lines(xx,yy,col="blue",lwd=2)
    ```
    Express the polynomial in **factored** form. Please assume that in standard form the leading coefficient would be 1 or -1.

\vfill

27. A polynomial function is plotted below.
    ```{r,echo=F,fig.dim=c(5,1.5),fig.align='center'}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-1,1),axes=F,ann=F)
    xx = seq(-10,10,0.01)
    yy = (xx+3)*(xx-5)^2
    yy = yy/max(abs(yy[abs(xx-1)<=4]))
    abline(v=0)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-0.1,0.1),col="grey")
      text(i,-0.3,i,col="grey")
    }
    abline(h=0)
    lines(xx,yy,col="blue",lwd=2)
    ```
    Express the polynomial in **expanded** form. Please assume that in standard form the leading coefficient would be 1 or -1.

\vfill


28. A polynomial is plotted below.
    ```{r,echo=F,fig.dim=c(5,1.5),fig.align='center'}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(0,2),axes=F,ann=F)
    xx = seq(-10,10,0.01)
    yy = (xx+3)*(xx)^2*(xx-5)
    yy = yy/max(abs(yy[abs(xx-1)<=4]))+1
    abline(v=0)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-0.1,0.1),col="grey")
      text(i,-0.3,i,col="grey")
    }
    abline(h=0)
    lines(xx,yy,col="blue",lwd=2)
    ```
    What is the minimum degree of the polynomial?

\vfill

\newpage

29. The discriminant, $b^2-4ac$, is the expression in the radicand in the quadratic formula. Describe the implications of the discriminant being less than 0, more than 0, or equal to 0.

\vfill

30. Express $\left(x+1\right)^{2}-3\left(x+1\right)-10$ in factored form.

\vfill

31. Check if $x-2$ is a factor of $x^3-x^2-10x-8$ by using synthetic division.

\vfill

32. Find solution set to $\sqrt{2x+8}-3=x+1$. Express your answer as a set (listed in curly braces).

\vfill

33. The graph of $y=p(x)$ below shows a polynomial.

    ```{r,echo=F,fig.dim=c(4,4),fig.align="center"}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
      lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    }
    for(i in c(-10,-5,5,10)){
      lines(c(i,i),c(-10,10),col="grey",lwd=1.2)
      lines(c(-10,10),c(i,i),col="grey",lwd=1.2)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
    x = seq(-10,10,0.01)
    y = x*(x+2)*(x-3)*(x-6)*(x+4)
    n = 4
    a = -3
    y = y/y[x==n]*a
    lines(x,y,col="blue",lwd=2)
    text(10,0,"10",adj=c(0.5,1.3))
    text(0,10,"10",adj=c(1.3,0.5))
    text(10,0,"x",adj=c(-0.5,-0.5))
    text(0,10,"y",adj=c(-0.5,-0.5))
    ```
    
    What is the remainder when $p(x)$ is divided by $x-4$?

\vfill

\newpage

34. Consider the function graphed below.

    ```{r,echo=F,fig.dim=c(3,3),fig.align="center"}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
      lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    }
    for(i in c(-10,-5,5,10)){
      lines(c(i,i),c(-10,10),col="grey",lwd=1.2)
      lines(c(-10,10),c(i,i),col="grey",lwd=1.2)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
    x = seq(-10,10,0.01)
    y = 10/x
    
    lines(x,y,col="blue",lwd=2)
    
    text(10,0,"10",adj=c(0.5,1.3),cex=0.8)
    text(0,10,"10",adj=c(1.3,0.5),cex=0.8)
    text(10,0,"x",adj=c(-0.4,-0.4),cex=0.8)
    text(0,10,"y",adj=c(-0.4,-0.4),cex=0.8)
    
    ```
    
    a. Is the function even?
    b. Is the function odd?
    c. Is the function one-to-one?

\vfill

35. Consider the function graphed below.

    ```{r,echo=F,fig.dim=c(3,3),fig.align="center"}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
      lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    }
    for(i in c(-10,-5,5,10)){
      lines(c(i,i),c(-10,10),col="grey",lwd=1.2)
      lines(c(-10,10),c(i,i),col="grey",lwd=1.2)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
    x = seq(-10,10,0.01)
    y = x^2/10-6
    
    lines(x,y,col="blue",lwd=2)
    
    text(10,0,"10",adj=c(0.5,1.3),cex=0.8)
    text(0,10,"10",adj=c(1.3,0.5),cex=0.8)
    text(10,0,"x",adj=c(-0.4,-0.4),cex=0.8)
    text(0,10,"y",adj=c(-0.4,-0.4),cex=0.8)
    
    ```
    
    a. Is the function even?
    b. Is the function odd?
    c. Is the function one-to-one?


\newpage

36. Consider the function graphed below.

    ```{r,echo=F,fig.dim=c(3,3),fig.align="center"}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
      lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    }
    for(i in c(-10,-5,5,10)){
      lines(c(i,i),c(-10,10),col="grey",lwd=1.2)
      lines(c(-10,10),c(i,i),col="grey",lwd=1.2)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
    x = seq(-10,10,0.01)
    y = 5*abs(x+2)^(1/3)*sign(x+2)-3
    
    lines(x,y,col="blue",lwd=2)
    
    text(10,0,"10",adj=c(0.5,1.3),cex=0.8)
    text(0,10,"10",adj=c(1.3,0.5),cex=0.8)
    text(10,0,"x",adj=c(-0.4,-0.4),cex=0.8)
    text(0,10,"y",adj=c(-0.4,-0.4),cex=0.8)
    
    ```
    
    a. Is the function even?
    b. Is the function odd?
    c. Is the function one-to-one?

\vfill

37. Find a cubic polynomial with leading coefficient 1 and roots of $2$ and $1+3i$.

\vfill

38. Find a cubic polynomial with integer coefficients and a positive leading coefficient that is as small as possible and roots of $\frac{2}{3}$ and $\frac{-3}{4}$ and $-2$.

\vfill

\newpage

39. Consider the function graphed below. Assume the domain is $x$ values between -10 and 10 (so the entire function is shown here).

    ```{r,echo=F,fig.dim=c(3,3),fig.align="center"}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-10,10),col="lightgrey",lwd=0.8)
      lines(c(-10,10),c(i,i),col="lightgrey",lwd=0.8)
    }
    for(i in c(-10,-5,5,10)){
      lines(c(i,i),c(-10,10),col="grey",lwd=1.2)
      lines(c(-10,10),c(i,i),col="grey",lwd=1.2)
    }
    abline(h=0,lwd=1.5)
    abline(v=0,lwd=1.5)
    x = seq(-10,-5,0.01)
    y = 2*(x+10)-4
    lines(x,y,col="blue",lwd=2)
    
    x = seq(-5,3,0.01)
    y = -1*(x+5)+6
    lines(x,y,col="blue",lwd=2)
    
    x = seq(3,6,0.01)
    y = 2*(x-3)-2
    lines(x,y,col="blue",lwd=2)
    
    x = seq(6,10,0.01)
    y = -1/2*(x-6)+4
    lines(x,y,col="blue",lwd=2)
    
    text(10,0,"10",adj=c(0.5,1.3),cex=0.8)
    text(0,10,"10",adj=c(1.3,0.5),cex=0.8)
    text(10,0,"x",adj=c(-0.4,-0.4),cex=0.8)
    text(0,10,"y",adj=c(-0.4,-0.4),cex=0.8)
    
    ```

    a. Using interval notation, express where the function is positive.
    b. Using interval notation, express where the function is negative.
    c. Using interval notation, express where the function is increasing.
    d. Using interval notation, express where the function is decreasing.
    
\vfill    

40. Sketch the polynomial on the axes below. Be accurate with the $x$ intercepts and where the function is positive or negative.
$$y=(x+3)^2\cdot (x-5)\cdot (x+8) \cdot (x-1)$$

    ```{r,echo=F,fig.dim=c(6,2),fig.align='center'}
    par(mar=c(0,0,0,0))
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-1,1),axes=F,ann=F)
    for(i in c(-10:-1,1:10)){
      lines(c(i,i),c(-0.05,0.05),col="grey")
      text(i,-0.2,i,cex=0.7,col="grey")
    }
    abline(h=0)
    abline(v=0)
    text(10.5,0.1,"x")
    text(0.3,1,"y")
    ```


\newpage

1. $x=2$
2. $f(-15)=6$
3. $f^{-1}(x)=(x-3)^5+4$
4. a. pass vertical line test. b. pass horizontal line test. c. the curve must pass both line tests.
5. $x=-1$
6. $x=\frac{3}{8}$ and $x=\frac{-6}{5}$
7. If $ax^2+bx+c=0$ then $x=\frac{-b\pm \sqrt{b^2-4ac}}{2a}$
8. $(x-9)(x-1)$
9. $(3x-5)(x+2)$
10. $x^2+13x+42$
11. $\frac{33+17i}{106}$
12. $x^2-10x+29$
13. $x = 3\pm 2i$
14. $f(x)=x+3$
15. $g(x)=-\sqrt{x+3}+2$
16. $x=-2$
17. $x=1$
18. $-1$
19. $81x^4+216x^3+216x^2+96x+16$
20. $x^7-4x^4+3x^3-12x-18$
21. $2x^2-7x+1+\frac{5}{x-3}$
22. Because the remainder when dividing $f(x)$ by $x-5$ is 0, then we know $f(5)=0$. This is a special case of the **remainder theorem**.
23. $(0,-8)$
24. $(x-1)(x+3)(x-4)$
25. $5\sqrt{3}$
26. $y=-(x+7)^2\cdot (x+2)\cdot (x-5)^2$
27. $y=x^3-7x^2-5x+75$
28. There are 3 extrema shown, so the minimum degree is 4.
29. If $b^2-4ac<0$, then two complex solutions. If $b^2-4ac>0$, then two real solutions. If $b^2-4ac=0$, then one real solution (with multiplicity 2).
30. $(x+3)(x-4)$
31. When you divide $x^3+5x^2+2x-8$ by $x-2$ the result is $x^2+7x+16+\frac{24}{x-2}$, so the remainder is 24. The remainder is not 0, so $x-2$ is **not** a factor.
32. The solution set is $\{-4,-2\}$, meaning both $x=-4$ and $x=-2$ are valid solutions to the equation.
33. The **remainder theorem** tells us that $p(4)$ equals the remainder when $p(x)$ is divided by $x-4$. Look at the graph to find the point $(4,-3)$ on the curve, which tells us $p(4)=-3$, so the remainder is -3.
34. This function is **not** even, but it **is** odd and it **is** one-to-one.
35. This function **is** even, but it **is not** odd and it **is not** one-to-one.
36. This function is **not** even and **not** odd, but it **is** one-to-one.
37. $f(x)=x^3-4x^2+6x-20$
38. $f(x)=12x^3+25x^2-4x-12$
39. 
    a. Positive: $(-8,1) \cup (4,10)$.
    b. Negative: $(-10,-8) \cup (1,4)$.
    c. Increasing: $(-10,-5) \cup (3,6)$.
    d. Decreasing: $(-5,3) \cup (6,10)$.
40. 
```{r,echo=F,fig.dim=c(5,1),fig.align="center"}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-1,1),axes=F,ann=F)
for(i in c(-10:-1,1:10)){
  lines(c(i,i),c(-0.05,0.05),col="grey")
  text(i,-0.2,i,cex=0.7,col="grey")
}
abline(h=0)
abline(v=0)
text(10.5,0.1,"x")
text(0.3,1,"y")

x = seq(-10,-8,0.01)
y = (x+8)
lines(x,y,col="blue",lwd=2)

x = seq(-8,-8+pi/2,0.01)
y = sin(x+8)
lines(x,y,col="blue",lwd=2)

x = seq(-8+pi/2,-3-pi/2,0.01)
y = rep(1,length(x))
lines(x,y,col="blue",lwd=2)

x = seq(-3-pi/2,-3+pi/2,0.01)
y = sin(x+3)^2
lines(x,y,col="blue",lwd=2)

x = seq(-3+pi/2,1-pi/2,0.01)
y = rep(1,length(x))
lines(x,y,col="blue",lwd=2)

x = seq(1-pi/2,1+pi/2,0.01)
y = -sin(x-1)
lines(x,y,col="blue",lwd=2)

x = seq(1+pi/2,5-pi/2,0.01)
y = rep(-1,length(x))
lines(x,y,col="blue",lwd=2)

x = seq(5-pi/2,5,0.01)
y = sin(x-5)
lines(x,y,col="blue",lwd=2)

x = seq(5,10,0.01)
y = x-5
lines(x,y,col="blue",lwd=2)


# (x+3)^2\cdot (x-5)\cdot (x+8) \cdot (x-1)


```
