```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
deg = 1
cn = function(a,b){
  cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
  cn = gsub("0+0i","0",cn,fixed=TRUE)
  cn = gsub("1i","i",cn,fixed=TRUE)
  cn = gsub("-1i","-i",cn,fixed=TRUE)
  cn = gsub("+0i","",cn,fixed=TRUE)
  cn = gsub("-0i","",cn,fixed=TRUE)
  if(nchar(cn)>1 && substr(cn,1,2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
  if(nchar(cn)>1 && substr(cn,1,2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
  return(cn)
}
ab = sample(2:10,2)
a1 = ab[1]*sample(c(-1,1),1)
b1 = ab[2]
as = c(a1,a1)
bs = c(b1,-b1)
cns = c(cn(a1,b1),cn(a1,-b1))

ex = paste0("(x-(",as,"+",bs,"*I))",collapse="*")
ex = gsub("+-","-",ex,fixed=TRUE)

asall = as
bsall = bs
cnall = cns
while(length(cnall)<10){
  if(length(cnall)==9 || sample(1:2,1,F,c(0.66,0.34))==1){
    a = sample(-5:5,1)
    b = 0
    cn1 = cn(a,b)
    if(sum(cn1==cnall)==0){
      asall = c(asall,a)
      bsall = c(bsall,b)
      cnall = c(cnall,cn1)
    }
  } else {
    a = sample(-5:5,1)
    b = sample(1:5,1)
    cn1 = cn(a,b)
    cn2 = cn(a,-b)
    if(sum(cn1==cnall)==0){
      asall = c(asall,a,a)
      bsall = c(bsall,b,-b)
      cnall = c(cnall,cn1,cn2)
    }
  }
}

ach = -10:10
al = paste0("* ",ach,collapse="\n")

achb = 1:10
alb = paste0("* ",achb,collapse="\n")

sol1 = paste0(1*(a1==ach),collapse="")
sol2 = paste0(1*(b1==achb),collapse="")

```


Question
========

```{python,echo=FALSE}
from sympy import *
x = symbols("x")
ex = sympify(r.ex)
ex2 = expand(ex)
lex = latex(ex2)
pex = str(ex2)
```

Find the solutions to the quadratic equation below.
$$`r gsub("x","z",py$lex)`=0$$

```{r,echo=FALSE}
link = gsub("**","%5E",py$pex,fixed=TRUE)
link = gsub("+","%2B",link,fixed=TRUE)
link = gsub(" ","",link,fixed=TRUE)
link = gsub("x","z",link,fixed=TRUE)
```

Both solutions will be complex numbers (because the discriminant is negative). To find the solutions, I'd recommend using [this website](https://samuelj.li/complex-function-plotter/#`r link`), which uses [domain coloring](https://en.wikipedia.org/wiki/Domain_coloring) to visualize the solutions. By default the solutions will appear as the center of concentric rings.

Whenever a quadratic equation with REAL coefficients has COMPLEX solutions, the two solutions are [complex conjugates](https://en.wikipedia.org/wiki/Complex_conjugate). In other words, the solutions can be expressed as $x=h-wi$ and $x=h+wi$, where $i=\sqrt{-1}$. Find $h$ and $w$.

$h=$ ##ANSWER1##

$w=$ ##ANSWER2##


Answerlist
--------

`r al`
`r alb`


Solution
========


Use [this website](https://samuelj.li/complex-function-plotter/#`r link`). It should automatically have the function typed in.


```{r,echo=F}
# Install and load necessary packages if you haven't already
# install.packages("ggplot2")
library(ggplot2)

# 1. Define the complex function
f <- function(z) {
  return(z^2)
}

# 2. Create a grid of complex numbers
# Define the range for the real and imaginary axes
x_range <- seq(-10, 10, by = 0.1)
y_range <- seq(-10, 10, by = 0.1)

# Create a complex grid using the outer function
z <- as.vector(outer(x_range, 1i * y_range, `+`))

# 3. Evaluate the function
w <- f(z)

# 4. Map output to HSV color space
# Hue (h) maps to the argument (phase) of the output, normalized to [0, 1]
# Saturation (s) and Value (v) map to the modulus of the output
h <- (Arg(w) + pi) / (2 * pi) # Map phase from [-pi, pi] to [0, 1]
s <- 1 # Can be adjusted for preference
v <- (log2(Mod(w))%%1)*0.8+0.2 # Normalize modulus for brightness/value

# Create a data frame for plotting
plot_data <- data.frame(
  x = Re(z),
  y = Im(z),
  h = h,
  s = s,
  v = v
)

# Remove infinite values (can occur with poles)
plot_data <- plot_data[is.finite(apply(plot_data, 1, sum)), ]

# 5. Plot the results using ggplot2
ggplot(data = plot_data, aes(x = x, y = y)) +
  geom_tile(fill = hsv(plot_data$h, plot_data$s, plot_data$v)) +
  theme_void() + # Use a clean theme
  coord_fixed() # Ensure the aspect ratio is 1:1
```
\



Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: domain_coloring