---
output: pdf_document
params:
    rseed: 0
    showsol: false
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]
```

Name: \vspace{5pt} \hrule

## a0121_example **DO NOT HAND THIS IN. MR. WORLEY WILL WORK THROUGH THESE EXAMPLES. PLEASE COPY DOWN THE WORK.**

```{r}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

cn = function(a,b){
  cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
  cn = gsub("0+0i","0",cn,fixed=TRUE)
  cn = gsub("+1i","+i",cn,fixed=TRUE)
  cn = gsub("-1i","-i",cn,fixed=TRUE)
  cn = gsub("+0i","",cn,fixed=TRUE)
  cn = gsub("-0i","",cn,fixed=TRUE)
  if(nchar(cn)>1 && substr(cn, start = 1, stop = 2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
  if(nchar(cn)>1 && substr(cn, start = 1, stop = 2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
  return(cn)
}
```


### Question 1

There are three common forms to express a quadratic function:

$$\begin{aligned}
\text{standard form} && y&=ax^2+bx+c \\
\text{factored form} && y&=a(x-r)(x-s) \\
\text{vertex form} && y&=a(x-h)^2+k
\end{aligned}$$

In the parabola graphed below, $|a|=1$. 

```{r,fig.dim=c(4,4)}
poss_pairs = list(c(-1,-3),
                  c(-1,3),
                  c(-1,-5),
                  c(-1,5),
                  c(-2,4),
                  c(2,4),
                  c(-2,-4),
                  c(2,-4))
a = sample(c(-1,1),1)
rs = poss_pairs[[sample(1:length(poss_pairs),1)]]
r = rs[1]*a
s = rs[2]*a
h = mean(c(r,s))
c = a*(-r)*(-s)
b = -2*a*h
k = a*(h-r)*(h-s)

par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
for(j in -10:10){
    lines(c(-10,10),c(j,j),col="grey",lwd=0.5)
    lines(c(j,j),c(-10,10),col="grey",lwd=0.5)
}
for(j in seq(-10,10,5)){
    lines(c(-10,10),c(j,j),col="darkgrey",lwd=1)
    lines(c(j,j),c(-10,10),col="darkgrey",lwd=1)
}
arrows(-11,0,11,0,0.05,20,3,lwd=1.5)
arrows(0,-11,0,11,0.05,20,3,lwd=1.5)
text(10,0,"10",adj=c(0.5,1.2))
text(0,10,"10",adj=c(1.2,0.5))
text(10,0,"x",adj=c(-0.2,-0.5))
text(0,10,"y",adj=c(-0.5,-0.2))

x = seq(-10,10,0.01)
y = a*x^2+b*x+c
x = x[abs(y)<=10]
y = y[abs(y)<=10]
lines(x,y,col="blue",lwd=2)
x = seq(-10,10,1)
y = a*x^2+b*x+c
x = x[abs(y)%%1==0]
y = y[abs(y)%%1==0]
x = x[abs(y)<11]
y = y[abs(y)<11]
points(x,y,col="blue",pch=19)

eq_sta = paste0("{",a,"}x^2+{",b,"}x+{",c,"}",collapse="")
eq_sta = gsub("{1}x","x",eq_sta,fixed=T)
eq_sta = gsub("{-1}x","-x",eq_sta,fixed=T)
eq_sta = gsub("+{-","-{",eq_sta,fixed=T)
eq_sta = gsub("+-","-",eq_sta,fixed=T)

eq_ver = paste0("{",a,"}(x+",-h,")^2+",k,collapse="")
eq_ver = gsub("{1}(","(",eq_ver,fixed=T)
eq_ver = gsub("{-1}(","-(",eq_ver,fixed=T)
eq_ver = gsub("+-","-",eq_ver,fixed=T)

eq_fac = paste0("{",a,"}(x+",-r,")(x+",-s,")",collapse="")
eq_fac = gsub("{1}(","(",eq_fac,fixed=T)
eq_fac = gsub("{-1}(","-(",eq_fac,fixed=T)
eq_fac = gsub("+-","-",eq_fac,fixed=T)
```

Write the equation of the graphed parabola in all three quadratic forms.

\vfill 

```{r,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat("$$\\begin{aligned}\n")
    cat("\\text{Standard:} && y=",eq_sta," \\\\\n")
    cat("\\text{Factored:} && y=",eq_fac," \\\\\n")
    cat("\\text{Vertex:} && y=",eq_ver," \n")
    cat("\\end{aligned}$$\n\n\\color{black}\n\n")
}
```


\vfill

\newpage

## a0121_example

### Question 2

```{r}
rs = sample(2:11,2)*sample(c(-1,1),2)
r = rs[1]
s = rs[2]
a = 1
b = -(r+s)
c = r*s
eq1 = paste0("x^2+{",b,"}x+",c,collapse="")
eq1 = gsub("{1}x","x",eq1,fixed=T)
eq1 = gsub("{-1}x","-x",eq1,fixed=T)
eq1 = gsub("+-","-",eq1,fixed=T)
eq1 = gsub("+{-","-{",eq1,fixed=T)

eq2 = paste0("(x+",-r,")(x+",-s,")",collapse="")
eq2 = gsub("+-","-",eq2,fixed=T)
```

A quadratic function is given in standard form.
$$y=`r eq1`$$

a. Write the function in factored form.
b. Find the $x$ intercepts. Express them as $(x,y)$ ordered-pair points.

\vfill

```{r,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat(paste0("$$y=",eq2,"$$\n"))
    cat(paste0("$$\\text{x intercepts: }~(",r,",0) ~\\text{ and }~(",s,",0)$$\n"))
    cat("\\color{black}\n\n")
}
```

\vfill

### Question 3

```{r}
# h+-p*i*sqrt(q)
while(T){
    h = sample(1:5,1)*sample(c(-1,1),1)
    p = sample(2:5,1)
    q = sample(c(1,2,3,5),1)
    a = 1
    b = -2*h
    c = h^2+p^2*q
    if(abs(c)<30){break}
}

eq3 = paste0("x=",h,"\\pm ",p,"i\\sqrt{",q,"}",collapse="")
if(q==1){
    eq3 = paste0("x=",h,"\\pm ",p,"i",collapse="")
}
```

The quadratic formula states that if $ax^2+bx+c=0$ then $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$. Use the quadratic formula to **find the complex solutions** of the following equation. 

$$`r pn(c(a,b,c),2:0)`=0$$

Remember, $i=\sqrt{-1}$.

\vfill

```{r,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat(paste0("$$",eq3,"$$\n"))
    cat("\\color{black}\n\n")
}
```

\vfill

\newpage

## a0121_example

### Question 4


```{r,echo=F}
while(T){
    pows = c("1","i","-1","-i")
    x = sort(sample(40:99,4))
    ans = pows[x%%4+1]
    if(length(unique(ans))==4 && min(diff(x))>5){break}
}
```


Simplify the following powers of $i$.

`r paste0("$i^{",x,"}$",collapse=" \\hfill ")`

\vfill

\color{red}
`r if(params$showsol){paste0("$",ans,"$",collapse=" \\hfill ")}`
\color{black}

\vfill

### Question 5

```{r,echo=F}
abcd = sample(1:9,4)
a = abcd[1]*sample(c(-1,1),1)
b = abcd[2]*sample(c(-1,1),1)
c = abcd[3]*sample(c(-1,1),1)
d = abcd[4]*sample(c(-1,1),1)
cn1 = cn(a,b)
cn2 = cn(c,d)
cn3 = cn(a+c,b+d)
```

Find the sum:
$$(`r cn1`)+(`r cn2`)$$

\vfill
\color{red}
`r if(params$showsol){paste0("$$",cn3,"$$")}`
\color{black}
\vfill

### Question 6

```{r,echo=F}
abcd = sample(1:9,4)
a = abcd[1]*sample(c(-1,1),1)
b = abcd[2]*sample(c(-1,1),1)
c = abcd[3]*sample(c(-1,1),1)
d = abcd[4]*sample(c(-1,1),1)
cn1 = cn(a,b)
cn2 = cn(c,d)
cn3 = cn(a-c,b-d)
```

Find the difference:
$$(`r cn1`)-(`r cn2`)$$

\vfill
\color{red}
`r if(params$showsol){paste0("$$",cn3,"$$")}`
\color{black}
\vfill



\newpage

## a0121_example

### Question 7

```{r,echo=F}
while(T){
    abcd = sample(1:9,4)
    a = abcd[1]*sample(c(-1,1),1)
    b = abcd[2]*sample(c(-1,1),1)
    c = abcd[3]*sample(c(-1,1),1)
    d = abcd[4]*sample(c(-1,1),1)
    cn1 = cn(a,b)
    cn2 = cn(c,d)
    cn3 = cn(a*c-b*d,a*d+b*c)
    if(min(abs(c(a*c-b*d,a*d+b*c)))>0){break}
}


exp3 = paste0(a*c,"+",-b*d,"+",a*d,"i+",b*c,"i")
exp3 = gsub("+-","-",exp3,fixed=T)

```

Find the product:
$$(`r cn1`)\cdot(`r cn2`)$$

\vfill
\color{red}
`r if(params$showsol){paste0("$$(",a*c,")~+~(",a*d,")i~+~(",b*c,")i~+~(",(b*d),")i^2$$")}`
`r if(params$showsol){paste0("$$",exp3,"$$")}`
`r if(params$showsol){paste0("$$",cn3,"$$")}`
\color{black}
\vfill



### Question 8

```{r}
library(numbers)
while(T){
    ac1 = sample(3:6,1)
    b = ac1*2*sample(c(-1,1),1)
    
    ac2 = primeFactors(ac1^2)
    npf = length(ac2)
    npfa = sample(0:npf,1)
    if(npfa==0){
        a = 1
    } else {
        a = prod(sample(ac2,npfa))
    }
    c = round(ac1^2/a)
    
    qt = sample(-1:1,1)
    wc = sample(1:2,1)
    
    if(wc == 1){
        a = a-qt
    } else {
        c = c-qt
    }
    
    D = b^2-4*a*c
    if(min(c(a,b,c))>0 && max(abs(c(a,b,c)))<13){break}
}

if(D<0){
    s1 = "D<0"
    s2 = "two complex solutions."
    sol = "001"
}
if(D==0){
    s1 = "D=0"
    s2 = "one real solution."
    sol = "010"
}
if(D>0){
    s1 = "D>0"
    s2 = "two real solutions."
    sol = "100"
}
```

In the context of finding solutions to $ax^2+bx+c=0$ where $a$, $b$, and $c$ represent real-number parameters...

a. Give a formula for the discriminant ($D$).
b. Describe the implications of the sign of the discriminant. (In other words, what can you know based on whether $D$ is positive, zero, or negative?)
c. Determine how many and what type (real or complex) of solutions there are to equation: $$`r pn(c(a,b,c),2:0)`=0$$

\vfill

```{r,results='asis'}
if(params$showsol){
    cat("\\color{red}\n\n")
    cat("$$D=b^2-4ac$$\n")
    cat("$$\\begin{aligned}")
    cat("\\text{If}&& D<0 &&& \\text{then two complex solutions.}\\\\\n")
    cat("\\text{If}&& D=0 &&& \\text{then one real solution.}\\\\\n")
    cat("\\text{If}&& D>0 &&& \\text{then two real solutions.}\\\\\n")
    cat("\\end{aligned}$$")
    cat(paste0("$$D=(",b,")^2-4(",a,")(",c,")=",b^2,"-",4*a*c,"=",D,"$$\n"))
    cat(paste0("In this case $",s1,"$, so ",s2,"\n"))
    cat("\\color{black}\n\n")
}
```


\vfill