```{r,echo=FALSE}
options(scipen=999)

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    ex1 = gsub("{","",ex1,fixed=T)
    ex1 = gsub("}","",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

while(T){
    mphk = sample(1:7,4)*sample(c(-1,1),4,T)
    m = mphk[1]
    p = mphk[2]
    h = mphk[3]
    k = mphk[4]
    if(abs(p)!=4 && abs(h+p)<10 && abs(k+m)<10 && abs(m)>1 && abs(p)>1){break}
}

ach = c(-7:7)
al = paste0("* ",ach,collapse="\n")

sol1 = paste0(1*(ach==m),collapse="")
sol2 = paste0(1*(ach==p),collapse="")
sol3 = paste0(1*(ach==h),collapse="")
sol4 = paste0(1*(ach==k),collapse="")

```

Question
========

A transformed square-root function was constructed by randomly choosing integers for the values of $m$, $p$, $h$, and $k$ in the equation below.

$$y~=~m\sqrt{\frac{1}{p}(x-h)}+k$$

The equation's curve is plotted below:

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
for(i in c(-10,-5,5,10)){
    text(i,0,i,adj=c(0.5,1.2))
    text(0,i,i,adj=c(0.5,1.2),srt=-90)
}
text(10.5,0,"x",adj=c(0.5,-0.5))
text(0,10.5,"y",adj=c(-0.5,0.5))

arrows(-11,0,11,0,0.1,15,3,lwd=1.2)
arrows(0,-11,0,11,0.1,15,3,lwd=1.2)

x = seq(h,10*sign(p),0.001*sign(p))
y = m*sqrt(1/p*(x-h))+k
x = x[abs(y)<=10]
y = y[abs(y)<=10]

lines(x,y,col="blue",lwd=2)
points(h,k,col="blue",pch=19)
points(h+p,k+m,col="blue",pch=19)
if(abs(h+4*p)<=10 && abs(k+2*m)<=10){
    points(h+4*p,k+2*m,col="blue",pch=19)
}

```
\

Notice, I've marked where the curve intersects the lattice points exactly. These points are where $x$ and $y$ are both integers. (*On the midterm, these points might not be marked.*)

Find the values of the parameters:

* $m=$ ##ANSWER1##
* $p=$ ##ANSWER2##
* $h=$ ##ANSWER3##
* $k=$ ##ANSWER4##

Answerlist
--------

`r al`
`r al`
`r al`
`r al`


Solution
========

I recommend opening up [Desmos](https://www.desmos.com/calculator) and typing in $y~=~m\sqrt{\frac{1}{p}(x-h)}+k$, using sliders for $m$, $p$, $h$, and $k$. Then see what happens as you adjust each slider. You might also add points $(h,k)$ and $(h+p,k+m)$ to see where those move.

The given equation represents a transformation that is best thought of as stretches and then shifts. Imagine the parent function stretched vertically by factor $m$ and horizontally by factor $p$. Then, the parent function is shifted horizontally by distance $h$ and vertically by distance $k$.

The parent function, $y=\sqrt{x}$, has its endpoint at the origin. This point on the curve is unaffected by the stretches, so its corresponding point at $(`r h`,`r k`)$ represents the shifts only.

$$h=`r h`$$
$$k=`r k`$$

The parent function also goes through $(1,1)$. Because both stretches are integer multipliers, we know the corresponding point will be a lattice point on the curve. This key lattice point on the curve is at $(`r h+p`,`r k+m`)$. We can find $m$ and $p$ by comparing this point to the endpoint.

```{r,echo=F,fig.dim=c(6,6)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)

for(i in -10:10){
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
}
for(i in c(-10,-5,5,10)){
    text(i,0,i,adj=c(0.5,1.2))
    text(0,i,i,adj=c(0.5,1.2),srt=-90)
}
text(10.5,0,"x",adj=c(0.5,-0.5))
text(0,10.5,"y",adj=c(-0.5,0.5))

arrows(-11,0,11,0,0.1,15,3,lwd=1.2)
arrows(0,-11,0,11,0.1,15,3,lwd=1.2)

x = seq(h,10*sign(p),0.001*sign(p))
y = m*sqrt(1/p*(x-h))+k
x = x[abs(y)<=10]
y = y[abs(y)<=10]

lines(x,y,col="blue",lwd=2)
points(h,k,col="blue",pch=19)
points(h+p,k+m,col="blue",pch=19)
if(abs(h+4*p)<=10 && abs(k+2*m)<=10){
    points(h+4*p,k+2*m,col="blue",pch=19)
}

arrows(h,k,h+p,k,0.1,20,col="purple",lwd=3)
text(h+p/2,k,p,col="purple",adj=c(0.5,0.5+sign(m)),cex=1.5)
arrows(h+p,k,h+p,k+m,0.1,20,col="red",lwd=3)
text(h+p,k+m/2,m,col="red",adj=c(0.5-sign(p),0.5),cex=1.5)

```
\


* $m=`r m`$
* $p=`r p`$
* $h=`r h`$
* $k=`r k`$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: trans_sqrt_params