---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

cn = function(a,b){
  cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
  cn = gsub("0+0i","0",cn,fixed=TRUE)
  cn = gsub("+1i","+i",cn,fixed=TRUE)
  cn = gsub("-1i","-i",cn,fixed=TRUE)
  cn = gsub("+0i","",cn,fixed=TRUE)
  cn = gsub("-0i","",cn,fixed=TRUE)
  if(nchar(cn)>1 && substr(cn, start = 1, stop = 2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
  if(nchar(cn)>1 && substr(cn, start = 1, stop = 2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
  return(cn)
}

```

Name: \vspace{5pt} \hrule

## a0109_MASTERY (v`r params$rseed`)

### Question 1

```{r,echo=F}
while(T){
    pows = c("1","i","-1","-i")
    x = sort(sample(40:99,4))
    ans = pows[x%%4+1]
    if(length(unique(ans))==4 && min(diff(x))>5){break}
}
```


Simplify the following powers of $i$.

`r paste0("$i^{",x,"}$",collapse=" \\hfill ")`

\vfill

\color{red}
`r if(params$showsol){paste0("$",ans,"$",collapse=" \\hfill ")}`
\color{black}

\vfill



### Question 2

```{r,echo=F}
p = sample(c(2,3,4,5,6),1)
q = sample(c(2,3,5,6,7,10),1)
radicand = -p^2*q
```

Simplify the radical expression.

$$\sqrt{`r radicand`}$$

\vfill

\color{red}
`r if(params$showsol){paste0("$$",p,"i\\sqrt{",q,"}$$")}`
\color{black}

\vfill

### Question 3

```{r,echo=F}
h = sample(2:9,1)*sample(c(-1,1),1)
p = sample(2:6,1)
q = sample(c(2,3,5,6,10),1)
a = 1
b = -2*h
c = h^2-p^2*q
eq = paste0(pn(c(a,b,c),2:0),"=0")
```

Solve.

$$`r eq`$$

\vfill

\color{red}
`r if(params$showsol){paste0("$$x=\\frac{",-b,"}{2}\\pm \\frac{\\sqrt{",b^2,"-(",4*a*c,")}}{2}$$")}`
`r if(params$showsol){paste0("$$x=\\frac{",-b,"}{2}\\pm \\frac{\\sqrt{",b^2-4*a*c,"}}{2}$$")}`
`r if(params$showsol){paste0("$$x=",h,"\\pm",p,"\\sqrt{",q,"}$$")}`
\color{black}

\vfill

### Question 4

```{r,echo=F}
h = sample(2:9,1)*sample(c(-1,1),1)
p = sample(2:6,1)
q = sample(c(2,3,5,6,10),1)
a = 1
b = -2*h
c = h^2+p^2*q
eq = paste0(pn(c(a,b,c),2:0),"=0")
```

Solve.

$$`r eq`$$

\vfill

\color{red}
`r if(params$showsol){paste0("$$x=\\frac{",-b,"}{2}\\pm \\frac{\\sqrt{",b^2,"-",4*a*c,"}}{2}$$")}`
`r if(params$showsol){paste0("$$x=\\frac{",-b,"}{2}\\pm \\frac{\\sqrt{",b^2-4*a*c,"}}{2}$$")}`
`r if(params$showsol){paste0("$$x=",h,"\\pm",p,"i\\sqrt{",q,"}$$")}`
\color{black}

\vfill

\newpage

### Question 5

```{r,echo=FALSE}
ab = sample(2:9,2)
a = ab[1]*sample(c(-1,1),1)
b = ab[2]*sample(c(-1,1),1)
cn = function(a,b){
  cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
  cn = gsub("0+0i","0",cn,fixed=TRUE)
  cn = gsub("+1i","+i",cn,fixed=TRUE)
  cn = gsub("-1i","-i",cn,fixed=TRUE)
  cn = gsub("+0i","",cn,fixed=TRUE)
  cn = gsub("-0i","",cn,fixed=TRUE)
  if(length(cn)>1 && substr(cn, start = 1, stop = 2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
  if(length(cn)>1 && substr(cn, start = 1, stop = 2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
  return(cn)
}
cn1 = cn(a,b)
```

What complex number is represented by the dot on the complex plane below?

```{r,fig.dim=c(2.5,2.5),echo=FALSE,results="asis"}
par(pty="s",mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),lwd=2,ylab="imaginary component",xlab="real component",ann=F,axes=F)
for(j in seq(-10,10,1)){
    lines(c(j,j),c(-10,10),lwd=0.5,col="grey")
    lines(c(-10,10),c(j,j),lwd=0.5,col="grey")
}
for(j in seq(-10,10,5)){
    lines(c(j,j),c(-10,10),lwd=1,col="darkgrey")
    lines(c(-10,10),c(j,j),lwd=1,col="darkgrey")
    if(j!=0){
        text(j,0,j,adj=c(0.5,1.2),cex=0.8)
        text(0,j,paste0(j,"i"),adj=c(1.2,0.5),cex=0.8)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
points(a,b,pch=20,cex=1,col="blue")
```
\

\color{red}
`r if(params$showsol){paste0("$$",cn1,"$$")}`
\color{black}



### Question 6

```{r,echo=F}
abcd = sample(1:9,4)
a = abcd[1]*sample(c(-1,1),1)
b = abcd[2]*sample(c(-1,1),1)
c = abcd[3]*sample(c(-1,1),1)
d = abcd[4]*sample(c(-1,1),1)
cn1 = cn(a,b)
cn2 = cn(c,d)
cn3 = cn(a+c,b+d)
```

Find the sum:
$$(`r cn1`)+(`r cn2`)$$

\vfill
\color{red}
`r if(params$showsol){paste0("$$",cn3,"$$")}`
\color{black}
\vfill

### Question 7

```{r,echo=F}
abcd = sample(1:9,4)
a = abcd[1]*sample(c(-1,1),1)
b = abcd[2]*sample(c(-1,1),1)
c = abcd[3]*sample(c(-1,1),1)
d = abcd[4]*sample(c(-1,1),1)
cn1 = cn(a,b)
cn2 = cn(c,d)
cn3 = cn(a-c,b-d)
```

Find the difference:
$$(`r cn1`)-(`r cn2`)$$

\vfill
\color{red}
`r if(params$showsol){paste0("$$",cn3,"$$")}`
\color{black}
\vfill


### Question 8

```{r,echo=F}
abcd = sample(1:9,4)
a = abcd[1]*sample(c(-1,1),1)
b = abcd[2]*sample(c(-1,1),1)
c = abcd[3]*sample(c(-1,1),1)
d = abcd[4]*sample(c(-1,1),1)
cn1 = cn(a,b)
cn2 = cn(c,d)
cn3 = cn(a*c-b*d,a*d+b*c)

exp3 = paste0(a*c,"+",-b*d,"+",a*d,"i+",b*c,"i")
exp3 = gsub("+-","-",exp3,fixed=T)

```

Find the product:
$$(`r cn1`)\cdot(`r cn2`)$$
\vfill
\vfill
\color{red}
`r if(params$showsol){paste0("$$(",a*c,")~+~(",a*d,")i~+~(",b*c,")i~+~(",(b*d),")i^2$$")}`
`r if(params$showsol){paste0("$$",exp3,"$$")}`
`r if(params$showsol){paste0("$$",cn3,"$$")}`
\color{black}
\vfill
\vfill







