---
output: pdf_document
params:
    rseed: 3
    showsol: true
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}
```

## `r bn`

Synthetic division is a rapid way to divide a polynomial by $x-r$, where $r$ is called the root. Synthetic division is rapid because it uses addition and multiplication, the two easiest operations. While performing synthetic division, we also just write down coefficients and intermediate numbers, not the powers of $x$, so there is less writing.

### Example

```{r,echo}
while(T){
    R = sample(1:9,1)*sample(c(-1,1),1)
    c3 = sample(2:9,4)*c(1,sample(c(-1,1),3,T))
    c1 = c(1,sample(2:9,1)*sample(c(-1,1),1))
    d3 = 3:0
    d1 = 1:0
    c4 = rep(0,5)
    for(i in 1:4){
        di = 4-i
        for(j in 1:2){
            dj = 2-j
            dk = di+dj
            k = 5-dk
            c4[k] = c4[k]+c3[i]*c1[j]
        }
    }
    c4[5] = c4[5]+R
    if(c4[3]==0 && abs(R)!=abs(c1[2])){break}
}

```

Use synthetic division to divide $`r pn(c4,4:0)`$ (the dividend) by $`r pn(c1,1:0)`$ (the divisor).

\vfill

\begin{minipage}[t]{0.45\textwidth}

1. The divisor is $`r pn(c1,1:0)`$, which is a linear binomial with a linear coefficient of 1, so we can use synthetic division. The constant term is $`r c1[2]`$, so we will its opposite ($`r -c1[2]`$) in the synthetic division table; we will refer to $`r -c1[2]`$ as {\bf the root}. Put the dividend's coefficients in the top row. (If any terms are "missing", put a 0 for its coefficient.)

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &     &  & & & \\ \cline{2-6}
  &  &  &  & & &
\end{array}$$

2. Drop the first coefficient to the last row.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &     &  & & & \\ \cline{2-6}
  & `r c4[1]`  &  &  & & &
\end{array}$$

3. Multiply the most recently written number by the root. Put the result in the second row, under the next term.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &   & `r -c4[1]*c1[2]` & & & \\ \cline{2-6}
  & `r c4[1]`  &  &  & & &
\end{array}$$

4. Add `r c4[2]` and `r -c4[1]*c1[2]`.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &   & `r -c4[1]*c1[2]` & & & \\ \cline{2-6}
  & `r c4[1]`  & `r c3[2]`  &  & & &
\end{array}$$

5. Multiply by the root.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &   & `r -c3[1]*c1[2]` & `r -c3[2]*c1[2]` & & \\ \cline{2-6}
  & `r c3[1]`  & `r c3[2]`  &  & & &
\end{array}$$


\end{minipage}
\hfill
\begin{minipage}[t]{0.45\textwidth}


6. Add `r c4[3]` and `r -c3[2]*c1[2]`.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &   & `r -c3[1]*c1[2]` & `r -c3[2]*c1[2]` & & \\ \cline{2-6}
  & `r c3[1]`  & `r c3[2]`  & `r c3[3]` &  & &
\end{array}$$


7. Multiply by the root.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &   & `r -c3[1]*c1[2]` & `r -c3[2]*c1[2]` & `r -c3[3]*c1[2]` & \\ \cline{2-6}
  & `r c3[1]`  & `r c3[2]`  & `r c3[3]` &  & &
\end{array}$$

8. Add to complete the next column.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &   & `r -c3[1]*c1[2]` & `r -c3[2]*c1[2]` & `r -c3[3]*c1[2]` & \\ \cline{2-6}
  & `r c3[1]`  & `r c3[2]`  & `r c3[3]` & `r c3[4]`  & &
\end{array}$$


9. Multiply by the root.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &   & `r -c3[1]*c1[2]` & `r -c3[2]*c1[2]` & `r -c3[3]*c1[2]` & `r -c3[4]*c1[2]` \\ \cline{2-6}
  & `r c3[1]`  & `r c3[2]`  & `r c3[3]` & `r c3[4]`  & &
\end{array}$$

10. Add.

$$\begin{array}{c|rrrrrr}
 & `r c4[1]`  & `r c4[2]` & `r c4[3]` & `r c4[4]` & `r c4[5]` \\
`r -c1[2]`  &   & `r -c3[1]*c1[2]` & `r -c3[2]*c1[2]` & `r -c3[3]*c1[2]` & `r -c3[4]*c1[2]` \\ \cline{2-6}
  & `r c3[1]`  & `r c3[2]`  & `r c3[3]` & `r c3[4]`  & `r R` &
\end{array}$$

The bottom row represents the coefficients of the result. The last number in the bottom row represents the remainder. Because we started with a 4th-degree polynomial (and divided by a 1st-degree polynomial), the result is a 3rd-degree polynomial.

The result can be expressed as:

$$`r pn(c3,3:0)`+\frac{`r R`}{`r pn(c1,1:0)`}$$

\end{minipage}

\vfill

\newpage

### Practice

```{r}
qs = character()
ws = character()
ss = character()
n = 20

set.seed(12)

D = 4
while(T){
    c2 = sample(c(1:9),D+1)*c(1,sample(c(-1,1),D,T))
    c1 = c(1,sample(c(-9:-2,2:9),1))
    R = sample(1:20,1)*sample(c(-1,1),1)
    d2 = D:0
    d1 = 1:0
    c3 = rep(0,D+2)
    for(i in 1:(D+1)){
        di = D+1-i
        for(j in 1:2){
            dj = 2-j
            dk = di+dj
            k = D+2-dk
            c3[k] = c3[k]+c2[i]*c1[j]
        }
    }
    c3[D+2] = c3[D+2]+R
    xx = -c1[2]
    if(max(abs(c3))<100 && abs(R)!=abs(xx)){break}
}

while(length(qs)<n){
    D = sample(3:5,1)
    c1 = c(1,sample(2:9,1)*sample(c(-1,1),1))
    while(T){
        c3 = c(sample(1:12,1),sample(-12:12,D))
        R = sample(1:20,1)*sample(c(-1,1),1)
        d3 = D:0
        d1 = 1:0
        c4 = rep(0,D+2)
        for(i in 1:(D+1)){
            di = D+1-i
            for(j in 1:2){
                dj = 2-j
                dk = di+dj
                k = D+2-dk
                c4[k] = c4[k]+c3[i]*c1[j]
            }
        }
        c4[D+2] = c4[D+2]+R
        q = paste0("\\left(",pn(c4,(D+1):0),"\\right)\\div(",pn(c1,1:0),")")
        w = paste0("\\begin{array}{c|",paste0(rep("r",D+4),collapse=""),"}\n & ",paste0(c4,collapse=" & ")," \\\\ \n", -c1[2],"  &   & ", paste0(-c1[2]*c3,collapse=" & ")," \\\\ \\cline{2-",D+3,"} \n & ", paste0(c3,collapse=" & "),"  & ", R," & \n \\end{array}",collapse="")
        s = paste0(pn(c3,D:0),"+\\frac{",R,"}{",pn(c1,1:0),"}")
        if(c4[1]!=0 && sum(c4==0)>0 && sum(c4==0)<3 && abs(R)!=abs(c1[2])){
            qs = c(qs,q)
            ws = c(ws,w)
            ss = c(ss,s)
            break
            }
    }
}

```


`r paste0(1:n,". $",qs,"$",collapse="\n\n\\vfill\n\n")`

\newpage

### Solutions

\begin{minipage}[t][8.5in]{0.45\textwidth}
`r paste0(1:10,". $",ws[1:10],"$",collapse="\n\n\\vfill\n\n")`
\end{minipage}
\hfill
\begin{minipage}[t][8.5in]{0.45\textwidth}
`r paste0("$",ss[1:10],"$",collapse="\n\n\\vfill\n\n")`

\vspace{0.3in}
\end{minipage}

\newpage

\begin{minipage}[t][9in]{0.45\textwidth}
`r paste0(11:20,". $",ws[11:20],"$",collapse="\n\n\\vfill\n\n")`
\end{minipage}
\hfill
\begin{minipage}[t][9in]{0.45\textwidth}
`r paste0("$",ss[11:20],"$",collapse="\n\n\\vfill\n\n")`

\vspace{0.3in}
\end{minipage}


