```{r,echo=F}
options(scipen=999)
pn = function(c,d){
    d = d[c!=0]
    c = c[c!=0]
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    p = gsub("{","",p,fixed=T)
    p = gsub("}","",p,fixed=T)
    return(p)
}

D = 4
while(T){
    c2 = sample(c(1:9),D+1)*c(1,sample(c(-1,1),D,T))
    c1 = c(1,sample(c(-9:-2,2:9),1))
    R = sample(1:20,1)*sample(c(-1,1),1)
    d2 = D:0
    d1 = 1:0
    c3 = rep(0,D+2)
    for(i in 1:(D+1)){
        di = D+1-i
        for(j in 1:2){
            dj = 2-j
            dk = di+dj
            k = D+2-dk
            c3[k] = c3[k]+c2[i]*c1[j]
        }
    }
    c3[D+2] = c3[D+2]+R
    xx = -c1[2]
    if(max(abs(c3))<100 && abs(R)!=abs(xx)){break}
}


p1 = pn(c1,1:0)
p2 = pn(c2,(D+1):0)
p3 = pn(c3,(D+2):0)
pr = paste0(p2,"+\\frac{",R,"}{",p1,"}",collapse="")

```



Question
========

1. Review the [remainder theorem](https://en.wikipedia.org/wiki/Polynomial_remainder_theorem).

2. When $f(x)=`r p3`$ is divided by $g(x)=`r p1`$ the result is $h(x)=`r pr`$.

3. Evaluate $f(`r -c1[2]`)$.



Solution
========

The trick is to realize that since $\frac{f(x)}{g(x)}=h(x)$ we know $f(x)=g(x)\cdot h(x)$, so:

$$f(x)~=~\left(`r p1`\right) \cdot \left(`r pr`\right)$$

We can partially distribute the linear binomial to clean up that nasty denominator under the remainder.

```{r,echo=F}
px2 = paste0("\\left(",p1,"\\right) \\cdot \\left(",p2,"\\right) +",R)
px2 = gsub("+-","-",px2,fixed=T)
```

$$f(x)~=~`r px2`$$

Now it becomes pretty easy to find $f(`r xx`)$.

```{r,echo=F}
px3 = paste0("\\left(",xx,"+",c1[2],"\\right) \\cdot \\left(\\text{something}\\right) +",R)
px3 = gsub("+-","-",px3,fixed=T)
px4 = paste0("0\\cdot \\left(\\text{something}\\right) +",R)
px4 = gsub("+-","-",px4,fixed=T)
# px4 = gsub("x",paste0("(",xx,")",collapse=""),px4,fixed=T)
px5 = paste0("0 +",R)
px5 = gsub("+-","-",px5,fixed=T)
```

$$f(`r xx`)=`r px3`$$

$$f(`r xx`)=`r px4`$$

$$f(`r xx`)=`r px5`$$

$$f(`r xx`)=`r R`$$

In other words, $f(`r xx`)$ equals the remainder when $f(x)$ is divided by $`r p1`$, as promised by [the remainder theorem](https://en.wikipedia.org/wiki/Polynomial_remainder_theorem).


Meta-information
============
extype: num
exsolution: `r R`
exname: remainder_thrm_01