```{r,echo=FALSE}
options(scipen=99)
b = 12
while(T){
    ndigs = sample(4:5,1)
    digits = c(sample(1:(b-1),1),sample(0:(b-1),ndigs-1,T))
    if(length(unique(digits))==ndigs){break}
}
tot = 0
for(i in 1:ndigs){
    tot = tot + digits[i]*b^(ndigs-i)
}

aldig = function(x=0,y=0,n=0,r=0.4,lwd=2,cex=0.7){
    th = seq(0,2*pi,pi/1000)
    # polygon(x+r*cos(th),y+r*sin(th),lwd=lwd)
    p1 = c(x-r,y+r)
    p2 = c(x,y+r)
    p3 = c(x+r,y+r)
    p4 = c(x-r,y)
    p5 = c(x,y)
    p6 = c(x+r,y)
    p7 = c(x-r,y-r)
    p8 = c(x,y-r)
    p9 = c(x+r,y-r)
    ps = list(p1,p2,p3,p4,p5,p6,p7,p8,p9)
    # points(c(x-r,x+r,x+r,x-r),c(y-r,y-r,y+r,y+r),pch=20,cex=cex)
    connects = list(c(1,3,9,7,1),
                    c(1,2,8,7,9),
                    c(1,3,7,9),
                    c(1,3,6,4,6,9,7),
                    c(1,4,6,3,9),
                    c(3,1,4,6,9,7),
                    c(3,1,7,9,6,4),
                    c(1,3,7),
                    c(1,3,9,7,1,4,6),
                    c(6,4,1,3,9),
                    c(1,9,5,7,3),
                    c(3,1,6,7,9))
    xx = numeric()
    yy = numeric()
    for(i in 1:length(connects[[n+1]])){
        xx = c(xx,ps[[connects[[n+1]][i]]][1])
        yy = c(yy,ps[[connects[[n+1]][i]]][2])
    }
    lines(xx,yy,lwd=lwd)
}

aln = function(xlc=0,ylc=0,digs=c(2,1,0),r=0.4,lwd=2,deltax=1,cex=0.7){
    for(i in 1:length(digs)){
        aldig(xlc+deltax*(i-1),ylc,digs[i],r=r,lwd=lwd,cex=cex)
    }
}

zaln = function(xlc=0,ylc=0,digs=c(2,1,0),r=0.4,lwd=2,deltax=1,nd=6){
    nlz = max(c(nd-length(digs),0))
    ddd = c(rep(0,nlz),digs)
    for(i in 1:length(ddd)){
        aldig(xlc+deltax*(i-1),ylc,ddd[i],r=r,lwd=lwd)
    }
}

adig = function(n,b){
    if(n>0){
        greatest_pow = floor(log(n)/log(b))
    } else {
        return(0)
    }
    tot = n
    digs = numeric()
    for(i in greatest_pow:0){
        dig = tot %/% (b^i)
        digs = c(digs,dig)
        tot = tot-dig*b^i
    }
    return(digs)
}


```

Question
========

Consider the base-12 number system from [Schoolhouse Rock's Little Twelvetoes](https://www.youtube.com/watch?v=pqGyUvZP0Zg).

```{r,echo=F,fig.dim=c(4,4)}

par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,20),ylim=c(0,20))
ccen = c(2,9,16)
for(i in 0:29){
    col = i%/%10
    row = i%%10
    # dd = adig(i,b)
    text(ccen[col+1],20-row*2-1,"=")
    text(ccen[col+1]-1,20-row*2-1,i,adj=1)
    dd = adig(i,b)
    aln(ccen[col+1]+1,20-row*2-1,dd,r=0.3)
}

```
\

When the twelve-toed aliens invented [mechanical counters](https://en.wikipedia.org/wiki/Mechanical_counter), each disk had `r b` markings. I think it can help to visualize the animated mechanical counter: 

```{r,echo=F,fig.show='animate',animation.hook='gifski',fig.dim=c(3,0.5)}
par(mar=c(0,0,0,0))

for(i in 0:100){
    plot(0,0,"n",axes=F,ann=F,xlim=c(0,12),ylim=c(0,2))
    text(2.5,1.5,"human")
    thos = i %/% 1000
    huns = (i-thos*1000) %/% 100
    tens = (i-thos*1000-huns*100) %/% 10
    ones = i-thos*1000-huns*100-tens*10
    text(1,0.5,thos)
    text(2,0.5,huns)
    text(3,0.5,tens)
    text(4,0.5,ones)
    polygon(c(0.5,4.5,4.5,0.5),c(0,0,1,1))
    dd = adig(i,b)
    text(9,1.5,"alien")
    zaln(7,0.5,dd,r=0.3,nd = 4)
}




```
\

As an alien-human translator, you run into this alien number:

```{r,echo=F,fig.dim=c(4.5,0.5)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,9),ylim=c(0,1))
for(i in 1:ndigs){
    aln(i,0.5,digits[i],r=0.3,lwd=4,cex=1.2)
}

```
\

What number is represented (expressed in our base-10 human way)?


Solution
========

Each symbol represents a number between 0 and `r b-1`. Each position represents a power of `r b`. The total value is found by adding up the products of each symbol's value times its corresponding power of `r b`.

$$`r paste0(digits,"\\cdot ",b,"^{",(ndigs-1):0,"}",collapse="+")`$$

You should get the answer:

$$`r tot`$$


Meta-information
============
extype: num
exsolution: `r tot`
exname: x_alien_base_5