```{r,echo=FALSE}
n = sample(100:800,1)
b = sample(c(4,5,6,7,8),1)

chars = character()
rems = numeric()

quot = n %/% b
rem = n-quot*b
rems = c(rems,rem)
while(quot != 0){
    quot2 = quot
    quot = quot %/% b
    rem = quot2-quot*b
    rems = c(rem,rems)
}
cc = c("0",LETTERS[1:(b-1)])

ans = paste0(cc[rems+1],collapse="")

```

Question
========

Consider an alien society that uses base-`r b` number system with the following symbols:

| Human number | Alien numeral |
|:---:|:---:|
| 0  |   0 |
`r paste0("| ",1:(b-1)," | ",LETTERS[1:(b-1)]," |",collapse="\n")`

Notice, the alien 0 is the same as our 0, but then they use uppercase letters in the order of our alphabet instead of Arabic numerals.

A human wants to convert the number `r n` to Alien. Do this for them.

Solution
========


```{r,echo=F,results='asis'}
q = n
while(q != 0){
    q2 = q
    q = q%/%b
    rr = q2-q*b
    cat(paste0("Divide ",q2," by the base ",b," to get a quotient and remainder.\n$$\\frac{",q2,"}{",b,"}~=~",q,"+\\frac{",rr,"}{",b,"}$$\n\n(The quotient was ",q," and the remainder was ",rr,".)\n\n"))
}
```

Now, write down the remainders in reverse order.

$$\text{remainders}~=~`r rems`$$

And, lastly, use the table to convert those amounts into alien symbols.

The answer: ``r ans``


Meta-information
============
extype: string
exsolution: `r ans`
exname: x_base_10_to_alph