```{r data generation, echo = FALSE, results = "hide"}
options(scipen=99)
b = sample(c(4,5,6,7,8),1)
s = c("0",LETTERS[1:(b-1)])

adig = function(n,b=b){
    if(n>0){
        greatest_pow = floor(log(n)/log(b))
    } else {
        return(0)
    }
    tot = n
    digs = numeric()
    for(i in greatest_pow:0){
        dig = tot %/% (b^i)
        digs = c(digs,dig)
        tot = tot-dig*b^i
    }
    return(digs)
}

ns = sample(50:200,2)
n1 = ns[1]
n2 = ns[2]
ad1 = adig(n1,b)
ad2 = adig(n2,b)
ad3 = adig(n1*n2,b)

# while(T){
#     ns = sample(100:500,2)
#     n1 = ns[1]
#     n2 = ns[2]
#     ad1 = adig(n1,b)
#     ad2 = adig(n2,b)
#     maxlength = max(length(ad1),length(ad2))
#     ad3 = numeric()
#     for(i in 1:maxlength){
#         ad1i = 0
#         ad2i = 0
#         if(length(ad1)-i+1>0){
#             ad1i = ad1[length(ad1)-i+1]
#         }
#         if(length(ad2)-i+1>0){
#             ad2i = ad2[length(ad2)-i+1]
#         }
#         ad3 = c(ad3,ad1i+ad2i)
#     }
#     if(abs(diff(ns))>50 && sum(ad3>b)>0){
#         break
#     }
# }
# 
an1 = paste0(s[adig(n1,b)+1],collapse="")
an2 = paste0(s[adig(n2,b)+1],collapse="")
an3 = paste0(s[adig(n1*n2,b)+1],collapse="")

ss1 = s[adig(n1,b)+1]
ss2 = s[adig(n2,b)+1]
ss3 = s[adig(n1*n2,b)+1]


```

Question
========

An alien society uses a base-`r b` positional numbering system. Luckily, they use the same symbol "0" for zero, and then symbols that match our uppercase letters. Below represents their single-digit addition table.

```{r,echo=F,fig.dim=c(0.5*b+1,0.5*b+1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,b+1),ylim=c(0,b+1),axes=F,ann=F)
abline(h=b)
abline(v=1)
text(0.5,b+0.5,"+")
for(i in 1:b){
    text(i+0.5,b+0.5,s[i])
    text(0.5,b-i+0.5,s[i])
}
for(i in 1:b){
    for(j in 1:b){
        text(i+0.5,b-j+0.5,paste0(s[adig(i+j-2,b)+1],collapse=""))
    }
}

```
\

We can also produce their single-digit multiplication table.


```{r,echo=F,fig.dim=c(0.5*b+1,0.5*b+1)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(0,b+1),ylim=c(0,b+1),axes=F,ann=F)
abline(h=b)
abline(v=1)
text(0.5,b+0.5,"*")
for(i in 1:b){
    text(i+0.5,b+0.5,s[i])
    text(0.5,b-i+0.5,s[i])
}
for(i in 1:b){
    for(j in 1:b){
        text(i+0.5,b-j+0.5,paste0(s[adig((i-1)*(j-1),b)+1],collapse=""))
    }
}

```
\


Use those tables to multiply:

`r an1` * `r an2`



Solution
========



Meta-information
============
extype: string
exsolution: `r an3`
exname: base_b_addition