```{r,echo=FALSE}
n = 5
pows = c("1","i","-1","-i")
while(T){
    x = sort(sample(10:99,n))
    ans = pows[(x%%4)+1]
    if(length(unique(ans))==4 || n<5){break}
}

qstr = paste0("* $i^{",x,"}=$ ##ANSWER",1:n,"##",collapse="\n")
p = c("i","-1","-i","1")
al = paste0("* ",p,collapse="\n")
tal = paste0(rep(al,n),collapse="\n")

sols = character()
for(i in 1:n){
    sol = paste0(1*(p==ans[i]),collapse="")
    sols = c(sols,sol)
}

```

Question
========

Simplify the following powers of $i$.

`r qstr`

Answerlist
--------

`r tal`


Solution
========

For any positive integer $n$, we can evaluate $i^n$ by determining the remainder when $n$ is divided by 4.

| Remainder of $n/4$ | $i^n$ |
|:---:|:---:|
| 0 | $1$ |
| 1 | $i$ |
| 2 | $-1$ |
| 3 | $-i$ |

In computer programming, the [modulo operator](https://en.wikipedia.org/wiki/Modulo) returns the remainder. This operation is used so frequently, that it is often abbreviated to a single symbol (for example, in Python, `5%2` represents the remainder when 5 is divided by 2.)

I will represent the remainders using the [Desmos](https://www.desmos.com/calculator) notation.

```{r,echo=F}
calcs = paste0("* $\\mathrm{mod}(",x,",4)","=",x%%4,"$ so $i^{",x,"}=",ans,"$",collapse="\n")
```

`r calcs`

To find the remainder using a scientific calculator, I would divide by 4, [floor](https://en.wikipedia.org/wiki/Floor_and_ceiling_functions) the result, multiply by 4, and subtract that amount from the original.

$$\mathrm{mod}(x,4)~=~x-4\cdot \left\lfloor\frac{x}{4}\right\rfloor$$


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: i_to_power