```{r,echo=FALSE}
library(MASS)
pn = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}

while(T){
    aposs = c(-3,-2,-1,-1/2,-1/3,-1/4,1/4,1/3,1/2,1,2,3)
    a = sample(aposs,1)
    h = sample(1:6,1)*sample(c(-1,1),1)
    k = sample(-6:6,1)
    b = -h*2*a
    c = a*h^2+k
    if(abs(b)<11 && abs(c)<11 && abs(b)>0 && abs(c)>0 && c%%1==0 && b%%1==0){break}
}

ashow = c("-3","-2","-1","\\frac{-1}{2}","\\frac{-1}{3}","\\frac{-1}{4}","\\frac{1}{4}","\\frac{1}{3}","\\frac{1}{2}","1","2","3")

ala = paste0("* ",fractions(aposs),collapse="\n")
alb = paste0("* ",-10:10,collapse="\n")
alc = paste0("* ",-10:10,collapse="\n")

sola = paste0(1*(aposs==a),collapse="")
solb = paste0(1*(-10:10==b),collapse="")
solc = paste0(1*(-10:10==c),collapse="")

anice = ashow[aposs==a]

```

Question
========

Consider the quadratic function graphed below.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
for(j in -10:10){
    lines(c(-10,10),c(j,j),col="grey",lwd=0.5)
    lines(c(j,j),c(-10,10),col="grey",lwd=0.5)
}
for(j in seq(-10,10,5)){
    lines(c(-10,10),c(j,j),col="darkgrey",lwd=1)
    lines(c(j,j),c(-10,10),col="darkgrey",lwd=1)
}
arrows(-11,0,11,0,0.05,20,3,lwd=1.5)
arrows(0,-11,0,11,0.05,20,3,lwd=1.5)
text(10,0,"10",adj=c(0.5,1.2))
text(0,10,"10",adj=c(1.2,0.5))
text(10,0,"x",adj=c(-0.2,-0.5))
text(0,10,"y",adj=c(-0.5,-0.2))

x = seq(-10,10,0.01)
y = a*x^2+b*x+c
x = x[abs(y)<=10]
y = y[abs(y)<=10]
lines(x,y,col="blue",lwd=2)
x = seq(-10,10,1)
y = a*x^2+b*x+c
x = x[abs(y)%%1==0]
y = y[abs(y)%%1==0]
x = x[abs(y)<11]
y = y[abs(y)<11]
points(x,y,col="blue",pch=19)
```
\

Find parameters $a$, $b$, and $c$, such that the above curve represents $y=ax^2+bx+c$.

* $a=$ ##ANSWER1##
* $b=$ ##ANSWER2##
* $c=$ ##ANSWER3##


Answerlist
--------

`r ala`
`r alb`
`r alc`



Solution
========

First, [based on the spacing of lattice-point intersections near the vertex](https://artockthedino.github.io/algtwo2026/u06/1218/Stretched_Parabolas_Reference.html), and also the up/down orientation, we can determine $a$.

$$a~=~`r anice`$$

Next, identify the location of the vertex is $(`r h`,`r k`)$, so $h=`r h`$. We know that $h=\frac{-b}{2a}$, so with a bit of algebra, we also know that $b=-2ah$.

$$b~=~-2(`r paste0(fractions(a))`)(`r h`)$$
$$b~=~`r b`$$

Lastly, getting $c$ is easy. Notice, if $x=0$, then $y=c$. Thus, we just need to find the $y$ intercept to get $c$.

$$c=`r c`$$

The function:

$$y=`r pn(c(anice,b,c),2:0)`$$


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice
exsolution: `r sola`|`r solb`|`r solc`
exname: standard_from_graph