```{r,echo=FALSE}
options(scipen=99)
library(numbers)
pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

# -b/2a +- sqrt(b^2-4ac)/2a
# (x-(h+p*sqrt(q)))(x-(h-p*sqrt(q)))
# (x-(h+sqrt(p^2*q)))(x-(h-sqrt(p^2*q)))

# x^2 - 2*h + h^2-p^2*q

h = sample(2:9,1)*sample(c(-1,1),1)
p = sample(2:6,1)
q = sample(c(2,3,5,6,7,10),1)
a = 1
b = -2*h
c = h^2-p^2*q

eq = paste0(pn(c(a,b,c),2:0),"=0")


ha = c(-9:-2,2:9)
pa = 2:6
qa = c(2,3,5,6,7,10)
ba = numeric()
ca = numeric()

for(hb in ha){
    for(pb in pa){
        for(qb in qa){
            ba = c(ba,-2*hb)
            ca = c(ca,hb^2-pb^2*qb)
        }
    }
}
ba = sort(unique(ba))
ca = sort(unique(ca))

ach1 = sample(unique(abs(ba)),4)
if(!(abs(b) %in% ach1)){
    ach1[1] = abs(b)
}
ach1 = sort(c(-ach1,ach1))

ach2 = sample(ca,8)
if(!(c %in% ach2)){
    ach2[1] = c
}
ach2 = sort(ach2)


al1 = paste0("* ",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")

sol1 = paste0(1*(ach1==b),collapse="")
sol2 = paste0(1*(ach2==c),collapse="")


```


Question
========

Below is a quadratic function written in factored form.

$$f(x)~=~\left[x-\left(`r h`-`r p`\sqrt{`r q`}\right)\right]\cdot\left[x-\left(`r h`+`r p`\sqrt{`r q`}\right)\right]$$

By finding parameters $b$ and $c$, the same function can be expressed in standard form:

$$f(x)~=~x^2+bx+c$$

Find $b$ and $c$.

$b=$ ##ANSWER1##

$c=$ ##ANSWER2##

Answerlist
--------

`r al1`
`r al2`

Solution
========

Start in factored form.

$$f(x)~=~\left[x-(`r h`-`r p`\sqrt{`r q`})\right]\cdot\left[x-(`r h`+`r p`\sqrt{`r q`})\right]$$

At this point, you can either FOIL or distribute away the inside parentheses. I think it'll be a bit cleaner to distribute the subtraction across the parentheses.

```{r,echo=F}
fac1 = paste0("x+",-h,"+",p,"\\sqrt{",q,"}")
fac2 = paste0("x+",-h,"-",p,"\\sqrt{",q,"}")
fac1 = gsub("+-","-",fac1,fixed=T)
fac2 = gsub("+-","-",fac2,fixed=T)
```

$$\left[`r fac1`\right]\cdot\left[`r fac2`\right]$$

But now, instead of FOIL, we need to generalize, because each factor has three terms: a linear term and two constant terms. You could probably guess that we simply multiply each of the first factor's terms by each of the second factor's terms.

```{r,echo=F}
# (x-h+psqrt(q))(x-h-psqrt(q))
# x^2-hx-psqrt(q)x-hx+h^2+hpsqrt(q)+psqrt(q)x-hpsqrt(q)-p^2*q

exp3 = paste0("x^2+",-h,"x-",p,"\\sqrt{",q,"}x+",-h,"x+",h^2,"+",h*p,"\\sqrt{",q,"}+",p,"\\sqrt{",q,"}x+",-h*p,"\\sqrt{",q,"}+",-p^2*q)
exp3 = gsub("+-","-",exp3,fixed=T)
```

$$`r exp3`$$

Combine like terms. Opposite terms cancel each other out.

```{r,echo=F}
# x^2-hx-psqrt(q)x-hx+h^2+hpsqrt(q)+psqrt(q)x-hpsqrt(q)-p^2*q
# x^2-hx-hx+h^2-p^2*q

exp4 = paste0("x^2+",-2*h,"x+",h^2-p^2*q)
exp4 = gsub("+-","-",exp4,fixed=T)
```


$$`r exp4`$$

Thus, $b=`r b`$ and $c=`r c`$.

Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: abc_from_hpsqrtq_roots