```{r,echo=FALSE}
library(reticulate)
options(scipen=999)
a = sample(c(-9:-1,1:9),1)
b = sample(c(-9:-1,1:9),1)
cn = function(a,b){
  cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
  cn = gsub("0+0i","0",cn,fixed=TRUE)
  cn = gsub("+1i","+i",cn,fixed=TRUE)
  cn = gsub("-1i","-i",cn,fixed=TRUE)
  cn = gsub("+0i","",cn,fixed=TRUE)
  cn = gsub("-0i","",cn,fixed=TRUE)
  if(length(cn)>1 && substr(cn, start = 1, stop = 2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
  if(length(cn)>1 && substr(cn, start = 1, stop = 2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
  return(cn)
}
cn1 = cn(a,b)
m = sqrt(a^2+b^2)
```

Question
========

Let $z$ be a complex number with integer components. It is graphed on a [complex plane](https://en.wikipedia.org/wiki/Complex_plane) below, along with a segment connecting it to the origin.


```{r,fig.dim=c(4,4),echo=FALSE,results="asis"}
par(pty="s",mar=c(0,0,0,0))
plot(0,0,type="n",xlim=c(-10,10),ylim=c(-10,10),lwd=2,ylab="imaginary component",xlab="real component",axes=F,ann=F)
for(j in seq(-10,10,1)){
    lines(c(j,j),c(-10,10),lwd=0.5,col="grey")
    lines(c(-10,10),c(j,j),lwd=0.5,col="grey")
}
for(j in seq(-10,10,5)){
    lines(c(j,j),c(-10,10),lwd=1,col="darkgrey")
    lines(c(-10,10),c(j,j),lwd=1,col="darkgrey")
    if(j!=0){
        text(j,0,j,adj=c(0.5,1.2),cex=0.8)
        text(0,j,paste0(j,"i"),adj=c(1.2,0.5),cex=0.8)
    }
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
lines(c(0,a),c(0,b),lwd=2,col="red")
points(a,b,pch=20,cex=1.5,col="blue")
```
\

Calculate $|z|$, the [modulus](https://en.wikipedia.org/wiki/Absolute_value#Complex_numbers) of the complex number graphed above. *The tolerance is $\pm 0.01$.*


Solution
========

The horizontal (real) component is `r a`. The vertical (imaginary) component is `r b`. So,
$$z_1 = `r cn1`$$

Use the formula.
$$|z_1| = \sqrt{(`r a`)^2+(`r b`)^2}$$
$$|z_1| = \sqrt{`r a^2`+`r b^2`}$$
$$|z_1| = \sqrt{`r a^2+b^2`} \approx `r m` $$

Meta-information
============
extype: num
exsolution: `r m`
exname: complex_modulus
extol: 0.01