---
output: pdf_document
params:
    rseed: 0
    showsol: true
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]
```

Name: \vspace{5pt} \hrule

## `r bn` (v`r params$rseed`)

**YOU MUST SHOW WORK FOR CREDIT.**

```{r}
gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

cn = function(a,b){
  cn = gsub("+-","-",paste0(a,"+",b,"i"),fixed=TRUE)
  cn = gsub("0+0i","0",cn,fixed=TRUE)
  cn = gsub("+1i","+i",cn,fixed=TRUE)
  cn = gsub("-1i","-i",cn,fixed=TRUE)
  cn = gsub("+0i","",cn,fixed=TRUE)
  cn = gsub("-0i","",cn,fixed=TRUE)
  if(nchar(cn)>1 && substr(cn, start = 1, stop = 2)=="0+"){cn = gsub("0+","",cn,fixed=TRUE)}
  if(nchar(cn)>1 && substr(cn, start = 1, stop = 2)=="0-"){cn = gsub("0-","-",cn,fixed=TRUE)}
  return(cn)
}
```


### Question 1

```{r,echo=FALSE}

while(T){
    p = sample(1:9,1)*sample(c(-1,1),1)
    q = sample(2:9,1)
    psi = sample(1:9,1)*sample(c(-1,1),1)
    # sqrt(mx+n)+k = x+psi+k
    m = 2*psi-2*p
    n = psi^2-p^2-q^2
    k = sample(1:9,1)*sample(c(-1,1),1)
    if(n!=0 && abs(m)>1 && abs(psi+k)>0){break}
}

p1 = p
q1 = q

fx = paste0("\\sqrt{",m,"x+",n,"}+",k)
lx = paste0("x+",psi+k)
fx = gsub("+-","-",fx,fixed=T)
lx = gsub("+-","-",lx,fixed=T)
gx = paste0("-\\sqrt{",m,"x+",n,"}+",k)
gx = gsub("+-","-",gx,fixed=T)

ach = -10:10
ach2 = 1:10
al = paste0("* ",ach,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")
sol1 = paste0(1*(ach==-p),collapse="")
sol2 = paste0(1*(ach2==q),collapse="")
```


Find the complex possible solutions to the equation.

$$`r fx`=`r lx`$$

\vfill

```{r,echo=F,results="asis",eval=params$showsol}
cat("\\color{red}")

eq2 = paste0("\\sqrt{",m,"x+",n,"}=x+",psi)
eq2 = gsub("+-","-",eq2,fixed=T)
cat(paste0("\n\n$$",eq2,"$$\n\n"))

eq3 = paste0(m,"x+",n,"=x^2+",2*psi,"x+",psi^2)
eq3 = gsub("+-","-",eq3,fixed=T)
cat(paste0("\n\n$$",eq3,"$$\n\n"))

eq4 = paste0("0=x^2+",2*psi-m,"x+",psi^2-n)
eq4 = gsub("+-","-",eq4,fixed=T)
cat(paste0("\n\n$$",eq4,"$$\n\n"))

a = 1
b = 2*psi-m
c = psi^2-n
qf1 = paste0("x=\\frac{-(",b,")\\pm\\sqrt{(",b,")^2-4(",a,")(",c,")}}{2(",a,")}")
cat(paste0("\n\n$$",qf1,"$$\n"))

qf2 = paste0("x=\\frac{",-b,"\\pm\\sqrt{",b^2,"-",4*a*c,"}}{",2*a,"}")
cat(paste0("\n\n$$",qf2,"$$\n"))

qf3 = paste0("x=\\frac{",-b,"\\pm\\sqrt{",b^2-4*a*c,"}}{",2*a,"}")
cat(paste0("\n\n$$",qf3,"$$\n"))

qf4 = paste0("x=\\frac{",-b,"\\pm",2*a*q,"i}{",2*a,"}")
cat(paste0("\n\n$$",qf4,"$$\n"))

qf5 = paste0("x=",-p,"\\pm",q,"i")
cat(paste0("\n\n$$",qf5,"$$\n"))
```


\hfill \color{gray} \tiny $x=`r -p`\pm `r q`i$ \normalsize \color{black}

```{r,echo=F,results="asis",eval=params$showsol}
cat("\\newpage")
```

### Question 2

```{r,echo=FALSE}

while(T){
    p = sample(1:9,1)*sample(c(-1,1),1)
    q = sample(2:9,1)
    psi = sample(1:9,1)*sample(c(-1,1),1)
    # sqrt(mx+n)+k = x+psi+k
    m = 2*psi-2*p
    n = psi^2-p^2-q^2
    k = sample(1:9,1)*sample(c(-1,1),1)
    if(n!=0 && abs(m)>1 && abs(psi+k)>0 && p!=p1 && q!=q1){break}
}

fx = paste0("\\sqrt{",m,"x+",n,"}+",k)
lx = paste0("x+",psi+k)
fx = gsub("+-","-",fx,fixed=T)
lx = gsub("+-","-",lx,fixed=T)
gx = paste0("-\\sqrt{",m,"x+",n,"}+",k)
gx = gsub("+-","-",gx,fixed=T)

ach = -10:10
ach2 = 1:10
al = paste0("* ",ach,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")
sol1 = paste0(1*(ach==-p),collapse="")
sol2 = paste0(1*(ach2==q),collapse="")
```


Find the complex possible solutions to the equation.

$$`r fx`=`r lx`$$

\vfill

```{r,echo=F,results="asis",eval=params$showsol}
cat("\\color{red}")

eq2 = paste0("\\sqrt{",m,"x+",n,"}=x+",psi)
eq2 = gsub("+-","-",eq2,fixed=T)
cat(paste0("\n\n$$",eq2,"$$\n\n"))

eq3 = paste0(m,"x+",n,"=x^2+",2*psi,"x+",psi^2)
eq3 = gsub("+-","-",eq3,fixed=T)
cat(paste0("\n\n$$",eq3,"$$\n\n"))

eq4 = paste0("0=x^2+",2*psi-m,"x+",psi^2-n)
eq4 = gsub("+-","-",eq4,fixed=T)
cat(paste0("\n\n$$",eq4,"$$\n\n"))

a = 1
b = 2*psi-m
c = psi^2-n
qf1 = paste0("x=\\frac{-(",b,")\\pm\\sqrt{(",b,")^2-4(",a,")(",c,")}}{2(",a,")}")
cat(paste0("\n\n$$",qf1,"$$\n"))

qf2 = paste0("x=\\frac{",-b,"\\pm\\sqrt{",b^2,"-",4*a*c,"}}{",2*a,"}")
cat(paste0("\n\n$$",qf2,"$$\n"))

qf3 = paste0("x=\\frac{",-b,"\\pm\\sqrt{",b^2-4*a*c,"}}{",2*a,"}")
cat(paste0("\n\n$$",qf3,"$$\n"))

qf4 = paste0("x=\\frac{",-b,"\\pm",2*a*q,"i}{",2*a,"}")
cat(paste0("\n\n$$",qf4,"$$\n"))

qf5 = paste0("x=",-p,"\\pm",q,"i")
cat(paste0("\n\n$$",qf5,"$$\n"))
```

\hfill \color{gray} \tiny $x=`r -p`\pm `r q`i$ \normalsize \color{black}



\newpage


### Question 3

```{r,echo=FALSE}

# sqrt(x+a)+b = sqrt(x+c)
# x+a + 2b*sqrt(x+a) + b^2 = x+c
# sqrt(x+a) = (c-a-b^2)/(2b)
# x+a = (c-a-b^2)^2/(4b^2)
# x = (c-a-b^2)^2/(4b^2)-a

isval = sample(c(T,F),1)
if(isval){
    ans2 = "valid"
} else {
    ans2 = "extraneous"
}

while(T){
    abc = sample(1:9,3)*sample(c(-1,1),3,T)
    a = abc[1]
    b = abc[2]
    c = abc[3]
    xposs = (c-a-b^2)^2/(4*b^2)-a
    ls = sqrt(xposs+a)+b
    rs = sqrt(xposs+c)
    if((ls==rs)==isval && xposs%%1==0 && abs(xposs)<100 && abs(c-a-b^2)>0){break}
}
eq = paste0("\\sqrt{x+",a,"}+",b,"=\\sqrt{x+",c,"}")
eq = gsub("+-","-",eq,fixed=T)

ans21 = ans2

abc1 = abc

```

Find the possible solution, and determine whether the solution is valid or extraneous.

$$`r eq`$$

\vfill

```{r,echo=F,results="asis",eval=params$showsol}
cat("\\color{red}")

eq = paste0("(\\sqrt{x+",a,"}+",b,")^2=(\\sqrt{x+",c,"})^2")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$"))

cat("\n\nThe left side will need to be FOILed. On the right side, the inverse operations cancel out.\n\n")

eq = paste0("(\\sqrt{x+",a,"}+",b,")(\\sqrt{x+",a,"}+",b,")=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("(x+",a,")+",2*b,"\\sqrt{x+",a,"}+(",b,")^2=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("x+",a,"+",2*b,"\\sqrt{x+",a,"}+",b^2,"=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("Subtract $x+",a,"+",b^2,"$ from both sides.\n\n"))

eq = paste0(2*b,"\\sqrt{x+",a,"}=",c-a-b^2)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("Divide both sides by $",2*b,"$.\n\n"))

eq = paste0("\\sqrt{x+",a,"}=",round((c-a-b^2)/(2*b)))
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat("Square both sides.\n\n")

eq = paste0("x+",a,"=",round((c-a-b^2)/(2*b))^2)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))


if(a>0){
    cat("Subtract ",a," from both sides.")
} else {
    cat("Add ",-a," to both sides.")
}

eq = paste0("x=",round((c-a-b^2)/(2*b))^2-a)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("So, our possible solution is $x=",round((c-a-b^2)/(2*b))^2-a,"$. We need to check if this satisfies the given equation."))


eq = paste0("\\sqrt{",xposs,"+",a,"}+",b,"\\stackrel{?}{=}\\sqrt{",xposs,"+",c,"}")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("\\sqrt{",xposs+a,"}+",b,"\\stackrel{?}{=}\\sqrt{",xposs+c,"}")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0(sqrt(xposs+a),"+",b,"\\stackrel{?}{=}",sqrt(xposs+c))
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

if(isval){
    eq = paste0(sqrt(xposs+a)+b,"=",sqrt(xposs+c))
    eq = gsub("+-","-",eq,fixed=T)
    cat(paste0("$$",eq,"$$\n\n"))
    cat(paste0("So, the possible solution $x=",xposs,"$ is valid."))
} else {
    eq = paste0(sqrt(xposs+a)+b,"\\ne ",sqrt(xposs+c))
    eq = gsub("+-","-",eq,fixed=T)
    cat(paste0("$$",eq,"$$\n\n"))
    cat(paste0("So, the possible solution $x=",xposs,"$ is extraneous."))
}

```

\hfill \color{gray} \tiny $x=`r xposs`$, `r ans2` \normalsize \color{black}

```{r,echo=F,results="asis",eval=params$showsol}
cat("\\newpage")
```

### Question 4

```{r,echo=FALSE}

# sqrt(x+a)+b = sqrt(x+c)
# x+a + 2b*sqrt(x+a) + b^2 = x+c
# sqrt(x+a) = (c-a-b^2)/(2b)
# x+a = (c-a-b^2)^2/(4b^2)
# x = (c-a-b^2)^2/(4b^2)-a

isval = !isval
if(isval){
    ans2 = "valid"
} else {
    ans2 = "extraneous"
}

while(T){
    abc = sample(1:9,3)*sample(c(-1,1),3,T)
    a = abc[1]
    b = abc[2]
    c = abc[3]
    xposs = (c-a-b^2)^2/(4*b^2)-a
    ls = sqrt(xposs+a)+b
    rs = sqrt(xposs+c)
    if((ls==rs)==isval && xposs%%1==0 && abs(xposs)<100 && abs(c-a-b^2)>0 && !(a%in%abc1) && !(c%in%abc1)){break}
}
eq = paste0("\\sqrt{x+",a,"}+",b,"=\\sqrt{x+",c,"}")
eq = gsub("+-","-",eq,fixed=T)

ans21 = ans2
```

Find the possible solution, and determine whether the solution is valid or extraneous.

$$`r eq`$$

\vfill

\hfill \color{gray} \tiny $x=`r xposs`$, `r ans2` \normalsize \color{black}

```{r,echo=F,results="asis",eval=params$showsol}

cat("\\color{red}")

eq = paste0("(\\sqrt{x+",a,"}+",b,")^2=(\\sqrt{x+",c,"})^2")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$"))

cat("\n\nThe left side will need to be FOILed. On the right side, the inverse operations cancel out.\n\n")

eq = paste0("(\\sqrt{x+",a,"}+",b,")(\\sqrt{x+",a,"}+",b,")=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("(x+",a,")+",2*b,"\\sqrt{x+",a,"}+(",b,")^2=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("x+",a,"+",2*b,"\\sqrt{x+",a,"}+",b^2,"=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("Subtract $x+",a,"+",b^2,"$ from both sides.\n\n"))

eq = paste0(2*b,"\\sqrt{x+",a,"}=",c-a-b^2)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("Divide both sides by $",2*b,"$.\n\n"))

eq = paste0("\\sqrt{x+",a,"}=",round((c-a-b^2)/(2*b)))
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat("Square both sides.\n\n")

eq = paste0("x+",a,"=",round((c-a-b^2)/(2*b))^2)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))


if(a>0){
    cat("Subtract ",a," from both sides.")
} else {
    cat("Add ",-a," to both sides.")
}

eq = paste0("x=",round((c-a-b^2)/(2*b))^2-a)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("So, our possible solution is $x=",round((c-a-b^2)/(2*b))^2-a,"$. We need to check if this satisfies the given equation."))


eq = paste0("\\sqrt{",xposs,"+",a,"}+",b,"\\stackrel{?}{=}\\sqrt{",xposs,"+",c,"}")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("\\sqrt{",xposs+a,"}+",b,"\\stackrel{?}{=}\\sqrt{",xposs+c,"}")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0(sqrt(xposs+a),"+",b,"\\stackrel{?}{=}",sqrt(xposs+c))
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

if(isval){
    eq = paste0(sqrt(xposs+a)+b,"=",sqrt(xposs+c))
    eq = gsub("+-","-",eq,fixed=T)
    cat(paste0("$$",eq,"$$\n\n"))
    cat(paste0("So, the possible solution $x=",xposs,"$ is valid."))
} else {
    eq = paste0(sqrt(xposs+a)+b,"\\ne ",sqrt(xposs+c))
    eq = gsub("+-","-",eq,fixed=T)
    cat(paste0("$$",eq,"$$\n\n"))
    cat(paste0("So, the possible solution $x=",xposs,"$ is extraneous."))
}

```