```{r,echo=FALSE}

while(T){
    p = sample(1:9,1)*sample(c(-1,1),1)
    q = sample(2:9,1)
    psi = sample(1:9,1)*sample(c(-1,1),1)
    # sqrt(mx+n)+k = x+psi+k
    m = 2*psi-2*p
    n = psi^2-p^2-q^2
    k = sample(1:9,1)*sample(c(-1,1),1)
    if(n!=0 && abs(m)>1 && abs(psi+k)>0){break}
}

fx = paste0("\\sqrt{",m,"x+",n,"}+",k)
lx = paste0("x+",psi+k)
fx = gsub("+-","-",fx,fixed=T)
lx = gsub("+-","-",lx,fixed=T)
gx = paste0("-\\sqrt{",m,"x+",n,"}+",k)
gx = gsub("+-","-",gx,fixed=T)

ach = -10:10
ach2 = 1:10
al = paste0("* ",ach,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")
sol1 = paste0(1*(ach==-p),collapse="")
sol2 = paste0(1*(ach2==q),collapse="")


```

Question
========

Consider solving the following equation:

$$`r fx`=`r lx`$$

If you graph $y=`r fx`$ and $y=`r lx`$, you'll notice no intersections of the linear and radical functions, so there are no valid real solutions. If you also graph $y=`r gx`$, you'll see there are no extraneous real solutions.

Using algebra to solve the equation will produce two [complex](https://en.wikipedia.org/wiki/Complex_number) possible solutions. Unfortunately, we do not have [the skills](https://math.stackexchange.com/questions/44406/how-do-i-get-the-square-root-of-a-complex-number) to check whether the possible complex solutions are valid or extraneous, but it is still good practice to find the possible complex solutions.

The possible complex solutions can be expressed as $p\pm qi$, where $p$ and $q$ are integers and $i=\sqrt{-1}$ . Find the possible complex solutions.

$p=$ ##ANSWER1##

$q=$ ##ANSWER2##


Answerlist
--------

`r al`
`r al2`

Solution
========

$$`r fx`=`r lx`$$

```{r,echo=F,results="asis"}
if(k<0){
    cat(paste0("Add ",abs(k)," to both sides."))
} else {
    cat(paste0("Subtract ",abs(k)," from both sides."))
}
eq2 = paste0("\\sqrt{",m,"x+",n,"}=x+",psi)
eq2 = gsub("+-","-",eq2,fixed=T)
cat(paste0("\n\n$$",eq2,"$$\n\n"))

cat("Square both sides.\n\n")
eq3 = paste0(m,"x+",n,"=x^2+",2*psi,"x+",psi^2)
eq3 = gsub("+-","-",eq3,fixed=T)
cat(paste0("\n\n$$",eq3,"$$\n\n"))

ls3 = paste0(m,"x+",n)
ls3 = gsub("+-","-",ls3,fixed=T)
cat("Subtract $(",ls3,")$ from both sides.\n\n")

eq4 = paste0("0=x^2+",2*psi-m,"x+",psi^2-n)
eq4 = gsub("+-","-",eq4,fixed=T)
cat(paste0("\n\n$$",eq4,"$$\n\n"))

cat("Now, the problem tells us the solutions are complex (not real), so jump right to quadratic formula (instead of trying to factor).\n\n")
a = 1
b = 2*psi-m
c = psi^2-n
qf1 = paste0("x=\\frac{-(",b,")\\pm\\sqrt{(",b,")^2-4(",a,")(",c,")}}{2(",a,")}")
cat(paste0("\n\n$$",qf1,"$$\n\n"))

qf2 = paste0("x=\\frac{",-b,"\\pm\\sqrt{",b^2,"-",4*a*c,"}}{",2*a,"}")
cat(paste0("\n\n$$",qf2,"$$\n\n"))

qf3 = paste0("x=\\frac{",-b,"\\pm\\sqrt{",b^2-4*a*c,"}}{",2*a,"}")
cat(paste0("\n\n$$",qf3,"$$\n\n"))

qf4 = paste0("x=\\frac{",-b,"\\pm",2*a*q,"i}{",2*a,"}")
cat(paste0("\n\n$$",qf4,"$$\n\n"))

qf5 = paste0("x=",-p,"\\pm",q,"i")
cat(paste0("\n\n$$",qf5,"$$\n\n"))

cat(paste0("So, $p=",-p,"$ and "))

```

So, $p=`r -p`$ and $q=`r q`$

Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: sqrt_line_complex