```{r,echo=FALSE}

# sqrt(x+a)+b = sqrt(x+c)
# x+a + 2b*sqrt(x+a) + b^2 = x+c
# sqrt(x+a) = (c-a-b^2)/(2b)
# x+a = (c-a-b^2)^2/(4b^2)
# x = (c-a-b^2)^2/(4b^2)-a

isval = sample(c(T,F),1)
if(isval){
    ans2 = "valid"
} else {
    ans2 = "extraneous"
}

while(T){
    abc = sample(1:9,3)*sample(c(-1,1),3,T)
    a = abc[1]
    b = abc[2]
    c = abc[3]
    xposs = (c-a-b^2)^2/(4*b^2)-a
    ls = sqrt(xposs+a)+b
    rs = sqrt(xposs+c)
    if((ls==rs)==isval && xposs%%1==0 && abs(xposs)<17 && abs(c-a-b^2)>0){break}
}
eq = paste0("\\sqrt{x+",a,"}+",b,"=\\sqrt{x+",c,"}")
eq = gsub("+-","-",eq,fixed=T)

ach1 = -16:16
ach2 = c("extraneous","valid")

al1 = paste0("* x=",ach1,collapse="\n")
al2 = paste0("* ",ach2,collapse="\n")

sol1 = paste0(1*(ach1==xposs),collapse="")
sol2 = paste0(1*(ach2==ans2),collapse="")

```

Question
========

Find the possible solution, and determine whether the solution is valid or extraneous.

$$`r eq`$$

To get rid of the radicals, you'll need to isolate them and square both sides of the equation, one radical at a time.


* Possible solution: ##ANSWER1##

* The possible solution is ##ANSWER2##.

Answerlist
--------

`r al1`
`r al2`

Solution
========

$$`r eq`$$

We begin with an isolated radical on the right side, so we can square both sides.

```{r,echo=F,results="asis"}
eq = paste0("(\\sqrt{x+",a,"}+",b,")^2=(\\sqrt{x+",c,"})^2")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$"))

cat("\n\nThe left side will need to be FOILed. On the right side, the inverse operations cancel out.\n\n")

eq = paste0("(\\sqrt{x+",a,"}+",b,")(\\sqrt{x+",a,"}+",b,")=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("(x+",a,")+",2*b,"\\sqrt{x+",a,"}+(",b,")^2=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("x+",a,"+",2*b,"\\sqrt{x+",a,"}+",b^2,"=x+",c)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("Subtract $x+",a,"+",b^2,"$ from both sides.\n\n"))

eq = paste0(2*b,"\\sqrt{x+",a,"}=",c-a-b^2)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("Divide both sides by $",2*b,"$.\n\n"))

eq = paste0("\\sqrt{x+",a,"}=",round((c-a-b^2)/(2*b)))
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat("Square both sides.\n\n")

eq = paste0("x+",a,"=",round((c-a-b^2)/(2*b))^2)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))


if(a>0){
    cat("Subtract ",a," from both sides.")
} else {
    cat("Add ",-a," to both sides.")
}

eq = paste0("x=",round((c-a-b^2)/(2*b))^2-a)
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

cat(paste0("So, our possible solution is $x=",round((c-a-b^2)/(2*b))^2-a,"$. We need to check if this satisfies the given equation."))


eq = paste0("\\sqrt{",xposs,"+",a,"}+",b,"\\stackrel{?}{=}\\sqrt{",xposs,"+",c,"}")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0("\\sqrt{",xposs+a,"}+",b,"\\stackrel{?}{=}\\sqrt{",xposs+c,"}")
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

eq = paste0(sqrt(xposs+a),"+",b,"\\stackrel{?}{=}",sqrt(xposs+c))
eq = gsub("+-","-",eq,fixed=T)
cat(paste0("$$",eq,"$$\n\n"))

if(isval){
    eq = paste0(sqrt(xposs+a)+b,"=",sqrt(xposs+c))
    eq = gsub("+-","-",eq,fixed=T)
    cat(paste0("$$",eq,"$$\n\n"))
    cat(paste0("So, the possible solution $x=",xposs,"$ is valid."))
} else {
    eq = paste0(sqrt(xposs+a)+b,"\\ne ",sqrt(xposs+c))
    eq = gsub("+-","-",eq,fixed=T)
    cat(paste0("$$",eq,"$$\n\n"))
    cat(paste0("So, the possible solution $x=",xposs,"$ is extraneous."))
}

```


Meta-information
============
extype: cloze
exclozetype: schoice|schoice
exsolution: `r sol1`|`r sol2`
exname: two_rad_eq