```{r,echo=FALSE}
library(latex2exp)
options(scipen=99)
# (x-(r+mi))(x-(r-mi))(dx-n)
# r+mi, r-mi, and n/d
# (x^2-2rx+(r^2+m^2))(dx-n)
# dx^3+(-n-2rd)x^2+(2rn+dr^2+dm^2)x+(-nr^2-nm^2)

ndposs = list(c(3,2),c(5,2),c(7,2),c(9,2),
              c(2,3),c(4,3),c(5,3),c(7,3),c(8,3),
              c(3,4),c(5,4),c(7,4),c(9,4),
              c(2,5),c(3,5),c(4,5),c(6,5),c(7,5),c(8,5),c(9,5),
              c(5,6),c(7,6),
              c(2,7),c(3,7),c(4,7),c(5,7),c(6,7),c(8,7),c(9,7),
              c(3,8),c(5,8),c(7,8),c(9,8),
              c(2,9),c(4,9),c(5,9),c(7,9))

nds = sample(ndposs,2)
r = nds[[1]][1]*sample(c(-1,1),1)
m = nds[[1]][2]*sample(c(-1,1),1)
n = sample(2:9,1)*sample(c(-1,1),1)
d = 1 #nds[[2]][2]
A = d
B = -n-2*r*d
C = 2*r*n+d*r^2+d*m^2
D = -n*r^2-n*m^2
cf3 = c(A,B,C,D)


cn = function(real,imag){
    ss = paste0(real,"+",imag,"i")
    ss = gsub("+-","-",ss,fixed=T)
    return(ss)
}

pn = function(c,d){
    d = d[c!=0]
    c = c[c!=0]
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}


```

Question
========

Consider the cubic function shown below:

$$f(x)~=~`r pn(cf3,3:0)`$$

One root is $`r cn(r,m)`$.

$$f(`r cn(r,m)`)=0$$

Find a real solution to the equation below.

$$`r pn(cf3,3:0)`=0$$

Solution
========

When polynomials with real coefficients have complex roots, we know complex roots come as complex-conjugate pairs. In other words, since $`r cn(r,m)`$ is a root, we also know $`r cn(r,-m)`$ is a root. Thus, if $a$ is the real root (the number we are looking for), we can express function $f$ as the product of three factors.

$$f(x)~=~(x-a)(x-(`r cn(r,m)`))(x-(`r cn(r,-m)`))$$

Distribute the negative across the inner parentheses.

```{r,echo=F}
f2 = paste0("(x-a)(x+",-r,"+",-m,"i)(x+",-r,"+",m,"i)")
f2 = gsub("+-","-",f2,fixed=T)
```

$$f(x)~=~`r f2`$$


Multiply the two complex-root factors using a box.

```{r,echo=F,fig.dim=c(3,2)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(0,4),ylim=c(0,4))
abline(v=1)
abline(h=3)
va = -0.5
text(0.5,3.5,"*")
text(0.5,2.1,"x",adj=c(0.5,va))
text(0.5,1.1,-r,adj=c(0.5,va))
text(0.5,0.1,paste0(-m,"i"),adj=c(0.5,va))
text(1.5,3.1,"x",adj=c(0.5,va))
text(2.5,3.1,-r,adj=c(0.5,va))
text(3.5,3.1,paste0(m,"i"),adj=c(0.5,va))

text(1.5,2.1,TeX(paste0("$x^2$")),adj=c(0.5,va))
text(2.5,2.1,TeX(paste0("$",-r,"x$")),adj=c(0.5,va))
text(3.5,2.1,TeX(paste0("$",m,"ix$")),adj=c(0.5,va))

text(1.5,1.1,TeX(paste0("$",-r,"x$")),adj=c(0.5,va))
text(2.5,1.1,r^2,adj=c(0.5,va))
text(3.5,1.1,TeX(paste0("$",-r*m,"i$")),adj=c(0.5,va))

text(1.5,0.1,TeX(paste0("$",-m,"ix$")),adj=c(0.5,va))
text(2.5,0.1,TeX(paste0("$",r*m,"i$")),adj=c(0.5,va))
text(3.5,0.1,TeX(paste0("$-",m^2,"i^2$")),adj=c(0.5,va))
```
\

Notice some of those terms cancel when combining like terms.

```{r,echo=F}

# (x-r-mi)(x-r+mi)

f3 = paste0("(x-a)(x^2+",-2*r,"x+",r^2,"+",-m^2,"i^2)")
f3 = gsub("+-","-",f3,fixed=T)
```

$$f(x)~=~`r f3`$$

Remember that $i^2=-1$.

```{r,echo=F}

# (x-r-mi)(x-r+mi)

f4 = paste0("(x-a)(x^2+",-2*r,"x+",r^2,"+",-m^2,"(-1))")
f4 = gsub("+-","-",f4,fixed=T)

f5 = paste0("(x-a)(x^2+",-2*r,"x+",r^2,"+",m^2,")")
f5 = gsub("+-","-",f5,fixed=T)

f6 = paste0("(x-a)(x^2+",-2*r,"x+",r^2+m^2,")")
f6 = gsub("+-","-",f6,fixed=T)
```


$$f(x)~=~`r f4`$$

$$f(x)~=~`r f5`$$

$$f(x)~=~`r f6`$$

NOT DONE... I guess show division from here...


Meta-information
============
extype: num
exsolution: `r n`
exname: x_standard_2_rat_1_comp