---
output: pdf_document
params:
    rseed: 0
    showsol: true
header-includes:
  - \usepackage{multicol}
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]

pn = function(c,d){
    p = paste0("{",c,"}x^{",d,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    p = gsub("-{1i}","-i",p,fixed=T)
    p = gsub("+{1i}","+i",p,fixed=T)
    return(p)
}

gcd2 <- function(a, b) {
  if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))
```

Name: \vspace{5pt} \hrule

## `r bn` (version `r params$rseed`)

### Multiply.

Expand the product and combine like terms to create an equivalent polynomial in standard form.

```{r}
while(T){
    ca = sample(1:6,3)*c(1,sample(c(-1,1),2,T))
    cb = sample(1:6,3)*c(1,sample(c(-1,1),2,T))
    c4 = ca[1]*cb[1]
    c3 = ca[1]*cb[2]+ca[2]*cb[1]
    c2 = ca[1]*cb[3]+ca[2]*cb[2]+ca[3]*cb[1]
    c1 = ca[2]*cb[3]+ca[3]*cb[2]
    c0 = ca[3]*cb[3]
    cr = c(c4,c3,c2,c1,c0)
    if(min(abs(cr))>0){break}
}
A = pn(ca,2:0)
B = pn(cb,2:0)
R = pn(cr,4:0)

```

$$\left(`r A`\right)\cdot\left(`r B`\right)$$
\vfill 

\color{red}

```{r,results='asis'}
cE = numeric()
dE = numeric()

for(i in 2:0){
    for(j in 2:0){
        cE = c(cE,ca[3-i]*cb[3-j])
        dE = c(dE,i+j)
    }
}

if(params$showsol){
    cat(paste0("$$",pn(cE,dE),"$$\n\n"))
    cat(paste0("$$",R,"$$"))
}
```

\color{black}

\vfill

\newpage

## `r bn` (version `r params$rseed`)

### Divide.

Use **polynomial long division** to find an equivalent expression in the form $p(x)+\frac{R}{d(x)}$, where $p(x)$ is a polynomial, $R$ is the remainder, and $d(x)$ is the divisor.

```{r}
while(T){
    cQ = sample(2:6,3)*c(1,sample(c(-1,1),2,T)) # ax^2 + bx + c
    cD = sample(1:6,1)*sample(c(-1,1),1) #x+d
    R = sample(1:9,1)*sample(c(-1,1),1)
    cN = c(cQ[1],cQ[1]*cD+cQ[2],cQ[2]*cD+cQ[3],cQ[3]*cD+R)
    Q = pn(cQ,2:0)
    D = pn(c(1,cD),1:0)
    N = pn(cN,3:0)
    if(min(abs(cN))>0){
        break
    }
}
```

$$\frac{`r N`}{`r D`}$$

\vfill

\color{red}

```{r,results='asis'}
if(params$showsol){
    cat(paste0("$$",Q,"+\\frac{",R,"}{",D,"}$$"))
}
```

\color{black}

\vfill