```{r,echo=F}
myorder = sample(1:4)
wrds = c("translation","rotation","glide","mirror")
mywrds = wrds[myorder]

al = paste0("* ",wrds,collapse="\n")
sol1 = paste0(1*(myorder[1]==1:4),collapse="")
sol2 = paste0(1*(myorder[2]==1:4),collapse="")
sol3 = paste0(1*(myorder[3]==1:4),collapse="")
sol4 = paste0(1*(myorder[4]==1:4),collapse="")

getbasedots = function(fg=1,n=4){
    x = runif(2*n,0.05,0.95)
    y = runif(2*n)-0.5
    h = runif(2*n)
    p = sample(c(15,16,18,19,20),2*n,T)
    dots = data.frame(x,y,h,p)
    return(dots)
}

translate = function(dots,dx=1){
    tdots = data.frame(dots)
    tdots$x = dots$x+dx
    return(tdots)
}
rotate = function(dots,xr){
    tdots = data.frame(dots)
    tdots$x = tdots$x-xr
    tdots$x = -tdots$x+xr
    tdots$y = -tdots$y
    return(tdots)
}
glide = function(dots,dx){
    tdots = data.frame(dots)
    tdots$x = tdots$x+dx
    tdots$y = -tdots$y
    return(tdots)
}
mirror = function(dots,xr){
    tdots = data.frame(dots)
    tdots$x = tdots$x-xr
    tdots$x = -tdots$x+xr
    return(tdots)
}

```

Question
========

Label the four transformations below:

## Transformation 1

```{r,echo=F,fig.dim=c(4,2)}
lwd=2
col = "grey"
par(mar=c(0,0,0,0))
dots = getbasedots(1,10)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[1]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
polygon(dots$x,dots$y,lwd=lwd,col=col)
polygon(d2$x,d2$y,lwd=lwd,col=col)
# cols = hsv(runif(length(dots$x),0,1),0.7,0.7)
cols = hsv(abs((dots$x)*(dots$y+0.5)+runif(1))%%1,0.7,0.7)
# points(dots$x,dots$y,col=cols,pch=dots$p,cex=2)
# points(d2$x,d2$y,col=cols,pch=dots$p,cex=2)
abline(v=seq(-0.1,2,1.1),lty=2)
```
\

* ##ANSWER1##


## Transformation 2

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
dots = getbasedots(1,10)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[2]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
polygon(dots$x,dots$y,lwd=lwd,col=col)
polygon(d2$x,d2$y,lwd=lwd,col=col)
# cols = hsv(runif(length(dots$x),0,1),0.7,0.7)
cols = hsv(abs((dots$x)*(dots$y+0.5)+runif(1))%%1,0.7,0.7)
# points(dots$x,dots$y,col=cols,pch=dots$p,cex=2)
# points(d2$x,d2$y,col=cols,pch=dots$p,cex=2)
abline(v=seq(-0.1,2,1.1),lty=2)
```
\

* ##ANSWER2##


## Transformation 3

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
dots = getbasedots(1,10)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[3]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
polygon(dots$x,dots$y,lwd=lwd,col=col)
polygon(d2$x,d2$y,lwd=lwd,col=col)
# cols = hsv(runif(length(dots$x),0,1),0.7,0.7)
cols = hsv(abs((dots$x)*(dots$y+0.5)+runif(1))%%1,0.7,0.7)
# points(dots$x,dots$y,col=cols,pch=dots$p,cex=2)
# points(d2$x,d2$y,col=cols,pch=dots$p,cex=2)
abline(v=seq(-0.1,2,1.1),lty=2)
```
\

* ##ANSWER3##

## Transformation 4

```{r,echo=F,fig.dim=c(4,2)}
par(mar=c(0,0,0,0))
dots = getbasedots(1,10)
funcs = list(translate(dots,1),rotate(dots,1),glide(dots,1),mirror(dots,1))
d2 = funcs[[myorder[4]]]
plot(0,0,type="n",xlim=c(0,2),ylim=c(-0.5,0.5),axes=F,ann=F)
polygon(dots$x,dots$y,lwd=lwd,col=col)
polygon(d2$x,d2$y,lwd=lwd,col=col)
# cols = hsv(runif(length(dots$x),0,1),0.7,0.7)
cols = hsv(abs((dots$x)*(dots$y+0.5)+runif(1))%%1,0.7,0.7)
# points(dots$x,dots$y,col=cols,pch=dots$p,cex=2)
# points(d2$x,d2$y,col=cols,pch=dots$p,cex=2)
abline(v=seq(-0.1,2,1.1),lty=2)
```
\

* ##ANSWER4##




Answerlist
--------

`r al`
`r al`
`r al`
`r al`


Solution
========

* Transformation 1: `r mywrds[1]`.
* Transformation 2: `r mywrds[2]`.
* Transformation 3: `r mywrds[3]`.
* Transformation 4: `r mywrds[4]`.

`r myorder`

Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: trarotglimir_rainbownet