---
output: pdf_document
params:
    rseed: 0
    showsol: true
header-includes:
  - \usepackage{multicol}
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]

qqq = 0
qn = function(){
    qqq <<- qqq+1
    return(qqq)
}

```

# `r bn`

## Question `r qn()`

Solve the linear equation. $$5=\frac{x}{3}-2$$

a. $x=13$
b. $x=17$
c. $x=19$
d. $x=21$

\vfill 

## Question `r qn()`

Let a function be defined as $$f(x)=\sqrt[3]{x+2}-5$$

Find the inverse function.

a. $f^{-1}(x)=(x+5)^3-2$
b. $f^{-1}(x)=(x+5)^3+2$
c. $f^{-1}(x)=(x+2)^3-5$
d. $f^{-1}(x)=(x+2)^3+5$

\vfill 

## Question `r qn()`

Solve the radical equation. $$8=17-\sqrt{3x}$$

a. $x=3$
b. $x=9$
c. $x=27$
d. $x=81$

\vfill 


## Question `r qn()`

Find both solutions to the quadratic equation.
$$(2x-3)(5x+7)=0$$

a. $x=\frac{3}{2}$ and $x=\frac{-7}{5}$
b. $x=\frac{-3}{2}$ and $x=\frac{7}{5}$
c. $x=\frac{2}{3}$ and $x=\frac{-5}{7}$
d. $x=\frac{-2}{3}$ and $x=\frac{5}{7}$

\vfill 


## Question `r qn()`

Which of the following represents the quadratic formula. If $ax^2+bx+c=0$, then:

a. $x=\frac{b\pm\sqrt{b^2+4ac}}{2a}$
b. $x=\frac{-b\pm\sqrt{b^2+4ac}}{2a}$
c. $x=\frac{b\pm\sqrt{b^2-4ac}}{2a}$
d. $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$



\newpage


## Question `r qn()`

Factor the quadratic expression $x^2+3x-4$.

a. $(x+4)(x-1)$
b. $(x-3)(x-1)$
c. $(x+2)(x-2)$
d. $(x-2)(x-2)$

\vfill 

## Question `r qn()`

Factor the quadratic expression $6x^2+x-12$.

a. $(6x+1)(x-12)$
b. $(6x-1)(x+12)$
c. $(3x+4)(2x-3)$
d. $(3x-4)(2x+3)$

\vfill

## Question `r qn()`

<!-- (x+1)(x+2) -->

Expand the quadratic expression $(x+1)(x+2)$

a. $x^2+2$
b. $2x+3$
c. $x^2+x+3$
d. $x^2+3x+2$

\vfill

## Question `r qn()`

Expand the quadratic polynomial with complex roots. $$(x-6-7i)(x-6+7i)$$

a. $x^2-12x+85$
b. $x^2-12x+13$
c. $x^2+12x+85$
d. $x^2+12x+13$

\vfill

## Question `r qn()`

Find both solutions to the quadratic equation.
$$0=x^2-8x+28$$

a. $x=4\pm2i\sqrt{3}$
b. $x=4\pm3i\sqrt{2}$
c. $x=4\pm4i\sqrt{11}$
d. $x=4\pm11i\sqrt{4}$

\vfill

\newpage

On this page, all questions refer to the figure below.

```{r,echo=F,fig.dim=c(3,3)}
# -sqrt(x+6)+5
# y = 1/2(x+5)+4
xr = seq(-6,10,0.001)
yr = -sqrt(xr+6)+5
xl = seq(-10,10,0.1)
yl = 1/2*(xl+5)+4
xl = xl[yl<=10]
yl = yl[yl<=10]

par(pty="s",mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),ann=F,axes=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(10,0,"x",adj=c(-0.2,-0.2))
text(0,10,"y",adj=c(-0.2,-0.2))
text(10,0,"10",adj=c(0.5,1.2),cex=0.7)
text(0,10,"10",adj=c(1.1,0.5),cex=0.7)

lines(xr,yr,col="red",lwd=2)
lines(xl,yl,col="blue",lwd=2)
legend(-9,-5,c("y=f(x)","y=g(x)"),col=c("blue","red"),lwd=c(2,2))
```
\

## Question `r qn()`

What is the equation of the line in point-slope form?

a. $f(x)=\frac{1}{2}(x-5)+4$
b. $f(x)=\frac{1}{2}(x+5)+4$
c. $f(x)=\frac{1}{2}(x-5)-4$
d. $f(x)=\frac{1}{2}(x+5)-4$


## Question `r qn()`

What is the equation of the radical curve?

a. $g(x)=-\sqrt{x+6}+5$
b. $g(x)=\sqrt{-(x+6)}+5$
c. $g(x)=-\sqrt{x-6}+5$
d. $g(x)=\sqrt{-(x-6)}+5$

## Question `r qn()`

What is the valid solution to $f(x)=g(x)$?

a. $x=-6$
b. $x=-5$
c. $x=3$
d. $x=4$

## Question `r qn()`

What is the extraneous solution to $f(x)=g(x)$?

a. $x=-6$
b. $x=-5$
c. $x=3$
d. $x=4$

\newpage

## Question `r qn()`

Expand the cubed binomial. $$(2x+1)^3$$

a. $8x^3+12x^2+6x+1$
b. $6x+3$
c. $8x^3+1$
d. $8x^3+4x^2+2x+1$


## Question `r qn()`

Expand the product. $$(2x^3+x^2+3)(5x^2-3x+1)$$

<!-- (2x^3+x^2+3)(5x^2-3x+1) = 10x^5-x^4-x^3+16x^2-9x+3 -->

a. $2x^3+6x^2-3x+4$
b. $10x^5-x^4+14x^3-8x^2+3$
c. $2x^3-6x^2+3x-4$
d. $10x^5-x^4-x^3+16x^2-9x+3$


## Question `r qn()`

Find the equivalent expression. $$\frac{3x^4-8x^3+6x+6}{x-2}$$

a. $3x^3-2x^2+x+8$
b. $3x^3-2x^2-4x-3-\frac{5}{x-2}$
c. $3x^3-14x-9-\frac{7}{x-2}$
d. $3x^3+2x-x-8$


## Question `r qn()`

If $f(x)$ is a polynomial such that $f(4)=0$, then we know:

a. The $y$ intercept is at $(0,-4)$.
a. The $y$ intercept is at $(0,4)$.
c. The remainder of $\frac{f(x)}{x-4}$ is 0.
d. The remainder of $\frac{f(x)}{x+4}$ is 0.

## Question `r qn()`

Consider the polynomial function $f(x)=10x^8-3x^4+5x^3-8x-10$. Where is the $y$ intercept?

a. $(-10,0)$
b. $(0,-10)$
c. $(10,0)$
d. $(0,10)$

\newpage

## Question `r qn()`

Factor the cubic polynomial.
$$x^3-5x^2-2x+24$$

a. $(x-2)(x-3)(x+4)$
b. $(x-2)(x+3)(x-4)$
c. $(x+2)(x-3)(x-4)$
d. $(x-2)(x-3)(x-4)$


## Question `r qn()`

Which polynomial matches the sketch below?

```{r,echo=F,fig.dim=c(6,2)}
# (x+3)(x-2)^2
# (x+3)(x^2-4x+4)
# x^3-x^2-8x+12

# -(x+3)^2(x-2)
# -(x^2+6x+9)(x-2)
# -(x^3+4x^2-3x-18)
# -x^3-4x^2+3x+18
# -3x^2-8x+3
# (8-sqrt(64+4*3*3))/(-6)
# (8-sqrt(64+4*3*3))/(-6)

xs = seq(-5,5,0.01)
ys = -(xs+3)^2*(xs-2)

par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-20,20),axes=F,ann=F)
for(i in 1:5){
    lines(c(i,i),c(-1,1))
    lines(c(-i,-i),c(-1,1))
}
abline(h=0)
abline(v=0)
text(5,0,"5",adj=c(0.5,1.5))
text(-5,0,"-5",adj=c(0.5,1.5))
text(5,0,"x",adj=c(-1,-0.2))
text(0,20,"y",adj=c(-0.5,0))
lines(xs,ys,col="blue",lwd=2)
```

a. $y=x^3+4x^2-3x-18$
b. $y=-x^3-4x^2+3x+18$
c. $y=x^3-x^2-8x+12$
d. $y=-x^3+x^2+8x-12$


## Question `r qn()`

```{r,echo=FALSE}
set.seed(8)
n = 5 #sample(2:5,1)
while(T){
    root = sort(sample(1:8,n)*sample(c(-1,1),n,T))
    pows = sample(1:2,n,T)
    pow2 = sample(1:2,n,T)
    if(min(diff(root))>1 && max(diff(root))<7 && sum(pows==pow2)!=n && sum(pows)>n && sum(pows)<2*n){break}
}

a = sample(c(-1,1),1)
ord = sample(1:n)
rmix = root[ord]
pmix = pows[ord]
pmix2 = pow2[ord]

if(a==1){
    exp1 = paste0("(x+",-rmix,")^",pmix,collapse="")
    exp2 = paste0("(x+",-rmix,")^",pmix2,collapse="")
    exp3 = paste0("-",paste0("(x+",-rmix,")^",pmix,collapse=""))
    exp4 = paste0("-",paste0("(x+",-rmix,")^",pmix2,collapse=""))
    exp5 = paste0("(x+",-root,")^",pows,collapse="")
    exp6 = paste0("a",paste0("(x+",-root,")^",pows,collapse=""))
} else {
    exp1 = paste0("-",paste0("(x+",-rmix,")^",pmix,collapse=""))
    exp2 = paste0("-",paste0("(x+",-rmix,")^",pmix2,collapse=""))
    exp3 = paste0("(x+",-rmix,")^",pmix,collapse="")
    exp4 = paste0("(x+",-rmix,")^",pmix2,collapse="")
    exp5 = paste0("-",paste0("(x+",-root,")^",pows,collapse=""))
    exp6 = paste0("a",paste0("(x+",-root,")^",pows,collapse=""))
}
exp1 = gsub("+-","-",exp1,fixed=T)
exp2 = gsub("+-","-",exp2,fixed=T)
exp3 = gsub("+-","-",exp3,fixed=T)
exp4 = gsub("+-","-",exp4,fixed=T)
exp5 = gsub("+-","-",exp5,fixed=T)
exp6 = gsub("+-","-",exp6,fixed=T)

exp1 = gsub("^1","",exp1,fixed=T)
exp2 = gsub("^1","",exp2,fixed=T)
exp3 = gsub("^1","",exp3,fixed=T)
exp4 = gsub("^1","",exp4,fixed=T)
exp5 = gsub("^1","",exp5,fixed=T)
exp6 = gsub("^1","",exp6,fixed=T)

exps = sample(c(exp1,exp2,exp3,exp4))
al = paste0(letters[1:4],". $y=",exps,"$",collapse="\n")
sol = paste0(1*(exps==exp1),collapse="")
```

A polynomial is sketched below.

```{r,echo=F,fig.dim=c(6,2)}
par(mar=c(0,0,0,0))
plot(0,0,"n",axes=F,ann=F,xlim=c(-10,10),ylim=c(-2,2))
abline(v=0,lwd=1)
abline(h=0,lwd=2)
for(i in -10:10){
    if(i%%5==0 && i!=0){
        lines(c(i,i),c(-0.1,0.1))
        text(i,-0.2,i)
    } else {
        lines(c(i,i),c(-0.05,0.05))
    }
}
xs = root
fx = function(x,a,root,pows){
    b = a
    for(i in 1:length(root)){
        b = b*(x-root[i])^pows[i]
    }
    return(b)
}
xmid = c(xs[1]-1,(xs[2:n]+xs[1:(n-1)])/2,xs[n]+1)
sss = 1.3
xx = xmid[1]
yy = sign(fx(xmid[1],a,root,pows))
mm = -yy*sss
for(i in 1:n){
    xx = c(xx,xs[i])
    yy = c(yy,0)
    if(sign(fx(xs[i]-0.1,a,root,pows))==sign(fx(xs[i]+0.1,a,root,pows))){
        mm = c(mm,0)
    }
    if(sign(fx(xs[i]-0.1,a,root,pows))==-1 && sign(fx(xs[i]+0.1,a,root,pows))==1){
        mm = c(mm,sss)
    }
    if(sign(fx(xs[i]-0.1,a,root,pows))==1 && sign(fx(xs[i]+0.1,a,root,pows))==-1){
        mm = c(mm,-sss)
    }
    xx = c(xx,xmid[i+1])
    if(i<n){
        mm = c(mm,0)
        yy = c(yy,pi/2*sign(fx(xmid[i+1],a,root,pows)))
    } else {
        mm = c(mm,sign(a)*sss)
        yy = c(yy,sign(fx(xmid[i+1],a,root,pows)))
    }
}

xwave = seq(min(xs),max(xs),0.1)
sf = splinefunH(xx,yy,mm)
lines(xwave,sin(sf(xwave)),col="blue",lwd=3)
points(root,rep(0,n),pch=19,col="blue")
xlo = seq(min(xs)-1,min(xs),0.1)
lines(xlo,sf(xlo),col="blue",lwd=3)
xhi = seq(max(xs),max(xs)+1,0.1)
lines(xhi,sf(xhi),col="blue",lwd=3)

# lines(c(max(root),max(root)+2),c(0,2*a),col="blue",lwd=3)
# lines(c(min(root),min(root)-2),c(0,2*a*(-1)^n),col="blue",lwd=3)
arrows(xx[2*n+1],yy[2*n+1],xx[2*n+1]+0.5,yy[2*n+1]+0.5*sign(a)*sss,col="blue",lwd=3,length=0.1,angle=15)
arrows(xx[1],yy[1],xx[1]-0.5,yy[1]+0.5*sign(yy[1])*sss,col="blue",lwd=3,length=0.1,angle=15)
```
\

Which polynomial is best represented by the sketch?

`r al`



\newpage


## Question `r qn()`

What is the minimum degree of the polynomial sketched below?


```{r,echo=F,fig.dim=c(6,2)}
# (x+3)(x-2)^2
# (x+3)(x^2-4x+4)
# x^3-x^2-8x+12

# -(x+3)^2(x-2)
# -(x^2+6x+9)(x-2)
# -(x^3+4x^2-3x-18)
# -x^3-4x^2+3x+18
# -3x^2-8x+3
# (8-sqrt(64+4*3*3))/(-6)
# (8-sqrt(64+4*3*3))/(-6)

xs = seq(-4,4,0.01)
ys = (xs-4)*(xs-2)*(xs)*(xs+2)*(xs+4)
ay = abs(max(ys))

xs = seq(-5,5,0.01)
ys = (xs-4)*(xs-2)*(xs)*(xs+2)*(xs+4)/ay*5+10

par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-5,20),axes=F,ann=F)
for(i in 1:5){
    lines(c(i,i),c(-1,1))
    lines(c(-i,-i),c(-1,1))
}
abline(h=0)
abline(v=0)
text(5,0,"5",adj=c(0.5,1.5))
text(-5,0,"-5",adj=c(0.5,1.5))
text(5,0,"x",adj=c(-1,-0.2))
text(0,20,"y",adj=c(-0.5,0))
lines(xs,ys,col="blue",lwd=2)
```

a. 3
b. 4
c. 5
d. 6


## Question `r qn()`

When using the quadratic formula, if the discriminant is positive, then:

a. There are two real solutions.
b. There is one real solution.
c. There are two complex solutions.
d. There is one complex solution and one real solution.

## Question `r qn()`

Which expression is equivalent to $(x+2)^2-5(x+2)+6$?

a. $x(x-1)$
b. $(x-3)(x-2)$
c. $(x-4)(x+3)$
d. $(x-6)(x+1)$


## Question `r qn()`

Which binomial is a factor of $x^3+6x^2+x-14$?

a. $x-1$
b. $x-2$
c. $x+1$
d. $x+2$

## Question `r qn()`

The solution set for the equation $x+1=\sqrt{4x+25}$ is

a. $\{\}$
b. $\{6\}$
c. $\{6,-4\}$
d. $\{-4\}$

\newpage

## Question `r qn()`

Consider the function plotted below.

```{r,echo=F,fig.dim=c(5,2)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-0.5,1.5),axes=F,ann=F)
abline(h=0)
abline(v=0)
text(5,0,"x",adj=c(0.5,1.2))
text(0,1.5,"y",adj=c(1.2,0.5))
x = seq(-5,5,0.01)
y = (1)/(x^2+1)
lines(x,y,lwd=2,col="blue")

```

The function is:

a. Periodic
b. Even
c. Odd
d. Complex


## Question `r qn()`

Consider the function plotted below.

```{r,echo=F,fig.dim=c(5,2)}
par(mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-5,5),ylim=c(-1.5,1.5),axes=F,ann=F)
abline(h=0)
abline(v=0)
text(5,0,"x",adj=c(0.5,1.2))
text(0,1.5,"y",adj=c(1.2,0.5))
x = seq(-5,5,0.01)
y = x^3/(x^4+1)
lines(x,y,lwd=2,col="blue")

```

The function is:

a. Periodic
b. Even
c. Odd
d. Complex

\newpage


## Question `r qn()`

Consider the function $y=f(x)$ plotted below.

```{r,echo=F,fig.dim=c(2,2)}
mkplot = function(){
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10))
    for(i in -10:10){
        lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
        lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
    }
    for(i in seq(-10,10,5)){
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
    }
    abline(h=0,lwd=2)
    abline(v=0,lwd=2)
    text(10,0,"x",adj=c(0.5,-0.2))
    text(0,10,"y",adj=c(-0.2,0.5))
    text(10,0,"10",adj=c(0.5,1.2),cex=0.7)
    text(0,10,"10",adj=c(1.1,0.5),cex=0.7)
}

par(mar=c(0,0,0,0),pty="s")
mkplot()
x = c(-2,7,9)
y = c(3,4,8)
lines(x,y,col="blue",lwd=2)
```


Which option represents the inverse function, $y=f^{-1}(x)$?

```{r,echo=F,fig.dim=c(5,5)}
par(mfrow=c(2,2),mar=c(2,2,2,2))

mkplot()
x2 = -x
y2 = y
lines(x2,y2,col="blue",lwd=2)
mtext("a",3)

mkplot()
x2 = x
y2 = -y
lines(x2,y2,col="blue",lwd=2)
mtext("b",3)

mkplot()
x2 = -x
y2 = -y
lines(x2,y2,col="blue",lwd=2)
mtext("c",3)

mkplot()
x2 = y
y2 = x
lines(x2,y2,col="blue",lwd=2)
mtext("d",3)
```








