---
output: pdf_document
params:
    rseed: 0
    showsol: true
header-includes:
  - \usepackage{multicol}
---

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]

qqq = 0
qn = function(){
    qqq <<- qqq+1
    return(qqq)
}

```

Name: \vspace{5pt} \hrule

# `r bn` (v`r params$rseed`)

## Question `r qn()`

Solve the linear equation. $$5=\frac{x}{3}-2$$

a. $x=13$
b. $x=17$
c. $x=19$
d. $x=21$

\vfill 

## Question `r qn()`

Solve the radical equation. $$8=17-\sqrt{3x}$$

a. $x=3$
b. $x=9$
c. $x=27$
d. $x=81$

\vfill 


## Question `r qn()`

Find both solutions to the quadratic equation.
$$(2x-3)(5x+7)=0$$

a. $x=\frac{3}{2}$ and $x=\frac{-7}{5}$
b. $x=\frac{-3}{2}$ and $x=\frac{7}{5}$
c. $x=\frac{2}{3}$ and $x=\frac{-5}{7}$
d. $x=\frac{-2}{3}$ and $x=\frac{5}{7}$

\vfill 

\newpage


## Question `r qn()`

Factor the quadratic expression $x^2+3x-4$.

a. $(x+4)(x-1)$
b. $(x-3)(x-1)$
c. $(x+2)(x-2)$
d. $(x-2)(x-2)$

\vfill 

## Question `r qn()`

<!-- (2x+3)(3x-4) = 6x^2-8x+9x-12 -->

Factor the quadratic expression $6x^2+x-12$.

a. $(6x+1)(x-12)$
b. $(6x-1)(x+12)$
c. $(3x+4)(2x-3)$
d. $(3x-4)(2x+2)$

\vfill

## Question `r qn()`

<!-- (x+1)(x+2) -->

Expand the quadratic expression $(x+1)(x+2)$

a. $x^2+2$
b. $2x+3$
c. $x^2+x+3$
d. $x^2+3x+2$

\vfill

## Question `r qn()`

Find both solutions to the quadratic equation.
$$0=x^2-8x+28$$

a. $x=4\pm2i\sqrt{3}$
b. $x=4\pm3i\sqrt{2}$
c. $x=4\pm4i\sqrt{11}$
d. $x=4\pm11i\sqrt{4}$

\vfill

\newpage

On this page, all questions refer to the figure below.

```{r,echo=F,fig.dim=c(3,3)}
# -sqrt(x+6)+5
# y = 1/2(x+5)+4
xr = seq(-6,10,0.001)
yr = -sqrt(xr+6)+5
xl = seq(-10,10,0.1)
yl = 1/2*(xl+5)+4
xl = xl[yl<=10]
yl = yl[yl<=10]

par(pty="s",mar=c(0,0,0,0))
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),ann=F,axes=F)
for(i in -10:10){
    lines(c(i,i),c(-10,10),col="grey",lwd=0.5)
    lines(c(-10,10),c(i,i),col="grey",lwd=0.5)
}
for(i in seq(-10,10,5)){
    lines(c(i,i),c(-10,10),col="darkgrey",lwd=1)
    lines(c(-10,10),c(i,i),col="darkgrey",lwd=1)
}
abline(h=0,lwd=2)
abline(v=0,lwd=2)
text(10,0,"x",adj=c(-0.2,-0.2))
text(0,10,"y",adj=c(-0.2,-0.2))
text(10,0,"10",adj=c(0.5,1.2),cex=0.7)
text(0,10,"10",adj=c(1.1,0.5),cex=0.7)

lines(xr,yr,col="red",lwd=2)
lines(xl,yl,col="blue",lwd=2)
legend(-9,-5,c("y=f(x)","y=g(x)"),col=c("blue","red"),lwd=c(2,2))
```
\

## Question `r qn()`

What is the equation of the line in point-slope form?

a. $f(x)=\frac{1}{2}(x-5)+4$
b. $f(x)=\frac{1}{2}(x+5)+4$
c. $f(x)=\frac{1}{2}(x-5)-4$
d. $f(x)=\frac{1}{2}(x+5)-4$


## Question `r qn()`

What is the equation of the radical curve?

a. $g(x)=-\sqrt{x+6}+5$
b. $g(x)=\sqrt{-(x+6)}+5$
c. $g(x)=-\sqrt{x-6}+5$
d. $g(x)=\sqrt{-(x-6)}+5$

## Question `r qn()`

What is the valid solution to $f(x)=g(x)$?

a. $x=-6$
b. $x=-5$
c. $x=3$
d. $x=4$

## Question `r qn()`

What is the extraneous solution to $f(x)=g(x)$?

a. $x=-6$
b. $x=-5$
c. $x=3$
d. $x=4$

\newpage

## Question `r qn()`

Expand the cubed binomial. $$(2x+1)^3$$

a. $8x^3+12x^2+6x+1$
b. $6x+3$
c. $8x^3+1$
d. $8x^3+4x^2+2x+1$


## Question `r qn()`

Expand the product. $$(2x^3+x^2+3)(5x^2-3x+1)$$

<!-- (2x^3+x^2+3)(5x^2-3x+1) = 10x^5-x^4-x^3+16x^2-9x+3 -->

a. $2x^3+6x^2-3x+4$
b. $10x^5-x^4+14x^3-8x^2+3$
c. $2x^3-6x^2+3x-4$
d. $10x^5-x^4-x^3+16x^2-9x+3$


## Question `r qn()`

Find the equivalent expression. $$\frac{3x^4-8x^3+6x+6}{x-2}$$

a. $3x^3-2x^2+x+8$
b. $3x^3-2x^2-4x-3-\frac{5}{x-2}$
c. $3x^3-14x-9-\frac{7}{x-2}$
d. $3x^3+2x-x-8$


## Question `r qn()`

If $f(x)$ is a polynomial such that $f(4)=0$, then we know:

a. The $y$ intercept is at $(0,-4)$.
a. The $y$ intercept is at $(0,4)$.
c. The remainder of $\frac{f(x)}{x-4}$ is 0.
d. The remainder of $\frac{f(x)}{x+4}$ is 0.

## Question `r qn()`

Consider the polynomial function $f(x)=10x^8-3x^4+5x^3-8x-10$. Where is the $y$ intercept?

a. $(-10,0)$
b. $(0,-10)$
c. $(10,0)$
d. $(0,10)$

\newpage

## Question `r qn()`

Factor the cubic polynomial.
$$x^3-5x^2-2x+24$$

a. $(x-2)(x-3)(x+4)$
b. $(x-2)(x+3)(x-4)$
c. $(x+2)(x-3)(x-4)$
d. $(x-2)(x-3)(x-4)$


## Question `r qn()`

Which polynomial matches the sketch below?

```{r,echo=F,fig.dim=c(6,2)}
# -(x+4)()

```






