---
output: pdf_document
params:
    rseed: 0
    showsol: false
---

\renewcommand{\arraystretch}{1.2}

```{r,echo=F,warning=FALSE,message=FALSE}
options(scipen=999)
if(params$rseed !=0){
    set.seed(params$rseed)
}
knitr::opts_chunk$set(echo = FALSE)
bn <- basename(knitr::current_input())
bn = strsplit(bn,".",fixed=T)[[1]][1]

pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    ex1 = gsub("{","",ex1,fixed=T)
    ex1 = gsub("}","",ex1,fixed=T)
    return(ex1)
}
```

Name: \vspace{0.1in} \hrule

## `r bn` (v_`r params$rseed`)

### Question 1: standard-form cubic equation from solutions (10 points)

```{r,echo=F}
rat_pairs = list(c(1,1),c(1,2),c(1,3),c(1,4),c(1,5),c(1,6),c(1,7),c(1,8),c(1,9),
                 c(2,1),c(2,3),c(2,5),c(2,7),c(2,9),
                 c(3,1),c(3,2),c(3,4),c(3,5),c(3,7),c(3,8),
                 c(4,1),c(4,3),c(4,5),c(4,7),c(4,9),
                 c(5,1),c(5,2),c(5,3),c(5,4),c(5,6),c(5,7),c(5,8),c(5,9),
                 c(6,1),c(6,5),c(6,7),
                 c(7,1),c(7,2),c(7,3),c(7,4),c(7,5),c(7,6),c(7,8),c(7,9),
                 c(8,1),c(8,3),c(8,5),c(8,7),c(8,9),
                 c(9,1),c(9,2),c(9,4),c(9,5),c(9,7),c(9,8))
while(T){
    rps = sample(rat_pairs,3)
    a = rps[[1]][1]
    b = rps[[1]][2]*sample(c(-1,1),1)
    c = rps[[2]][1]
    d = rps[[2]][2]*sample(c(-1,1),1)
    e = rps[[3]][1]
    f = rps[[3]][2]*sample(c(-1,1),1)
    A = a*c*e
    B = a*c*f+a*d*e+b*c*e
    C = a*d*f+b*c*f+b*d*e
    D = b*d*f
    p = c*e
    q = c*f+d*e
    r = d*f
    p2 = a*e
    q2 = a*f+b*e
    r2 = b*f
    p3 = a*c
    q3 = a*d+b*c
    r3 = b*d
    cfs = c(a,b,c,d,e,f,A,B,C,D,p,q,r)
    cubic = pn(c(A,B,C,D),3:0)
    if(min(abs(cfs))>0 && max(abs(cfs))<1000 && max(c(c,e))>1 && a>1 && A!=D && abs(sum(sign(c(b,d,f))))<3 && cubic != "8x^3+42x^2+19x-105"){break}
}

cubic1 = cubic

mkfrac = function(top,bot){
    if(bot>1){
        return(paste0("\\frac{",top,"}{",bot,"}"))
    } else {
        return(paste0(top))
    }
}
f1 = pn(c(a,b),1:0)
f2 = pn(c(c,d),1:0)
f3 = pn(c(e,f),1:0)
frac1 = mkfrac(-b,a)
frac2 = mkfrac(-d,c)
frac3 = mkfrac(-f,e)
```

Express a cubic equation in standard form with integer coefficients and with the following solutions:
$$\text{solution 1}:~~~x=`r frac3`$$

$$\text{solution 2}:~~~x=`r frac2`$$

$$\text{solution 3}:~~~x=`r frac1`$$

\vfill

\color{red}

```{r,echo=F,results='asis',eval=params$showsol}
cat("First, express the equation in factored form.\n\n")
cat(paste0("$$(",f3,")(",f2,")(",f1,")=0$$\n\n"))
cat("FOIL two of the factors.\n\n")
cat(paste0("\\begin{align*}(",pn(c(p,q,r),2:0),")(",f1,")&=0 &&\\text{or}& (",pn(c(p2,q2,r2),2:0),")(",f2,")&=0 &&\\text{or}& (",pn(c(p3,q3,r3),2:0),")(",f3,")&=0 \\end{align*}\n\n"))
cat("Expand (with a box).\n\n")

tab_lin_qua = function(lc,qc){
    s = paste0("\n\n\\begin{center}\\begin{tabular}{c|ccc}\n")
    s = paste0(s,"$\\cdot$ & ",paste0("$",qc,c("x^2","x",""),"$",collapse=" & ")," \\\\ \\hline\n")
    s = paste0(s,"$",lc[1],"x$ & ",paste0("$",qc*lc[1],c("x^3","x^2","x"),"$",collapse=" & ")," \\\\ \n")
    s = paste0(s,"$",lc[2],"$ & ",paste0("$",qc*lc[2],c("x^2","x",""),"$",collapse=" & "),"\n")
    s = paste0(s,"\\end{tabular}\\end{center}\n\n")
}

cat(tab_lin_qua(c(a,b),c(p,q,r)))
cat("or")
cat(tab_lin_qua(c(c,d),c(p2,q2,r2)))
cat("or")
cat(tab_lin_qua(c(e,f),c(p3,q3,r3)))

cat("\n\nWhichever of the 3 paths you take, you should end up at the same equation by combining like terms.\n\n")
cat(paste0("\\begin{center}\\begin{tabular}{|c|}\\hline \n $",cubic,"~=~0$ \\\\ \\hline \n\\end{tabular}\\end{center}"))

```

\color{black}

\vfill


\newpage

### Question 2: rational solutions from standard-form cubic equation (10 points)


```{r,echo=F}
rat_pairs = list(c(1,1),c(1,2),c(1,3),c(1,4),c(1,5),c(1,6),c(1,7),c(1,8),c(1,9),
                 c(2,1),c(2,3),c(2,5),c(2,7),c(2,9),
                 c(3,1),c(3,2),c(3,4),c(3,5),c(3,7),c(3,8),
                 c(4,1),c(4,3),c(4,5),c(4,7),c(4,9),
                 c(5,1),c(5,2),c(5,3),c(5,4),c(5,6),c(5,7),c(5,8),c(5,9),
                 c(6,1),c(6,5),c(6,7),
                 c(7,1),c(7,2),c(7,3),c(7,4),c(7,5),c(7,6),c(7,8),c(7,9),
                 c(8,1),c(8,3),c(8,5),c(8,7),c(8,9),
                 c(9,1),c(9,2),c(9,4),c(9,5),c(9,7),c(9,8))
while(T){
    rps = sample(rat_pairs,3)
    a = rps[[1]][1]
    b = rps[[1]][2]*sample(c(-1,1),1)
    c = rps[[2]][1]
    d = rps[[2]][2]*sample(c(-1,1),1)
    e = rps[[3]][1]
    f = rps[[3]][2]*sample(c(-1,1),1)
    A = a*c*e
    B = a*c*f+a*d*e+b*c*e
    C = a*d*f+b*c*f+b*d*e
    D = b*d*f
    p = c*e
    q = c*f+d*e
    r = d*f
    cfs = c(a,b,c,d,e,f,A,B,C,D,p,q,r)
    cubic = pn(c(A,B,C,D),3:0)
    if(min(abs(cfs))>0 && max(abs(cfs))<100 && max(c(c,e))>1 && cubic != cubic1 && a==1 && abs(b)>1 && cubic!="35x^3-53x^2-70x+72"){break}
}

mkfrac = function(top,bot){
    if(bot>1){
        return(paste0("\\frac{",top,"}{",bot,"}"))
    } else {
        return(paste0(top))
    }
}
f1 = pn(c(a,b),1:0)
f2 = pn(c(c,d),1:0)
f3 = pn(c(e,f),1:0)
frac1 = mkfrac(-b,a)
frac2 = mkfrac(-d,c)
frac3 = mkfrac(-f,e)
```

Find the three distinct rational solutions (as integers or reduced fractions [improper not mixed if relevant]) to the given cubic equation.  

$$`r cubic`=0$$

Hint: one factor of the cubic polynomial is $`r f1`$.

\vfill

\color{red}

```{r,echo=F,eval=params$showsol,results='asis'}
cat(paste0("Factor out $",f1,"$ from the cubic polynomial.\n\n"))
cat("If you use synthetic division:\n\n")
cat("\\begin{center}\\begin{tabular}{c | c c c c}\n & ",paste0(c(A,B,C,D),collapse=" & "),"\\\\ \n")
cat(paste0(-b," & & ",paste0(c(p,q,r)*-b/a,collapse=" & "),"\\\\ \\cline{2-5} \n"))
cat(paste0(" & ",paste0(c(p,q,r,0),collapse=" & "),"\n\\end{tabular}\\end{center}"))
cat("\n\n")
cat("If you use the box method of division:\n\n")
cat("\\renewcommand{\\arraystretch}{1.2}\n\n")
cat(paste0("\\begin{center}\\begin{tabular}{ | c | c c c | c}\\cline{1-4}\n"))
cat(paste0("$\\cdot$ & ",paste0("$",c(p,q,r),c("x^2","x",""),"$",collapse=" & ")," & remainder \\\\ \\cline{1-4} \n"))
cat("$x$ & ",paste0("$",c(p,q,r),c("x^3","x^2","x"),"$",collapse=" & "), "& 0 \\\\ \n")
cat("$",b,"$ & ",paste0("$",c(p,q,r)*b,c("x^2","x",""),"$",collapse=" & ")," & \\\\ \\cline{1-4}")
cat("\\end{tabular}\\end{center}\n\n")
cat("However you do the work, you can now write an equivalent equation in semi-factored form.\n\n")
cat(paste0("$$(",f1,")(",pn(c(p,q,r),2:0),")=0$$\n\n"))
cat("Use the zero-product property. One solution is found by setting the given linear factor equal to 0. If ")
cat(paste0("$",f1,"=0$ then we know a solution is $x=",-b,"$. "))
cat("The other solutions are found by setting the quadratic factor to 0.")
cat(paste0("$$",pn(c(p,q,r),2:0),"=0$$"))
cat(paste0("$$x~=~\\frac{-(",q,")\\pm\\sqrt{(",q,")^2-4(",p,")(",r,")}}{2(",p,")}$$\n\n"))
if(4*p*r>=0){
    cat(paste0("$$x~=~\\frac{",-q,"\\pm\\sqrt{",q^2,"-",4*p*r,"}}{",2*p,"}$$\n\n"))
} else {
    cat(paste0("$$x~=~\\frac{",-q,"\\pm\\sqrt{",q^2,"-(",4*p*r,")}}{",2*p,"}$$\n\n"))
}
cat(paste0("$$x~=~\\frac{",-q,"\\pm\\sqrt{",q^2-4*p*r,"}}{",2*p,"}$$\n\n"))
cat(paste0("$$x~=~\\frac{",-q,"\\pm ",sqrt(q^2-4*p*r),"}{",2*p,"}$$\n\n"))
cat(paste0("\\begin{align*}x&=",frac2,"&&\\text{or}& x&=",frac3,"\\end{align*}\n\n"))
cat("So, we can write a fully factored equation.")
cat(paste0("\n$$(",f1,")(",f2,")(",f3,")=0$$"))
cat(paste0("And we know the solutions are $x=",frac1,"$ and $x=",frac2,"$ and $x=",frac3,"$.\n"))
cat(paste0("\\begin{center}\\begin{tabular}{|c c c|}\\hline\n $x=",frac1,"$ & $x=",frac2,"$ & $x=",frac3,"$ \\\\ \\hline \n\\end{tabular}\\end{center}"))

```

\color{black}

\vfill


