---
output:
  pdf_document:
    includes:
      in_header: "preamble.tex"
geometry:
  - top=1.5in
  - bottom=1in
  - left=1in
  - right=1in
params:
    rseed: 0
    showsol: false
    useseed: false
---

```{r,echo=F,eval=params$useseed}
set.seed(params$rseed)
```

### Example $5_{90^{\circ}}$

```{=latex}
\begin{minipage}{2in}
```

* Start at the star.
```{r,echo=F,results="asis"}
nums = 1:5
dirs = c("Right","Down","Left","Up")

N = 20
for(i in 0:(N-1)){
    cat(paste0("* ",dirs[i%%length(dirs)+1]," ",nums[i%%length(nums)+1],"\n",collapse=""))
}

```

```{=latex}
\end{minipage}
\begin{minipage}{4.5in}
```

```{r,echo=F,fig.dim=c(3.5,3.5)}
pch = 8

par(mar=c(0,0,0,0),pty="s")
turn = -pi/2
a1 = 0
lengths = 1:5
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
for(i in xlow:xhi){
    for(j in ylow:yhi){
        points(i,j,pch=19,cex=0.4)
    }
}
points(0,0,pch=pch,cex=1)
if(params$showsol){
    lines(xs,ys,col="red")
}

```

```{=latex}
\end{minipage}
```

Notice: four directions and five numbers took **4 cycles** of counting to return to start.


### Example $6_{90^{\circ}}$

```{=latex}
\begin{minipage}{2in}
```

* Start at the star.
```{r,echo=F,results="asis"}
nums = 1:6
dirs = c("Right","Down","Left","Up")

N = 12
for(i in 0:(N-1)){
    cat(paste0("* ",dirs[i%%length(dirs)+1]," ",nums[i%%length(nums)+1],"\n",collapse=""))
}

```

```{=latex}
\end{minipage}
\begin{minipage}{4.5in}
```

```{r,echo=F,fig.dim=c(3.5,3.5)}
pch = 8

par(mar=c(0,0,0,0),pty="s")
turn = -pi/2
a1 = 0
lengths = 1:6
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
for(i in xlow:xhi){
    for(j in ylow:yhi){
        points(i,j,pch=19,cex=0.4)
    }
}
points(0,0,pch=pch,cex=1)
if(params$showsol){
    lines(xs,ys,col="red")
}

```

```{=latex}
\end{minipage}
```

Notice: four directions and six numbers took **2 cycles** of counting to return to start.

\newpage

### Practice $7_{90^{\circ}}$

* Start at the star
* For direction use right, down, left, up (turning clockwise)
* For length use 1, 2, 3, 4, 5, 6, 7 (count from 1 to 7)

```{r,echo=F,fig.dim=c(5,5),fig.align='center'}
pch = 8
par(mar=c(0,0,0,0),pty="s")
turn = -pi/2
a1 = 0
lengths = 1:7
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
for(i in xlow:xhi){
    for(j in ylow:yhi){
        points(i,j,pch=19,cex=0.4)
    }
}
points(0,0,pch=pch,cex=1)
if(params$showsol){
    lines(xs,ys,col="red")
}

```


**How many cycles of counting did it take to return to the start?**


\newpage



\newpage

## Practice $5_{60^{\circ}}$

* Start at star heading down.
* Turn **120° clockwise** after each segment.
    * Down (South)
    * Up-Left (Northwest)
    * Up-Right (Northeast)
* Distances are 1, 2, 3, 4, 5

```{r,echo=F,fig.dim=c(5,5),fig.align='center'}
par(mar=c(0,0,0,0),pty="s")
turn = -2*pi/3
a1 = -pi/2
lengths = 1:5
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
ndl = ceiling(-xlow/cos(pi/3))
ndr = ceiling(xhi/cos(pi/3))
ndd = ceiling(-ylow/sin(pi/3))
ndu = ceiling(yhi/sin(pi/3))

for(i in -ndl:ndr){
    for(j in -ndd:ndu){
        points(i*cos(pi/6),j+0.5*(i%%2),pch=19,cex=0.3)
    }
}
points(0,0,pch=pch,cex=0.8)
# lines(xs[1:5],ys[1:5],col="black")

if(params$showsol){
    lines(xs,ys,col="red")
}
```

* **How many cycles?**

\newpage

## Practice $5_{120^{\circ}}$

* Start at star heading down.
* Turn **60° clockwise** after each segment.
    * Down (South)
    * Down-Left (Southwest)
    * Up-Left (Northwest)
    * Up (North)
    * Up-Right (Northeast)
    * Down-Right (Southeast)
* Distances are 1, 2, 3, 4, 5

```{r,echo=F,fig.dim=c(5,5),fig.align='center'}
par(mar=c(0,0,0,0),pty="s")
turn = -pi/3
a1 = -pi/2
lengths = 1:5
n = 50
a = a1
x = 0
y = 0
xs = c(x)
ys = c(y)
for(i in 0:n){
    l = lengths[(i %% length(lengths)) +1]
    x2 = x+l*cos(a)
    y2 = y+l*sin(a)
    xs = c(xs,x2)
    ys = c(ys,y2)
    x = x2
    y = y2
    a = a+turn
}
minx = min(xs)
maxx = max(xs)
midx = mean(c(minx,maxx))
dx = maxx-minx
miny = min(ys)
maxy = max(ys)
midy = mean(c(miny,maxy))
dy = maxy-miny
dd = max(dx,dy)
rr = dd/2
plot(0,0,"n",xlim=c(midx-rr-2,midx+rr+2),ylim=c(midy-rr-2,midy+rr+2))
xlow = floor(midx-rr)-4
xhi = ceiling(midx+rr)+4
ylow = floor(midy-rr)-4
yhi = ceiling(midy+rr)+4
ndl = ceiling(-xlow/cos(pi/3))
ndr = ceiling(xhi/cos(pi/3))
ndd = ceiling(-ylow/sin(pi/3))
ndu = ceiling(yhi/sin(pi/3))

for(i in -ndl:ndr){
    for(j in -ndd:ndu){
        points(i*cos(pi/6),j+0.5*(i%%2),pch=19,cex=0.3)
    }
}
points(0,0,pch=pch,cex=0.8)
# lines(xs[1:5],ys[1:5],col="black")

if(params$showsol){
    lines(xs,ys,col="red")
}
```

* **How many cycles?**
