```{r,echo=FALSE}
# All right turns
# Expressed with right, up, left, down

n = 5


while(T){
    handles = character()
    x = sample(2:5,n,T)
    turns = sample(c(-1,1),n,T)
    st = cumsum(turns)
    # ths = c(0,pi/2,pi,3*pi/2)
    # dis = c("East","North","West","South")
    ths = c(pi/2,0,3*pi/2,pi)
    dis = c("North","East","South","West")
    j0 = sample(0:3,1)
    jj = (j0+st)%%4+1
    
    tt = ths[jj]
    dd = dis[jj]
    
    xx = c(0)
    yy = c(0)
    
    for(i in 1:n){
        xnew = xx[i]+x[i]*cos(tt[i])
        ynew = yy[i]+x[i]*sin(tt[i])
        xx = c(xx,xnew)
        yy = c(yy,ynew)
        if(dd[i] %in% c("East","West")){
            handles = c(handles,paste0("h",ynew))
        } else {
            handles = c(handles,paste0("v",xnew))
        }
    }
    if(max(abs(xx))<=10 && max(abs(yy))<=10 && length(unique(dd))>2 && length(unique(x))>1 && length(unique(handles))==length(handles)){break}
}


acho = dis
ache = 1:5

alo = paste0("* ",acho,collapse="\n")
ale = paste0("* ",ache,collapse="\n")

sols = character()
for(i in 1:n){
    solo = paste0(1*(dd[i]==acho),collapse="")
    sole = paste0(1*(x[i]==ache),collapse="")
    sols = c(sols,solo,sole)
}

```

Question
========

A turtle starts at the star in the middle. By dragging markers along a grid, she makes `r n` line segments. The first segment is red, and then she changes color after each turn, following the progression of a rainbow.

The distance between adjacent dots is 1 unit. The grid is oriented with North pointing up and East pointing right.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    points(rep(i,21),-10:10,pch=20,cex=0.6)
    points(-10:10,rep(i,21),pch=20,cex=0.6)
}
points(0,0,pch=8,cex=1)

# lines(xx,yy,lwd=2,col="blue")
cols = hsv(seq(0,1,length.out=n+1),0.9,0.9)
for(i in 1:n){
    lines(c(xx[i],xx[i+1]),c(yy[i],yy[i+1]),col=cols[i],lwd=2)
}
```

Describe the path taken by the turtle.

```{r,echo=F,results='asis'}
for(i in 1:n){
    cat(paste0("* ##ANSWER",2*i-1,"## ##ANSWER",2*i,"##\n"))
}
```

Answerlist
--------


```{r,echo=F,results='asis'}
for(i in 1:n){
    cat(alo)
    cat("\n")
    cat(ale)
    cat("\n")
}
```

Solution
========

`r paste0("* ",dd," ",x,collapse="\n")`


Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n*2),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: turtle_path_01