```{r,echo=FALSE}
# All 60-deg turns
n = 6

th0 = pi/2
while(T){
    x = 0
    y = 0
    ends = character()
    dists = sample(1:5,n,T)
    turns = sample(c(-1,1),n-1,T)
    sumturn = cumsum(turns)
    ths = c(th0,th0+sumturn*pi/3+8*pi)%%(2*pi)
    for(i in 1:n){
        xnew = x[i]+dists[i]*cos(ths[i])
        ynew = y[i]+dists[i]*sin(ths[i])
        x = c(x,xnew)
        y = c(y,ynew)
    }
    ends = paste0(x,",",y)
    if(max(abs(x))<=12 && max(abs(y))<=12 && length(unique(turns))>1 && length(unique(dists))>1 && length(ends)==length(unique(ends))){break}
}

acho = 1:5
ache = c("right","left")
turnnames = ache[round(turns/2+1.5)]

sols = paste0(1*(acho==dists[1]),collapse="")

for(i in 2:n){
    sols = c(sols,paste0(1*(ache==turnnames[i-1]),collapse=""))
    sols = c(sols,paste0(1*(acho==dists[i]),collapse=""))
}

alo = paste0("* ",acho,collapse="\n")
ale = paste0("* ",ache,collapse="\n")

```

Question
========

A turtle starts at the star in the middle, facing North. She walks forward for a while, then turns 60° either to her right (clockwise) or to her left (counterclockwise). She repeats this, marking her path with various colors, until she has drawn `r n` segments.

The distance between adjacent dots is 1 unit.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-12,12),ylim=c(-12,12),axes=F,ann=F)
# 
# for(i in -10:10){
#     points(rep(i,21),-10:10,pch=20,cex=0.6)
#     points(-10:10,rep(i,21),pch=20,cex=0.6)
# }
points(0,0,pch=8,cex=1)

# lines(xx,yy,lwd=2,col="blue")
cols = hsv(seq(0,1,length.out=n+1),0.9,0.9)
for(i in 1:n){
    lines(c(x[i],x[i+1]),c(y[i],y[i+1]),col=cols[i],lwd=2)
}

for(i in -20:20){
    for(j in -20:20){
        points(i*cos(pi/6),j+0.5*(i%%2),pch=19,cex=0.2)
    }
}
points(0,0,pch=8,cex=0.8)
```
\


Describe the path taken by the turtle.

```{r,echo=F,results='asis'}
cat(paste0("* Go ##ANSWER1##\n"))
for(i in 2:n){
    cat(paste0("* Turn ##ANSWER",i*2-2,"##\n"))
    cat(paste0("* Go ##ANSWER",i*2-1,"##\n"))
}

```


Answerlist
--------

`r alo`
```{r,echo=F,results='asis'}
for(i in 2:n){
    cat(ale)
    cat("\n")
    cat(alo)
    cat("\n")
}
```



Solution
========

```{r,echo=F,results='asis'}
cat(paste0("* Go ",dists[1],"\n"))
for(i in 2:n){
    cat(paste0("* Turn ",turnnames[i-1],"\n"))
    cat(paste0("* Go ",dists[i],"\n"))
}
```



Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n*2-1),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: turtle_path_C