```{r,echo=F}
options(scipen=999)
gcd2 <- function(a, b) {
    if (b == 0) a else Recall(b, a %% b)
}
gcd <- function(...) Reduce(gcd2, c(...))

drawit = function(L=16,dD=-pi/2,D=-pi/2,n=10000,lwd=1,col="blue"){
    x = c(0)
    y = c(0)
    l = L
    for(i in 1:n){
        x0 = x[i]
        y0 = y[i]
        x2 = x[i]+l*cos(D)
        y2 = y[i]+l*sin(D)
        l = (l-2)%%L+1
        D = D+dD
        x = c(x,x2)
        y = c(y,y2)
        if(abs(x2)<0.001 && abs(y2)<0.001){break}
    }
    xmin = min(x)
    xmax = max(x)
    xmid = mean(c(xmin,xmax))
    ymin = min(y)
    ymax = max(y)
    ymid = mean(c(ymin,ymax))
    r = max(c(xmax-xmid,ymax-ymid))
    xlo = xmid-r
    xhi = xmid+r
    ylo = ymid-r
    yhi = ymid+r
    plot(0,0,"n",ann=F,xlim=c(xlo,xhi),ylim=c(ylo,yhi),axes=F)
    lines(x,y,lwd=lwd,col=col)
}

while(T){
    turnb = sample(3:60,1)
    turna = sample(1:(turnb-1),1)
    cdm = sample(5:20,1)
    A = turna/gcd(c(turna,turnb))
    B = turnb/gcd(c(turna,turnb))
    nloop = B/gcd(c(B,cdm))
    if(nloop>1 && nloop<99 && (180*turna/turnb)%%1==0){break}
}

angles = c(turna/turnb*pi)
degs = c(turna/turnb*180)
cdms = c(cdm)
handles = c(paste0(degs[1],cdm,collapse="#"))

while(length(angles)<8){
    bb = sample(3:60,1)
    aa = sample(1:(bb-1),1)
    cc = sample(5:20,1)
    A = aa/gcd(c(aa,bb))
    B = bb/gcd(c(aa,bb))
    nloop = B/gcd(c(B,cc))
    deg= c(aa/bb*180)
    handle = c(paste0(deg,cc,collapse="#"))
    if(!(handle %in% handles) && nloop>1 && nloop<99 && (180*aa/bb)%%1==0 && deg>10){
        angles = c(angles,aa/bb*pi)
        cdms = c(cdms,cc)
        degs = c(degs,degs)
        handles = c(handles,handle)
    }
}

ord = sample(1:8)

sol = paste0(1*(1==ord),collapse="")

al = paste0("* ",LETTERS[1:8],collapse="\n")

```



Question
========

Let's say you want to make a [spirolateral](https://en.wikipedia.org/wiki/Spirolateral).

If the turn angle is $\theta=`r turna/turnb*180`^{\circ}$ and the maximum segment length is $n=`r cdm`$, then which spirolateral is created?

You can use this tool:

[https://artockthedino.github.io/pbl/spirolateral/spirolateral_generator.html](https://artockthedino.github.io/pbl/spirolateral/spirolateral_generator.html)

```{r,echo=F,fig.dim=c(5,10)}
par(mar=c(1,1,3,1),mfrow=c(4,2),pty="s")
for(i in 1:8){
    drawit(cdms[ord[i]],angles[ord[i]])
    mtext(LETTERS[i],3)
}
```
\

Answerlist
--------

`r al`


Solution
========

The correct answer is `r LETTERS[which(ord==1)]`.

Below I've listed the parameters used to generate all patterns:

```{r,echo=F,fig.dim=c(2,2),results="asis"}

par(mar=c(0,0,0,0),pty="s")
for(i in 1:8){
    cat(paste0("* ",LETTERS[i],": \n"))
    cat(paste0("  * Turn angle = ",round(angles[ord[i]]/pi*180),"\n"))
    cat(paste0("  * Count max = ",cdms[ord[i]],"\n\n"))
    drawit(cdms[ord[i]],angles[ord[i]])
    
    cat("\n\n")
}
```
\


Meta-information
============
extype: schoice
exsolution: `r sol`
exname: spiral
