```{r,echo=FALSE}
pfix = function(c,d){
    cc = c[c!=0]
    dd = d[c!=0]
    p = paste0("{",cc,"}x^{",dd,"}",collapse="+")
    p = gsub("x^{0}","",p,fixed=T)
    p = gsub("x^{1}","x",p,fixed=T)
    p = gsub("+{-","-{",p,fixed=T)
    p = gsub("+{1}x","+x",p,fixed=T)
    p = gsub("-{1}x","-x",p,fixed=T)
    p = gsub("{-1}x","-x",p,fixed=T)
    p = gsub("{1}x","x",p,fixed=T)
    return(p)
}


qt = sample(1:3,1)
abc = sample(1:9,3,T)*sample(c(-1,1),3,T)
a = abc[1]
b = abc[2]
c = abc[3]

disc = b^2-4*a*c

```

Question
========

A parabola is randomly generated by randomly choosing parameters $a$, $h$, and $k$ in the vertex-form equation:

$$y~=~a(x-h)^2+k$$

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
plot(0,0,"n",xlim=c(-11,11),ylim=c(-11,11),axes=F,ann=F)
for(j in -10:10){
    lines(c(-10,10),c(j,j),col="grey",lwd=0.5)
    lines(c(j,j),c(-10,10),col="grey",lwd=0.5)
}
for(j in seq(-10,10,5)){
    lines(c(-10,10),c(j,j),col="darkgrey",lwd=1)
    lines(c(j,j),c(-10,10),col="darkgrey",lwd=1)
}
arrows(-11,0,11,0,0.05,20,3,lwd=1.5)
arrows(0,-11,0,11,0.05,20,3,lwd=1.5)
text(10,0,"10",adj=c(0.5,1.2))
text(0,10,"10",adj=c(1.2,0.5))
text(10,0,"x",adj=c(-0.2,-0.5))
text(0,10,"y",adj=c(-0.5,-0.2))
x = seq(-10,10,0.01)
y = a*(x-h)^2+k
x = x[abs(y)<=10]
y = y[abs(y)<=10]
lines(x,y,col="blue",lwd=2)
x = seq(-10,10,1)
y = a*(x-h)^2+k
x = x[abs(y)<=10]
y = y[abs(y)<=10]
x = x[y%%1==0]
y = y[y%%1==0]
points(x,y,col="blue",pch=19)

```
\

Find the parameters.

* $a=$ ##ANSWER1##
* $h=$ ##ANSWER2##
* $k=$ ##ANSWER3##

How many $x$-intercepts does the parabola have? (Some might not show on the graph.)

* ##ANSWER4##

Answerlist
-------

`r al1`
`r al2`
`r al3`
`r al4`

Solution
========

To find $a$, you might use [this reference](https://artockthedino.github.io/algtwo2026/u06/1218/Stretched_Parabolas_Reference.html). Notice, if $a$ is negative, the parabola faces down, and if $a$ is positive, the parabola faces up. If $|a|$ is bigger than 1, then the parent $y=x^2$ is stretched vertically. If $|a|$ is less than 1, then the parent $y=x^2$ is shrunk vertically. To find the exact value, you need to look at precisely where the curve intersects the lattice points.

To find $h$ and $k$, you can just find the coordinates of the vertex.

To determine the number of roots... 

* If the vertex is on the $x$ axis, there is one root.
* If the parabola opens **up** and the vertex is **above** the $x$ axis, then 0 roots.
* If the parabola opens **down** and the vertex is **above** the $x$ axis, then 2 roots.
* If the parabola opens **up** and the vertex is **below** the $x$ axis, then 2 roots.
* If the parabola opens **down** and the vertex is **below** the $x$ axis, then 0 roots.


Meta-information
============
extype: cloze
exclozetype: schoice|schoice|schoice|schoice
exsolution: `r sol1`|`r sol2`|`r sol3`|`r sol4`
exname: ahk_count_roots