```{r,echo=FALSE}
# All 90-deg turns
# Expressed with right, up, left, down

n = 5

while(T){
    handles = character()
    x = sample(2:5,n,T)
    turns = c(0,sample(c(-1,1),n-1,T))
    tops = c("left","right")
    tus = tops[turns[2:n]/2+1.5]
    st = cumsum(turns)
    # ths = c(0,pi/2,pi,3*pi/2)
    # dis = c("East","North","West","South")
    ths = c(pi/2,0,3*pi/2,pi)
    dis = c("North","East","South","West")
    j0 = 0 #sample(0:3,1)
    jj = (j0+st)%%4+1
    tt = ths[jj]
    dd = dis[jj]
    xx = c(0)
    yy = c(0)
    for(i in 1:n){
        xnew = round(xx[i]+x[i]*cos(tt[i]))
        ynew = round(yy[i]+x[i]*sin(tt[i]))
        xx = c(xx,xnew)
        yy = c(yy,ynew)
        if(i%%2==0){
            handles = c(handles,paste0("e",round(ynew)))
        } else {
            handles = c(handles,paste0("o",round(xnew)))
        }
    }
    
    if(max(abs(xx))<=10 && max(abs(yy))<=10 && length(unique(dd))>2 && length(unique(x))>1 && length(unique(handles))==length(handles)){break}
}

# acho = dis
# ache = 1:5
# 
# alo = paste0("* ",acho,collapse="\n")
# ale = paste0("* ",ache,collapse="\n")
# 
# sols = character()
# for(i in 1:n){
#     solo = paste0(1*(dd[i]==acho),collapse="")
#     sole = paste0(1*(x[i]==ache),collapse="")
#     sols = c(sols,solo,sole)
# }

acho = 1:5
ache = c("left","right")

sols = c(paste0(1*(x[1]==acho),collapse=""))
for(i in 2:n){
    sole = paste0(1*(tus[i-1]==ache),collapse="")
    solo = paste0(1*(x[i]==acho),collapse="")
    sols = c(sols,sole,solo)
}

alo = paste0("* ",acho,collapse="\n")
ale = paste0("* ",ache,collapse="\n")

```

Question
========

A turtle starts at the star in the middle, facing North. While dragging markers, she walks forward for a while, then turns either to her right (clockwise) or to her left (counterclockwise) by 90°. She repeats this, starting with a red marker, until she has drawn `r n` segments.

The distance between adjacent dots is 1 unit.

```{r,echo=F,fig.dim=c(4,4)}
par(mar=c(0,0,0,0),pty="s")
plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)

for(i in -10:10){
    points(rep(i,21),-10:10,pch=20,cex=0.6)
    points(-10:10,rep(i,21),pch=20,cex=0.6)
}
points(0,0,pch=8,cex=1)

# lines(xx,yy,lwd=2,col="blue")
cols = hsv(seq(0,1,length.out=n+1),0.9,0.9)
for(i in 1:n){
    lines(c(xx[i],xx[i+1]),c(yy[i],yy[i+1]),col=cols[i],lwd=2)
}
```
\

Describe the path taken by the turtle.

```{r,echo=F,results='asis'}
cat(paste0("* Go ##ANSWER1##\n"))
for(i in 2:n){
    cat(paste0("* Turn ##ANSWER",2*i-2,"##\n"))
    cat(paste0("* Go ##ANSWER",2*i-1,"##\n"))
}
```

Answerlist
--------


```{r,echo=F,results='asis'}
cat(alo)
cat("\n")
for(i in 2:n){
    cat(ale)
    cat("\n")
    cat(alo)
    cat("\n")
}
```

Solution
========

* Go `r x[1]`
```{r,echo=F,results='asis'}
for(i in 2:n){
    cat(paste0("* Turn ",tus[i-1],"\n"))
    cat(paste0("* Go ",x[i],"\n"))
}
```



Meta-information
============
extype: cloze
exclozetype: `r paste0(rep("schoice",n*2-1),collapse="|")`
exsolution: `r paste0(sols,collapse="|")`
exname: turtle_path_B