---
output: pdf_document
---

\pagenumbering{gobble}

```{r,echo=F}
set.seed(2)
pn = function(coeffs,pows){
    pows = pows[coeffs!=0]
    coeffs = coeffs[coeffs!=0]
    ex1 = paste0("{",coeffs,"}x^{",pows,"}",collapse="+")
    ex1 = gsub("+{-","-{",ex1,fixed=T)
    ex1 = gsub("{1}x^{0}","1",ex1,fixed=T)
    ex1 = gsub("{-1}x^{0}","-1",ex1,fixed=T)
    ex1 = gsub("{1}x","x",ex1,fixed=T)
    ex1 = gsub("{-1}x","-x",ex1,fixed=T)
    ex1 = gsub("x^{0}","",ex1,fixed=T)
    ex1 = gsub("x^{1}","x",ex1,fixed=T)
    ex1 = gsub("+-","-",ex1,fixed=T)
    ex1 = gsub("{","",ex1,fixed=T)
    ex1 = gsub("}","",ex1,fixed=T)
    if(ex1 == ""){
        ex1 = "0"
    }
    return(ex1)
}

funs = list(c("x^2","squaring",function(x){x^2},"$(-\\infty,\\infty)$","$[k,\\infty)$","$(h,\\infty)$","$(-\\infty,h)$","None","Minimum at $(h,k)$",function(x){list(c(-20,20))},"(x-h)^2+k"),
            c("\\frac{1}{x}","reciprocal",function(x){1/x},"$(-\\infty,h)\\cup(h,\\infty)$","$(-\\infty,k)\\cup(k,\\infty)$","$\\emptyset$","$(-\\infty,h)\\cup(h,\\infty)$","Vertical asymptote at $x=h$. Horizontal asymptote at $y=k$.","None",function(x){list(c(-20,-0.00001),c(0.00001,20))},"\\frac{1}{x-h}+k"),
            c("\\sqrt{x}","square root",function(x){x^(1/2)},"$[h,\\infty)$","$[k,\\infty)$","$[h,\\infty)$","$\\emptyset$","None","Minimum at $(h,k)$",function(x){list(c(0,20))},"\\sqrt{x-h}+k"),
            c("2^x","exponential",function(x){2^x},"$(-\\infty,\\infty)$","$(k,\\infty)$","$(-\\infty,\\infty)$","$\\emptyset$","Horizontal asymptote at $y=k$.","None",function(x){list(c(-20,20))},"2^{x-h}+k"),
            c("\\log_2(x)","logarithmic",function(x){log(x)/log(2)},"$(h,\\infty)$","$(-\\infty,\\infty)$","$(h,\\infty)$","$\\emptyset$","Vertical asymptote at $x=h$","None",function(x){list(c(0.00001,20))},"\\log_2(x-h)+k")
            )

```


# Identify features of translated child functions from graph

Below are graphs of 9 child functions, each created by simply translating a parent function. For each child-function graph, identify:

1. The equation of the parent function.
2. The equation of the (graphed) child function.
3. The domain.
4. The range.
5. Interval of increase.
6. Interval of decrease.
7. Asymptotes.
8. Maximums or minimums (extrema).

(*Answers are on back of this page.*)


```{r,echo=F}
ngraph = 9
nfuns = length(funs)
extrafun = sample(1:4,4)
fns = sample(c(1:5,extrafun))
hs = sample(1:5,ngraph,T)*sample(c(-1,1),ngraph,T)
ks = sample(1:5,ngraph,T)*sample(c(-1,1),ngraph,T)
```


```{r,echo=F,fig.dim=c(6.5,6.5)}
par(mar=c(1,1,1,1),mfrow=c(3,3),pty="s")

for(n in 1:9){
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    mtext(n,3,cex=0.8)
    for(i in -10:10){
        lines(c(-10,10),c(i,i),col="grey",lwd=0.4)
        lines(c(i,i),c(-10,10),col="grey",lwd=0.4)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
    }
    arrows(-10.5,0,10.5,0,0.04,15,3,lwd=1)
    arrows(0,-10.5,0,10.5,0.04,15,3,lwd=1)
    
    fn = fns[n]
    h = hs[n]
    k = ks[n]
    getlim = funs[[fn]][10][[1]]
    limits = getlim(h)
    for(j in 1:length(limits)){
        x = seq(limits[[j]][1],limits[[j]][2],length.out=1000)
        y = funs[[fn]][3][[1]](x)
        lines(x+h,y+k,col="blue",lwd=1.5)
    }
    text(10.5,-0.75,"x",cex=0.8)
    text(-0.75,10.5,"y",cex=0.8)
}
```



\newpage

```{r,echo=F,results='asis'}
for(i in 1:9){
    h = hs[i]
    k = ks[i]
    ff = funs[[fns[i]]]
    dom = gsub("h",h,ff[4],fixed=T)
    ran = gsub("k",k,ff[5],fixed=T)
    inc = gsub("h",h,ff[6],fixed=T)
    dec = gsub("h",h,ff[7],fixed=T)
    asy = gsub("k",k,gsub("h",h,ff[8],fixed=T),fixed=T)
    ext = gsub("k",k,gsub("h",h,ff[9],fixed=T),fixed=T)
    chi = gsub("k",k,gsub("h",h,ff[11],fixed=T),fixed=T)
    chi = gsub("+-","-",chi,fixed=T)
    chi = gsub("--","+",chi,fixed=T)
    cat(paste0(i,". \n\n* Parent: $y=",ff[1],"$\\hspace{15pt} Child: $y=",chi,"$\n* Domain: ",dom," \\hspace{15pt} Range: ",ran,"\n* Increasing: ",inc,"\\hspace{15pt} Decreasing: ",dec,"\n* Asymptotes: ",asy," \\hspace{15pt} Extrema: ",ext))
    cat("\n\n\\vfill\n\n")
}
```



\newpage


# Identify features of translated child functions from equation

Below are equations of 9 child functions, each created by simply translating a parent function. For each child-function, identify:

1. The equation of the parent function.
2. The domain.
3. The range.
4. Interval of increase.
5. Interval of decrease.
6. Asymptotes.
7. Maximums or minimums (extrema).

(*Answers are on back of this page. I'd recommend drawing a sketch for each.*)


```{r,echo=F,results='asis'}
ngraph = 9
nfuns = length(funs)
extrafun = sample(1:4,4)
fns = sample(c(1:5,extrafun))
hs = sample(1:5,ngraph,T)*sample(c(-1,1),ngraph,T)
ks = sample(1:5,ngraph,T)*sample(c(-1,1),ngraph,T)
for(i in 1:9){
    h = hs[i]
    k = ks[i]
    ff = funs[[fns[i]]]
    chi = gsub("k",k,gsub("h",h,ff[11],fixed=T),fixed=T)
    chi = gsub("+-","-",chi,fixed=T)
    chi = gsub("--","+",chi,fixed=T)
    cat(paste0(i,". $$y=",chi,"$$\n\n\\vfill\n\n"))
}

```


\newpage

```{r,echo=F,results='asis'}
for(i in 1:9){
    h = hs[i]
    k = ks[i]
    ff = funs[[fns[i]]]
    dom = gsub("h",h,ff[4],fixed=T)
    ran = gsub("k",k,ff[5],fixed=T)
    inc = gsub("h",h,ff[6],fixed=T)
    dec = gsub("h",h,ff[7],fixed=T)
    asy = gsub("k",k,gsub("h",h,ff[8],fixed=T),fixed=T)
    ext = gsub("k",k,gsub("h",h,ff[9],fixed=T),fixed=T)
    cat(paste0(i,". \n\n* Parent: $y=",ff[1],"$ \n* Domain: ",dom," \\hspace{15pt} Range: ",ran,"\n* Increasing: ",inc,"\\hspace{15pt} Decreasing: ",dec,"\n* Asymptotes: ",asy," \\hspace{15pt} Extrema: ",ext))
    cat("\n\n\\vfill\n\n")
}
```


\newpage


# Graph translated and reflected children

Each equation below represents a child function that has been created by reflecting (either horizontally or vertically) and then shifting a parent function. Plot them as accurately as possible. Pay attention to asymptotes, extrema, and key points.

(*Answers on back of this page.*)

```{r,echo=F}
funs = list(c(function(x,a,b,h,k){a*(b*(x-h))^2+k},"-(x-h)^2+k","(-(x-h))^2+k"),
            c(function(x,a,b,h,k){a/(b*(x-h))+k},"-\\frac{1}{x-h}+k","\\frac{1}{-(x-h)}+k"),
            c(function(x,a,b,h,k){a*sqrt(b*(x-h))+k},"-\\sqrt{x-h}+k","\\sqrt{-(x-h)}+k"),
            c(function(x,a,b,h,k){a*2^(b*(x-h))+k},"-2^{x-h}+k","2^{-(x-h)}+k"),
            c(function(x,a,b,h,k){a*log2(b*(x-h))+k},"-\\log_2(x-h)+k","\\log_2(-(x-h))+k")
            )

fns = sample(c(1:4,1:5))
as = numeric()
bs = numeric()
for(i in 1:9){
    ab = sample(c(-1,1))
    aa = ab[1]
    bb = ab[2]
    as = c(as,aa)
    bs = c(bs,bb)
}
hs = sample(1:5,9,T)*sample(c(-1,1),9,T)
ks = sample(1:5,9,T)*sample(c(-1,1),9,T)

```

```{r,echo=F,fig.dim=c(6.5,6.5)}
par(mar=c(0,1,3,1),mfrow=c(3,3),pty="s")
library(latex2exp)

for(n in 1:9){
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in -10:10){
        lines(c(-10,10),c(i,i),col="grey",lwd=0.4)
        lines(c(i,i),c(-10,10),col="grey",lwd=0.4)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
    }
    arrows(-10.5,0,10.5,0,0.04,15,3,lwd=1)
    arrows(0,-10.5,0,10.5,0.04,15,3,lwd=1)
    text(10.5,-0.75,"x",cex=0.8)
    text(-0.75,10.5,"y",cex=0.8)
    
    fn = fns[n]
    h = hs[n]
    k = ks[n]
    a = as[n]
    b = bs[n]
    if(a<0){
        eq = funs[[fn]][2]
    } else {
        eq = funs[[fn]][3]
    }
    eq = gsub("h",h,eq,fixed=T)
    eq = gsub("k",k,eq,fixed=T)
    eq = gsub("+-","-",eq,fixed=T)
    eq = gsub("--","+",eq,fixed=T)
    mtext(TeX(paste0("$y=",eq,"$")),3,cex=0.7)
}
```


\newpage



```{r,echo=F,fig.dim=c(6.5,6.5)}
par(mar=c(0,1,3,1),mfrow=c(3,3),pty="s")
library(latex2exp)

for(n in 1:9){
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in -10:10){
        lines(c(-10,10),c(i,i),col="grey",lwd=0.4)
        lines(c(i,i),c(-10,10),col="grey",lwd=0.4)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
    }
    arrows(-10.5,0,10.5,0,0.04,15,3,lwd=1)
    arrows(0,-10.5,0,10.5,0.04,15,3,lwd=1)
    text(10.5,-0.75,"x",cex=0.8)
    text(-0.75,10.5,"y",cex=0.8)
    
    fn = fns[n]
    h = hs[n]
    k = ks[n]
    a = as[n]
    b = bs[n]
    if(a<0){
        eq = funs[[fn]][2]
    } else {
        eq = funs[[fn]][3]
    }
    eq = gsub("h",h,eq,fixed=T)
    eq = gsub("k",k,eq,fixed=T)
    eq = gsub("+-","-",eq,fixed=T)
    eq = gsub("--","+",eq,fixed=T)
    mtext(TeX(paste0("$y=",eq,"$")),3,cex=0.7)
    if(fn==1){
        xx = list(seq(-20,20,0.001))
    }
    if(fn==2){
        xx = list(seq(-20,-0.001,length.out=1000),seq(0.001,20,length.out=1000))
    }
    if(fn==3){
        xx = list(seq(0,20,0.001))
    }
    if(fn==4){
        xx = list(seq(-20,20,0.001))
    }
    if(fn==5){
        xx = list(seq(0.00001,20,length.out=1000))
    }
    for(jj in 1:length(xx)){
        xxx = xx[[jj]]
        yyy = funs[[fn]][[1]](xxx,1,1,0,0)
        X = b*xxx+h
        Y = a*yyy+k
        lines(X,Y,col="red",lwd=1.5)
    }
    
}
```

\newpage



# Graph translated and reflected children

Each equation below represents a child function that has been created by reflecting (either horizontally or vertically) and then shifting a parent function. Plot them as accurately as possible. Pay attention to asymptotes, extrema, and key points.

(*Answers on back of this page.*)

```{r,echo=F}
funs = list(c(function(x,a,b,h,k){a*(b*(x-h))^2+k},"-(x-h)^2+k","(-(x-h))^2+k"),
            c(function(x,a,b,h,k){a/(b*(x-h))+k},"-\\frac{1}{x-h}+k","\\frac{1}{-(x-h)}+k"),
            c(function(x,a,b,h,k){a*sqrt(b*(x-h))+k},"-\\sqrt{x-h}+k","\\sqrt{-(x-h)}+k"),
            c(function(x,a,b,h,k){a*2^(b*(x-h))+k},"-2^{x-h}+k","2^{-(x-h)}+k"),
            c(function(x,a,b,h,k){a*log2(b*(x-h))+k},"-\\log_2(x-h)+k","\\log_2(-(x-h))+k")
            )

fns = sample(c(1:4,1:5))
as = numeric()
bs = numeric()
for(i in 1:9){
    ab = sample(c(-1,1))
    aa = ab[1]
    bb = ab[2]
    as = c(as,aa)
    bs = c(bs,bb)
}
hs = sample(1:5,9,T)*sample(c(-1,1),9,T)
ks = sample(1:5,9,T)*sample(c(-1,1),9,T)

```

```{r,echo=F,fig.dim=c(6.5,6.5)}
par(mar=c(0,1,3,1),mfrow=c(3,3),pty="s")
library(latex2exp)

for(n in 1:9){
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in -10:10){
        lines(c(-10,10),c(i,i),col="grey",lwd=0.4)
        lines(c(i,i),c(-10,10),col="grey",lwd=0.4)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
    }
    arrows(-10.5,0,10.5,0,0.04,15,3,lwd=1)
    arrows(0,-10.5,0,10.5,0.04,15,3,lwd=1)
    text(10.5,-0.75,"x",cex=0.8)
    text(-0.75,10.5,"y",cex=0.8)
    
    fn = fns[n]
    h = hs[n]
    k = ks[n]
    a = as[n]
    b = bs[n]
    if(a<0){
        eq = funs[[fn]][2]
    } else {
        eq = funs[[fn]][3]
    }
    eq = gsub("h",h,eq,fixed=T)
    eq = gsub("k",k,eq,fixed=T)
    eq = gsub("+-","-",eq,fixed=T)
    eq = gsub("--","+",eq,fixed=T)
    mtext(TeX(paste0("$y=",eq,"$")),3,cex=0.7)
}
```


\newpage



```{r,echo=F,fig.dim=c(6.5,6.5)}
par(mar=c(0,1,3,1),mfrow=c(3,3),pty="s")
library(latex2exp)

for(n in 1:9){
    plot(0,0,"n",xlim=c(-10,10),ylim=c(-10,10),axes=F,ann=F)
    for(i in -10:10){
        lines(c(-10,10),c(i,i),col="grey",lwd=0.4)
        lines(c(i,i),c(-10,10),col="grey",lwd=0.4)
    }
    for(i in seq(-10,10,5)){
        lines(c(-10,10),c(i,i),col="darkgrey",lwd=0.8)
        lines(c(i,i),c(-10,10),col="darkgrey",lwd=0.8)
    }
    arrows(-10.5,0,10.5,0,0.04,15,3,lwd=1)
    arrows(0,-10.5,0,10.5,0.04,15,3,lwd=1)
    text(10.5,-0.75,"x",cex=0.8)
    text(-0.75,10.5,"y",cex=0.8)
    
    fn = fns[n]
    h = hs[n]
    k = ks[n]
    a = as[n]
    b = bs[n]
    if(a<0){
        eq = funs[[fn]][2]
    } else {
        eq = funs[[fn]][3]
    }
    eq = gsub("h",h,eq,fixed=T)
    eq = gsub("k",k,eq,fixed=T)
    eq = gsub("+-","-",eq,fixed=T)
    eq = gsub("--","+",eq,fixed=T)
    mtext(TeX(paste0("$y=",eq,"$")),3,cex=0.7)
    if(fn==1){
        xx = list(seq(-20,20,0.001))
    }
    if(fn==2){
        xx = list(seq(-20,-0.001,length.out=1000),seq(0.001,20,length.out=1000))
    }
    if(fn==3){
        xx = list(seq(0,20,0.001))
    }
    if(fn==4){
        xx = list(seq(-20,20,0.001))
    }
    if(fn==5){
        xx = list(seq(0.00001,20,length.out=1000))
    }
    for(jj in 1:length(xx)){
        xxx = xx[[jj]]
        yyy = funs[[fn]][[1]](xxx,1,1,0,0)
        X = b*xxx+h
        Y = a*yyy+k
        lines(X,Y,col="red",lwd=1.5)
    }
    
}
```









